### 2019-09-26 document.tex
Init

% ****** Start of file aipsamp.tex ******
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 aip,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
%\usepackage{multirow}
%\usepackage{makecell}
\graphicspath{{Pictures/}}
\begin{document}
	\preprint{AIP/123-QED}

	\title[Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system]{Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system\\~}

	\author{G.P. Fedorov}
	\email{gleb.fedorov@phystech.edu}

	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

	\author{A.V. Ustinov}
	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{%
		Karlsruhe Institute of Technology, Karlsruhe, Germany
	}%

	\date{\today}% It is always \today, today,
	%  but any date may be explicitly specified

	\begin{abstract}
		To build a full-scale quantum processor it is necessary to automate as many steps as possible on the physical, hardware level. Circuit quantum electrodynamics (cQED) is a contemporary architecture for dispersive readout and Purcell protection of superconducting qubits of various types, and thus it is necessary to develop software that is able to perform every kind of automatic calibration of such systems from scratch without any human participation. An important step towards this goal is to build a noise-insensitive and accurate computer vision tool to process three-dimensional spectroscopic data. In this work, we present and describe two scalable algorithms that are able to extract the Hamiltonian parameters of the cQED systems from spectroscopic data. 
	\end{abstract}

	\maketitle
\section{Introduction}
Over the past twenty years, significant progress has been achieved in the research of the superconducting quantum circuits.

We investigate a system of two interacting transmons. The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit). This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
means of an external magnetic flux $\Phi$. The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. The system of two transmons and their connection forms a level system.
A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations

A quantum system exposed to external driving, can experience a number of quantum phenomena due to the resonant transitions between energy levels. The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels. 
The main attention in our work is paid to the last effect, which related to the dressed states.
The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.

If the driving field is strong the interaction between the system and the field become significant and leads to oscillates with Rabi frequency. The new energy state called dressed states. If an additional weak probing field is applied, the spectra of the strongly driven system can be probed. In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.

For example, the implementation of the controlled-PHASE quantum gate for typical alkali atoms (such as Rb or Cs)  is based on the effect of dressed states in conjunction with the effect of Rydberg-blockade\cite{sun2018analysis}. One of the possible way to build quantum memory with trapped atomic ions based on dressed states is described in this work\cite{timoney2011quantum}.

In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.\autoref{sec:level1}

\section{Methods}
\subsection{Theoretical description of the system}
In this section we analyse theoretically two qubit system.
 In our study we used transmons.The transmon Hamiltonian is $H = 4\cdot E_C(n-n_g)^2 -E_J\cos(\phi)$, where $E_c $ and $E_J$ -charge and Josephson energy respectively. The symbols $n$ and $\phi$ denote the number of Cooper pairs transferred between the islands and the
 gauge-invariant phase difference between the superconductors,
 respectively.
 When the ratio $\frac{E_C}{E_J}$ is large the perturbation approach can
 be employed. After the expansion of the cosine for small angles and neglecting of the small terms the Hamiltonian can be
 viewed as a harmonic oscillator with a quartic perturbation describing the leading-order anharmonicity.
 After conversion to dimensionless variables and neglecting small terms and set $\hbar = 1$, we move to the new Hamiltonian of transmon. 
\begin{equation}
H_{tr}= \omega_{tr} b^{\dagger}b +\frac{1}{2}\alpha b^{\dagger}b(b^{\dagger}b-1)
\end{equation}
Where $\alpha=-E_C$, $\omega_{tr}=\sqrt{8E_CE_J}+\alpha$.

The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line. In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source.

For simplifications select the dependence on time:
\begin{equation}
H_{dr} = \Omega\cos(\omega_d t)(b+b^{\dagger})
\end{equation}
Let's move on to the consideration of the two-qubit system. The complete Hamiltonian will contain the members responsible for transmons, the drives on each of them separately with frequencies $\omega_d$ and $\omega_d+\delta_{\omega}$ respectively, and the interaction term between qubits:
\begin{equation}
H_{system}= H_{tr1}+H_{tr2}+H_{dr1}+H_{dr2}+H_{int}
\end{equation}
Where $H_{int}= J(bc^{\dagger}+b^{\dagger}c)$, $b^{\dagger}$;$b$ and $c^{\dagger}$,$c$ - denote the regular annihilation and creation operators
for the harmonic oscillator approximating both of qubits respectively.

Let's consider our system in rotating frame. Moving to this frame is achieved by the rotation:
\begin{equation}
R = \exp(-i\omega_d t (b^{\dagger}b+c^{\dagger}c))
\end{equation}  
After this transformation the effective Hamiltonian can be found from equation:
\begin{equation}
H_{system}^R = R^{\dagger}H_{system}R-iR^{\dagger}\dot{R}
\end{equation}

From the simulation follows that a two-level approximation for first qubit and three-level approximation for second is sufficient to observe the effect we are interested in. The Hamiltonian in matrix form is given by the following expression:
\begin{widetext}
	\begin{equation}\label{matrix} 
	\text{$H^R$} = \left(\begin{matrix}
	0 & \text{$\Omega_1 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t} & 0 & 0 & 0 \\
	\text{$\Omega_1 $} & 0 & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t} & 0 & 0 \\
	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & J & -\text{$\Delta_2 $} &
	\text{$\Omega_1$} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t} & 0 \\
	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & \text{$\Omega_1$} &
	-\text{$\Delta_2 $} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
			$} t} \\
	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t} & \sqrt{2} J &
	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1$} \\
	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & \text{$\Omega_1
		$} & \text{$\alpha$}-2 \text{$\Delta_2$} \\
	\end{matrix}\right)
	\end{equation}
\end{widetext}
Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.

\subsection{Master equation solution in QuTip}

\subsection{Experiment}
\subsubsection{Device design and fabrication}
The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons. Qubit control is achieved by external microwave driving line and two flux bias lines. 
\subsubsection{Experimental parameters}
\subsubsection{Experimental setup}
The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK. The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator. The sample was 
flux biased using YOKOGAWA GS200 current source.

Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source. After leaving the sample the signal passed through two isolators and a hybrid coupler. Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.

\section{Results}
\subsection{\label{sec:level1} Experimental and numerical parts}
Two tone spectroscopy was found experimentally and shows good agreement with modelling data\autoref{fig:two-tone}. 
\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{two-tone}
	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
	\label{fig:two-tone}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{drawing}
	\caption{papapa}
	\label{fig:difdrive}
\end{figure}

\subsection{Theoretical description of AF}
Let's consider the Hamiltonian (\ref{matrix}) in details. Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
\begin{equation}
	H^R=H_0+V_J+V_t
\end{equation}
The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues. After that according to the perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions.

\section{Text}

In order to determine which transitions correspond to the lines, the stationary Schrödinger equation was solved \autoref{fig:spectr} in three-level approximation for both of qubits. With the Hamiltonian of the system:
\begin{equation}
	H_{system} = H_{tr1}\otimes\mathbbm{1}+\mathbbm{1}\otimes H_{tr2}+H_{int}
\end{equation}
\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{spectr}
	\caption{Two-tone spectroscopy with transitions lines. In the red frame, four transitions intersect, three of which originate from the state $\ket{00}$ to $\ket{10}$, two-photon
		$\ket{02}$, three-photon
		$\ket{12}$ and the fourth from  $\ket{10}$ to  $\ket{02}$, where $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively}
	\label{fig:spectr}
\end{figure}

 Let's described the anti-crossing highlighted in red in the picture.

\newpage
In this section we analyse theoretically two qubit system in the three-level approximation for both of them. Let $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively, and set $\hbar = 1$. First of all, we consider the small range  of the external magnetic flux and choose a narrow frequency range. In this region, the workspace is limited to four levels. The Hamiltonian of the system at the operating point without drives and interaction between qubits can define as

\begin{equation}
\hat{H_0} = \omega \ket{10}\bra{10} + 2\cdot\omega\ket{02}\bra{02}+3\cdot\omega\ket{12}\bra{12}
\end{equation}
Then define the interaction Hamiltonian as
\begin{equation}
	\hat{H_i} = g_{q}\cdot\sigma_x\otimes
\sigma_x
\end{equation}
\bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	
\end{document}

### 2019-09-30 document.tex
Added authors, added main scheme

@@
 \graphicspath{{Pictures/}}
+
+\newcommand{\mytitile}{Effects of intense light-matter interaction in a superconducting artificial molecule}
 \begin{document}
@@
 
-	\title[Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system]{Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system\\~}
+	\title[\mytitile]{\mytitile\\~}
 
@@
 
-	\author{A.V. Ustinov}
+	\author{V.B. Yursa}
 	\affiliation{ 
-		Russian Quantum Center, Skolkovo village, Russia
+		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
 	}%
-	\affiliation{%
-		Karlsruhe Institute of Technology, Karlsruhe, Germany
+
+	\author{A. Efimov}
+
+	\affiliation{ 
+		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
+	}%
+
+	\author{K. Shiyanov}
+
+	\affiliation{ 
+		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
+	}%
+
+	\author{O.V. Astafiev}
+	\affiliation{ 
+		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
 	}%
@@
 \end{equation}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=.9\linewidth]{main_scheme}
+	\caption{Explaining the origin of the AT satellites.
+\textbf{(a)} System level structure at 3.65 mA.
+At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha/2$ ($\omega_2 - \omega_1 = \alpha/2$), and thus $E_{02} - E_{10} = \hbar\omega_1$.
+Since $E_{12} - E_{02} = \omega_1$ as well, both $00\rightarrow 10$, two-photon $00 \rightarrow 02/2$ and three-photon $00\rightarrow 12/3$ transitions can occur around the same frequency of $\omega_1$.
+During the two-tone spectroscopy, the first transmon is driven by a strong signal of amplitude $\Omega_1$ (possibly, at a small detuning $\Delta_1$ from $\omega_1$ shown in green).
+The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles.
+\textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$).
+However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$ (the first transmon becomes light-dressed).
+\textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by the corresponding drive operator are shown as blue ellipses).
+In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted.
+The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the orange are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$.
+However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
+When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites may be observed.}
+\end{figure*}
 

### 2019-10-01 document.tex
Added division by 2

--- 2019-09-26 document.tex
@@
 The complete Hamiltonian will contain the members responsible for transmons, the drives on each of them separately with frequencies $\omega_d$ and $\omega_d+\delta_{\omega}$ respectively, and the interaction term between qubits:
-\begin{equation}
+\begin{equation}\label{Hsystem}
 H_{system}= H_{tr1}+H_{tr2}+H_{dr1}+H_{dr2}+H_{int}
@@
 for the harmonic oscillator approximating both of qubits respectively.
-
-Let's consider our system in rotating frame. Moving to this frame is achieved by the rotation:
-\begin{equation}
-R = \exp(-i\omega_d t (b^{\dagger}b+c^{\dagger}c))
-\end{equation}  
-After this transformation the effective Hamiltonian can be found from equation:
-\begin{equation}
-H_{system}^R = R^{\dagger}H_{system}R-iR^{\dagger}\dot{R}
-\end{equation}
-
-From the simulation follows that a two-level approximation for first qubit and three-level approximation for second is sufficient to observe the effect we are interested in.
-The Hamiltonian in matrix form is given by the following expression:
-\begin{widetext}
-	\begin{equation}\label{matrix} 
-	\text{$H^R$} = \left(\begin{matrix}
-	0 & \text{$\Omega_1 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t} & 0 & 0 & 0 \\
-	\text{$\Omega_1 $} & 0 & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t} & 0 & 0 \\
-	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & J & -\text{$\Delta_2 $} &
-	\text{$\Omega_1$} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t} & 0 \\
-	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & \text{$\Omega_1$} &
-	-\text{$\Delta_2 $} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
-			$} t} \\
-	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t} & \sqrt{2} J &
-	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1$} \\
-	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t} & \text{$\Omega_1
-		$} & \text{$\alpha$}-2 \text{$\Delta_2$} \\
-	\end{matrix}\right)
-	\end{equation}
-\end{widetext}
-Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.
 
@@
 
+We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
 \begin{figure}[h]
@@
 	\includegraphics[width=\linewidth]{drawing}
-	\caption{papapa}
+	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
 	\label{fig:difdrive}
@@
 \subsection{Theoretical description of AF}
-Let's consider the Hamiltonian (\ref{matrix}) in details.
+Let's consider our system (\autoref{Hsystem}) in rotating frame. Moving to this frame is achieved by the rotation:
+\begin{equation}
+R = \exp(-i\omega_d t (b^{\dagger}b+c^{\dagger}c))
+\end{equation}  
+After this transformation the effective Hamiltonian can be found from equation:
+\begin{equation}
+H_{system}^R = R^{\dagger}H_{system}R-iR^{\dagger}\dot{R}
+\end{equation}
+
+From the simulation follows that a two-level approximation for first qubit and three-level approximation for second is sufficient to observe the effect we are interested in.
+The Hamiltonian in matrix form is given by the following expression:
+\begin{widetext}
+	\begin{equation}\label{matrix} 
+	\text{$H^R$} = \left(\begin{matrix}
+	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
+	\text{$\Omega_1/2 $} & 0 & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
+	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
+	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
+	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
+	-\text{$\Delta_2 $} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
+			$} t}/2 \\
+	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
+	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
+	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
+		$} & \text{$\alpha$}-2 \text{$\Delta_2$} \\
+	\end{matrix}\right)
+	\end{equation}
+\end{widetext}
+Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.
+Let's consider the Hamiltonian (\autoref{matrix}) in details.
 Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
@@
 \end{equation}
+The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$.
 The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues.
-After that according to the perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions.
+The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width os the dressed states.
+Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
+Therefore a non-zero interaction between qubits is necessary to observe AT effect.
+
+After that according to the perturbation theory (with perturbation $V_J$) to $H_0$ we found the first-order corrections to the wave functions.
+We can use Fermi Golden Rule to find the probability of transition.
 
@@
 
-\newpage
-In this section we analyse theoretically two qubit system in the three-level approximation for both of them.
-Let $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively, and set $\hbar = 1$.
-First of all, we consider the small range  of the external magnetic flux and choose a narrow frequency range.
-In this region, the workspace is limited to four levels.
-The Hamiltonian of the system at the operating point without drives and interaction between qubits can define as
-
-\begin{equation}
-\hat{H_0} = \omega \ket{10}\bra{10} + 2\cdot\omega\ket{02}\bra{02}+3\cdot\omega\ket{12}\bra{12}
-\end{equation}
-Then define the interaction Hamiltonian as
-\begin{equation}
-	\hat{H_i} = g_{q}\cdot\sigma_x\otimes
-\sigma_x
-\end{equation}
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-10-02 document.tex
Main picture added

--- 2019-09-30 document.tex
@@
 However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
-When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites may be observed.}
+When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites become visible.
+Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be two $\Omega_1^R$.}
 \end{figure*}
@@
 Two tone spectroscopy was found experimentally and shows good agreement with modelling data\autoref{fig:two-tone}. 
-\begin{figure}[h]
+\begin{figure*}[h]
 	\centering
-	\includegraphics[width=\linewidth]{two-tone}
+	\includegraphics[width=\linewidth]{main_picture}
 	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
 	\label{fig:two-tone}
-\end{figure}
+\end{figure*}
 

### 2019-10-02 Pictures/Plotting/MainPicturePlot.py

@@ -1,0 +1,135 @@
+import pickle
+import numpy as np
+import matplotlib
+from matplotlib import ticker, colorbar as clb
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+
+
+class MainPicturePlot:
+
+    def __init__(self):
+        self._cache_file = "main_pic_cache.pkl"
+        self.nstate = 0
+        try:
+            with open(self._cache_file, "rb") as f:
+                self._cache = pickle.load(f)
+        except:
+            self._cache = {}
+            with open(self._cache_file, "wb") as f:
+                pickle.dump(self._cache, f)
+
+    def plot(self):
+        self._load_data()
+
+        fig, axes = plt.subplots(nrows=1, ncols=2, figsize=(12, 5), sharey=True)
+        plt.subplots_adjust(wspace=.1)
+
+        ax1, ax2 = axes
+
+        self.plot_experiment(ax1)
+        self.plot_theory(ax2)
+
+        plt.savefig("../main_picture.pdf", bbox_inches="tight", dpi=600)
+
+        with open(self._cache_file, "wb") as f:
+            pickle.dump(self._cache, f)
+
+
+    def plot_experiment(self, ax):
+        data = self._X_exp, self._Y_exp, self._C_exp.real
+        img1 = ax.pcolormesh(*data, rasterized=True)
+        cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
+        cb1 = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
+        ax.set_xlabel('Current [$10^{-4}$ A]');
+        ax.set_ylabel('Frequency [GHz]');
+        cb1.ax.set_title(r"$\mathfrak{Re} [S_{21}]$", position=(1.1,-1.5))
+
+        plt.text(-0.2, 1.05, "(a)", fontdict={"name": "STIX"}, fontsize=22,
+                 transform=ax.transAxes)
+
+        self._zoom(ax, data)
+
+    def plot_theory(self, ax):
+
+        try:
+            C = self._cache[self.nstate]
+        except KeyError:
+            C = np.zeros(self._C_th.shape)
+            for i in range(C.shape[0]):
[…]

### 2019-10-03 document.tex

--- 2019-10-01 document.tex
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=.9\linewidth]{main_scheme}
+	\caption{Explaining the origin of the AT satellites.
+\textbf{(a)} System level structure at 3.65 mA.
+At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha/2$ ($\omega_2 - \omega_1 = \alpha/2$), and thus $E_{02} - E_{10} = \hbar\omega_1$.
+Since $E_{12} - E_{02} = \omega_1$ as well, both $00\rightarrow 10$, two-photon $00 \rightarrow 02/2$ and three-photon $00\rightarrow 12/3$ transitions can occur around the same frequency of $\omega_1$.
+During the two-tone spectroscopy, the first transmon is driven by a strong signal of amplitude $\Omega_1$ (possibly, at a small detuning $\Delta_1$ from $\omega_1$ shown in green).
+The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles.
+\textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$).
+However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$ (the first transmon becomes light-dressed).
+\textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by the corresponding drive operator are shown as blue ellipses).
+In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted.
+The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the orange are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$.
+However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
+When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites may be observed.}
+\end{figure*}
+
 \subsection{Master equation solution in QuTip}
@@
 	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
-	\text{$\Omega_1/2 $} & 0 & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
+	\text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
 	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
@@
 	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
-	-\text{$\Delta_2 $} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
+	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
 			$} t}/2 \\
@@
 	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
-		$} & \text{$\alpha$}-2 \text{$\Delta_2$} \\
+		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
 	\end{matrix}\right)
@@
 We can use Fermi Golden Rule to find the probability of transition.
+\appendix
+\section{Theoretical description of two-photon process}
 

### 2019-10-03 document.tex
Minor changes

--- 2019-10-02 document.tex
@@
 %\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
+
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
 %\linenumbers\relax % Commence numbering lines
-\usepackage{hyperref}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{bbm}
+\usepackage{hyperref}
 %\usepackage{multirow}
@@
 \graphicspath{{Pictures/}}
+
+\renewcommand*{\figureautorefname}{Fig.}
 
@@
 \section{Introduction}
-Over the past twenty years, significant progress has been achieved in the research of the superconducting quantum circuits.
+Over the past twenty years, many
 
-We investigate a system of two interacting transmons.
-The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
-This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
-means of an external magnetic flux $\Phi$.
-The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-The system of two transmons and their connection forms a level system.
 A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
@@
 
-In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.\autoref{sec:level1}
+In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.%\autoref{sec:level1}
 
@@
 \subsection{Theoretical description of the system}
+
+We investigate a system of two interacting transmons.
+The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
+This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
+means of an external magnetic flux $\Phi$.
+The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
+The system of two transmons and their connection forms a level system.
+
 In this section we analyse theoretically two qubit system.
@@
 Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be two $\Omega_1^R$.}
+	\label{fig:main_scheme}
 \end{figure*}
@@
 Two tone spectroscopy was found experimentally and shows good agreement with modelling data\autoref{fig:two-tone}.
-\begin{figure*}[h]
+
+\begin{figure*}
 	\centering
 	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
+	\caption{Two-tone spectroscopy: \textbf{(a)} Experiment;\textbf{(b)} Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
 	\label{fig:two-tone}

### 2019-10-03 Pictures/Plotting/MainPicturePlot.py

@@ -78,18 +78,20 @@ class MainPicturePlot:
 
 
     def _zoom(self, ax, data):
+
+        color = "black"
         axins = zoomed_inset_axes(ax, 2.5, loc=4)  # zoom-factor: 2.5, location: upper-left
         axins1 = zoomed_inset_axes(ax, 2.5, loc=3)
         axinss1 = zoomed_inset_axes(ax, 2.5, loc=2)
         # ax1.broken_barh([(3.1,0.4)],(5.31,0.02),edgecolors = 'r', facecolors = 'none',linewidth= 1, linestyle = '--')
         for axis in ['top', 'bottom', 'left', 'right']:
-            axins.spines[axis].set_color('C1')
+            axins.spines[axis].set_color(color)
         axins.pcolormesh(*data, rasterized=True)
         for axis in ['top', 'bottom', 'left', 'right']:
-            axins1.spines[axis].set_color('C1')
+            axins1.spines[axis].set_color(color)
         axins1.pcolormesh(*data, rasterized=True)
         for axis in ['top', 'bottom', 'left', 'right']:
-            axinss1.spines[axis].set_color('C1')
+            axinss1.spines[axis].set_color(color)
         axinss1.pcolormesh(*data, rasterized=True)
         x1, x2, y1, y2 = 3.5, 3.8, 5.25, 5.29  # specify the limits
         axins.set_xlim(x1, x2)  # apply the x-limits
@@ -107,9 +109,9 @@ class MainPicturePlot:
         axinss1.set_yticklabels([])
         axinss1.set_xticklabels([])
         from mpl_toolkits.axes_grid1.inset_locator import mark_inset
-        mark_inset(ax, axins, loc1=3, loc2=1, fc="none", ec='C1', linestyle='--')
-        mark_inset(ax, axins1, loc1=4, loc2=2, fc="none", ec='C1', linestyle='--')
-        mark_inset(ax, axinss1, loc1=3, loc2=1, fc="none", ec='C1', linestyle='--')
+        mark_inset(ax, axins, loc1=3, loc2=1, fc="none", ec=color, linestyle='--')
+        mark_inset(ax, axins1, loc1=4, loc2=2, fc="none", ec=color, linestyle='--')
+        mark_inset(ax, axinss1, loc1=3, loc2=1, fc="none", ec=color, linestyle='--')
 
 
     def _load_data(self):

### 2019-10-04 document.tex
CRLF to LF
Main picture updated, introduction started

@@
 %\usepackage{dcolumn}% Align table columns on decimal point
-
+\usepackage{fixme}
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
@@
 
-\newcommand{\mytitile}{Effects of intense light-matter interaction in a superconducting artificial molecule}
+\newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}
 \begin{document}
@@
 \section{Introduction}
-Over the past twenty years, many
+Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
+Due to their synthetic nature, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics.
+Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
+For example, the strong coupling regime when the coupling strength between light and a quantum system approaches 1\% of their frequency has been a major milestone for atoms, molecules, etc and was only reached using high-finesse cavities.
+In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
+Moreover, SAAs do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
+The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already in the ultra-strong coupling regime.
 
-A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
-
-A quantum system exposed to external driving, can experience a number of quantum phenomena due to the resonant transitions between energy levels.
+A quantum system exposed to external driving can experience a number of quantum phenomena due to the resonant transitions between energy levels.
 The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels.
@@
 One of the possible way to build quantum memory with trapped atomic ions based on dressed states is described in this work\cite{timoney2011quantum}.
+
+A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
 

### 2019-10-04 Pictures/Plotting/MainPicturePlot.py

@@ -40,38 +40,46 @@ class MainPicturePlot:
 
 
     def plot_experiment(self, ax):
-        data = self._X_exp, self._Y_exp, self._C_exp.real
+        data = self._X_exp, self._Y_exp, np.real(self._C_exp)
         img1 = ax.pcolormesh(*data, rasterized=True)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
-        cb1 = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
+        cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
         ax.set_ylabel('Frequency [GHz]');
-        cb1.ax.set_title(r"$\mathfrak{Re} [S_{21}]$", position=(1.1,-1.5))
-
-        plt.text(-0.2, 1.05, "(a)", fontdict={"name": "STIX"}, fontsize=22,
+        cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$", position=(1.125,-1.5))
+        loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
+        cb.locator = loc
+        cb.update_ticks()
+        plt.text(-0.15, 1.1, "(a)", fontdict={"name": "STIX"}, fontsize=22,
                  transform=ax.transAxes)
 
         self._zoom(ax, data)
 
     def plot_theory(self, ax):
 
-        try:
-            C = self._cache[self.nstate]
-        except KeyError:
-            C = np.zeros(self._C_th.shape)
-            for i in range(C.shape[0]):
-                for j in range(C.shape[1]):
-                    C[i,j] = self._C_th[i][j][self.nstate][0][self.nstate].real
-            self._cache[self.nstate] = C
+        # try:
+        #     C = self._cache[self.nstate]
+        # except KeyError:
+        #     C = np.zeros(self._C_th.shape)
+        #     for i in range(C.shape[0]):
+        #         for j in range(C.shape[1]):
+        #             C[i,j] = self._C_th[i][j][self.nstate][0][self.nstate].real
+        #     self._cache[self.nstate] = C
+
+        C = np.real(self._C_th.T)
[…]

### 2019-10-04 document.tex
Small fix for scheme and introduction continued

@@
 
-A quantum system exposed to external driving can experience a number of quantum phenomena due to the resonant transitions between energy levels.
+In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels.
 The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels.
-The main attention in our work is paid to the last effect, which related to the dressed states.
-The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.
 
-If the driving field is strong the interaction between the system and the field become significant and leads to oscillates with Rabi frequency.
-The new energy state called dressed states.
+Our work is focused on the last effect, which has been studied in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and also was observed for SAAs in several experiments\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
+
+The main cause of the AT effect is the dressing of the atomic levels by strong EM radiation.
+This dressing The new energy state called dressed states.
 If an additional weak probing field is applied, the spectra of the strongly driven system can be probed.

### 2019-10-04 document.tex
matrix labeled

--- 2019-10-03 document.tex
@@
 %\usepackage{dcolumn}% Align table columns on decimal point
-
+\usepackage{bm}% bold math
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
 %\linenumbers\relax % Commence numbering lines
+\usepackage{hyperref}
+\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
 \usepackage[utf8]{inputenc}
@@
 \usepackage{bbm}
-\usepackage{hyperref}
+\usepackage{nicematrix}
 %\usepackage{multirow}
@@
 \graphicspath{{Pictures/}}
-
-\renewcommand*{\figureautorefname}{Fig.}
 
@@
 \section{Introduction}
-Over the past twenty years, many
+Over the past twenty years, significant progress has been achieved in the research of the superconducting quantum circuits.
 
+We investigate a system of two interacting transmons.
+The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
+This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
+means of an external magnetic flux $\Phi$.
+The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
+The system of two transmons and their connection forms a level system.
 A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
@@
 
-In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.%\autoref{sec:level1}
+In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.\autoref{sec:level1}
 
@@
 \subsection{Theoretical description of the system}
-
-We investigate a system of two interacting transmons.
-The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
-This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
-means of an external magnetic flux $\Phi$.
-The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-The system of two transmons and their connection forms a level system.
-
 In this section we analyse theoretically two qubit system.
@@
 Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be two $\Omega_1^R$.}
-	\label{fig:main_scheme}
 \end{figure*}
@@
 Two tone spectroscopy was found experimentally and shows good agreement with modelling data\autoref{fig:two-tone}. 
-
-\begin{figure*}
+\begin{figure*}[h]
 	\centering
 	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: \textbf{(a)} Experiment;\textbf{(b)} Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
+	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
 	\label{fig:two-tone}
@@
 The Hamiltonian in matrix form is given by the following expression:
+
+\renewcommand{\kbldelim}{(}% Left delimiter
+\renewcommand{\kbrdelim}{)}% Right delimiter
 \begin{widetext}
 	\begin{equation}\label{matrix} 
-	\text{$H^R$} = \left(\begin{matrix}
+	\text{$H^R$} = \kbordermatrix{
+	\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
 	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
@@
 		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
-	\end{matrix}\right)
+}
 	\end{equation}
@@
 \section{Theoretical description of two-photon process}
+Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
 

### 2019-10-06 document.tex
Introduction continued, added intro picture

--- 2019-10-04 document.tex
@@
 Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
-Due to their synthetic nature, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics.
+Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered, and this makes them a particularly versatile tool for studies in quantum optics.
 Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
@@
 In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
-Moreover, SAAs do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already in the ultra-strong coupling regime.
+Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
+The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime.
 
 In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels.
-The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels.
+The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.
 
-Our work is focused on the last effect, which has been studied in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and also was observed for SAAs in several experiments\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
+In this work, we are studying effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule (SAM).
+In our experiment, we use two transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
+Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.
 
-The main cause of the AT effect is the dressing of the atomic levels by strong EM radiation.
+It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we have discovered.
+The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAAs as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
+However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics; instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
+
+Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
+
+In  cause of the AT effect is the dressing of the atomic levels by strong EM radiation.
 This dressing The new energy state called dressed states.
@@
 In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{intro_scheme}
+	\caption{Illustrating the AT splitting in the rotating frame ($\hbar=1$ here).
+\textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
+It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
+\textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
+However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
+Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ with frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
+\end{figure}
 
@@
 We investigate a system of two interacting transmons.
-The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
+The transmon represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
 This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
@@
 \appendix
+
+\subsection{The standard Autler-Townes effect}
+
 \section{Theoretical description of two-photon process}

### 2019-10-07 document.tex
Added theory for standard AT

@@
 It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we have discovered.
-The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAAs as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
+The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
 However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics; instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
@@
 Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
-
-In  cause of the AT effect is the dressing of the atomic levels by strong EM radiation.
-This dressing The new energy state called dressed states.
-If an additional weak probing field is applied, the spectra of the strongly driven system can be probed.
-In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{intro_scheme}
-	\caption{Illustrating the AT splitting in the rotating frame ($\hbar=1$ here).
-\textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
-It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
-\textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
-However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
-Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ with frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
-\end{figure}
 
@@
 
-\subsection{The standard Autler-Townes effect}
+\section{Theory of the standard Autler-Townes effect}
+
+The underlying cause of the A-T effect is the dressing of the atomic levels by strong EM radiation. There are two equivalent mathematical models for it: the light may be classical or quantized.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{intro_scheme}
+	\caption{Illustrating the A-T splitting in the rotating frame ($\hbar=1$ here).
+\textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
+It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
+\textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
+However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
+Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ with frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
+	\label{fig:at-standard}
+\end{figure}
+
+In the classical case, the mathematical description goes as follows.
+At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$.
+Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_2$ between $\ket{1}$ and $\ket{2}$.
+This step is illustrated in \autoref{fig:at-standard}~(a).
+The Hamiltonian for such system is as follows:
+
+\begin{equation}
+\hat H_0 = \left[\begin{matrix}
+0 & \Omega_{1} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
+\Omega_{1} \cos{\left(\omega_{01} - \Delta \right)t}   & \omega_{01} &\Omega_{2} \cos\omega_p t  \\
+0 & \Omega_{2} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
+\end{equation}
+
+Next, we move to the rotating frame by using an operator
+\[
+\hat U = \left[\begin{matrix} 
+1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
+\]
+Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$.
+The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat U^\dag \hat H_0 \hat U - i \dot{\hat{U}}^\dag \hat U$.
+The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b).
+Applying the RWA, we obtain:
+\begin{equation}
+\hat H_1 = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{- i t \omega_p}/2\\0 & \Omega_{2} e^{i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
+\end{equation}
+
+Next, moving to the basis where the upper left 2x2 corner is diagonal (the right part of \autoref{fig:at-standard}~(b)), we obtain:
+
+\begin{equation}
+\hat H_3 = \left[\begin{matrix} 
+\frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
+0 &
+\frac{\Omega_{2} e^{i t \omega_{p}}}{2}\sin(\theta)
+\\
+0 & 
+\frac{\Delta}{2} + \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
+\frac{\Omega_{2} e^ {i t \omega_p}}{2}\cos(\theta)
+\\
+\frac{\Omega_{2} e^{-i t \omega_{p}} }{2}\sin(\theta) & 
+\frac{\Omega_{2} e^{-i t \omega_{p}}}{2} \cos(\theta) & 
+\omega_{12} +\Delta 
+\end{matrix}\right].
+\end{equation}
+
+One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + \dfrac{(\Delta \pm \Omega^R)}{2}$, where $\Omega^R = \sqrt{\Omega_1^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\frac{\Omega_1}{\Delta}$.
 

### 2019-10-09 document.tex
Introduction finished, methods started, A-T appendix done

@@
 
+	\author{A. Yu. Dmitriev}
+	\affiliation{ 
+	Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
+	}%
+
 	\author{O.V. Astafiev}
@@
 The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
-However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics; instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
-
+However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}); instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
 Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
 
-For example, the implementation of the controlled-PHASE quantum gate for typical alkali atoms (such as Rb or Cs)  is based on the effect of dressed states in conjunction with the effect of Rydberg-blockade\cite{sun2018analysis}.
-One of the possible way to build quantum memory with trapped atomic ions based on dressed states is described in this work\cite{timoney2011quantum}.
-
-A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
-
-In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.%\autoref{sec:level1}
+The manuscript consists of four main parts and an Appendix.
+Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects.
+The Appendix contains important details of the theoretical framework that we use to model the observed processes.
 
 \section{Methods}
+
+In this section, we provide the mathematical formulation of the employed models, specify the numerical approaches that were used in simulations and describe the experimental equipment and some measurement aspects.
+
 \subsection{Theoretical description of the system}
 
-We investigate a system of two interacting transmons.
-The transmon represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
-This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
-means of an external magnetic flux $\Phi$.
-The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-The system of two transmons and their connection forms a level system.
+A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
+Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$:
+\begin{equation}
+\hat H_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
+\end{equation}
+where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
+Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
 
-In this section we analyse theoretically two qubit system.
- In our study we used transmons.The transmon Hamiltonian is $H = 4\cdot E_C(n-n_g)^2 -E_J\cos(\phi)$, where $E_c $ and $E_J$ -charge and Josephson energy respectively.
-The symbols $n$ and $\phi$ denote the number of Cooper pairs transferred between the islands and the
- gauge-invariant phase difference between the superconductors,
- respectively.
- When the ratio $\frac{E_C}{E_J}$ is large the perturbation approach can
- be employed. After the expansion of the cosine for small angles and neglecting of the small terms the Hamiltonian can be
- viewed as a harmonic oscillator with a quartic perturbation describing the leading-order anharmonicity.
- After conversion to dimensionless variables and neglecting small terms and set $\hbar = 1$, we move to the new Hamiltonian of transmon. 
+To induce state transitions in a transmon one should irradiate it by a monochromatic external microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
+The interaction term between the transmon and this classical EM field is then modelled by the following operator:
 \begin{equation}
-H_{tr}= \omega_{tr} b^{\dagger}b +\frac{1}{2}\alpha b^{\dagger}b(b^{\dagger}b-1)
+\hat H_{dr}/\hbar = \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger}),
 \end{equation}
-Where $\alpha=-E_C$, $\omega_{tr}=\sqrt{8E_CE_J}+\alpha$.
+where $\Omega$ stands for the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.
 
-The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
-In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
-Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source.
+Now, for the molecule composed of two coupled transmons, the complete Hamiltonian contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the qubit-qubit interaction term:
+\begin{equation}\label{Hsystem}
+\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
+\end{equation}
+where $\hat H_{int}/\hbar= J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
 
-For simplifications select the dependence on time:
+Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon.
+They are modelled using the Lindblad equation with the following collapse operators:
+\begin{equation}\
+\begin{split}
+\hat{\mathcal{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
+\hat{\mathcal{O}}_{\phi, 1} = \sqrt{2\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
+\hat{\mathcal{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
+\hat{\mathcal{O}}_{\phi,2} = \sqrt{2\gamma_{ \phi,2}}\, \hat c^\dag \hat c.
+\end{split}
+\end{equation}
+As one can see, the collapse operators are in a separable form, i.e.
+acting only upon a single transmon each.
+This is a valid approach until the coupling strength $J$ is not too large\cite{beaudoin2011dissipation}.
+Therefore, the complete evolution equation for the system density matrix $\hat \rho$ is
 \begin{equation}
-H_{dr} = \Omega\cos(\omega_d t)(b+b^{\dagger})
+\partial_t \hat \rho = \frac{i}{\hbar} [\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{\mathcal{O}}_{\alpha, i}] \hat \rho, \label{eq:master}
 \end{equation}
-Let's move on to the consideration of the two-qubit system.
-The complete Hamiltonian will contain the members responsible for transmons, the drives on each of them separately with frequencies $\omega_d$ and $\omega_d+\delta_{\omega}$ respectively, and the interaction term between qubits:
-\begin{equation}\label{Hsystem}
-H_{system}= H_{tr1}+H_{tr2}+H_{dr1}+H_{dr2}+H_{int}
-\end{equation}
-Where $H_{int}= J(bc^{\dagger}+b^{\dagger}c)$, $b^{\dagger}$;$b$ and $c^{\dagger}$,$c$ - denote the regular annihilation and creation operators
-for the harmonic oscillator approximating both of qubits respectively.
+where $\mathcal{D}[\hat{\mathcal{O}}]\hat \rho = \hat{\mathcal{O}} \hat \rho \hat{\mathcal{O}}^\dag - \frac{1}{2}\{ \hat{\mathcal{O}}^\dag \hat{\mathcal{O}}, \hat \rho\}$.
+
+\subsection{Master equation solution in QuTiP}
+
+Numerical simulations are crucial in studying the equation \eqref{eq:master} since is does not allow an analytical solution.
+We have been using the \textit{qutip}\cite{johansson2013qutip} quantum optics toolbox to simulate the dynamics and find the steady state of the system for various parameter combinations of the Hamiltonian.
+
+When modelling the experimental behaviour, we
+
+\subsection{Experiment}
+\subsubsection{Device design and fabrication}
+The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
+Qubit control is achieved by external microwave driving line and two flux bias lines.
+\subsubsection{Experimental parameters}
+\subsubsection{Experimental setup}
+The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
+represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK.
+The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator.
+The sample was
+flux biased using YOKOGAWA GS200 current source.
+
+Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source.
+After leaving the sample the signal passed through two isolators and a hybrid coupler.
+Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.
+
+\section{Results}
+
+\subsection{\label{sec:level1} Experimental and numerical parts}
+Two tone spectroscopy was found experimentally and shows good agreement with modelling data \autoref{fig:two-tone}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\linewidth]{main_picture}
+	\caption{Two-tone spectroscopy: \textbf{(a)} Experiment;\textbf{(b)} Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
+	\label{fig:two-tone}
+\end{figure*}
 
@@
 
-\subsection{Master equation solution in QuTip}
-
-\subsection{Experiment}
-\subsubsection{Device design and fabrication}
-The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
-Qubit control is achieved by external microwave driving line and two flux bias lines.
-\subsubsection{Experimental parameters}
-\subsubsection{Experimental setup}
-The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
-represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK.
-The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator.
-The sample was
-flux biased using YOKOGAWA GS200 current source.
-
-Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source.
-After leaving the sample the signal passed through two isolators and a hybrid coupler.
-Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.
-
-\section{Results}
-\subsection{\label{sec:level1} Experimental and numerical parts}
-Two tone spectroscopy was found experimentally and shows good agreement with modelling data\autoref{fig:two-tone}.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: \textbf{(a)} Experiment;\textbf{(b)} Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
-	\label{fig:two-tone}
-\end{figure*}
-
 We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
-\begin{figure}[h]
+\begin{figure}
 	\centering
@@
 
-\subsection{Theoretical description of AF}
-Let's consider our system (\autoref{Hsystem}) in rotating frame. Moving to this frame is achieved by the rotation:
+\subsection{Theoretical description of the observed spectral lines}
+For the three-level system, the A-T effect is described in Appendix \ref{sec:3-level-at}.
+Let's consider our system (\autoref{Hsystem}) in rotating frame.
+Moving to this frame is achieved by the rotation:
 \begin{equation}
@@
 
-\section{Theory of the standard Autler-Townes effect}
+\section{Standard Autler-Townes effect for a three-level atom} \label{sec:3-level-at}
 
@@
 	\includegraphics[width=\linewidth]{intro_scheme}
-	\caption{Illustrating the A-T splitting in the rotating frame ($\hbar=1$ here).
+	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here).
 \textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
@@
 However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
-Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ with frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
+Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
 	\label{fig:at-standard}
@@
 
-In the classical case, the mathematical description goes as follows.
+\paragraph{Classical derivation.} In the classical case, the mathematical description goes as follows.
 At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$.
@@
 
-\begin{equation}
-\hat H_0 = \left[\begin{matrix}
+\begin{equation*}
+\hat H^c_0 = \left[\begin{matrix}
 0 & \Omega_{1} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
@@
 0 & \Omega_{2} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
-\end{equation}
+\end{equation*}
 
@@
 \[
-\hat U = \left[\begin{matrix} 
-1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
+\hat R = \left[\begin{matrix} 
+1 & 0 & 0\\0 & e^{i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
 \]
 Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$.
-The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat U^\dag \hat H_0 \hat U - i \dot{\hat{U}}^\dag \hat U$.
+The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R + i \dot{\hat{R}}^\dag \hat R$.
 The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b).
 Applying the RWA, we obtain:
-\begin{equation}
-\hat H_1 = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{- i t \omega_p}/2\\0 & \Omega_{2} e^{i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
-\end{equation}
+\begin{equation*}
+\hat H^c_1 = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{i t \omega_p}/2\\0 & \Omega_{2} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
+\end{equation*}
 
@@
 
-\begin{equation}
-\hat H_3 = \left[\begin{matrix} 
+\begin{equation*}
+\hat H^c_3 = \left[\begin{matrix} 
 \frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
@@
 \end{matrix}\right].
-\end{equation}
+\end{equation*}
 
 One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + \dfrac{(\Delta \pm \Omega^R)}{2}$, where $\Omega^R = \sqrt{\Omega_1^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\frac{\Omega_1}{\Delta}$.
+
+\paragraph{Quantum derivation.} For the fully quantum interpretation, we model the incident radiation at the frequency $\omega_{01}-\Delta$ as a single-mode quantum oscillator which is coupled to the system.
+The Hamiltonian for this model will be as follows:
+\[
+\begin{split}
+\hat H^q_0 = \omega_{01} \ket{1}\bra{1} + \omega_{02} \ket{2}\bra{2} + (\omega_{01}-\Delta) \hat a^\dag \hat a + \\\ g (\hat a^\dag + \hat a)\otimes (\ket{1}\bra{0}+\ket{0}\bra{1}),
+\end{split}
+\]
+where $g$ is the coupling strength and $a$ is the photon annihilation operator.
+After moving to the rotating frame with $\hat R = \exp[i t (\omega_{01}-\Delta)(\hat a^\dag \hat a + \ket{1}\bra{1}+\ket{2}\bra{2})]$ and applying the RWA, the Hamiltonian transforms into
+\[
+\begin{split}
+\hat H^q_1 = \Delta \ket{1}\bra{1} + (\omega_{12}+\Delta) \ket{2}\bra{2} + \\\ g \left[\hat a^\dag \otimes \ket{0}\bra{1} + \hat a \otimes \ket{1}\bra{0}\right].
+\end{split}
+\]
+If we presume that the resonator is in a coherent state $\ket{\alpha e^{-it(\omega_{01}-\Delta)}}$ with $\langle N\rangle = \alpha^2$ photons and average $\hat H_1^q$ over the resonator subspace, we from the interaction term will obtain again the classical driving strength $\Omega_1 = 2 \sqrt{\langle N \rangle} g$ in correspondence with the classical driving case.
+Similarly, the energy levels $\ket{1, N-1}$ and $\ket{0, N}$ become mixed due to the coupling, and their splitting changes from $\Delta$ to $\Omega_R = \sqrt{\Omega_1+\Delta}$.
+The following steps completely reproduce the classical case if we add the probe tone $\Omega_2$ in the last equation.
 

### 2019-10-09 document.tex
New appendics

--- 2019-10-06 document.tex
@@
 %\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{fixme}
+\usepackage{bm}% bold math
 %\usepackage[mathlines]{lineno}% Enable numbering of text and display math
 %\linenumbers\relax % Commence numbering lines
+\usepackage{hyperref}
+\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
 \usepackage[utf8]{inputenc}
@@
 
-\renewcommand*{\figureautorefname}{Fig.}
-
-\newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}
+\newcommand{\mytitile}{Effects of intense light-matter interaction in a superconducting artificial molecule}
 \begin{document}
@@
 \section{Introduction}
-Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
-Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered, and this makes them a particularly versatile tool for studies in quantum optics.
-Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
-For example, the strong coupling regime when the coupling strength between light and a quantum system approaches 1\% of their frequency has been a major milestone for atoms, molecules, etc and was only reached using high-finesse cavities.
-In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
-Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime.
+Over the past twenty years, significant progress has been achieved in the research of the superconducting quantum circuits.
 
-In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels.
-The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.
+We investigate a system of two interacting transmons.
+The transmon\cite{koch2007charge} represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
+This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
+means of an external magnetic flux $\Phi$.
+The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
+The system of two transmons and their connection forms a level system.
+A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
 
-In this work, we are studying effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule (SAM).
-In our experiment, we use two transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
-Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.
+A quantum system exposed to external driving, can experience a number of quantum phenomena due to the resonant transitions between energy levels.
+The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (AT) splitting\cite{autler1955stark} which can happen in systems with just three energy levels.
+The main attention in our work is paid to the last effect, which related to the dressed states.
+The AT effect has been studied in atomic\cite{picque1976direct} and molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and superconducting qubits\cite{li2011decoherence, novikov2013autler}.
 
-It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we have discovered.
-The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAAs as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
-However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics; instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
-
-Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
-
-In  cause of the AT effect is the dressing of the atomic levels by strong EM radiation.
-This dressing The new energy state called dressed states.
+If the driving field is strong the interaction between the system and the field become significant and leads to oscillates with Rabi frequency.
+The new energy state called dressed states.
 If an additional weak probing field is applied, the spectra of the strongly driven system can be probed.
 In particular the dressed state model nicely explains the emergence of the Mollow triplet\cite{newstein1968spontaneous} spectrum, which consists of a central peak with two side bands separated by the Rabi frequency.
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{intro_scheme}
-	\caption{Illustrating the AT splitting in the rotating frame ($\hbar=1$ here).
-\textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
-It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
-\textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
-However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
-Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ with frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
-\end{figure}
 
@@
 
-A sufficiently large anharmonicity is needed to prevent qubit operations from exciting other transitions in the system. Therefore, we will use two- and three-level approximations for our calculations
-
-In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.%\autoref{sec:level1}
+In this article will be shown how the spectrum of the system depends on drivers on different qubits and explicitly shown the dressed states.\autoref{sec:level1}
 
@@
 \subsection{Theoretical description of the system}
-
-We investigate a system of two interacting transmons.
-The transmon represents two Josephson junctions (dc-SQUID) which are shunted by an additional large capacitance(compared to other capacitances in the circuit).
-This dc-SQUID setup allows for the tuning of the Josephson energy $E_J = E_J^{max}|\cos(\pi \frac{\Phi}{\Phi_0})|$  by
-means of an external magnetic flux $\Phi$.
-The transmon can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-The system of two transmons and their connection forms a level system.
-
 In this section we analyse theoretically two qubit system.
@@
 In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
-Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source.
+Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
 
@@
 \appendix
+\section{Theoretical description of two-photon process}
+Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
 
-\subsection{The standard Autler-Townes effect}
+Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$ .
+After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
+The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
+A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
+\begin{equation}\label{forpsi}
+	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
+\end{equation}
 
-\section{Theoretical description of two-photon process}
+The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest.
+Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
+
+Solving \autoref{forpsi} by simple iteration gives the series solution
+\begin{equation}
+	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
+\end{equation}
+\begin{equation}
+	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
+\end{equation}
+For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
+In our case the interaction in interaction picture satisfies the following relation
+\begin{equation}
+	\tilde{V}(t)=\exp(i H_0 t) \exp(-i H_0 t)
+\end{equation}
 

### 2019-10-10 document.tex
LF format
Added the sample design picture

--- 2019-10-09 document.tex
@@
 
+\subsection{Experiment}
+\subsubsection{Device design and fabrication}
+The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
+Qubit control is achieved by external microwave driving line and two flux bias lines.
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{experiment}
+	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
+\end{figure}
+
+\subsubsection{Experimental parameters}
+\subsubsection{Experimental setup}
+The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
+represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK.
+The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator.
+The sample was
+flux biased using YOKOGAWA GS200 current source.
+
+Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source.
+After leaving the sample the signal passed through two isolators and a hybrid coupler.
+Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.
+
 \subsection{Theoretical description of the system}
@@
 \end{equation}
-where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
+where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
 Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
@@
 
-\subsection{Master equation solution in QuTiP}
+\subsection{Master equation solution in \textit{qutip}}
 
@@
 
-When modelling the experimental behaviour, we
-
-\subsection{Experiment}
-\subsubsection{Device design and fabrication}
-The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
-Qubit control is achieved by external microwave driving line and two flux bias lines.
-\subsubsection{Experimental parameters}
-\subsubsection{Experimental setup}
-The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
-represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK.
-The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator.
-The sample was
-flux biased using YOKOGAWA GS200 current source.
-
-Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source.
-After leaving the sample the signal passed through two isolators and a hybrid coupler.
-Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.
+Two distinct modes of operation were used during the
 

### 2019-10-11 document.tex

--- 2019-10-09 document.tex
@@
 %\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
 \usepackage{fixme}
@@
 %\linenumbers\relax % Commence numbering lines
+\usepackage{hyperref}
+\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
 \usepackage[utf8]{inputenc}
@@
 \newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}
+
 \begin{document}
@@
 \section{Introduction}
+
 Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
@@
 Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
+
+The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
+In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
+Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
 
@@
 \subsection{\label{sec:level1} Experimental and numerical parts}
+
 Two tone spectroscopy was found experimentally and shows good agreement with modelling data \autoref{fig:two-tone}.
@@
 \begin{figure*}
+
 	\centering
 	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: \textbf{(a)} Experiment;\textbf{(b)} Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
+	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
 	\label{fig:two-tone}
@@
 \section{Theoretical description of two-photon process}
+Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
+
+Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$ .
+After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
+The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
+A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
+\begin{equation}\label{forpsi}
+	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
+\end{equation}
+
+The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest.
+Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
+
+Solving \autoref{forpsi} by simple iteration gives the series solution
+\begin{equation}
+	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
+\end{equation}
+\begin{equation}
+	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
+\end{equation}
+For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
+In our case the interaction in interaction picture satisfies the following relation
+\begin{equation}
+	\begin{split}
+	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
+	\end{split}
+\end{equation}
+Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
+\begin{equation}
+	\begin{split}
+	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
+	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
+	\end{split}
+\end{equation}
+To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
+\begin{equation}
+	\begin{split}
+	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
+	\end{split}
+\end{equation}
+Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
+\begin{equation}
+	\begin{split}
+	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
+	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
+	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
+	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
+	\end{split}
+\end{equation}
 
@@
 \begin{equation}
-	H_{system} = H_{tr1}\otimes\mathbbm{1}+\mathbbm{1}\otimes H_{tr2}+H_{int}
+	H_{system} = H_{tr1}\otimes \mathbbm{1}+\mathbbm{1}\otimes H_{tr2}+H_{int}
 \end{equation}

### 2019-10-12 document.tex
Experimental details added

--- 2019-10-10 document.tex
@@
 \subsection{Experiment}
+
 \subsubsection{Device design and fabrication}
-The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
-Qubit control is achieved by external microwave driving line and two flux bias lines.
+We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states.
+In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components.
+The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed.
+In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler.
+Flux lines that allow independent control of the $ge$ transitions of the transmons are coming from the sides.
+Finally, the excitation waveguide coming from below directs microwave signal towards the SAM.
+In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device.
+The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances.
+The capacitively coupled excitation line is also shown in green.
+Finally, in \autoref{fig:experiment}~(c) we show schematically the $ge$ transitions of the transmons depending on the external magnetic flux.
+Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
+Using both coils, it is possible to align them so that the lower sweet-spot of the orange qubit.
+As will be shown, this arrangement allows to see multiple energy level intersections including higher transmon levels, and thus we are measuring the SAM in the region shown with the dashed rectangle.
 
@@
 	\includegraphics[width=\linewidth]{experiment}
-	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
+	\caption{Experimental device.
+\textbf{(a)} Optical photograph of the device (false coloured).
+Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
+From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green).
+\textbf{(b)} The equivalent electrical circuit.
+Tunable Josephson junctions are in fact SQUIDs with magnetic flux control.
+\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly).
+In this work, we concentrate on the area inside the dashed rectangle.}
+	\label{fig:experiment}
 \end{figure}
+
+\begin{table}
+	\begin{tabular}{c|c|c|c}
+	Parameter & Resonator & Qubit 1 & Qubit 2\\\hline
+	$\omega/2\pi$ [GHz] & 7 & 5.12 - 6.9 & 4 - 5.45\\
+	$\Gamma_1$ [$\mu$s] & 0.1 & $\leq$ 10  &  $\leq$ 5\\
+	$\Gamma_2$ [$\mu$s] & - & $\leq$ 7  &  $\leq$ 1
+	\end{tabular}
+	\caption{Device parameters}
+\end{table}
 

### 2019-10-13 document.tex
Table parameters

@@
 \begin{table}
-	\begin{tabular}{c|c|c|c}
-	Parameter & Resonator & Qubit 1 & Qubit 2\\\hline
-	$\omega/2\pi$ [GHz] & 7 & 5.12 - 6.9 & 4 - 5.45\\
-	$\Gamma_1$ [$\mu$s] & 0.1 & $\leq$ 10  &  $\leq$ 5\\
-	$\Gamma_2$ [$\mu$s] & - & $\leq$ 7  &  $\leq$ 1
+	\begin{ruledtabular}
+	\begin{tabular}{rll}
+	Parameter & Transmon 1  & Transmon 2\\\hline
+	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
+	$\alpha/2\pi$ [MHz] & 250 & 250 \\
+	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
+	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
+	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
 	\end{tabular}
-	\caption{Device parameters}
+	\end{ruledtabular}
+	\caption{SAM parameters.
+Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
 \end{table}

### 2019-10-13 Pictures/Plotting/MainPicturePlot.py

@@ -67,10 +67,11 @@ class MainPicturePlot:
         #     self._cache[self.nstate] = C
 
         C = np.real(self._C_th.T)
-        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.039+0.005
+        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.039+0.005# + np.random.normal(scale=0.001,
+                                                           #                    size=C.shape)
 
         data = self._X_th, self._Y_th, C
-        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.05*np.max(C))
+        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.0*np.max(C))
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(1,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');

### 2019-10-13 document.tex

--- 2019-10-11 document.tex
@@
 	\includegraphics[width=\linewidth]{experiment}
-	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
+	\caption{Experimental device.
+\textbf{(a)} Optical photograph of the device (false coloured).
+Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
+From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green).
+\textbf{(b)} The equivalent electrical circuit.
+Tunable Josephson junctions are in fact SQUIDs with magnetic flux control.
+\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly).
+In this work, we concentrate on the area inside the dashed rectangle.}
+	\label{fig:experiment}
 \end{figure}
+
+\begin{table}
+	\begin{ruledtabular}
+	\begin{tabular}{rll}
+	Parameter & Transmon 1  & Transmon 2\\\hline
+	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
+	$\alpha/2\pi$ [MHz] & 250 & 250 \\
+	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
+	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
+	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
+	\end{tabular}
+	\end{ruledtabular}
+	\caption{SAM parameters.
+Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
+\end{table}
 

### 2019-10-15 document.tex
Methods

@@
 \usepackage{bbm}
-\usepackage{nicematrix}
 %\usepackage{multirow}
@@
 
-In this section, we provide the mathematical formulation of the employed models, specify the numerical approaches that were used in simulations and describe the experimental equipment and some measurement aspects.
-
-\subsection{Experiment}
-
-\subsubsection{Device design and fabrication}
-We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states.
+\subsection{Device design and fabrication}
+We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states.
 In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components.
@@
 Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
-Using both coils, it is possible to align them so that the lower sweet-spot of the orange qubit.
-As will be shown, this arrangement allows to see multiple energy level intersections including higher transmon levels, and thus we are measuring the SAM in the region shown with the dashed rectangle.
+Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
+This is convenient as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency.
+Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
+
+The fabrication process...
 
@@
 	\includegraphics[width=\linewidth]{experiment}
-	\caption{Experimental device.
-\textbf{(a)} Optical photograph of the device (false coloured).
+	\caption{\textbf{(a)} Optical photograph of the device (false coloured).
 Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
@@
 
-\subsubsection{Experimental parameters}
-\subsubsection{Experimental setup}
-The sample was measured in laboratory of artificial quantum systems at Moscow Institute of Physics and Technology. Cryogenic equipment was
-represented by BlueFors LD250 dilution refrigerator, with base temperature of 16 mK.
-The microwave equipment included KEYSIGHT PNA-L N5232A 300 kHz-20 GHz vector network analyser, Agilent MXG N5183B 9 kHz - 40 GHz analog signal generator.
-The sample was
-flux biased using YOKOGAWA GS200 current source.
-
-Microwave line was thermalized with 60 dB of attenuation, additional 20 dB of attenuation were introduced on a directional coupler which added the second tone from the $\mu$-wave source.
-After leaving the sample the signal passed through two isolators and a hybrid coupler.
-Finally, the signal was amplified with 4-8 GHz LNF amplifier at 4 K and a with a room-temperature amplifier.
-
-\subsection{Theoretical description of the system}
+\subsection{Theoretical description of the SAM}
 
 A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$:
+Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
 \begin{equation}
-\hat H_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
+\hat{{H}}_{tr} = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
 \end{equation}
@@
 Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
+In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).
 
-The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
-In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
-Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
-
-To induce state transitions in a transmon one should irradiate it by a monochromatic external microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
-The interaction term between the transmon and this classical EM field is then modelled by the following operator:
+To induce state transitions in a transmon one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
+The interaction term between the transmon and the field is then modelled by the following operator:
 \begin{equation}
-\hat H_{dr}/\hbar = \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger}),
+\hat H_{dr} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
 \end{equation}
@@
 
-Now, for the molecule composed of two coupled transmons, the complete Hamiltonian contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the qubit-qubit interaction term:
+Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
@@
 \end{equation}
-where $\hat H_{int}/\hbar= J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
+where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
+In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
+\begin{align}
+&\hat R = \exp[i (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)t],\\
+&\hat H_R = \hat R^{\dagger}\hat H \hat R + i\hat R^{\dagger}\partial_t \hat R.
+\end{align}
+After the transformation and application of RWA:
+\begin{equation}
+\begin{aligned}
+	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
+	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
+	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
+	\hat H_{dr}^2 &\rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
+\end{aligned}
+\label{eq:RWA}
+\end{equation}
 
@@
 \begin{split}
-\hat{\mathcal{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
-\hat{\mathcal{O}}_{\phi, 1} = \sqrt{2\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
-\hat{\mathcal{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
-\hat{\mathcal{O}}_{\phi,2} = \sqrt{2\gamma_{ \phi,2}}\, \hat c^\dag \hat c.
+\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
+\hat{{O}}_{\phi, 1} = \sqrt{2\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
+\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
+\hat{{O}}_{\phi,2} = \sqrt{2\gamma_{ \phi,2}}\, \hat c^\dag \hat c.
 \end{split}
@@
 \begin{equation}
-\partial_t \hat \rho = \frac{i}{\hbar} [\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{\mathcal{O}}_{\alpha, i}] \hat \rho, \label{eq:master}
+\partial_t \hat \rho = {i}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
 \end{equation}
-where $\mathcal{D}[\hat{\mathcal{O}}]\hat \rho = \hat{\mathcal{O}} \hat \rho \hat{\mathcal{O}}^\dag - \frac{1}{2}\{ \hat{\mathcal{O}}^\dag \hat{\mathcal{O}}, \hat \rho\}$.
+where $\mathcal{D}[\hat{{O}}]\hat \rho = \hat{{O}} \hat \rho \hat{{O}}^\dag - \frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat \rho\}$ and $\mathcal{L}$ is the Liouville superoperator or the Liouvillian.
 
-\subsection{Master equation solution in \textit{qutip}}
+The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM.
+The readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
+Another way to find $\hat M(f_p)$ is to calculate the transmission using the dispersive shifts for these states by correspondingly offsetting the experimental resonance curve.
+Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters.
+Finally, the observable value for any state $\hat \rho$ is calculated as $S_{21}^{sim}(f_p) = \Tr[\hat M(f_p) \hat \rho]$.
 
-Numerical simulations are crucial in studying the equation \eqref{eq:master} since is does not allow an analytical solution.
-We have been using the \textit{qutip}\cite{johansson2013qutip} quantum optics toolbox to simulate the dynamics and find the steady state of the system for various parameter combinations of the Hamiltonian.
+\subsection{Numerical solution in \textit{qutip}}
 
-Two distinct modes of operation were used during the
+Numerical simulations are crucial for studying the equation \eqref{eq:master} since is does not allow  analytical solution.
+Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.
+
+Two distinct modes of simulation were used during the modelling.
+The first one is for the Liouvillians that do not explicitly depend on time (stationary case).
+In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}:
+\begin{equation}
+\partial_t \hat \rho = 0 = \mathcal{L} \hat \rho
+\end{equation}
+This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
+This method is applicable when the driving of the two transmons is at the same frequency since from \eqref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.
+
+The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian.
+This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$).
+From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results.
+In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions.
+The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
+\begin{equation}
+\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
+\end{equation}
+where $\mathcal T$ is the time-ordering superoperator.
+Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}.
+Upon infinite applications of $\Lambda$:
+\[
+\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
+\]
 
@@
 In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted.
-The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the orange are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$.
+The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$.
 However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
@@
 We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\label{fig:difdrive}
-\end{figure}
+\end{figure*}
 
@@
 
-\renewcommand{\kbldelim}{(}% Left delimiter
-\renewcommand{\kbrdelim}{)}% Right delimiter
+\renewcommand{\kbldelim}{[}% Left delimiter
+\renewcommand{\kbrdelim}{]}% Right delimiter
 \begin{widetext}
@@
 	\text{$H^R$} = \kbordermatrix{
-	\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
-	0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
-	\text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
-	\text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
+	&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
+	\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
+	\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
+	\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
 	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
-	0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
+	\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
 	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
 			$} t}/2 \\
-	0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
+	\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
 	\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
-	0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
+	\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
 		$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
@@
 
+\section{Measurement setup}
+The sample was measured in a BlueFors LD250 dilution refrigerator at 16 mK.
+For the readout a Keysight PNA-L N5232A VNA was used.
+For the coherent excitation of the SAM, we used an Agilent MXG N5183B analog signal generator.
+The sample was
+flux biased using Yokogawa GS200 current sources (two for the flux lines and one for the external coil wrapped around the sample).
+
+Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters.
+Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well.
+Output path contained two 20 dB isolators and two amplifiers: the 4-14 GHz LNF amplifier at the 4 K stage and the room-temperature LNF amplifier.
+
 \section{Text}
@@
 
+ The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
+In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
+ Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
+
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-10-15 Pictures/Plotting/MainPicturePlot.py

@@ -41,7 +41,7 @@ class MainPicturePlot:
 
     def plot_experiment(self, ax):
         data = self._X_exp, self._Y_exp, np.real(self._C_exp)
-        img1 = ax.pcolormesh(*data, rasterized=True)
+        img1 = ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
@@ -53,7 +53,7 @@ class MainPicturePlot:
         plt.text(-0.15, 1.1, "(a)", fontdict={"name": "STIX"}, fontsize=22,
                  transform=ax.transAxes)
 
-        self._zoom(ax, data)
+        self._zoom(ax, data, vmin=-0.005, vmax = 0.022)
 
     def plot_theory(self, ax):
 
@@ -67,11 +67,11 @@ class MainPicturePlot:
         #     self._cache[self.nstate] = C
 
         C = np.real(self._C_th.T)
-        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.039+0.005# + np.random.normal(scale=0.001,
+        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.027+(0.027/2-0.005)# + np.random.normal(scale=0.001,
                                                            #                    size=C.shape)
-
+        C = C
         data = self._X_th, self._Y_th, C
-        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.0*np.max(C))
+        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.025*np.max(C))
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(1,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
@@ -83,10 +83,10 @@ class MainPicturePlot:
         plt.text(-0.075, 1.1, "(b)", fontdict={"name": "STIX"}, fontsize=22,
                  transform=ax.transAxes)
 
-        self._zoom(ax, data)
[…]

### 2019-10-23 document.tex
AppenB

--- 2019-10-13 document.tex
@@
 \subsection{Experiment}
-
 \subsubsection{Device design and fabrication}
-We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states.
-In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components.
-The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed.
-In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler.
-Flux lines that allow independent control of the $ge$ transitions of the transmons are coming from the sides.
-Finally, the excitation waveguide coming from below directs microwave signal towards the SAM.
-In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device.
-The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances.
-The capacitively coupled excitation line is also shown in green.
-Finally, in \autoref{fig:experiment}~(c) we show schematically the $ge$ transitions of the transmons depending on the external magnetic flux.
-Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
-Using both coils, it is possible to align them so that the lower sweet-spot of the orange qubit.
-As will be shown, this arrangement allows to see multiple energy level intersections including higher transmon levels, and thus we are measuring the SAM in the region shown with the dashed rectangle.
+The chip consist the transmission line capacitively couple to $\lambda/4$ coplanar waveguide resonator which capacitively couple to two transmons.
+Qubit control is achieved by external microwave driving line and two flux bias lines.
 
@@
 	\includegraphics[width=\linewidth]{experiment}
-	\caption{Experimental device.
-\textbf{(a)} Optical photograph of the device (false coloured).
-Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
-From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green).
-\textbf{(b)} The equivalent electrical circuit.
-Tunable Josephson junctions are in fact SQUIDs with magnetic flux control.
-\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly).
-In this work, we concentrate on the area inside the dashed rectangle.}
-	\label{fig:experiment}
+	\caption{Experimental details. \textbf{(a)} Sample optical photograph \textbf{(b)} Electrical scheme \textbf{(c)} Spectral lines of the qubits}
 \end{figure}
-
-\begin{table}
-	\begin{ruledtabular}
-	\begin{tabular}{rll}
-	Parameter & Transmon 1  & Transmon 2\\\hline
-	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
-	$\alpha/2\pi$ [MHz] & 250 & 250 \\
-	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
-	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
-	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
-	\end{tabular}
-	\end{ruledtabular}
-	\caption{SAM parameters.
-Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
-\end{table}
 
@@
 \end{widetext}
-Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{tr1}=0$,$\Delta_2 = \omega_d-\omega_{tr2}$.
+Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{1}=0$,$\Delta_2 = \omega_d-\omega_{2}$, $\delta_{\omega} = \omega_{dr1}-\omega_{dr2}$.
 Let's consider the Hamiltonian (\autoref{matrix}) in details.
@@
 \end{equation}
-The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$.
-The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues.
-The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width os the dressed states.
+The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b).
+The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width off the dressed states.
 Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
@@
 \section{Theoretical description of two-photon process}
-Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
+Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.
 
-Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$ .
-After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
-The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
+Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$.
+After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\tilde{\psi}(t)}{t}=\tilde{V}(t)\tilde{\psi}(t)$.
+The reference states of $H_0$ will be denoted as $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
 A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
 \begin{equation}\label{forpsi}
-	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
+	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
 \end{equation}
 
-The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest.
+Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state.
 Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
@@
 \end{equation}
+The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude.
+So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
+The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
+\begin{equation}
+	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
+\end{equation}
+For simplifier the equation we have made use of the relation:
+\begin{equation}\nonumber
+	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
+\end{equation} 
+For $\omega_f=\omega_i+2\omega_d$.
+\begin{equation}
+	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)
+\end{equation}
 
@@
 
- Let's described the anti-crossing highlighted in red in the picture.
-
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-10-24 document.tex
Experimental results started

--- 2019-10-15 document.tex
@@
 
-Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
+Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
@@
 \begin{align}
-&\hat R = \exp[i (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)t],\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R + i\hat R^{\dagger}\partial_t \hat R.
+&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\\
+&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.
 \end{align}
@@
 \begin{aligned}
-	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
-	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
+	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_d^{(1,2)}-\omega_{(1,2)},\\
+	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
 	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
@@
 The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM.
-The readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
-Another way to find $\hat M(f_p)$ is to calculate the transmission using the dispersive shifts for these states by correspondingly offsetting the experimental resonance curve.
+Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
+Another way to find $\hat M(f_p)$ is to calculate the transmission by offsetting the experimental resonance curve using the dispersive shifts corresponding to these states.
 Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters.
@@
 \Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
+\label{eq:propagator}
 \end{equation}
@@
 
-\subsection{\label{sec:level1} Experimental and numerical parts}
-
-Two tone spectroscopy was found experimentally and shows good agreement with modelling data \autoref{fig:two-tone}.
+\subsection{\label{sec:level1} Spectroscopy: experiment and numerical simulation}
 
@@
 	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
+	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}.
+Colour shows the real part of complex transmission  through the sample.
+Two transmons are aligned as in \autoref{fig:experiment}~(c) and thus the picture is symmetric.
+Panel \textbf{(a)} contains an additional horizontal line which origins from a parasitic resonance interacting with the readout resonator but not with the SAM.
+Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; some other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
+In panel \textbf{(b)}, we also denote where possible some of the transitions $\ket{00}\rightarrow \ket{ij/n}$ where $i,j$ stand for the transmon eigenstates and $/n$ is optional for an $n$-photon process.}
 	\label{fig:two-tone}
 \end{figure*}
+
+Experiment was conducted as described in Appendix \ref{sec:meas_setup}.
+We have used high-power two-tone spectroscopy (qubit Rabi frequencies $\Omega_1$ and $\Omega_2$ were around 20 MHz) to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a).
+As one can see, several spectral lines are visible besides the $ge$ ones shown in \autoref{fig:experiment}~(c).
+Their frequency depends on the applied current, and at multiple points they become resonant with each other.
+At three pairs of these resonant points, we observe three distinct features shown in insets marked with Roman numerals.
+Some secondary details are shown with Arabic-numbered markers.
+
+Remarkably, in areas I, II and III we could observe avoided crossings which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
+We confirm this by numerically diagonalizing it taking 3 levels for each transmon (and total 9 states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix.
+While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects.
+Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show below.
+
+To check whether these avoided crossings are observable in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$.
+Strikingly, all the experimental features are immediately reproduced using this approach even with only 9 SAM states.
+We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the result; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
+3 minutes with RWA.
+
+Next, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other (not shown, should we show?).
+Upon this, it has become clear that feature II and feature III actually have the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with a two-photon one to $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
+
+All of the observed features depend significantly on power.
 
@@
 
-We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
 \begin{figure*}
@@
 
-Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$ .
+Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$.
 After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
@@
 
-\section{Measurement setup}
+\section{Measurement setup and methods}\label{sec:meas_setup}
 The sample was measured in a BlueFors LD250 dilution refrigerator at 16 mK.
@@
 Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters.
+The additional on-chip attenuation (due to the small capacitive coupling) between the qubit drive line and the qubits was calculated in Sonnet to be around 70 dB @ 6 GHz.
 Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well.
 Output path contained two 20 dB isolators and two amplifiers: the 4-14 GHz LNF amplifier at the 4 K stage and the room-temperature LNF amplifier.
+
+As the main experimental method, we have employed the two-tone spectroscopy which consists of exciting the SAM with monochromatic light at certain frequency until steady state is reached while simultaneously measuring the signal transmission at the readout resonator frequency.
+This measurement yields the average value of the joint measurement operator $\hat M$ in the steady-state.
 
@@
 		$\ket{12}$ and the fourth from  $\ket{10}$ to  $\ket{02}$, where $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively}
-	\label{fig:spectr}
+	\label{fig:statinary_levels}
 \end{figure}

### 2019-10-24 Pictures/Plotting/MainPicturePlot.py

@@ -53,6 +53,35 @@ class MainPicturePlot:
         plt.text(-0.15, 1.1, "(a)", fontdict={"name": "STIX"}, fontsize=22,
                  transform=ax.transAxes)
 
+        plt.text(.53, .815, r"$\omega_2(\Phi_e)/2\pi$", fontdict={"name": "STIX"}, fontsize=7.5,
+                 transform=ax.transAxes, ha='center')
+
+        plt.text(.54, .355, r"$\omega_1(\Phi_e)/2\pi$", fontdict={"name": "STIX"}, fontsize=7.5,
+                 transform=ax.transAxes, ha='center')
+
+        ax.annotate('spurious\nresonance', xy=(5, 5.37), xytext=(5.1, 5.45), ha="center", fontsize=10,
+                    arrowprops=dict(facecolor='black', width =1, headwidth = 5, headlength = 7, shrink=0.05))
+
+
+        ax.annotate("1", xy=(3.48, 5.23), xytext=(3.55, 5.21), ha="center", fontsize=10,
+                    arrowprops=dict(facecolor='black', width =.5, headwidth = 3, headlength = 3.5, shrink=0.05))
+
+        ax.annotate('2', xy=(5.07, 5.21), xytext=(5.07, 5.185), ha="center", fontsize=10,
+                    arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                    shrink=0.05))
+
+        ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.26), ha="center", fontsize=10,
+                    arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                    shrink=0.05))
+
+        ax.annotate('4', xy=(4.9, 5.195), xytext=(4.8, 5.195), ha="center", va="top", fontsize=10,
+                    arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                    shrink=0.05))
+
+        ax.annotate("5", xy=(3.515, 5.177), xytext=(3.585, 5.1795), ha="center", va="bottom", fontsize=10,
+                    arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                    shrink=0.05))
+
         self._zoom(ax, data, vmin=-0.005, vmax = 0.022)
 
     def plot_theory(self, ax):
@@ -80,8 +109,48 @@ class MainPicturePlot:
[…]

### 2019-10-27 document.tex
Spectral line analysis

@@
 \usepackage{bbm}
+\usepackage{xcolor}
+
 %\usepackage{multirow}
@@
 	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
-	$\alpha/2\pi$ [MHz] & 250 & 250 \\
+	$\alpha/2\pi$ [MHz] & 220 & 220 \\
 	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
@@
 A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-Therefore, in the main text we avoid using the standard charge and phase operators (this approach is covered Appendix) and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
+Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
 \begin{equation}
@@
 
-Remarkably, in areas I, II and III we could observe avoided crossings which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
-We confirm this by numerically diagonalizing it taking 3 levels for each transmon (and total 9 states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix.
+Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
+We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix.
 While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects.
-Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show below.
+Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show in the following.
 
-To check whether these avoided crossings are observable in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$.
-Strikingly, all the experimental features are immediately reproduced using this approach even with only 9 SAM states.
-We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the result; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
+To check whether the described features are present in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$.
+Strikingly, all the experimental features are immediately reproduced using this approach with just 9 SAM states.
+We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the results; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
 3 minutes with RWA.
 
-Next, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other (not shown, should we show?).
-Upon this, it has become clear that feature II and feature III actually have the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with a two-photon one to $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
+\subsection{Analysis of the spectra}
 
-All of the observed features depend significantly on power.
+\begin{figure}
+	\includegraphics[width=\linewidth]{zoom_picture}
+	\caption{Zoomed-in simulation of feature III with increasing amplitude of the driving of the first transmon $\Omega_1/2\pi=$2, 4, 10 and 20 MHz while the second drive is fixed at $\Omega_2/2\pi=$10 MHz; other parameters as in \autoref{fig:two-tone}.
+Note that now colours show the population of the ground state ($\ket{00}$).
+The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.
+Interestingly, population inversion is observed inside the red-coloured areas of the graph: $\ket{00}$ population is less than 20\% there.}
+	\label{fig:zoom}
+\end{figure}
+
+\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to find which spectral lines correspond to which transitions in the system.
+In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $\ket{ij/n}$ where $i,j$ denote the final transmon states after the transition from $\ket{00}$, and $/n$ is optional for an $n$-photon process.
+We put the labels at the line of symmetry where the transmons are in their sweet spots; the SAM states at this point are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
+
+Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$.
+The $\ket{02/2}$ and $\ket{20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
+Another two-photon process appears as $\ket{11/2}$ line when two qubits are excited simultaneously.
+This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I.
+A three-photon process $\ket{00}\rightarrow\ket{12/3}$ is also clearly visible just below the $\ket{02/2}$ line.
+As we will see, it is involved in forming features II and III.
+
+Notably, transitions $\ket{11/2}$ and $\ket{12/3}$ are forbidden when there is no interaction ($J=0$).
+Therefore, it is expected that all Roman-numbered features should only appear with non-vanishing $\hat H_{int}$.
+
+When two lines intersect, they may form an avoided crossing if the corresponding matrix element is non-zero in $\hat H_{int}$.
+In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states.
+For a two-transmon SAM, such points are, for instance, crossings between $\ket{01}$, $\ket{10}$ or $ \ket{11} $, $ \ket{02} $($ \ket{20} $).
+Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between $\ket{12},\ \ket{21}$ at the same $\Phi_e$ where $\ket{01}$, $\ket{10}$ cross.
+
+\paragraph{Analysing features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other \textbf{(not shown, should we show?)}.
+Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
+
+From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and usually invisible $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$.
+From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}.
+There is no dependence on the drive power of the second transmon, though.
+As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line.
+
+We come to the same conclusion for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits an avoided crossing with a proportionally enlarging splitting (see \autoref{fig:difdrive}).
+Notably, two qualitatively different patterns of avoided crossings arise when the first or the second qubit is strongly driven.
+
+These observation lead to understanding that the effect is caused by the light-dressing.
+In case III, the first transmon is dressed by a strong resonant field, in case II the second one, and in case I both transmons are dressed at the same time.
+The exact origin of the triplet structure of the resulting
+
+\paragraph{Analysing }
+
+Finally, we have found that when the coupling is turned off ($J=0$), the system does not demonstrate at all any of the Roman-numbered features highlighted in \autoref{fig:two-tone} (similarly, Arabic ones also disappear).
+This is expected due to the lines participating in them  means that these effects can only be attributed molecule as a whole and not the SAAs themselves.
 
@@
 	\label{fig:main_scheme}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\linewidth]{drawing}
-	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
-	\label{fig:difdrive}
 \end{figure*}
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=\linewidth]{drawing}
+	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
+	\label{fig:difdrive}
+\end{figure*}
+
  Let's described the anti-crossing highlighted in red in the picture.

### 2019-10-27 Pictures/Plotting/MainPicturePlot.py

@@ -13,6 +13,7 @@ class MainPicturePlot:
 
     def __init__(self):
         self._cache_file = "main_pic_cache.pkl"
+        self._cmap = "Spectral"
         self.nstate = 0
         try:
             with open(self._cache_file, "rb") as f:
@@ -41,7 +42,7 @@ class MainPicturePlot:
 
     def plot_experiment(self, ax):
         data = self._X_exp, self._Y_exp, np.real(self._C_exp)
-        img1 = ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022)
+        img1 = ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap = self._cmap)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
@@ -100,7 +101,7 @@ class MainPicturePlot:
                                                            #                    size=C.shape)
         C = C
         data = self._X_th, self._Y_th, C
-        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.025*np.max(C))
+        img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.025*np.max(C), cmap = self._cmap)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(1,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
@@ -173,13 +174,13 @@ class MainPicturePlot:
         # ax1.broken_barh([(3.1,0.4)],(5.31,0.02),edgecolors = 'r', facecolors = 'none',linewidth= 1, linestyle = '--')
         for axis in ['top', 'bottom', 'left', 'right']:
             axins.spines[axis].set_color(color)
-        axins.pcolormesh(*data, rasterized=True, vmax = vmax, vmin=vmin)
+        axins.pcolormesh(*data, rasterized=True, vmax = vmax, vmin=vmin, cmap = self._cmap)
         for axis in ['top', 'bottom', 'left', 'right']:
             axins1.spines[axis].set_color(color)
[…]

### 2019-10-27 Pictures/Plotting/StationaryPlot.py

@@ -1,0 +1,24 @@
+import pickle
+from numpy import *
+import matplotlib
+from matplotlib import ticker, colorbar as clb
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+
+
+class StationaryPlot:
+
+    def __init__(self):
+
+        with open("stationary.pkl", "rb") as f:
+            currs, freqs, population10, energies = pickle.load(f)
+
+        plt.pcolormesh(currs, freqs, log10(array(population10)), rasterized=True, cmap="Spectral_r")
+
+        plt.savefig("../stationary.pdf", bbox_inches="tight", dpi=600)
+
+
+StationaryPlot()

### 2019-10-27 Pictures/Plotting/ZoomPlot.py

@@ -1,0 +1,60 @@
+import pickle
+from numpy import *
+import matplotlib
+from matplotlib import ticker, colorbar as clb
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+
+
+class ZoomPlot:
+
+    def __init__(self):
+        with open('zoom.pkl', 'rb') as f:
+            self._X, self._Y, self._plots = pickle.load(f)
+
+        fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(4, 4))
+        plt.subplots_adjust(wspace=.2, hspace=.2)
+
+        for idx, ax in enumerate(axes.ravel()):
+            m = ax.pcolormesh(self._X, self._Y, real(array(self._plots[idx]).T),
+                              vmax=1, vmin=0, rasterized=True, cmap="Spectral")
+            if idx % 2 == 0:
+                ax.set_ylabel('Frequency [GHz]');
+            if idx > 1:
+                ax.set_xlabel('Current [$10^{-4}$ A]');
+
+        plt.text(.1, .65, r"$\left|10\right\rangle$", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[0,0].transAxes, ha='center', color="white")
+
+
+        plt.text(.7, .9, r"$\left|02/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[0,0].transAxes, ha='center', color="white")
+
+
+        plt.text(.25, .025, r"$\Omega_1/2\pi =$2 MHz", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[0,0].transAxes, ha='left', color="white")
+
+
+        plt.text(.66, .025, r"5 MHz", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[0,1].transAxes, ha='left', color="black")
+
+        plt.text(.6, .025, r"10 MHz", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[1,0].transAxes, ha='left', color="black")
+
+        plt.text(.6, .025, r"20 MHz", fontdict={"name": "STIX"}, fontsize=10,
+                 transform=axes[1,1].transAxes, ha='left', color="black")
+
+
[…]

### 2019-10-29 document.tex
AppenB and results

--- 2019-10-24 document.tex
@@
 
-Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
+Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$ and the $ge$ frequencies $\omega_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
@@
 \begin{align}
-&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.
+&\hat R = \exp[i (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)t],\\
+&\hat H_R = \hat R^{\dagger}\hat H \hat R + i\hat R^{\dagger}\partial_t \hat R.
 \end{align}
@@
 \begin{aligned}
-	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_d^{(1,2)}-\omega_{(1,2)},\\
-	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
+	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
+	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
 	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
@@
 The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM.
-Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
-Another way to find $\hat M(f_p)$ is to calculate the transmission by offsetting the experimental resonance curve using the dispersive shifts corresponding to these states.
+The readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
+Another way to find $\hat M(f_p)$ is to calculate the transmission using the dispersive shifts for these states by correspondingly offsetting the experimental resonance curve.
 Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters.
@@
 \Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
-\label{eq:propagator}
 \end{equation}
@@
 
-\subsection{\label{sec:level1} Spectroscopy: experiment and numerical simulation}
+\subsection{\label{sec:level1} Experimental and numerical parts}
+
+Two tone spectroscopy was found experimentally and shows good agreement with modelling data \autoref{fig:two-tone}.
 
@@
 	\includegraphics[width=\linewidth]{main_picture}
-	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}.
-Colour shows the real part of complex transmission  through the sample.
-Two transmons are aligned as in \autoref{fig:experiment}~(c) and thus the picture is symmetric.
-Panel \textbf{(a)} contains an additional horizontal line which origins from a parasitic resonance interacting with the readout resonator but not with the SAM.
-Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; some other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
-In panel \textbf{(b)}, we also denote where possible some of the transitions $\ket{00}\rightarrow \ket{ij/n}$ where $i,j$ stand for the transmon eigenstates and $/n$ is optional for an $n$-photon process.}
+	\caption{Two-tone spectroscopy: (a) Experiment;b(b) Modelling ; the colorbar is common.  Clear flux-dependent transmon transitions are visible.}
 	\label{fig:two-tone}
 \end{figure*}
-
-Experiment was conducted as described in Appendix \ref{sec:meas_setup}.
-We have used high-power two-tone spectroscopy (qubit Rabi frequencies $\Omega_1$ and $\Omega_2$ were around 20 MHz) to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a).
-As one can see, several spectral lines are visible besides the $ge$ ones shown in \autoref{fig:experiment}~(c).
-Their frequency depends on the applied current, and at multiple points they become resonant with each other.
-At three pairs of these resonant points, we observe three distinct features shown in insets marked with Roman numerals.
-Some secondary details are shown with Arabic-numbered markers.
-
-Remarkably, in areas I, II and III we could observe avoided crossings which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
-We confirm this by numerically diagonalizing it taking 3 levels for each transmon (and total 9 states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix.
-While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects.
-Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show below.
-
-To check whether these avoided crossings are observable in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$.
-Strikingly, all the experimental features are immediately reproduced using this approach even with only 9 SAM states.
-We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the result; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
-3 minutes with RWA.
-
-Next, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other (not shown, should we show?).
-Upon this, it has become clear that feature II and feature III actually have the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with a two-photon one to $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
-
-All of the observed features depend significantly on power.
 
@@
 
+We obtain illustrative example of dressed states\autoref{fig:difdrive}. On this figure the microwave drive acts only on the one of qubits. 
 \begin{figure*}
@@
 \end{equation}
-The $\Omega_1\gg \Omega_2,\Delta_2\gg J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$.
-The Hamiltonian $H_0$ is station and we can find eigenvectors and eigenvalues.
-The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width os the dressed states.
-Firstly, we consider the system of non-interacting qubits $(J=0)$. In this case some transitions are prohibited and the splitting we are interested in is not observed. 
-Therefore a non-zero interaction between qubits is necessary to observe AT effect.
+The $\Omega_1\gg \Omega_2,\Delta_2> J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b).
+The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width of the dressed states.
+At our working point the condition $\Delta_2=\alpha/2$ is met and $H_0$ becomes degenerate.
 
-After that according to the perturbation theory (with perturbation $V_J$) to $H_0$ we found the first-order corrections to the wave functions.
-We can use Fermi Golden Rule to find the probability of transition.
+According to the degenerate perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions.
+Calculating the probability of two-photon transition per unit interaction time using the \autoref{prob} for corrected  wave functions and neglecting small terms we obtain:
+\begin{equation}
+	A^{(2)}_{1\rightarrow 6} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}+19 \text{$\Omega_1 $})^2}{\text{$\alpha
+			$}^6 \text{$\Omega_1$}^2}
+\end{equation}
+\begin{equation}
+A^{(2)}_{2\rightarrow 5} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}-19 \text{$\Omega_1 $})^2}{\text{$\alpha
+		$}^6 \text{$\Omega_1$}^2}
+\end{equation}
+
+So, in the system of non-interacting qubits $(J=0)$ some transitions are prohibited and the splitting we are interested in is not observed.
+Therefore a non-zero interaction between qubits is necessary to observe AT effect in our system.
+
 \appendix
@@
 
+\section{Degenerate perturbation theory}
+\begin{equation}
+H^R=H_0+V_J
+\end{equation}
+At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
+\begin{equation}
+H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
+\end{equation}
+The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation.
+However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined.
+To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace.
+However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$.
+This means that the degeneracy is not lifted at first-order in perturbation theory.
+We have to pick eigenvectors which diagonalize following matrix:
+\begin{equation}
+	\begin{matrix}
+	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
+	\end{matrix}
+\end{equation}
+Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
+For example, in our case for one of degenerate subspaces:
+\begin{equation}
+	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
+\end{equation}
+The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
+The first-order correction to the states from degenerate subspace:
+\begin{equation}
+	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
+\end{equation}
+The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
+The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
+\begin{equation}
+	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
+\end{equation}
+
 \section{Theoretical description of two-photon process}
-Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
+Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.
 
-Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$.
-After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
-The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
+Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$.
+After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\tilde{\psi}(t)}{t}=\tilde{V}(t)\tilde{\psi}(t)$.
+The reference states of $H_0$ will be denoted as $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
 A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
 \begin{equation}\label{forpsi}
-	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
+	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
 \end{equation}
 
-The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest.
+Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state.
 Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
@@
 \end{equation}
+The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude.
+So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
+The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
+\begin{equation}
+	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
+\end{equation}
+For simplifier the equation we have made use of the relation:
+\begin{equation}\nonumber
+	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
+\end{equation} 
+For $\omega_f=\omega_i+2\omega_d$.
+\begin{equation}\label{prob}
+\begin{split}
+	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
+\end{split}
+\end{equation}
 
-\section{Measurement setup and methods}\label{sec:meas_setup}
+\section{Measurement setup}
 The sample was measured in a BlueFors LD250 dilution refrigerator at 16 mK.
@@
 Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters.
-The additional on-chip attenuation (due to the small capacitive coupling) between the qubit drive line and the qubits was calculated in Sonnet to be around 70 dB @ 6 GHz.
 Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well.
 Output path contained two 20 dB isolators and two amplifiers: the 4-14 GHz LNF amplifier at the 4 K stage and the room-temperature LNF amplifier.
-
-As the main experimental method, we have employed the two-tone spectroscopy which consists of exciting the SAM with monochromatic light at certain frequency until steady state is reached while simultaneously measuring the signal transmission at the readout resonator frequency.
-This measurement yields the average value of the joint measurement operator $\hat M$ in the steady-state.
 
@@
 		$\ket{12}$ and the fourth from  $\ket{10}$ to  $\ket{02}$, where $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively}
-	\label{fig:statinary_levels}
+	\label{fig:spectr}
 \end{figure}
-
- Let's described the anti-crossing highlighted in red in the picture.
-
- The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
-In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
- Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
 

### 2019-10-29 document.tex
Added stationary picture

--- 2019-10-27 document.tex
@@
 
-\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to find which spectral lines correspond to which transitions in the system.
+\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}).
 In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $\ket{ij/n}$ where $i,j$ denote the final transmon states after the transition from $\ket{00}$, and $/n$ is optional for an $n$-photon process.
@@
 As we will see, it is involved in forming features II and III.
-
 Notably, transitions $\ket{11/2}$ and $\ket{12/3}$ are forbidden when there is no interaction ($J=0$).
@@
 
-When two lines intersect, they may form an avoided crossing if the corresponding matrix element is non-zero in $\hat H_{int}$.
+When two lines intersect, they may form an avoided crossing if the corresponding matrix element of $\hat H_{int}$ is non-zero.
 In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states.
 For a two-transmon SAM, such points are, for instance, crossings between $\ket{01}$, $\ket{10}$ or $ \ket{11} $, $ \ket{02} $($ \ket{20} $).
-Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between $\ket{12},\ \ket{21}$ at the same $\Phi_e$ where $\ket{01}$, $\ket{10}$ cross.
+Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between $\ket{12},\ \ket{21}$ at the same $\Phi_e$ where $\ket{01}$, $\ket{10}$ intersect.
 
-\paragraph{Analysing features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other \textbf{(not shown, should we show?)}.
+\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other \textbf{(not shown, should we show?)}.
 Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
@@
 
-These observation lead to understanding that the effect is caused by the light-dressing.
-In case III, the first transmon is dressed by a strong resonant field, in case II the second one, and in case I both transmons are dressed at the same time.
-The exact origin of the triplet structure of the resulting
+These observation lead to understanding that the effect is caused by light dressing.
+In case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
+In the following section we will discuss this process in detail.
 
-\paragraph{Analysing }
+\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we conclude that
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{spectr}
-	\caption{Two-tone spectroscopy with transitions lines. In the red frame, four transitions intersect, three of which originate from the state $\ket{00}$ to $\ket{10}$, two-photon
-		$\ket{02}$, three-photon
-		$\ket{12}$ and the fourth from  $\ket{10}$ to  $\ket{02}$, where $\ket{ij}$ denote the $ij-th$ energy eigenstate of the transmon system, i,j represent first and second qubit respectively}
+	\includegraphics[width=\linewidth]{stationary}
+	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
+Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid.
+The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
 	\label{fig:statinary_levels}

### 2019-10-29 document.tex

--- 2019-10-27 document.tex
@@
 
+\section{Degenerate perturbation theory}
+\begin{equation}
+H^R=H_0+V_J
+\end{equation}
+At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
+\begin{equation}
+H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
+\end{equation}
+The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation.
+However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined.
+To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace.
+However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$.
+This means that the degeneracy is not lifted at first-order in perturbation theory.
+We have to pick eigenvectors which diagonalize following matrix:
+\begin{equation}
+	\begin{matrix}
+	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
+	\end{matrix}
+\end{equation}
+Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
+For example, in our case for one of degenerate subspaces:
+\begin{equation}
+	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
+\end{equation}
+The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
+The first-order correction to the states from degenerate subspace:
+\begin{equation}
+	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
+\end{equation}
+The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
+The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
+\begin{equation}
+	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
+\end{equation}
+
 \section{Theoretical description of two-photon process}
-Perturbation theory allows semianalytical calculation of the transition rates (Rabi oscillation frequencies) for single and multi-photon processes.
+Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.
 
@@
 A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
+
 \begin{equation}\label{forpsi}
-	\psi_i(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\psi_i(t_1)}
+	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
 \end{equation}
 
-The quantity of primary interest is not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state of interest.
+Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state.
 Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
@@
 \end{equation}
+The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude.
+So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
+The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
+\begin{equation}
+	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
+\end{equation}
+For simplifier the equation we have made use of the relation:
+\begin{equation}\nonumber
+	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
+\end{equation} 
+For $\omega_f=\omega_i+2\omega_d$.
+\begin{equation}\label{prob}
+\begin{split}
+	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
+\end{split}
+\end{equation}
 
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\linewidth]{drawing}
-	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
-	\label{fig:difdrive}
-\end{figure*}
-
- Let's described the anti-crossing highlighted in red in the picture.
-
  The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.

### 2019-10-31 document.tex
Results theory started

@@
 \begin{align}
-&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.
+&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
+&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
 \end{align}
@@
 \begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{stationary}
+	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
+Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid.
+The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
+	\label{fig:statinary_levels}
+\end{figure}
+
+\begin{figure}
 	\includegraphics[width=\linewidth]{zoom_picture}
@@
 
-\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the other \textbf{(not shown, should we show?)}.
+\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2.
 Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
 
-From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and usually invisible $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$.
+From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$.
+The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}.
 From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}.
 There is no dependence on the drive power of the second transmon, though.
-As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line.
+As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.
 
@@
 In case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
-In the following section we will discuss this process in detail.
+We will discuss these effects in greater detail in \autoref{sec:theory}.
 
-\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we conclude that
+\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1-5 as well.
+Feature2 is a small avoided crossing between $\ket{02/2}$ and $\ket{21/3}$.
+It is missing in the stationary solution and thus is a manifestation of dressing by light.
+Feature 2 is its twin: $\ket{12/3}$ and $\ket{20/2}$ intersect but the avoided crossing is smaller and is not resolved due to the asymmetry of the driving strengths.
+Feature 3 is a large avoided crossing between $\ket{12/3}$ and $\ket{21/3}$ predicted by the model.
+A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator.
+Feature 4 is explained by the stationary model and is a consequence of multiple spectral lines of a peculiar shape formed by a pair of avoided crossings passing through a single point (dotted lines in \autoref{fig:statinary_levels}).
+It appears at the point where $\ket{02/2}$ intersects $\ket{20/2}$ and is just barely visible in the experimental data due to the noise.
+Feature 5 is located at the intersection between $\ket{20/2}$ and normally invisible $\ket{10}\rightarrow \ket{02}$.
+It is hardly visible in the experimental data, too.
 
-Finally, we have found that when the coupling is turned off ($J=0$), the system does not demonstrate at all any of the Roman-numbered features highlighted in \autoref{fig:two-tone} (similarly, Arabic ones also disappear).
-This is expected due to the lines participating in them  means that these effects can only be attributed molecule as a whole and not the SAAs themselves.
+Finally, when the coupling is turned off ($J=0$) in modelling, the system does not demonstrate any of the described details.
+This means that all these effects can only be attributed to the SAM as a whole.
 
@@
 	\includegraphics[width=.9\linewidth]{main_scheme}
-	\caption{Explaining the origin of the AT satellites.
+	\caption{Explaining the origin of the AT satellites for feature III.
 \textbf{(a)} System level structure at 3.65 mA.
-At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha/2$ ($\omega_2 - \omega_1 = \alpha/2$), and thus $E_{02} - E_{10} = \hbar\omega_1$.
-Since $E_{12} - E_{02} = \omega_1$ as well, both $00\rightarrow 10$, two-photon $00 \rightarrow 02/2$ and three-photon $00\rightarrow 12/3$ transitions can occur around the same frequency of $\omega_1$.
-During the two-tone spectroscopy, the first transmon is driven by a strong signal of amplitude $\Omega_1$ (possibly, at a small detuning $\Delta_1$ from $\omega_1$ shown in green).
+At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$.
+The first transmon is driven by a strong signal of amplitude $\Omega_1$ at a small detuning $\Delta_1$ from $\omega_1$ shown in green.
 The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles.
 \textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$).
-However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$ (the first transmon becomes light-dressed).
-\textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by the corresponding drive operator are shown as blue ellipses).
-In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted.
-The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$.
+However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = (\Omega_1^2 + \Delta_1^2)^{\frac{1}{2}}$ (the first transmon becomes light-dressed).
+\textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{dr}^2$ are shown with blue ellipses).
+In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
 However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
-When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites become visible.
-Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be two $\Omega_1^R$.}
+When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2$ and the satellites become visible.
+Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.}
 	\label{fig:main_scheme}
@@
 
-\subsection{Theoretical description of the observed spectral lines}
-For the three-level system, the A-T effect is described in Appendix \ref{sec:3-level-at}.
-Let's consider our system (\autoref{Hsystem}) in rotating frame.
-Moving to this frame is achieved by the rotation:
+\subsection{Explaining extra avoided crossings}\label{sec:theory}
+
+Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to play a part.
+For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
+However, in our case the situation is more complicated.
+We will first explain the feature III.
+Feature II is explained in the exactly same way.
+Feature I is of the same origin but is not discussed here in such detail.
+
+First of all, during the spectroscopy we apply only a single microwave tone, and thus is has to be simultaneously the coupler tone and the probe tone to observe the A-T effect.
+This configuration is possible due to the resonance condition between the transmons at III: the light is resonant with $\ket{10}$ and detuned from $\ket{01}$; however, it is instead resonant with a two-photon transition $\ket{02/2}$ (the resonance condition is $\omega_1 = \omega_2+\alpha_2/2$).
+Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure.
+In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime).
+Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.
+
+In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III.
+\autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM.
+Orange (blue) levels correspond to first (second) qubit excited, the other being in the ground state.
+Orange ellipses denote the driving (detuned by $\Delta_1$ from $\omega_1$) of the first transmon.
+Note that it acts upon every pair of states $\ket{0j},\,\ket{1j},\ j=0..2$.
+The off-resonant two-photon drive on the second qubit is not shown here.
+Since from numerical simulation we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line.
+From here, we consider the first transmon to be a two-level qubit: $\ket{22}$ is not shown, $\hat H_{int}$ in RWA couples only $\ket{01},\,\ket{10}$ and $\ket{11},\,\ket{12}$.
+
+The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)).
+Just as in Appendix \ref{sec:3-level-at}, after rediagonalization it may be regarded as dressed by light, and the whole level system rearranges.
+Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are $\ket{a}$ and $\ket{b}$.
+The second transmon energies stay the same, and thus in overall we obtain just three doublets.
+
+Mathematically, this procedure looks as follows.
+In the calculation below, we will use the following rotation operator (different from \eqref{eq:R}) to move to the rotating frame with \eqref{eq:rotation}:
 \begin{equation}
-R = \exp(-i\omega_d t (b^{\dagger}b+c^{\dagger}c))
-\end{equation}  
-After this transformation the effective Hamiltonian can be found from equation:
-\begin{equation}
-H_{system}^R = R^{\dagger}H_{system}R-iR^{\dagger}\dot{R}
+R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
 \end{equation}
 
-From the simulation follows that a two-level approximation for first qubit and three-level approximation for second is sufficient to observe the effect we are interested in.
-The Hamiltonian in matrix form is given by the following expression:
+Note that for brevity reasons we rotate both transmon subspaces simultaneously (in contrast to what is shown in \autoref{fig:main_scheme}).
+Moreover, we consider a general case when $\omega_d^1 - \omega_d^2 = \delta \neq 0 $ and $\Delta_{1,2} = \omega_d^1-\omega_{1,2}$ and $\omega_1 - \omega_2$ not necessary equals $\alpha_2/2$.
+The resulting Hamiltonian with RWA:
 
@@
 		&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
-	\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 & 0 \\
-	\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 & 0 \\
-	\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & J & -\text{$\Delta_2 $} &
-	\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}$} t}/2 & 0 \\
-	\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2$} &
-	\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta_{\omega}
+		\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta$} t}/2 & 0 & 0 & 0 \\
+		\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 & 0 \\
+		\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & J & -\text{$\Delta_2 $} &
+		\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 \\
+		\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2$} &
+		\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta
 				$} t}/2 \\
-	\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega}$} t}/2 & \sqrt{2} J &
+		\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & \sqrt{2} J &
 		\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
-	\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta_{\omega} $} t}/2 & \text{$\Omega_1/2
+		\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2
 			$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
@@
 \end{widetext}
-Where $\Omega_1$, $\Omega_2$ - amplitudes of the drives, $\Delta_1 = \omega_d-\omega_{1}=0$,$\Delta_2 = \omega_d-\omega_{2}$, $\delta_{\omega} = \omega_{dr1}-\omega_{dr2}$.
+Here , $\delta = \omega_{dr}^1 - \omega_{dr}^2$.
+
+Finally, in \autoref{fig:main_scheme}
+
 Let's consider the Hamiltonian (\autoref{matrix}) in details.
@@
 \paragraph{Classical derivation.} In the classical case, the mathematical description goes as follows.
-At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$.
-Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_2$ between $\ket{1}$ and $\ket{2}$.
+At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$ (the \textit{coupler} tone).
+Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_2$ between $\ket{1}$ and $\ket{2}$ (the \textit{probe} tone).
 This step is illustrated in \autoref{fig:at-standard}~(a).
@@
 \end{equation}
-\begin{figure}[h]
+
+\begin{figure}
 	\centering
-	\includegraphics[width=\linewidth]{stationary}
-	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
-Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid.
-The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
-	\label{fig:statinary_levels}
+	\includegraphics[width=\linewidth]{drawing}
+	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
+	\label{fig:difdrive}
 \end{figure}

### 2019-10-31 Pictures/Plotting/StationaryPlot.py

@@ -1,7 +1,7 @@
 import pickle
 from numpy import *
 import matplotlib
-from matplotlib import ticker, colorbar as clb
+from matplotlib import ticker, colorbar as clb, patches
 
 matplotlib.use('Qt5Agg')
 
@@ -20,6 +20,43 @@ class StationaryPlot:
 
         mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
                            cmap="Spectral_r")
+
+        for ax in axes:
+            rect1 = patches.Rectangle((3.5, 5.25), .3, .04,
+                                      linewidth=1, edgecolor='black',
+                                      facecolor='none', linestyle=":")
+            ax.add_patch(rect1)
+            rect2 = patches.Rectangle((2.925, 5.2275),
+                                      3.225-2.925,
+                                      5.2675-5.2275,
+                                      linewidth=1, edgecolor='black',
+                                      facecolor='none', linestyle=":")
+            ax.add_patch(rect2)
+            rect3 = patches.Rectangle((3.16, 5.3), .3, .04,
+                                      linewidth=1, edgecolor='black',
+                                      facecolor='none', linestyle=":")
+            ax.add_patch(rect3)
+            ax.annotate("1", xy=(3.48, 5.23), xytext=(3.575, 5.205), ha="center", fontsize=10,
+                        arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                        shrink=0.05))
+
+            ax.annotate('2', xy=(5.08, 5.21), xytext=(5.08, 5.18), ha="center", fontsize=10,
+                        arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                        shrink=0.05))
+
+            ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.26), ha="center", fontsize=10,
+                        arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                        shrink=0.05))
+
+            ax.annotate('4', xy=(4.9, 5.195), xytext=(4.75, 5.195), ha="center", va="top", fontsize=10,
+                        arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
+                                        shrink=0.05))
+
[…]

### 2019-11-03 document.tex
Results 1st pass done

@@
 \end{align}
-After the transformation and application of RWA:
+After the transformation and application of the RWA:
 \begin{equation}
 \begin{aligned}
-	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_d^{(1,2)}-\omega_{(1,2)},\\
-	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
-	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\\ 
-	\hat H_{dr}^2 &\rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
+	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
+	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
+	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
 \end{aligned}
@@
 While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects.
-Taking into account more energy levels of each transmon does not help, and is not even necessary to reproduce this effect, as we will show in the following.
+Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.
 
@@
 \paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2.
-Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b) where the spectral lines are identified with the corresponding transitions.
+Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).
 
@@
 From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}.
-There is no dependence on the drive power of the second transmon, though.
+There is no dependence on the drive power on the second transmon, though.
 As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.
@@
 These observation lead to understanding that the effect is caused by light dressing.
-In case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
+In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
 We will discuss these effects in greater detail in \autoref{sec:theory}.
@@
 In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
-However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
-When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2$ and the satellites become visible.
-Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.}
+In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
 	\label{fig:main_scheme}
@@
 
-Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to play a part.
+Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to cause them.
 For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
@@
 We will first explain the feature III.
-Feature II is explained in the exactly same way.
-Feature I is of the same origin but is not discussed here in such detail.
 
-First of all, during the spectroscopy we apply only a single microwave tone, and thus is has to be simultaneously the coupler tone and the probe tone to observe the A-T effect.
-This configuration is possible due to the resonance condition between the transmons at III: the light is resonant with $\ket{10}$ and detuned from $\ket{01}$; however, it is instead resonant with a two-photon transition $\ket{02/2}$ (the resonance condition is $\omega_1 = \omega_2+\alpha_2/2$).
+First of all, since during the spectroscopy we apply only a single microwave tone, it has to be simultaneously the coupler tone and the probe tone to observe the A-T effect.
+This is possible due to the resonance condition $\omega_1 = \omega_2+\alpha_2/2$ at III which means that we can simultaneously excite transitions $\ket{10}$ and $\ket{02/2}$.
 Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure.
+In contrast, the single-photon excitation is enough to dress the system.
 In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime).
@@
 \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM.
-Orange (blue) levels correspond to first (second) qubit excited, the other being in the ground state.
-Orange ellipses denote the driving (detuned by $\Delta_1$ from $\omega_1$) of the first transmon.
-Note that it acts upon every pair of states $\ket{0j},\,\ket{1j},\ j=0..2$.
-The off-resonant two-photon drive on the second qubit is not shown here.
-Since from numerical simulation we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line.
-From here, we consider the first transmon to be a two-level qubit: $\ket{22}$ is not shown, $\hat H_{int}$ in RWA couples only $\ket{01},\,\ket{10}$ and $\ket{11},\,\ket{12}$.
+Since from numerical simulations we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line, and hereinafter we consider the first transmon as a two-level system.
 
-The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)).
-Just as in Appendix \ref{sec:3-level-at}, after rediagonalization it may be regarded as dressed by light, and the whole level system rearranges.
-Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are $\ket{a}$ and $\ket{b}$.
-The second transmon energies stay the same, and thus in overall we obtain just three doublets.
+The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}.
+Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$.
+At the same time, the second transmon energies stay the same.
 
-Mathematically, this procedure looks as follows.
-In the calculation below, we will use the following rotation operator (different from \eqref{eq:R}) to move to the rotating frame with \eqref{eq:rotation}:
+Finally, in \autoref{fig:main_scheme}~(c) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{dr}^2$.
+In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$.
+The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states.
+From here it becomes obvious that without the transmon-transmon interaction the sideband transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$.
+However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.
+Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.
+
+Now, we will repeat this reasoning in a quantitative mathematical model.
+We start from the initial Hamiltonian \eqref{Hsystem}.
+To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
 \begin{equation}
@@
 \end{equation}  
+Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
+\begin{equation}
+\begin{aligned}
+\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
+\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
+\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
+\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
+\end{aligned}
+\end{equation}
+where $\delta = \omega_{dr}^2 - \omega_{dr}^1$.
 
-Note that for brevity reasons we rotate both transmon subspaces simultaneously (in contrast to what is shown in \autoref{fig:main_scheme}).
-Moreover, we consider a general case when $\omega_d^1 - \omega_d^2 = \delta \neq 0 $ and $\Delta_{1,2} = \omega_d^1-\omega_{1,2}$ and $\omega_1 - \omega_2$ not necessary equals $\alpha_2/2$.
-The resulting Hamiltonian with RWA:
+Since $\hat H_{dr}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
+After that, the Hamiltonian may be split into three parts:
+\begin{equation}
+\begin{aligned}
+\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
+\hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
+\hat V_t &= \hat S^\dag \hat H_{dr}^{2} \hat S \equiv \hat H_{dr}^{2}.
+\end{aligned}
+\end{equation}
+The first part is diagonal, and the remaining two will be treated as perturbations.
+To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2= - \alpha/2$.
+In these conditions, $H^D$ becomes degenerate as can be seen below in \eqref{eq:ham_matrix}:
 
@@
 \begin{widetext}
-	\begin{equation}\label{matrix} 
-	\text{$H^R$} = \kbordermatrix{
-		&\ket{00} & \ket{10} & \ket{01} & \ket{11} & \ket{02} & \ket{12} \\
-		\ket{00}& 0 & \text{$\Omega_1/2 $} & \text{$\Omega _2$} e^{i \text{$\delta$} t}/2 & 0 & 0 & 0 \\
-		\ket{10} & \text{$\Omega_1/2 $} & \text{$-\Delta_1 $} & J & \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 & 0 \\
-		\ket{01} & \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & J & -\text{$\Delta_2 $} &
-		\text{$\Omega_1$/2} & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta$} t}/2 & 0 \\
-		\ket{11} & 0 & \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2$} &
-		\text{$-\Delta_2 -\Delta_1$} & \sqrt{2} J & \sqrt{2} \text{$\Omega_2$} e^{i \text{$\delta
-				$} t}/2 \\
-		\ket{02} & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta$} t}/2 & \sqrt{2} J &
-		\text{$\alpha$}-2 \text{$\Delta_2$} & \text{$\Omega_1/2$} \\
-		\ket{12} & 0 & 0 & 0 & \sqrt{2} \text{$\Omega_2$} e^{-i \text{$\delta $} t}/2 & \text{$\Omega_1/2
-			$} & \text{$\alpha$}-2 \text{$\Delta_2$}- \text{$\Delta_1$} \\
+	\begin{equation}
+	\hat H^D + \hat V_J + \hat V_t  = \kbordermatrix{
+		&\ket{a,0} & \ket{b,0} & \ket{a,1} & \ket{b,1} & \ket{a,2} & \ket{b,2} \\
+		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & \frac{\Omega_{2}e^{i \text{$\delta$} t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 \\
+		\ket{b,0} & 0 & \frac{\Omega_1}{2} & -\frac{J}{2} & \frac{\Omega_2 e^{i \delta t}}{2} + \frac{J}{2} & 0 & 0 \\
+		\ket{a,1} &\frac{\Omega_2 e^{-i \text{$\delta$} t} }{2}  - \frac{J}{2} & -\frac{J}{2} & - \frac{\alpha}{2} - \frac{\Omega_1}{2}&
+		0 & \frac{\text{$\Omega_2$} e^{i \text{$\delta$} t}}{\sqrt{2}} -\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
+		\ket{b,1} & \frac{J}{2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{2} +\frac{J}{2} & 0 & - \frac{\alpha}{2} + \frac{\Omega_1}{2} & -\frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{i \text{$\delta
+					$} t}}{\sqrt 2} + \frac{J}{\sqrt 2} \\
+		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i \delta t}}{2} - \frac{J}{\sqrt 2} & -\frac{J}{\sqrt 2} &
+		-\frac{\Omega_{1}}{2} & 0 \\
+		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{\sqrt 2} + \frac{J}{\sqrt 2} & 0 & \frac{\Omega_{1}}{2}\\
 	}
+	\label{eq:ham_matrix}
 	\end{equation}
 \end{widetext}
-Here , $\delta = \omega_{dr}^1 - \omega_{dr}^2$.
 
-Finally, in \autoref{fig:main_scheme}
+Using the degenerate perturbation theory with $\hat V_J$ summarized in Appendix \ref{sec:dpt}, we have found the first-order corrected wave functions of $\hat H^D$, labelled $\ket{k},\ k=1..6$.
 
-Let's consider the Hamiltonian (\autoref{matrix}) in details.
-Divide it into three parts: time-dependent $(V_t)$, the part responsible for the interaction between the qubits $(V_J)$ and all the rest $(H_0)$.
-\begin{equation}
-	H^R=H_0+V_J+V_t
-\end{equation}
-The $\Omega_1\gg \Omega_2,\Delta_2> J$, so the driven field on the first qubit is strong and form the dressed states defined by the Hamiltonian $H_0$, which is stationary, so the levels can be found and schematically depicted in \autoref{fig:main_scheme}~(b).
-The drive on the second qubit is weak with very low intensity, so we can neglect any perturbation introduced by second drive on the position, width of the dressed states.
-At our working point the condition $\Delta_2=\alpha/2$ is met and $H_0$ becomes degenerate.
-
-According to the degenerate perturbation theory (with perturbation $V_J$) we found the first-order corrections to the wave functions.
-Calculating the probability of two-photon transition per unit interaction time using the \autoref{prob} for corrected  wave functions and neglecting small terms we obtain:
+The theory for two-photon processes is given in Appendix \ref{sec:2pp}.
+The probability rate of two-photon transition per unit interaction time using corrected eigenstates $\ket{k}$ and neglecting small terms we obtain:
 \begin{equation}
@@
 
-So, in the system of non-interacting qubits $(J=0)$ some transitions are prohibited and the splitting we are interested in is not observed.
-Therefore a non-zero interaction between qubits is necessary to observe AT effect in our system.
+From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.
 
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{intro_scheme}
+	\includegraphics[width=.9\linewidth]{intro_scheme}
 	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here).
@@
 
-\section{Degenerate perturbation theory}
+\section{Degenerate perturbation theory} \label{sec:dpt}
 \begin{equation}
@@
 
-\section{Theoretical description of two-photon process}
+\section{Theoretical description of two-photon process}\label{sec:2pp}
 Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.

### 2019-11-03 document.tex
Proofread a bit

@@
 Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects.
-The Appendix contains important details of the theoretical framework that we use to model the observed processes.
+The Appendix contains important details of the theoretical framework that we use.
 
@@
 \subsection{Device design and fabrication}
-We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which serves both to couple\cite{majer2007coupling} the qubits and for the joint\cite{chow2010detecting} readout of their states.
-In \autoref{fig:experiment}~(a) the optical photograph of the device is shown depicting the layout of the components.
+We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the qubits and allows the joint\cite{chow2010detecting} readout of their states.
+In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components.
 The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed.
 In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler.
-Flux lines that allow independent control of the $ge$ transitions of the transmons are coming from the sides.
+Flux lines that allow independent control of the transmon frequencies are coming from the sides.
 Finally, the excitation waveguide coming from below directs microwave signal towards the SAM.
@@
 The capacitively coupled excitation line is also shown in green.
-Finally, in \autoref{fig:experiment}~(c) we show schematically the $ge$ transitions of the transmons depending on the external magnetic flux.
+Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux.
 Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
 Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
-This is convenient as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency.
+This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency.
 Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
@@
 where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
-Additionally, by applying external magnetic flux $\Phi_e$ it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
+Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
 In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

### 2019-11-09 document.tex
Transition probabilities
Added experimental zoom

@@
 
+\begin{figure*}
+	\includegraphics[width=.49\linewidth]{powerscan}
+	\includegraphics[width=.49\linewidth]{zoom2_picture}
+	\caption{Investigation of the power dependence of feature II.
+\textbf{(a)} Experiment (second cooldown, the parameters are different).
+The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed.
+\textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4, 8, 15 and 30; other parameters as in \autoref{fig:two-tone}.
+Note that now colours show the population of the ground state ($\ket{00}$).
+The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
+	\label{fig:zoom}
+\end{figure*}
+
 Experiment was conducted as described in Appendix \ref{sec:meas_setup}.
@@
 
-\subsection{Analysis of the spectra}
-
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\label{fig:statinary_levels}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
-	\includegraphics[width=\linewidth]{zoom_picture}
-	\caption{Zoomed-in simulation of feature III with increasing amplitude of the driving of the first transmon $\Omega_1/2\pi=$2, 4, 10 and 20 MHz while the second drive is fixed at $\Omega_2/2\pi=$10 MHz; other parameters as in \autoref{fig:two-tone}.
-Note that now colours show the population of the ground state ($\ket{00}$).
-The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.
-Interestingly, population inversion is observed inside the red-coloured areas of the graph: $\ket{00}$ population is less than 20\% there.}
-	\label{fig:zoom}
-\end{figure}
+\subsection{Analysis of the spectra}
 

### 2019-11-09 Pictures/Plotting/Powerscan.py

@@ -12,15 +12,22 @@ from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
 class ZoomPlot:
 
     def __init__(self):
-        with open('zoom2.pkl', 'rb') as f:
-            self._X, self._Y, self._plots = pickle.load(f)
+
+        self._load_data()
 
         fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(5, 5))
         plt.subplots_adjust(wspace=.2, hspace=.2)
 
         for idx, ax in enumerate(axes.ravel()):
-            m = ax.pcolormesh(self._X, self._Y, real(array(self._plots[idx]).T),
-                              vmax=1, vmin=0, rasterized=True, cmap="Spectral")
+
+            X, Y, data = self._data[idx]["Current [A]"]*1e4,\
+                         self._data[idx]["Frequency [Hz]"]/1e9, \
+                         real(self._data[idx]["data"]*exp(1j*pi/2)).T*1e3
+
+            if idx in [0]:
+                data = data - median(data, axis=0)
+
+            m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 2 == 0:
                 ax.set_ylabel('Frequency [GHz]');
             if idx > 1:
@@ -31,31 +38,42 @@ class ZoomPlot:
         plt.text(.8, .9, r"$\left|01\right\rangle$", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='center', color="black")
 
-
-        plt.text(.25, .025, r"$\Omega_{1,2}/2\pi =$8 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.375, .025, r"$P_{exc} =$-20 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='left', color="black")
 
 
-        plt.text(.66, .025, r"15 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.66, .025, r"-12 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,1].transAxes, ha='left', color="black")
 
-        plt.text(.6, .025, r"30 MHz", fontdict={"name": "STIX"}, fontsize=12,
[…]

### 2019-11-09 Pictures/Plotting/StationaryPlot.py

@@ -15,8 +15,8 @@ class StationaryPlot:
         with open("stationary.pkl", "rb") as f:
             currs, freqs, population10, energies = pickle.load(f)
 
-        fig, axes = plt.subplots(2, 1, figsize=(4, 7), sharex=True)
-        plt.subplots_adjust(wspace=.2, hspace=.1)
+        fig, axes = plt.subplots(1, 2, figsize=(8, 3), sharey=True)
+        plt.subplots_adjust(wspace=.1, )
 
         mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
                            cmap="Spectral_r")
@@ -137,14 +137,15 @@ class StationaryPlot:
 
         plt.ylim(5.1, 5.5)
         plt.xlim(2,6)
-        plt.xlabel("Current [$10^{-4}$ A]")
+        axes[0].set_ylabel("Frequency [GHz]")
+
         for ax in axes:
-            ax.set_ylabel("Frequency [GHz]")
+            ax.set_xlabel("Current [$10^{-4}$ A]")
         plt.legend(ncol=3, fontsize=5)
 
-        cbaxes1 = fig.add_axes([0.125, .925, 0.65, .01])
-        cb = plt.colorbar(mappable, ax=axes[0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$\lg P_{\left|10\right\rangle}$", position=(1.125, -2))
+        cbaxes1 = fig.add_axes([.925, 0.11, 0.01, .7])
+        cb = plt.colorbar(mappable, ax=axes[0], cax=cbaxes1, orientation="vertical")
+        cb.ax.set_title(r"$\lg\, P_{\left|10\right\rangle}$", position=(3, 1))
         # print([val.get_text() for val in cb.ax.get_xticklabels()])
         # cbaxes1.set_xticklabels(["$10^{%s}$"%val.get_text() for val in  cb.ax.get_xticklabels()])
         plt.savefig("../stationary.pdf", bbox_inches="tight", dpi=600)

### 2019-11-16 Pictures/Plotting/MainPicturePlot.py
Plot updates

@@ -26,7 +26,7 @@ class MainPicturePlot:
     def plot(self):
         self._load_data()
 
-        fig, axes = plt.subplots(nrows=1, ncols=2, figsize=(12, 5), sharey=True)
+        fig, axes = plt.subplots(nrows=1, ncols=2, figsize=(10, 4), sharey=True)
         plt.subplots_adjust(wspace=.1)
 
         ax1, ax2 = axes
@@ -131,25 +131,25 @@ class MainPicturePlot:
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        plt.text(.53, .82, r"$\left|01\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
+        plt.text(.67, .77, "01", fontsize=10,
+                 transform=ax.transAxes, ha='center', rotation=-45)
+
+        plt.text(.8, .77, "10", fontsize=10,
+                 transform=ax.transAxes, ha='center', rotation=55)
+
+        plt.text(.42, .6, "11/2", fontsize=10,
+                 transform=ax.transAxes, ha='center', rotation=10)
+
+        plt.text(.475, .525, "02/2", fontsize=10,
+                 transform=ax.transAxes, ha='center', rotation=20)
+
+        plt.text(.53, .465, "12/3", fontsize=10,
                  transform=ax.transAxes, ha='center')
 
-        plt.text(.53, .35, r"$\left|10\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
+        plt.text(.53, .07, "20/2", fontsize=10,
                  transform=ax.transAxes, ha='center')
 
-        plt.text(.53, .6, r"$\left|11/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
-                 transform=ax.transAxes, ha='center')
-
-        plt.text(.53, .525, r"$\left|02/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
-                 transform=ax.transAxes, ha='center')
-
-        plt.text(.53, .465, r"$\left|12/3\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
-                 transform=ax.transAxes, ha='center')
-
-        plt.text(.53, .07, r"$\left|20/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=6,
[…]

### 2019-11-16 Pictures/Plotting/Powerscan.py

@@ -7,7 +7,7 @@ matplotlib.use('Qt5Agg')
 
 from matplotlib import pyplot as plt
 from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
-
+from matplotlib.pyplot import MultipleLocator
 
 class ZoomPlot:
 
@@ -15,10 +15,11 @@ class ZoomPlot:
 
         self._load_data()
 
+
         fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(5, 5))
         plt.subplots_adjust(wspace=.2, hspace=.2)
 
-        for idx, ax in enumerate(axes.ravel()):
+        for idx, ax in enumerate(axes.ravel()[:]):
 
             X, Y, data = self._data[idx]["Current [A]"]*1e4,\
                          self._data[idx]["Frequency [Hz]"]/1e9, \
@@ -30,13 +31,25 @@ class ZoomPlot:
             m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 2 == 0:
                 ax.set_ylabel('Frequency [GHz]');
+                ax.yaxis.set_major_locator(MultipleLocator(0.01))
             if idx > 1:
                 ax.set_xlabel('Current [$10^{-4}$ A]');
 
-        plt.text(.15, .8, r"$\left|20/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=12,
-                 transform=axes[0,0].transAxes, ha='center', color="black")
-        plt.text(.8, .9, r"$\left|01\right\rangle$", fontdict={"name": "STIX"}, fontsize=12,
-                 transform=axes[0,0].transAxes, ha='center', color="black")
+        self._Omega_2s = array([6e-3, 15e-3, 30e-3, 60e-3])*0.75
+        self._plot_theory(axes)
+        print(self._Omega_2s)
+
+        plt.text(.28, .9, r"$20/2$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0,0].transAxes, ha='center', color="black", rotation=-70)
+
+        plt.text(.52, .9, r"$01-20$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0,0].transAxes, ha='center', color="black", rotation=-85)
+
[…]

### 2019-11-16 Pictures/Plotting/StationaryPlot.py

@@ -15,7 +15,7 @@ class StationaryPlot:
         with open("stationary.pkl", "rb") as f:
             currs, freqs, population10, energies = pickle.load(f)
 
-        fig, axes = plt.subplots(1, 2, figsize=(8, 3), sharey=True)
+        fig, axes = plt.subplots(1, 2, figsize=(10, 3.33), sharey=True)
         plt.subplots_adjust(wspace=.1, )
 
         mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
@@ -40,7 +40,7 @@ class StationaryPlot:
                         arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                         shrink=0.05))
 
-            ax.annotate('2', xy=(5.08, 5.21), xytext=(5.08, 5.18), ha="center", fontsize=10,
+            ax.annotate('2', xy=(5.080001, 5.21), xytext=(5.08, 5.18), ha="center", fontsize=10,
                         arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                         shrink=0.05))
 
@@ -141,7 +141,7 @@ class StationaryPlot:
 
         for ax in axes:
             ax.set_xlabel("Current [$10^{-4}$ A]")
-        plt.legend(ncol=3, fontsize=5)
+        plt.legend(ncol=3, fontsize=7)
 
         cbaxes1 = fig.add_axes([.925, 0.11, 0.01, .7])
         cb = plt.colorbar(mappable, ax=axes[0], cax=cbaxes1, orientation="vertical")

### 2019-11-16 Pictures/Plotting/ZoomPlot.py

@@ -26,23 +26,33 @@ class ZoomPlot:
             if idx > 1:
                 ax.set_xlabel('Current [$10^{-4}$ A]');
 
-        plt.text(.15, .8, r"$\left|20/2\right\rangle$", fontdict={"name": "STIX"}, fontsize=12,
-                 transform=axes[0,0].transAxes, ha='center', color="black")
-        plt.text(.8, .9, r"$\left|01\right\rangle$", fontdict={"name": "STIX"}, fontsize=12,
-                 transform=axes[0,0].transAxes, ha='center', color="black")
 
+        self._Omega_2s = array([6e-3, 15e-3, 30e-3, 60e-3])*0.75
+        self._plot_theory(axes)
 
-        plt.text(.25, .025, r"$\Omega_{1,2}/2\pi =$8 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.28, .9, r"$20/2$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0, 0].transAxes, ha='center', color="black", rotation=-70)
+
+        plt.text(.52, .9, r"$01-20$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0, 0].transAxes, ha='center', color="black", rotation=-85)
+
+        plt.text(.85, .32, r"$21/3$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0, 0].transAxes, ha='center', color="black", rotation=-27.5)
+
+        plt.text(.7, .9, r"$01$", fontdict={"name": "STIX"}, fontsize=12,
+                 transform=axes[0, 0].transAxes, ha='center', color="black", rotation=70)
+
+        plt.text(.15, .025, r"$\Omega_{1,2} / 2\pi  = $4.5 MHz ", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='left', color="black")
 
 
-        plt.text(.66, .025, r"15 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.57, .025, r"11.25 MHz", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,1].transAxes, ha='left', color="black")
 
-        plt.text(.6, .025, r"30 MHz", fontdict={"name": "STIX"}, fontsize=12,
[…]

### 2019-11-16 Pictures/Plotting/TopologicalSplitting.py
Added 01-10-11 splitting plot

@@ -1,0 +1,87 @@
+import pickle
+from numpy import *
+import matplotlib
+from matplotlib import ticker, colorbar as clb
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+from matplotlib.pyplot import MultipleLocator
+
+
+class TopologicalSplitting:
+
+    def __init__(self):
+        with open('10-01-11.pkl', 'rb') as f:
+            self._X, self._Y, self._plots = pickle.load(f)
+        with open("transitions.pkl", "rb") as f:
+            self._currs, self._transitions_1, self._transitions_2 = pickle.load(f)
+
+        Omegas = array([(15, 7.5),
+                        (30, 7.5),
+                        (45, 7.5),
+                        (7.5, 15),
+                        (7.5, 30),
+                        (7.5, 45)])
+
+        fig, axes = plt.subplots(3, 2, sharex=True, sharey=True, figsize=(5, 5))
+        plt.subplots_adjust(wspace=.1, hspace=.2)
+
+        for idx, ax in enumerate(axes.T.ravel()):
+            m = ax.pcolormesh(self._X, self._Y, array(self._plots[idx]).T,
+                              vmin=0, vmax=1, cmap="Spectral", rasterized=True)
+            if idx in [2, 5]:
+                ax.set_xlabel("Current [$10^{-4}$ A]")
+            if idx < 3:
+                ax.set_ylabel("$\omega_d^{1,2}/2\pi$ [GHz]")
+
+            if idx in [0]:
+                plt.text(.5, .7, "$\Omega_1: {0}$ MHz\n$\Omega_2: {1}$ MHz".format(Omegas[idx][0],
+                                                                                     Omegas[idx][
+                                                                                         1]),
+                         fontsize=10,
+                         transform=ax.transAxes, ha='center', color="black")
+            else:
+                plt.text(.5, .7, "${0}$ MHz\n${1}$ MHz".format(Omegas[idx][0],
+                                                                                     Omegas[idx][
+                                                                                         1]),
+                         fontsize=10,
+                         transform=ax.transAxes, ha='center', color="black")
+
[…]

### 2019-11-16 Pictures/Plotting/ZoomPlot_for_1D.py
Added zoom plot+.pdfs

@@ -1,0 +1,122 @@
+import pickle
+from numpy import *
+import matplotlib
+from matplotlib import ticker, colorbar as clb
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+from matplotlib.pyplot import MultipleLocator
+
+class Powerscan1D:
+
+    def __init__(self):
+
+        self._load_data()
+
+
+        fig, axes = plt.subplots(4, 3, sharex=False, sharey=False, figsize=(8, 6))
+        plt.subplots_adjust(wspace=.3, hspace=.3)
+
+        for idx, ax in enumerate(axes.ravel()[:-1]):
+
+            X, Y, data = self._data[idx]["Current [A]"]*1e4,\
+                         self._data[idx]["Frequency [Hz]"]/1e9, \
+                         real(self._data[idx]["data"]*exp(1j*pi/2)).T*1e3
+
+            # if idx in [0]:
+            #     data = data - median(data, axis=0)
+
+            m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
+            if idx % 3 == 0:
+                ax.set_ylabel('Frequency [GHz]');
+                ax.yaxis.set_major_locator(MultipleLocator(0.01))
+                ax.set_xlabel("")
+                ax.set_xticklabels([])
+            if idx > 8:
+                ax.set_xlabel('Current [$10^{-4}$ A]');
+
+        self._Omega_2s = array([6e-3, 7.55e-3, 9.5e-3, 11.9e-3, 15e-3, 19e-3,
+                                23e-3, 30e-3, 37.8e-3, 47.65e-3, 60e-3])*0.75
+        self._plot_theory(axes)
+        print(self._Omega_2s)
+
+
+
+        cbaxes1 = fig.add_axes([0.125,.95,0.5,.015])
+        # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
+        #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
+        cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
[…]

### 2019-11-16 document.tex
Updates

@@
 
-	\author{K. Shiyanov}
+	\author{K. Shiianov}
 
@@
 \begin{figure*}
-	\includegraphics[width=.49\linewidth]{powerscan}
-	\includegraphics[width=.49\linewidth]{zoom2_picture}
-	\caption{Investigation of the power dependence of feature II.
-\textbf{(a)} Experiment (second cooldown, the parameters are different).
-The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed.
-\textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4, 8, 15 and 30; other parameters as in \autoref{fig:two-tone}.
-Note that now colours show the population of the ground state ($\ket{00}$).
-The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
-	\label{fig:zoom}
+	\centering
+	\includegraphics[width=\linewidth]{stationary}
+	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
+Left picture is same as the right one but with transitions from the stationary Hamiltonian overlaid.
+The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
+	\label{fig:statinary_levels}
 \end{figure*}
@@
 Experiment was conducted as described in Appendix \ref{sec:meas_setup}.
-We have used high-power two-tone spectroscopy (qubit Rabi frequencies $\Omega_1$ and $\Omega_2$ were around 20 MHz) to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a).
+We have used high-power two-tone spectroscopy to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a).
 As one can see, several spectral lines are visible besides the $ge$ ones shown in \autoref{fig:experiment}~(c).
 Their frequency depends on the applied current, and at multiple points they become resonant with each other.
-At three pairs of these resonant points, we observe three distinct features shown in insets marked with Roman numerals.
+At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numerals.
 Some secondary details are shown with Arabic-numbered markers.
@@
 Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
-We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels} in Appendix.
-While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}, it completely misses the Roman-numbered effects.
+We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels}.
+While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects.
 Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.
 
-To check whether the described features are present in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady state of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcome $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$.
-Strikingly, all the experimental features are immediately reproduced using this approach with just 9 SAM states.
+To check whether the described features are present in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady states of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcomes $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$ depending on the excitation frequency and magnetic flux.
+Strikingly, all the experimental features are immediately reproduced using this approach with just 9 SAM states as shown in \autoref{fig:two-tone}~(b).
 We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the results; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
@@
 \begin{figure*}
-	\centering
-	\includegraphics[width=\linewidth]{stationary}
-	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
-Bottom picture is same as the top one but with transitions from the stationary Hamiltonian overlaid.
-The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
-	\label{fig:statinary_levels}
+	\includegraphics[width=.49\linewidth]{powerscan}
+	\includegraphics[width=.49\linewidth]{zoom2_picture}
+	\caption{Investigation of the power dependence of feature II.
+Dashed are the model curves turning to dotted when the model is no longer expected to be valid (see Section \ref{sec:theory}).
+Model values for $\Omega_2$ are the same for both panels and shown as annotations in (b).
+\textbf{(a)} Experiment (second cooldown; the parameters are different from \autoref{fig:experiment}).
+The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed.
+\textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4.5, 11.25, 22.5 and 45 MHz; other parameters as in \autoref{fig:two-tone}.
+Note that now colours show the population of the ground state ($\ket{00}$).
+The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
+	\label{fig:zoom}
 \end{figure*}
@@
 The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}.
-From additional simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}.
-There is no dependence on the drive power on the second transmon, though.
-As one can see, the growth of the splitting with increasing power is approximately linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.
+From additional measurements and simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}~(a),(b).
+As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.
+To fully quantify the size of the splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines
 
@@
 We will discuss these effects in greater detail in \autoref{sec:theory}.
-
-\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1-5 as well.
-Feature2 is a small avoided crossing between $\ket{02/2}$ and $\ket{21/3}$.
-It is missing in the stationary solution and thus is a manifestation of dressing by light.
-Feature 2 is its twin: $\ket{12/3}$ and $\ket{20/2}$ intersect but the avoided crossing is smaller and is not resolved due to the asymmetry of the driving strengths.
-Feature 3 is a large avoided crossing between $\ket{12/3}$ and $\ket{21/3}$ predicted by the model.
-A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator.
-Feature 4 is explained by the stationary model and is a consequence of multiple spectral lines of a peculiar shape formed by a pair of avoided crossings passing through a single point (dotted lines in \autoref{fig:statinary_levels}).
-It appears at the point where $\ket{02/2}$ intersects $\ket{20/2}$ and is just barely visible in the experimental data due to the noise.
-Feature 5 is located at the intersection between $\ket{20/2}$ and normally invisible $\ket{10}\rightarrow \ket{02}$.
-It is hardly visible in the experimental data, too.
-
-Finally, when the coupling is turned off ($J=0$) in modelling, the system does not demonstrate any of the described details.
-This means that all these effects can only be attributed to the SAM as a whole.
 
@@
 
+\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1-5 as well.
+Feature2 is a small avoided crossing between $\ket{02/2}$ and $\ket{21/3}$.
+It is missing in the stationary solution and thus is a manifestation of dressing by light.
+Feature 2 is its twin: $\ket{12/3}$ and $\ket{20/2}$ intersect but the avoided crossing is smaller and is not resolved due to the asymmetry of the driving strengths.
+Feature 3 is a large avoided crossing between $\ket{12/3}$ and $\ket{21/3}$ predicted by the model.
+A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator.
+Feature 4 is explained by the stationary model and is a consequence of multiple spectral lines of a peculiar shape formed by a pair of avoided crossings passing through a single point (dotted lines in \autoref{fig:statinary_levels}).
+It appears at the point where $\ket{02/2}$ intersects $\ket{20/2}$ and is just barely visible in the experimental data due to the noise.
+Feature 5 is located at the intersection between $\ket{20/2}$ and normally invisible $\ket{10}\rightarrow \ket{02}$, and can be found in the experimental data, too.
+
+Finally, when the coupling is turned off ($J=0$) in modelling, the system does not demonstrate any of the described details.
+This means that all these effects can only be attributed to the SAM as a whole.
+
 \subsection{Explaining extra avoided crossings}\label{sec:theory}
@@
 For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
-However, in our case the situation is more complicated.
-We will first explain the feature III.
+However, in our case the level structure is more complicated.
 
-First of all, since during the spectroscopy we apply only a single microwave tone, it has to be simultaneously the coupler tone and the probe tone to observe the A-T effect.
-This is possible due to the resonance condition $\omega_1 = \omega_2+\alpha_2/2$ at III which means that we can simultaneously excite transitions $\ket{10}$ and $\ket{02/2}$.
+First of all, since during the spectroscopy we apply only a single microwave tone ($\omega_d^1 = \omega_d^2$), for the A-T effect it has to be simultaneously the coupler and the probe; the latter must be much weaker than the former, as well.
+These conditions are satisfied when $\omega_{(2,1)} = \omega_{(1,2)}+\alpha_{(1,2)}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively) because the of the two-photon probe.
 Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure.
@@
 
-In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III.
-\autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM.
+Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$.
+However, as we will show, for the avoided crossing of feature I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
+Below, we give the detailed explanation concerning features II and III, and finally, I.
+
+\paragraph{Features II and III.}
+
+In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect would occur for feature III.
+For simplicity, we  \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM.
 Since from numerical simulations we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line, and hereinafter we consider the first transmon as a two-level system.
@@
 
-Now, we will repeat this reasoning in a quantitative mathematical model.
+Now, we will repeat this reasoning using a quantitative mathematical model.
 We start from the initial Hamiltonian \eqref{Hsystem}.
@@
 
+\vspace{1cm}
+
  \renewcommand{\kbldelim}{[}% Left delimiter
@@
 The probability rate of two-photon transition per unit interaction time using corrected eigenstates $\ket{k}$ and neglecting small terms we obtain:
+
 \begin{equation}
-	A^{(2)}_{1\rightarrow 6} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}+19 \text{$\Omega_1 $})^2}{\text{$\alpha
-			$}^6 \text{$\Omega_1$}^2}
+A^{(2)}_{1\rightarrow 6} =\pi\Omega_2^4 \frac{16 J^4 \left(3 \alpha ^2+7 \text{$\Omega_1
+		$}^2\right)^2}{\alpha ^{10}}
 \end{equation}
 \begin{equation}
-A^{(2)}_{2\rightarrow 5} =\frac{\pi\Omega_2^4}{8} \frac{8 J^4 (6 \text{$\alpha $}-19 \text{$\Omega_1 $})^2}{\text{$\alpha
-		$}^6 \text{$\Omega_1$}^2}
+A^{(2)}_{2\rightarrow 5} =\pi\Omega_2^4 \frac{4 J^4 (5 \alpha +3 \text{$\Omega_1$})^2}{\alpha ^8}
+\end{equation}
+From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.
+
+\subsection{Shape of the extra avoided crossings}
+
+In this section we will employ the model from \autoref{fig:main_scheme} to explain the experimentally observed splittings when only a single frequency excitation is applied.
+From here, we will use feature II as the example.
+In the laboratory frame, the two transitions forming the avoided crossing are $\left|01\right\rangle \rightarrow \left|20\right\rangle$ (one-photon) and $\left|00\right\rangle \rightarrow \left|21/3\right\rangle$ (three-photon).
+In the rotating frame with the second qubit at a small detuning $\Delta_2$ they both become two-photon since the second qubit splitting $\omega_2$ is replaced by $\Delta_2$ which is close to 0, and we are looking at transitions near $\omega_1+\alpha_1/2$.
+
+When $\Omega_2$ = 0 (no driving yet on the second qubit), the corresponding frequencies are:
+\begin{equation}
+\begin{aligned}
+\omega_{(01-20)/2} &= (\alpha_1 + 2 \omega_{1} - \Delta_2)/2\\
+ \omega_{21/2} &= (\alpha_1 + 2 \omega_{1} + \Delta_2)/2
+\end{aligned}
+\end{equation}
+When the second qubit becomes dressed by $\Omega_2 \neq 0$, its splitting becomes $\Omega^R_2 =\sqrt{\Omega_{2}^2 + \left(\omega_{2} - \omega_{d}\right)^{2}}$, where $\omega_d$ is the driving frequency.
+Since we are simultaneously dressing the $\left|i0\right\rangle, \left|i1\right\rangle$ states and probing transitions between them, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines appear:
+\begin{equation}
+\begin{aligned}
+\omega_{(01-20)/2} &= \omega_d,\\
+\omega_{21/2} &= \omega_d
+\end{aligned}
 \end{equation}
 
-From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.
+When $\Omega_2 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_2 - \omega_d|$.
+Intriguingly, they are the three-photon $\left|00\right\rangle \rightarrow \left|21/3\right\rangle$ and single-photon $\left|01\right\rangle \rightarrow \left|20\right\rangle$ transition frequencies in the laboratory frame:
+\begin{equation}
+\omega_d = \begin{cases} \frac{\alpha_1}{3} + \frac{2 \omega_{1}}{3} + \frac{\omega_{2}}{3}, \\ \alpha_1 + 2 \omega_{1} - \omega_{2}\end{cases}
+\end{equation}
+When $\Omega_2 \neq 0$, we obtain the following solutions:
+\begin{equation}
+\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{1}}{3} - \frac{\omega_{2}}{3} \pm \frac{\sqrt{3 \Omega_{2}^{2} + \left( \alpha_1 + 2 (\omega_{1} - \omega_{2})\right)^{2}}}{3}
+\label{eq:splitting_model}
+\end{equation}
+The minimal splitting between these lines is found at the resonant point where $\omega_2 = \omega_1 +  \alpha_1/2$ and equals $\frac{2}{\sqrt{3}} \Omega_2$.
+We find excellent agreement between our analytical model \eqref{eq:splitting_model} and both the experimental and simulated data as can be seen in \autoref{fig:zoom}.
+To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \eqref{eq:splitting_model}; $\alpha_2$ is known from spectroscopy.
+T																																																																																																																																																																																								he only free parameter left was $\Omega_2$.
+We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting (see \autoref{fig:splitting_linear}).
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{powerscan_1d}
+	\caption{Linear dependence of the splitting size on the driving voltage from the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$.}
+	\label{fig:splitting_linear}
+\end{figure}
+
+The upper branch is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
+The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon which has offset the avoided crossing 3 which becomes closer to the feature II; it is not important for our reasoning.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{topological_splittings}
+	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$.
+In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$.
+Two topologically different splittings may be observed}
+	\label{fig:difdrive}
+\end{figure}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{drawing}
-	\caption{Drive acts on the one of qubit, with different amplitude 100,200,300 MHz}
-	\label{fig:difdrive}
-\end{figure}
-
  The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.

### 2019-11-21 document.tex
Massive updates, pictures recolouring

@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{experiment}
+	\includegraphics[width=\linewidth]{experiment_2}
 	\caption{\textbf{(a)} Optical photograph of the device (false coloured).
@@
 \begin{equation}
-\hat H_{dr} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
+\hat H_{d} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
 \end{equation}
@@
 \begin{equation}\label{Hsystem}
-\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{dr1}+\hat H_{dr2}+\hat H_{int},
+\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
 \end{equation}
@@
 	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
-	\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
+	\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
 \end{aligned}
@@
 Colour shows the real part of complex transmission  through the sample.
-Two transmons are aligned as in \autoref{fig:experiment}~(c) and thus the picture is symmetric.
-Panel \textbf{(a)} contains an additional horizontal line which origins from a parasitic resonance interacting with the readout resonator but not with the SAM.
-Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; some other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
-In panel \textbf{(b)}, we also denote where possible some of the transitions $\ket{00}\rightarrow \ket{ij/n}$ where $i,j$ stand for the transmon eigenstates and $/n$ is optional for an $n$-photon process.}
+Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture.
+Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator.
+Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
+We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.}
 	\label{fig:two-tone}
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
@@
 	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
-Left picture is same as the right one but with transitions from the stationary Hamiltonian overlaid.
-The legend labels the transitions (notation as in the the main text) at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
+Lines show various transition frequencies from the stationary Hamiltonian.
+The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
 	\label{fig:statinary_levels}
-\end{figure*}
+\end{figure}
 
@@
 	\includegraphics[width=.49\linewidth]{zoom2_picture}
-	\caption{Investigation of the power dependence of feature II.
-Dashed are the model curves turning to dotted when the model is no longer expected to be valid (see Section \ref{sec:theory}).
-Model values for $\Omega_2$ are the same for both panels and shown as annotations in (b).
-\textbf{(a)} Experiment (second cooldown; the parameters are different from \autoref{fig:experiment}).
-The power of the microwave source is increased from -20 to 0 dBm so that the amplitude grows linearly, and the proportional growth of the splitting is observed.
-\textbf{(b)} Simulation with an equal and increasing amplitudes of the driving $\Omega_{1,2}/2\pi=$4.5, 11.25, 22.5 and 45 MHz; other parameters as in \autoref{fig:two-tone}.
-Note that now colours show the population of the ground state ($\ket{00}$).
-The growth of the splitting is a clear indication of the light-dressing to be at the root of the effect.}
+	\caption{Power dependence of feature II: experiment and theory.
+Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz.
+\textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}).
+The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed.
+\textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}.
+Note that now colours show the population of the ground state.}
 	\label{fig:zoom}
 \end{figure*}
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{powerscan_1d}
+	\caption{Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV.
+From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
+	\label{fig:splitting_linear}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{topological_splittings}
+	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$ but at the same frequency.
+In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
+Gray dashed lines show the stationary solution, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
+	\label{fig:difdrive}
+\end{figure}
 
@@
 \paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}).
-In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $\ket{ij/n}$ where $i,j$ denote the final transmon states after the transition from $\ket{00}$, and $/n$ is optional for an $n$-photon process.
-We put the labels at the line of symmetry where the transmons are in their sweet spots; the SAM states at this point are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
+In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process.
+We put the labels at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
 
 Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$.
-The $\ket{02/2}$ and $\ket{20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
-Another two-photon process appears as $\ket{11/2}$ line when two qubits are excited simultaneously.
+The ${02/2}$ and ${20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
+Another two-photon process appears as $11/2$ line when two qubits are excited simultaneously.
 This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I.
-A three-photon process $\ket{00}\rightarrow\ket{12/3}$ is also clearly visible just below the $\ket{02/2}$ line.
+A three-photon process $12/3$ is also clearly visible just below the $02/2$ line.
 As we will see, it is involved in forming features II and III.
-Notably, transitions $\ket{11/2}$ and $\ket{12/3}$ are forbidden when there is no interaction ($J=0$).
+Notably, transitions $11/2$ and ${12/3}$ are forbidden when there is no interaction ($J=0$).
 Therefore, it is expected that all Roman-numbered features should only appear with non-vanishing $\hat H_{int}$.
@@
 In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states.
-For a two-transmon SAM, such points are, for instance, crossings between $\ket{01}$, $\ket{10}$ or $ \ket{11} $, $ \ket{02} $($ \ket{20} $).
-Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between $\ket{12},\ \ket{21}$ at the same $\Phi_e$ where $\ket{01}$, $\ket{10}$ intersect.
+For a two-transmon SAM, such points are, for instance, crossings between ${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $).
+Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between ${12}/3,\ {21}/3$ at the same $\Phi_e$ where ${01}$, ${10}$ intersect.
 
 \paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2.
-Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition from $\ket{00}$ to $\ket{01}$ intersects with the two-photon one $\ket{20/2}$ ($\ket{10}$ intersects $\ket{02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).
+Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition ${01}$ intersects with the two-photon one ${20/2}$ (${10}$ intersects ${02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).
 
-From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: $\ket{00}\rightarrow\ket{12/3}$ and $\ket{10}\rightarrow \ket{02}$ which are of the same frequency when $\omega_1 = \omega_2-\alpha_2/2$.
-The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates $\ket{10}$, but is not visible in \autoref{fig:two-tone}.
-From additional measurements and simulations, we have found that the size of the splitting depends on the driving power on the first transmon; the results are shown in \autoref{fig:zoom}~(a),(b).
-As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the $\ket{10}$ spectral line which is approximately $\Omega_1/2\pi$ Hz.
-To fully quantify the size of the splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines
+From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
+The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}.
+In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$.
+From additional measurements and simulations, we have found that the size of these anticrossings depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b).
+As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the ${01}$ spectral line which is approximately $\Omega_2/2\pi$ Hz.
+To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}.
+By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:splitting_linear}).
 
-We come to the same conclusion for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits an avoided crossing with a proportionally enlarging splitting (see \autoref{fig:difdrive}).
-Notably, two qualitatively different patterns of avoided crossings arise when the first or the second qubit is strongly driven.
+We see a similar behaviour for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits avoided crossings with the proportional size.
+In \autoref{fig:difdrive} we show only the simulation results; an experiment is not possible with our sample because there is no way to adjust the driving amplitudes $\Omega_{1,2}$ individually.
+We note that two qualitatively different patterns arise depending on which of the transmons is driven stronger than the other.
+From this and from the shape of the splitting in feature I of \autoref{fig:experiment}~(a), we can infer that $\Omega_1 \approx 2\Omega_2$ there.
 
-These observation lead to understanding that the effect is caused by light dressing.
+These observations mean that I -- III are caused by light dressing.
 In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=.9\linewidth]{main_scheme}
-	\caption{Explaining the origin of the AT satellites for feature III.
-\textbf{(a)} System level structure at 3.65 mA.
-At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$.
-The first transmon is driven by a strong signal of amplitude $\Omega_1$ at a small detuning $\Delta_1$ from $\omega_1$ shown in green.
-The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles.
-\textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$).
-However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = (\Omega_1^2 + \Delta_1^2)^{\frac{1}{2}}$ (the first transmon becomes light-dressed).
-\textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{dr}^2$ are shown with blue ellipses).
-In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
-In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
-	\label{fig:main_scheme}
-\end{figure*}
+\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1 -- 5 as well.
 
-\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1-5 as well.
-Feature2 is a small avoided crossing between $\ket{02/2}$ and $\ket{21/3}$.
-It is missing in the stationary solution and thus is a manifestation of dressing by light.
-Feature 2 is its twin: $\ket{12/3}$ and $\ket{20/2}$ intersect but the avoided crossing is smaller and is not resolved due to the asymmetry of the driving strengths.
-Feature 3 is a large avoided crossing between $\ket{12/3}$ and $\ket{21/3}$ predicted by the model.
-A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator.
-Feature 4 is explained by the stationary model and is a consequence of multiple spectral lines of a peculiar shape formed by a pair of avoided crossings passing through a single point (dotted lines in \autoref{fig:statinary_levels}).
-It appears at the point where $\ket{02/2}$ intersects $\ket{20/2}$ and is just barely visible in the experimental data due to the noise.
-Feature 5 is located at the intersection between $\ket{20/2}$ and normally invisible $\ket{10}\rightarrow \ket{02}$, and can be found in the experimental data, too.
+Feature 1 is a small avoided crossing between ${02/2}$ and ${21/3}$.
+It is missing in the stationary solution and thus is caused by the light dressing just as I -- III.
+Feature 2 is its twin: ${12/3}$ and ${20/2}$ intersect there but the anticrossing is smaller due to the asymmetry of the driving strengths and is not resolved.
 
-Finally, when the coupling is turned off ($J=0$) in modelling, the system does not demonstrate any of the described details.
+Feature 3 is a large avoided crossing between three-photon processes ${12/3}$ and ${21/3}$.
+It is predicted by the stationary model, and direct diagonalization yields the splitting of $\frac{4}{3}J$.
+A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator in the third order.
+
+Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:statinary_levels}).
+It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise.
+Feature 5 is located at the intersection between ${20/2}$ and normally invisible ${10} - {02}$, and can be found in the experimental data, too.
+
+Finally, when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details.
 This means that all these effects can only be attributed to the SAM as a whole.
@@
 
-Since we had already connected the additional avoided crossings with light dressing, it was natural to expect the Autler-Townes effect to cause them.
+Since we had already connected the additional avoided crossings with the light dressing, it was natural to expect the Autler-Townes effect to be at the root of the avoided crossings.
 For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
-However, in our case the level structure is more complicated.
+However, in our case the level structure and the effect itself are more complicated.
 
@@
 In contrast, the single-photon excitation is enough to dress the system.
-In other words, in our case the A-T coupling operator is $\hat H_{dr}^1$ (strong), and the probing operator is $\hat H_{dr}^2$ (weak in the two-photon regime).
+In other words, in our case the A-T coupling operator is $\hat H_{d}^1$ (strong), and the probing operator is $\hat H_{d}^2$ (weak in the two-photon regime).
 Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.
@@
 Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$.
-However, as we will show, for the avoided crossing of feature I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
-Below, we give the detailed explanation concerning features II and III, and finally, I.
+However, as we have demonstrated in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
+
+Below, we give the detailed explanation of features II and III, and finally, I.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{main_scheme_2}  
+	\caption{Explaining feature III.
+\textbf{(a)} Schematic of the transition frequencies near III (not to scale).
+Red dashed line shows the current (0.36 mA) where the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$ and several transitions become resonant.
+So far we assume that each transmon is driven at its own frequency.
+\textbf{(b)} System level structure at the resonant point including the driving $\hat H_{d}^1$ of the first transmon by a strong signal of amplitude $\Omega_1$ (orange ellipses) at a small detuning $\Delta_1$ from $\omega_1$.
+The second transmon driving is not shown here.
+Action of $\hat H_{int}$ in RWA is depicted as orange-blue circles.
+\textbf{(c)} In the frame rotating with the drive of the first transmon, all the states $\ket{0j},\ket{1j}$ become nearly degenerate ($\omega_1 \rightarrow \Delta_1$).
+Dressing by the strong excitation increases this splitting to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$.
+\textbf{(d)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{d}^2$ are shown with blue ellipses).
+In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
+In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
+	\label{fig:main_scheme}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=.9\linewidth]{topo_scheme}
+	\caption{Explaining feature I.
+(a) Schematic of the transitions near I.
+(b) Transitions in the frame rotating with the second transmon with dressing.
+As will be shown in Section \ref{sec:münchhausen}, in our experiment there can only be one visible transition to the left or to the right from the resonance.}
+	\label{fig:featureI}
+\end{figure}
 
@@
 
-In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect would occur for feature III.
-For simplicity, we  \autoref{fig:main_scheme}~(a) demonstrates the unmodified level structure of the SAM.
-Since from numerical simulations we know that level $\ket{02}$ is not necessary to observe the splitting, it is only shown with a dashed line, and hereinafter we consider the first transmon as a two-level system.
+In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III.
+For simplicity, we will temporarily assume that each transmon is driven at its own frequency (this assumption will be lifted in the following section).
+For convenience, in \autoref{fig:main_scheme}~(a) we schematically reproduce the transitions near III where the first transmon (orange) is below the second (blue), and the resonance point in current is shown with dashed red line.
+Next, \autoref{fig:main_scheme}~(b) demonstrates the stationary level structure of the SAM at 0.36 mA.
+Nearly-resonant with $10$ (detuning $\Delta_1$) single-photon driving with $\hat H_d^1$ is shown with orange ellipses while much weaker two-photon $\hat H_d^2$ is not shown yet.
+Since from numerical simulations we know that the third level of the first transmon is not necessary to observe the splitting, $\ket{02}$ is shown transparent, and hereinafter the states $\ket{j2},\ j=0..2$ are not used in the modelling.
 
-The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(b)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}.
+The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(c)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}.
 Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$.
-At the same time, the second transmon energies stay the same.
+Meanwhile, the second transmon energies stay the same.
 
-Finally, in \autoref{fig:main_scheme}~(c) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{dr}^2$.
+Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{d}^2$.
 In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$.
@@
 \hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
-\hat H_{dr}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
-\hat H_{dr}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
+\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
+\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
 \end{aligned}
 \end{equation}
-where $\delta = \omega_{dr}^2 - \omega_{dr}^1$.
+where $\delta = \omega_{d}^2 - \omega_{d}^1$.
 
-Since $\hat H_{dr}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
+Since $\hat H_{d}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
 After that, the Hamiltonian may be split into three parts:
@@
 \begin{aligned}
-\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
+\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
 \hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
-\hat V_t &= \hat S^\dag \hat H_{dr}^{2} \hat S \equiv \hat H_{dr}^{2}.
+\hat V_t &= \hat S^\dag \hat H_{d}^{2} \hat S \equiv \hat H_{d}^{2}.
 \end{aligned}
@@
 The first part is diagonal, and the remaining two will be treated as perturbations.
-To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2= - \alpha/2$.
+To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
 In these conditions, $H^D$ becomes degenerate as can be seen below in \eqref{eq:ham_matrix}:
-
-\vspace{1cm}
-
- \renewcommand{\kbldelim}{[}% Left delimiter
-\renewcommand{\kbrdelim}{]}% Right delimiter
-\begin{widetext}
-	\begin{equation}
-	\hat H^D + \hat V_J + \hat V_t  = \kbordermatrix{
-		&\ket{a,0} & \ket{b,0} & \ket{a,1} & \ket{b,1} & \ket{a,2} & \ket{b,2} \\
-		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & \frac{\Omega_{2}e^{i \text{$\delta$} t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 \\
-		\ket{b,0} & 0 & \frac{\Omega_1}{2} & -\frac{J}{2} & \frac{\Omega_2 e^{i \delta t}}{2} + \frac{J}{2} & 0 & 0 \\
-		\ket{a,1} &\frac{\Omega_2 e^{-i \text{$\delta$} t} }{2}  - \frac{J}{2} & -\frac{J}{2} & - \frac{\alpha}{2} - \frac{\Omega_1}{2}&
-		0 & \frac{\text{$\Omega_2$} e^{i \text{$\delta$} t}}{\sqrt{2}} -\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
-		\ket{b,1} & \frac{J}{2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{2} +\frac{J}{2} & 0 & - \frac{\alpha}{2} + \frac{\Omega_1}{2} & -\frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{i \text{$\delta
-					$} t}}{\sqrt 2} + \frac{J}{\sqrt 2} \\
-		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i \delta t}}{2} - \frac{J}{\sqrt 2} & -\frac{J}{\sqrt 2} &
-		-\frac{\Omega_{1}}{2} & 0 \\
-		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{\sqrt 2} + \frac{J}{\sqrt 2} & 0 & \frac{\Omega_{1}}{2}\\
-	}
-	\label{eq:ham_matrix}
-	\end{equation}
-\end{widetext}
 
@@
 \begin{equation}
-A^{(2)}_{1\rightarrow 6} =\pi\Omega_2^4 \frac{16 J^4 \left(3 \alpha ^2+7 \text{$\Omega_1
-		$}^2\right)^2}{\alpha ^{10}}
+A^{(2)}_{1\rightarrow 6} =\pi\Omega_2^4 \frac{16 J^4 \left(3 \alpha_2 ^2+7 \text{$\Omega_1
+		$}^2\right)^2}{\alpha_2 ^{10}}
 \end{equation}
 \begin{equation}
-A^{(2)}_{2\rightarrow 5} =\pi\Omega_2^4 \frac{4 J^4 (5 \alpha +3 \text{$\Omega_1$})^2}{\alpha ^8}
+A^{(2)}_{2\rightarrow 5} =\pi\Omega_2^4 \frac{4 J^4 (5 \alpha_2 +3 \text{$\Omega_1$})^2}{\alpha_2 ^8}
 \end{equation}
@@
 
-\subsection{Shape of the extra avoided crossings}
+\paragraph{Feature I.} Finally, we discuss the last of the dressing effects observed in the SAM.
+Its explanation is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$.
+In this case, the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
+For the opposite case, the explanation is the same.
+As one can see, only the two-photon transition $11/2$ is affected.
+When the transitions $01$ and $10$ are close resonance, its frequency is $\omega_{11/2} \approx \omega_1 \approx \omega_2$ Similarly to the previous case with II and III, in the dressed basis, this transitions becomes a single-photon doublet transition for $\hat H_d^2$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
+Note that in the experiment with only a single excitation frequency, it is not possible to observe both transitions at the same magnetic flux, and this is clearly visible in \autoref{fig:difdrive}.
+Instead, we observe one line to the left and the other to the right from the $01-10$ intersection.
+This behaviour will be explained in the following section.
 
-In this section we will employ the model from \autoref{fig:main_scheme} to explain the experimentally observed splittings when only a single frequency excitation is applied.
-From here, we will use feature II as the example.
-In the laboratory frame, the two transitions forming the avoided crossing are $\left|01\right\rangle \rightarrow \left|20\right\rangle$ (one-photon) and $\left|00\right\rangle \rightarrow \left|21/3\right\rangle$ (three-photon).
-In the rotating frame with the second qubit at a small detuning $\Delta_2$ they both become two-photon since the second qubit splitting $\omega_2$ is replaced by $\Delta_2$ which is close to 0, and we are looking at transitions near $\omega_1+\alpha_1/2$.
+\subsection{Self-consistent equations for the avoided crossings}
+\label{sec:münchhausen}
 
-When $\Omega_2$ = 0 (no driving yet on the second qubit), the corresponding frequencies are:
+Before, we have assumed that the transmons are driven independently at two different frequencies.
+In this section, we will employ the same model from \autoref{fig:main_scheme} to explain the experimentally observed splittings when only a single frequency $\omega_d$ is sent at the SAM.
+
+\paragraph{Features II, III.}As shown in \autoref{fig:main_scheme}~(d), the sideband transitions are formed by two-photon processes for $\hat H_d^2$.
+On the other hand, we know from the stationary solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon).
+This means that there should be a smooth transformation between 1-, 2- and 3-photon processes when the system approaches the resonant point.
+Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$.
+In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are:
 \begin{equation}
 \begin{aligned}
-\omega_{(01-20)/2} &= (\alpha_1 + 2 \omega_{1} - \Delta_2)/2\\
- \omega_{21/2} &= (\alpha_1 + 2 \omega_{1} + \Delta_2)/2
+\omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
+ \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_2)/2.
 \end{aligned}
 \end{equation}
-When the second qubit becomes dressed by $\Omega_2 \neq 0$, its splitting becomes $\Omega^R_2 =\sqrt{\Omega_{2}^2 + \left(\omega_{2} - \omega_{d}\right)^{2}}$, where $\omega_d$ is the driving frequency.
-Since we are simultaneously dressing the $\left|i0\right\rangle, \left|i1\right\rangle$ states and probing transitions between them, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines appear:
+When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$.
+At this point it becomes clear that at the resonant point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$, $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established above and thus should be used to model the splitting behaviour.
+
+Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ both at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear:
 \begin{equation}
 \begin{aligned}
-\omega_{(01-20)/2} &= \omega_d,\\
-\omega_{21/2} &= \omega_d
+\omega_{(10-02)/2} &= \omega_d,\\
+\omega_{12/2} &= \omega_d
 \end{aligned}
@@
 
-When $\Omega_2 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_2 - \omega_d|$.
-Intriguingly, they are the three-photon $\left|00\right\rangle \rightarrow \left|21/3\right\rangle$ and single-photon $\left|01\right\rangle \rightarrow \left|20\right\rangle$ transition frequencies in the laboratory frame:
+When $\Omega_1 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_1 - \omega_d|$.
+Intriguingly, they are the three-photon and single-photon transition frequencies in the laboratory frame:
 \begin{equation}
-\omega_d = \begin{cases} \frac{\alpha_1}{3} + \frac{2 \omega_{1}}{3} + \frac{\omega_{2}}{3}, \\ \alpha_1 + 2 \omega_{1} - \omega_{2}\end{cases}
+\omega_d = \begin{cases} \frac{\alpha_2}{3} + \frac{2 \omega_{2}}{3} + \frac{\omega_{1}}{3}, \\ \alpha_2 + 2 \omega_{2} - \omega_{1}\end{cases}
 \end{equation}
-When $\Omega_2 \neq 0$, we obtain the following solutions:
+When $\Omega_1 \neq 0$, we obtain the following solutions:
 \begin{equation}
-\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{1}}{3} - \frac{\omega_{2}}{3} \pm \frac{\sqrt{3 \Omega_{2}^{2} + \left( \alpha_1 + 2 (\omega_{1} - \omega_{2})\right)^{2}}}{3}
+\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{2}}{3} - \frac{\omega_{1}}{3} \pm \frac{\sqrt{3 \Omega_{1}^{2} + \left( \alpha_2 + 2 (\omega_{2} - \omega_{1})\right)^{2}}}{3}
 \label{eq:splitting_model}
 \end{equation}
-The minimal splitting between these lines is found at the resonant point where $\omega_2 = \omega_1 +  \alpha_1/2$ and equals $\frac{2}{\sqrt{3}} \Omega_2$.
+The minimal splitting between these lines is found at the resonant point and equals $\frac{2 \sqrt{3}}{{3}} \Omega_1$.
+All these calculations may be repeated exactly for the feature II by reversing the order of the transmons; in that case, the maximal splitting will be $\frac{2 \sqrt{3}}{{3}} \Omega_2$
+
 We find excellent agreement between our analytical model \eqref{eq:splitting_model} and both the experimental and simulated data as can be seen in \autoref{fig:zoom}.
-To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \eqref{eq:splitting_model}; $\alpha_2$ is known from spectroscopy.
-T																																																																																																																																																																																								he only free parameter left was $\Omega_2$.
-We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting (see \autoref{fig:splitting_linear}).
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{powerscan_1d}
-	\caption{Linear dependence of the splitting size on the driving voltage from the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$.}
-	\label{fig:splitting_linear}
-\end{figure}
+To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \eqref{eq:splitting_model}; $\alpha_1$ is known from spectroscopy.
+The only free parameter left was $\Omega_2$.
+We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting on excitation amplitude (see \autoref{fig:splitting_linear}).
 
 The upper branch is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
-The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon which has offset the avoided crossing 3 which becomes closer to the feature II; it is not important for our reasoning.
+The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon moving the avoided crossing 3 closer to the feature II; however, it is not important for our reasoning.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{topological_splittings}
-	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$.
-In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$.
-Two topologically different splittings may be observed}
-	\label{fig:difdrive}
-\end{figure}
+\paragraph{Feature I.} Feature I may be explained using the same dressing model.
+Looking at \autoref{fig:featureI} for the case $\Omega_2 \gg \Omega_1$, we can write the other pair of self-consistent equations:
+\begin{equation}
+\omega_{1} \pm \Omega_2^R = \omega_d.
+\end{equation}
+Due to the fact that $\Omega_2^R = \sqrt{\Omega_2^2 + (\omega_2 - \omega_d)^2}$, these equations only have the same single solution:
+\begin{equation}
+\omega_d = \frac{\omega_1 + \omega_2}{2} - \frac{ \Omega_{2}^{2}}{2 \left(\omega_{1} - \omega_{2}\right)},
+\label{eq:topo_1}
+\end{equation}
+which gives back the frequency of $11/2$ in the laboratory frame when $\Omega_2$ is zero.
+When $\Omega_2$ is non-zero, the solution near the point $\omega_1 \approx \omega_2$ is a hyperbolic curve, which agrees well with the numerical simulation.
+However, due to the finite coupling $J$ between the transmons, they never reach each other in frequency, and thus this model is not applicable when $|\omega_1 - \omega_2| \leq J$.
+
+When $\Omega_1 \gg \Omega_2$, besides the replacement $\Omega_2 \rightarrow \Omega_1$, the equation \eqref{eq:topo_1} changes the sign:
+\begin{equation}
+\omega_d = \frac{\omega_1 + \omega_2}{2} + \frac{ \Omega_{1}^{2}}{2 \left(\omega_{1} - \omega_{2}\right)},
+\label{eq:topo_1_inv}
+\end{equation}
+yielding the reversed shape of the splitting.
+
+Continuing this logic, we can write down the resonance condition in the doubly-rotating frame when both transmons are dressed simultaneously:
+\begin{equation}
+\Omega_1^R \pm \Omega_2^R = 0.
+\end{equation}
+Solving it for $\omega_d$, we obtain the generalization of \eqref{eq:topo_1} and \eqref{eq:topo_1_inv}:
+\begin{equation}
+\omega_d = \frac{\omega_{1} - \omega_{2}}{2} + \frac{\Omega_{1}^{2} - \Omega_{2}^{2}}{ 2\left(\omega_{1} - \omega_{2}\right)}
+\label{eq:topo_comm}
+\end{equation}
+
+The equation \eqref{eq:topo_comm} is used to plot the black dashed curves in \autoref{fig:difdrive} taking the $\Omega_{1,2}$ values from the simulation parameters shown therein.
+The frequencies $\omega_{1,2}$ are extracted from the fits to the visible spectral lines.
+We find good agreement between the model and the simulated data.
 
@@
 \begin{figure}
-	\includegraphics[width=.9\linewidth]{intro_scheme}
+	\includegraphics[width=\linewidth]{intro_scheme}
 	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here).
-\textbf{(a)} The three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$.
-It induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
+\textbf{(a)} A three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$ which induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
 \textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
-However, when RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
+However, when the RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
 Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
@@
 The following steps completely reproduce the classical case if we add the probe tone $\Omega_2$ in the last equation.
+
+\section{The dressed Hamiltonian in the matrix form}
+
+\vspace{1cm}
+
+\renewcommand{\kbldelim}{[}% Left delimiter
+\renewcommand{\kbrdelim}{]}% Right delimiter
+\begin{widetext}
+	\begin{equation}
+	\hat H^D + \hat V_J + \hat V_t  = \kbordermatrix{
+		&\ket{a,0} & \ket{b,0} & \ket{a,1} & \ket{b,1} & \ket{a,2} & \ket{b,2} \\
+		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & \frac{\Omega_{2}e^{i \text{$\delta$} t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 \\
+		\ket{b,0} & 0 & \frac{\Omega_1}{2} & -\frac{J}{2} & \frac{\Omega_2 e^{i \delta t}}{2} + \frac{J}{2} & 0 & 0 \\
+		\ket{a,1} &\frac{\Omega_2 e^{-i \text{$\delta$} t} }{2}  - \frac{J}{2} & -\frac{J}{2} & - \frac{\alpha}{2} - \frac{\Omega_1}{2}&
+		0 & \frac{\text{$\Omega_2$} e^{i \text{$\delta$} t}}{\sqrt{2}} -\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
+		\ket{b,1} & \frac{J}{2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{2} +\frac{J}{2} & 0 & - \frac{\alpha}{2} + \frac{\Omega_1}{2} & -\frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{i \text{$\delta
+					$} t}}{\sqrt 2} + \frac{J}{\sqrt 2} \\
+		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i \delta t}}{2} - \frac{J}{\sqrt 2} & -\frac{J}{\sqrt 2} &
+		-\frac{\Omega_{1}}{2} & 0 \\
+		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{\sqrt 2} + \frac{J}{\sqrt 2} & 0 & \frac{\Omega_{1}}{2}\\
+	}
+	\label{eq:ham_matrix}
+	\end{equation}
+\end{widetext}
 
@@
 
- The implementations of the transitions between the eigenstates is achieved by external microwave driving through a capacitively coupled transition line.
-In the notations used above, the pump Hamiltonian can be written generically as $ 	H_{dr} = -2e n\beta V_{dr}(t)=\Omega(t)(b+b^{\dagger})$.
- Where $2en$ -- the charge on island, $\beta$ -- dimensionless coefficient depending on the geometry of the system and the ratio of capacities, $V_{dr}(t)$ -- the voltage on the external source; $n =\frac{1}{\sqrt{2}} (\frac{E_J}{8E_C})^{1/4}(b+b^{\dagger})$.
-
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-11-21 Pictures/Plotting/MainPicturePlot.py

@@ -51,7 +51,7 @@ class MainPicturePlot:
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc
         cb.update_ticks()
-        plt.text(-0.15, 1.1, "(a)", fontdict={"name": "STIX"}, fontsize=22,
+        plt.text(-0.15, 1.1, "(a)", fontdict={"name": "STIX"}, fontsize=17,
                  transform=ax.transAxes)
 
         plt.text(.53, .815, r"$\omega_2(\Phi_e)/2\pi$", fontdict={"name": "STIX"}, fontsize=7.5,
@@ -149,7 +149,7 @@ class MainPicturePlot:
         plt.text(.53, .07, "20/2", fontsize=10,
                  transform=ax.transAxes, ha='center')
 
-        plt.text(-0.09, 1.1, "(b)", fontdict={"name": "STIX"}, fontsize=22,
+        plt.text(-0.09, 1.1, "(b)", fontdict={"name": "STIX"}, fontsize=17,
                  transform=ax.transAxes)
 
 

### 2019-11-21 Pictures/Plotting/Powerscan.py

@@ -71,7 +71,7 @@ class ZoomPlot:
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
         cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$ [mU]", position=(1.3,-2))
 
-        plt.text(-0.35, 1.15, "(a)", fontdict={"name": "STIX"}, fontsize=22,
+        plt.text(-0.35, 1.15, "(a)", fontdict={"name": "STIX"}, fontsize=20,
                  transform=axes[0,0].transAxes)
 
 

### 2019-11-21 Pictures/Plotting/StationaryPlot.py

@@ -15,49 +15,47 @@ class StationaryPlot:
         with open("stationary.pkl", "rb") as f:
             currs, freqs, population10, energies = pickle.load(f)
 
-        fig, axes = plt.subplots(1, 2, figsize=(10, 3.33), sharey=True)
-        plt.subplots_adjust(wspace=.1, )
+        fig, ax = plt.subplots(1, 1, figsize=(4.25, 2.75), sharey=True)
 
-        mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
-                           cmap="Spectral_r")
+        # mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
+        #                    cmap="Spectral_r")
 
-        for ax in axes:
-            rect1 = patches.Rectangle((3.5, 5.25), .3, .04,
-                                      linewidth=1, edgecolor='black',
-                                      facecolor='none', linestyle=":")
-            ax.add_patch(rect1)
-            rect2 = patches.Rectangle((2.925, 5.2275),
-                                      3.225-2.925,
-                                      5.2675-5.2275,
-                                      linewidth=1, edgecolor='black',
-                                      facecolor='none', linestyle=":")
-            ax.add_patch(rect2)
-            rect3 = patches.Rectangle((3.16, 5.3), .3, .04,
-                                      linewidth=1, edgecolor='black',
-                                      facecolor='none', linestyle=":")
-            ax.add_patch(rect3)
-            ax.annotate("1", xy=(3.48, 5.23), xytext=(3.575, 5.205), ha="center", fontsize=10,
-                        arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
-                                        shrink=0.05))
+        rect1 = patches.Rectangle((3.5, 5.25), .3, .04,
+                                  linewidth=1, edgecolor='black',
+                                  facecolor='none', linestyle=":")
+        ax.add_patch(rect1)
+        rect2 = patches.Rectangle((2.925, 5.2275),
+                                  3.225-2.925,
+                                  5.2675-5.2275,
+                                  linewidth=1, edgecolor='black',
[…]

### 2019-11-21 Pictures/Plotting/TopologicalSplitting.py

@@ -35,22 +35,68 @@ class TopologicalSplitting:
                 ax.set_xlabel("Current [$10^{-4}$ A]")
             if idx < 3:
                 ax.set_ylabel("$\omega_d^{1,2}/2\pi$ [GHz]")
-
             if idx in [0]:
                 plt.text(.5, .7, "$\Omega_1: {0}$ MHz\n$\Omega_2: {1}$ MHz".format(Omegas[idx][0],
-                                                                                     Omegas[idx][
-                                                                                         1]),
+                                                                                   Omegas[idx][
+                                                                                       1]),
                          fontsize=10,
                          transform=ax.transAxes, ha='center', color="black")
             else:
                 plt.text(.5, .7, "${0}$ MHz\n${1}$ MHz".format(Omegas[idx][0],
-                                                                                     Omegas[idx][
-                                                                                         1]),
+                                                               Omegas[idx][
+                                                                   1]),
                          fontsize=10,
                          transform=ax.transAxes, ha='center', color="black")
 
-            ax.plot(self._currs, self._transitions_1, "--", color= "gray", linewidth=1)
-            ax.plot(self._currs, self._transitions_2, "--", color= "gray", linewidth=1)
+            # ax.plot(self._currs[len(self._currs) // 2 + 10:],
+            #         self._transitions_1[len(self._currs) // 2 + 10:], "--", color="gray",
+            #         linewidth=1)
+            ax.plot(self._currs[len(self._currs) // 2 + 10:],
+                    self._transitions_2[len(self._currs) // 2 + 10:], "--", color="gray",
+                    linewidth=1)
+
+            def transmon_spec(Ej, Ec, d, sws, period, offset, currs):
+                Ej = Ej * abs(cos(pi * (currs - sws) / period + offset * pi) * \
+                              sqrt((1 + d ** 2 * tan(
+                                  pi * (currs - sws) / period + offset * pi) ** 2)))
[…]

### 2019-11-21 Pictures/Plotting/ZoomPlot.py

@@ -62,7 +62,7 @@ class ZoomPlot:
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
         cb.ax.set_title(r"$P_{\left|00\right\rangle}$", position=(1.125,-2))
 
-        plt.text(-0.35, 1.15, "(b)", fontdict={"name": "STIX"}, fontsize=22,
+        plt.text(-0.35, 1.15, "(b)", fontdict={"name": "STIX"}, fontsize=20,
                  transform=axes[0,0].transAxes)
 
 

### 2019-11-21 Pictures/Plotting/ZoomPlot_for_1D.py

@@ -9,21 +9,21 @@ from matplotlib import pyplot as plt
 from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
 from matplotlib.pyplot import MultipleLocator
 
+
 class Powerscan1D:
 
     def __init__(self):
 
         self._load_data()
 
-
         fig, axes = plt.subplots(4, 3, sharex=False, sharey=False, figsize=(8, 6))
         plt.subplots_adjust(wspace=.3, hspace=.3)
 
         for idx, ax in enumerate(axes.ravel()[:-1]):
 
-            X, Y, data = self._data[idx]["Current [A]"]*1e4,\
-                         self._data[idx]["Frequency [Hz]"]/1e9, \
-                         real(self._data[idx]["data"]*exp(1j*pi/2)).T*1e3
+            X, Y, data = self._data[idx]["Current [A]"] * 1e4, \
+                         self._data[idx]["Frequency [Hz]"] / 1e9, \
+                         real(self._data[idx]["data"] * exp(1j * pi / 2)).T * 1e3
 
             # if idx in [0]:
             #     data = data - median(data, axis=0)
@@ -38,37 +38,42 @@ class Powerscan1D:
                 ax.set_xlabel('Current [$10^{-4}$ A]');
 
         self._Omega_2s = array([6e-3, 7.55e-3, 9.5e-3, 11.9e-3, 15e-3, 19e-3,
-                                23e-3, 30e-3, 37.8e-3, 47.65e-3, 60e-3])*0.75
+                                23e-3, 30e-3, 37.8e-3, 47.65e-3, 60e-3]) * 0.75
         self._plot_theory(axes)
         print(self._Omega_2s)
 
-
-
-        cbaxes1 = fig.add_axes([0.125,.95,0.5,.015])
+        cbaxes1 = fig.add_axes([0.125, .95, 0.5, .015])
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$ [mU]", position=(1.3,-2))
[…]

### 2019-11-26 document.tex
Changing in appendix D

@@
 \begin{equation}
-A^{(2)}_{1\rightarrow 6} =\pi\Omega_2^4 \frac{16 J^4 \left(3 \alpha_2 ^2+7 \text{$\Omega_1
-		$}^2\right)^2}{\alpha_2 ^{10}}
+A^{(2)}_{1\rightarrow 6} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1
+		$}\right)^2}{\alpha ^{6}\Omega_1^2}
 \end{equation}
 \begin{equation}
-A^{(2)}_{2\rightarrow 5} =\pi\Omega_2^4 \frac{4 J^4 (5 \alpha_2 +3 \text{$\Omega_1$})^2}{\alpha_2 ^8}
+A^{(2)}_{2\rightarrow 5} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
+		$}\right)^2}{\alpha ^{6}\Omega_1^2}
 \end{equation}
@@
 	\begin{split}
-	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)\overset{RWA}{=}\\ \exp(i H_0 t) \Omega(\hat b^{\dagger} e^{-i\omega_d t}+\hat be^{i\omega_d t})\exp(-i H_0 t)
+	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)=\\\frac{\Omega}{2} \exp(i H_0 t) \hat{B}(e^{-i\omega_d t}+e^{i\omega_d t})\exp(-i H_0 t)
 	\end{split}
 \end{equation}
+Where, $\hat{b}^{\dagger}+\hat{b}=\hat{B}$.
 Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
@@
 	\begin{split}
-	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}b^{\dagger}\ket{i}+\\
-	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}b\ket{i}\big]
+	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}\hat{B}\ket{i}+\\
+	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}\hat{B}\ket{i}\big]
 	\end{split}
@@
 	\begin{split}
-	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}b\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
-	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
-	\sum_j\frac{\bra{f}b\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
-	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
+	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
+	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
+	\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
+	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
 	\end{split}
@@
 \begin{split}
-	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}b^{\dagger}\ket{j}\bra{j}b^{\dagger}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
+	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
 \end{split}
@@
 
-\section{Text}
-
-In order to determine which transitions correspond to the lines, the stationary Schrödinger equation was solved \autoref{fig:spectr} in three-level approximation for both of qubits.
-With the Hamiltonian of the system:
-\begin{equation}
-	H_{system} = H_{tr1}\otimes \mathbbm{1}+\mathbbm{1}\otimes H_{tr2}+H_{int}
-\end{equation}
-
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-11-26 document.tex
Oleg's edits

--- 2019-11-21 document.tex
@@
 	\begin{abstract}
-		To build a full-scale quantum processor it is necessary to automate as many steps as possible on the physical, hardware level.
-Circuit quantum electrodynamics (cQED) is a contemporary architecture for dispersive readout and Purcell protection of superconducting qubits of various types, and thus it is necessary to develop software that is able to perform every kind of automatic calibration of such systems from scratch without any human participation.
-An important step towards this goal is to build a noise-insensitive and accurate computer vision tool to process three-dimensional spectroscopic data.
-In this work, we present and describe two scalable algorithms that are able to extract the Hamiltonian parameters of the cQED systems from spectroscopic data.
+	Since their demonstration, superconducting artificial atoms have been extensively used for studies in quantum optics.
+Their particular advantages compared to natural systems are the strong coupling to radiation and the high level of control over their state; these properties open the way to previously unexplored physics.
+In this work, we have irradiated a superconducting artificial molecule composed of two flux-tunable transmons with intense light while monitoring its state via joint dispersive readout.
+At certain configurations of its energy levels, the molecule has demonstrated a complex spectrum deviating qualitatively from the stationary solution.
+However, it was reproduced accurately by numerical simulations, and turned out to be a consequence of a modified Autler-Townes effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates.
+To quantify this effect, self-consistent models were employed accounting for both these processes at the same time.
+We note that this study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
 	\end{abstract}
@@
 Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
-For example, the strong coupling regime when the coupling strength between light and a quantum system approaches 1\% of their frequency has been a major milestone for atoms, molecules, etc and was only reached using high-finesse cavities.
-In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
-Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime.
+For example, the strong coupling regime, when the coupling strength between light and a quantum system approaches 1\% of their frequency, has been a major challenge for atoms, molecules, etc and was only reached using high-finesse cavities.
+In contrast, superconducting quantum systems have rapidly attained this milestone using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first demonstration\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
+Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all.
+The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime\cite{forn2019ultrastrong}.
 
-In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels.
+Strong interaction of a quantum system with light lead to various phenomena explained by resonant single- and multi-photon excitation of transitions between energy levels.
 The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.
 
-In this work, we are studying effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule (SAM).
-In our experiment, we use two transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
+In this work, we study effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM).
+In our experiment, we use two X-mons\cite{barends2013coherent} interacting with each other through a cavity bus\cite{majer2007coupling}.
 Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.
 
-It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we have discovered.
+It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we observe.
 The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
@@
 The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances.
-The capacitively coupled excitation line is also shown in green.
+A capacitively coupled excitation line is also shown in green.
 Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux.
-Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
+Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
 Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
-This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency.
+This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency.
 Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
@@
 Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
-From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green).
+Frequency control lines come from both sides, and from below a microwave excitation waveguide is connected (green).
 \textbf{(b)} The equivalent electrical circuit.
-Tunable Josephson junctions are in fact SQUIDs with magnetic flux control.
-\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly).
-In this work, we concentrate on the area inside the dashed rectangle.}
+Tunable Josephson junctions are SQUIDs with magnetic flux control.
+\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (proportional to the currents applied to control lines).
+In this work, we focus on the area inside the dashed rectangle.}
 	\label{fig:experiment}
@@
 
-\subsection{Theoretical description of the SAM}
+\subsection{Theoretical background}
 
 A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
+Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
 \begin{equation}
-\hat{{H}}_{tr} = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
+\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
 \end{equation}
-where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
+where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
 Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
@@
 
-To induce state transitions in a transmon one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
-The interaction term between the transmon and the field is then modelled by the following operator:
+To drive a quantum system, one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
+The driving term between the transmon and the field is then modelled by the following operator:
 \begin{equation}
-\hat H_{d} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
+\hat H_{d} = \hbar \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
 \end{equation}
-where $\Omega$ stands for the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.
+where $\Omega$ is the driving amplitude coinciding with the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.
 
@@
 \begin{equation}\label{Hsystem}
-\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
+\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
 \end{equation}
-where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
-In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
+where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
+In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
 \begin{align}
 &\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
+&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
 \end{align}
-After the transformation and application of the RWA:
+Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA:
 \begin{equation}
@@
 	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
-	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
-	\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
+	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
+	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
 \end{aligned}
@@
 \begin{equation}
-\partial_t \hat \rho = {i}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
+\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
 \end{equation}
@@
 
-The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM.
+The readout resonator is not included in the model since in the dispersive regime it does not affect the dynamics of the SAM.
 Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
@@
 Their frequency depends on the applied current, and at multiple points they become resonant with each other.
-At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numerals.
+At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numbers.
 Some secondary details are shown with Arabic-numbered markers.
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
 	\includegraphics[width=\linewidth]{topological_splittings}
-	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$ but at the same frequency.
-In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
+	\caption{Simulated population of the ground state when the transmons are driven at the same frequency but at different amplitudes $\Omega_{1,2}$.
+In the top row (middle row), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const} \ll \Omega_{1(2)}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
+In the bottom row, we show how the splittings vanish when the weaker driving is increased to match with the stronger one.
 Gray dashed lines show the stationary solution, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
 	\label{fig:difdrive}
-\end{figure}
+\end{figure*}
 
@@
 Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$.
-However, as we have demonstrated in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
+However, as we demonstrate in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
 
@@
 \omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
-\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
-\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
-\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
+\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
+\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
+\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
 \end{aligned}
@@
 To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
-In these conditions, $H^D$ becomes degenerate as can be seen below in \eqref{eq:ham_matrix}:
+In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:H_mat}.
 
@@
 \end{aligned}
+\label{eq:two-photon}
 \end{equation}
@@
 \Omega_1^R \pm \Omega_2^R = 0.
+\label{eq:zero-photon}
 \end{equation}
@@
 
+\section{Discussion}
+
+We have performed spectroscopy measurements of an isolated diatomic superconducting artificial molecule (SAM) in a regime of strong interaction with classical light.
+Using joint dispersive readout to directly access population of the SAM eigenstates, we have located several anomalies in the spectral data that were impossible to explain using the simple stationary model of the system.
+By using extensive numerical modelling explicitly including the interaction with light, we have reproduced the experimentally discovered effects and attributed them to an altered version of the well-known Autler-Townes effect.
+
+In the standard A-T effect, the coupler and the probe tone are separated in frequency and power.
+In our case, there is only a single spectroscopic frequency interacting with the system; therefore, the is has to be the coupler tone and the probe tone at the same time.
+However, since there are two components in the driving operator (one for each transmon), the separation between the coupler and the probe may be in the Hilbert space rather than in frequency.
+Moreover, the effectively weak driving for the probe is achieved when it stimulates a two-photon transition while the coupler tone is resonant with a single-photon one and is dressing the system.
+We have build a self-consistent model in the frame rotating with the dressed qubit to model the experimental splittings induced by the same field that probes them, and found a good agreement between the model, the experiment, and the numerical simulation.
+Interestingly, just as in the standard A-T effect on transmons reported previously, no new transitions appear in this more complex case.
+Instead, for example, spectral lines $12/3$ (three-photon) and $10-02$ (single photon) form an avoided crossing of a non-standard size of $\frac{2\sqrt{3}}{3} \Omega_1$.
+
+Another interesting effect occurs when both components of the driving operator are in the single-photon regime.
+Now, both transmons are dressed and probed simultaneously.
+In this case, the $11/2$ transition is split at the resonance into a hyperbolic curve, never forming a doublet in frequency.
+Moreover, its shape and visibility depends on the relation between the driving amplitudes: if they are equal, it disappears completely.
+In our sample, we have a fixed ratio of approximately 2 between $\Omega_1$ and $\Omega_2$ which allows us to distinguish the splitting experimentally.
+In additional simulations with full freedom of choice for the parameter values, we have studied this effect in detail and observed two possible topologically different configurations of this splitting depending on which driving amplitude is larger.
+Notably, the frequency of $11/2$ transition far from resonance is also changed noticeably with changing power, which means that a fast bSWAP gate should be performed at a different frequency than the stationary model predicts.
+
+Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may change their order.
+For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \eqref{eq:two-photon}, and a two-photon to a zero-photon in \eqref{eq:zero-photon}.
+
+In overall, irradiating an individual diatomic artificial molecule with intense light calls forth a plethora of effects which can not be directly observed in natural systems and extend the validity of the well-known light-dressing models.
+Relative ease in attaining powers that cause multiphoton transitions promises even more complex dynamics in multi-atom systems.
+We are looking forward to investigating strong interaction with light in larger artificial structures such as one-dimensional and two dimensional chains and arrays of superconducting artificial atoms.
+
 \appendix
@@
 
-\begin{figure}
+\begin{figure}[b]	
 	\includegraphics[width=\linewidth]{intro_scheme}
@@
 \hat R = \left[\begin{matrix} 
-1 & 0 & 0\\0 & e^{i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
+1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
 \]
 Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$.
-The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R + i \dot{\hat{R}}^\dag \hat R$.
+The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R - i \hat{R}^\dag \partial_t  \hat R$.
 The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b).
@@
 
-\section{The dressed Hamiltonian in the matrix form}
+\section{The dressed Hamiltonian in the matrix form} \label{sec:H_mat}
 
-\vspace{1cm}
+Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \eqref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
+
+Note that $\hat V_J = \hat S^T \hat H_{int} \hat S$ now has an sub- and super-diagonal block form coupling all the states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, \ket{b,j+1}$.
+
+The degeneracy between states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, \ket{b,2}$ occurs only in the resonant case $2\Delta_2   + \alpha_2 = 0$ meaning that the second transmon frame is rotated at its two-photon transition frequency.
+In this situation, its single-photon subspace is detuned by $-\alpha/2$.
 

### 2019-11-26 Pictures/Plotting/MainPicturePlot.py

@@ -46,7 +46,7 @@ class MainPicturePlot:
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current [$10^{-4}$ A]');
-        ax.set_ylabel('Frequency [GHz]');
+        ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
         cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$", position=(1.125,-1.5))
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc

### 2019-11-26 Pictures/Plotting/Powerscan.py

@@ -30,7 +30,7 @@ class ZoomPlot:
 
             m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 2 == 0:
-                ax.set_ylabel('Frequency [GHz]');
+                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
                 ax.yaxis.set_major_locator(MultipleLocator(0.01))
             if idx > 1:
                 ax.set_xlabel('Current [$10^{-4}$ A]');

### 2019-11-26 Pictures/Plotting/TopologicalSplitting.py

@@ -15,6 +15,9 @@ class TopologicalSplitting:
     def __init__(self):
         with open('10-01-11.pkl', 'rb') as f:
             self._X, self._Y, self._plots = pickle.load(f)
+        with open('10-01-11-2.pkl', 'rb') as f:
+            dummy1, dummy2, plots2 = pickle.load(f)
+            self._plots += plots2
         with open("transitions.pkl", "rb") as f:
             self._currs, self._transitions_1, self._transitions_2 = pickle.load(f)
 
@@ -23,17 +26,20 @@ class TopologicalSplitting:
                         (45, 7.5),
                         (7.5, 15),
                         (7.5, 30),
-                        (7.5, 45)])
+                        (7.5, 45),
+                        (15, 45),
+                        (30, 45),
+                        (45, 45)])
 
-        fig, axes = plt.subplots(3, 2, sharex=True, sharey=True, figsize=(5, 5))
+        fig, axes = plt.subplots(3, 3, sharex=True, sharey=True, figsize=(10, 5))
         plt.subplots_adjust(wspace=.1, hspace=.2)
 
-        for idx, ax in enumerate(axes.T.ravel()):
+        for idx, ax in enumerate(axes.ravel()):
             m = ax.pcolormesh(self._X, self._Y, array(self._plots[idx]).T,
                               vmin=0, vmax=1, cmap="Spectral", rasterized=True)
-            if idx in [2, 5]:
+            if idx in [8, 7, 6]:
                 ax.set_xlabel("Current [$10^{-4}$ A]")
-            if idx < 3:
+            if idx in [0, 3, 6]:
                 ax.set_ylabel("$\omega_d^{1,2}/2\pi$ [GHz]")
             if idx in [0]:
                 plt.text(.5, .7, "$\Omega_1: {0}$ MHz\n$\Omega_2: {1}$ MHz".format(Omegas[idx][0],
@@ -114,13 +120,13 @@ class TopologicalSplitting:
 
         plt.text(.42, .45, "11/2", fontsize=10,
                  transform=axes[0, 0].transAxes,
-                 ha='center', color="black", rotation=12.5)
+                 ha='center', color="black", rotation=10)
 
         plt.text(.61, .26, "02/2", fontsize=10,
                  transform=axes[0, 0].transAxes,
-                 ha='center', color="black", rotation=-55)
[…]

### 2019-11-26 Pictures/Plotting/ZoomPlot.py

@@ -22,7 +22,7 @@ class ZoomPlot:
             m = ax.pcolormesh(self._X, self._Y, real(array(self._plots[idx]).T),
                               vmax=1, vmin=0, rasterized=True, cmap="Spectral")
             if idx % 2 == 0:
-                ax.set_ylabel('Frequency [GHz]');
+                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
             if idx > 1:
                 ax.set_xlabel('Current [$10^{-4}$ A]');
 

### 2019-12-02 document.tex
Picture fixes

@@
 \documentclass[%
- aip,
+ pra,
 % jmp,
@@
 		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
+	}
+	\affiliation{
+		National University of Science and Technology MISiS, Moscow, Russia
 	}%
-
 	\author{V.B. Yursa}
@@
 \end{equation}
-where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
+where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or from ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
 Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
@@
 \end{align}
-Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA:
+Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
 \begin{equation}
@@
 The first one is for the Liouvillians that do not explicitly depend on time (stationary case).
-In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}:
+In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}
 \begin{equation}
@@
 Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}.
-Upon infinite applications of $\Lambda$:
+Upon infinite applications of $\Lambda$
 \[
@@
 	\includegraphics[width=\linewidth]{main_picture}
+
+	\includegraphics[width=.55\linewidth]{stationary}
 	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}.
@@
 Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
-We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.}
+We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.
+\textbf{(c)} Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
+Lines show various transition frequencies from the stationary Hamiltonian.
+The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
 	\label{fig:two-tone}
 \end{figure*}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{stationary}
-	\caption{Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
-Lines show various transition frequencies from the stationary Hamiltonian.
-The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
-	\label{fig:statinary_levels}
-\end{figure}
 
@@
 Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
-We confirm this by numerically diagonalizing $\hat H_{tr1}+\hat H_{tr2}+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:statinary_levels}.
+We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(c).
 While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects.
@@
 	\includegraphics[width=.49\linewidth]{zoom2_picture}
+
+	\includegraphics[width=.7\linewidth]{powerscan_1d}
 	\caption{Power dependence of feature II: experiment and theory.
@@
 \textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}.
-Note that now colours show the population of the ground state.}
+Note that now colours show the population of the ground state.
+\textbf{(c)} Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV.
+From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
 	\label{fig:zoom}
 \end{figure*}
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{powerscan_1d}
-	\caption{Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV.
-From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
-	\label{fig:splitting_linear}
-\end{figure}
 
@@
 
-\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:statinary_levels}).
+\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:two-tone}~(c)).
 In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process.
@@
 
-From \autoref{fig:statinary_levels} we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
-The latter process is discernible in \autoref{fig:statinary_levels} as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}.
+From \autoref{fig:two-tone}~(c) we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
+The latter process is discernible in \autoref{fig:two-tone}~(c) as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}.
 In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$.
@@
 To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}.
-By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:splitting_linear}).
+By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:zoom}~(c)).
 
@@
 
-\paragraph{Secondary features.} Using \autoref{fig:statinary_levels}, we can get an insight into the features 1 -- 5 as well.
+\paragraph{Secondary features.} Using \autoref{fig:two-tone}~(c), we can get an insight into the features 1 -- 5 as well.
 
@@
 
-Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:statinary_levels}).
+Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:two-tone}~(c)).
 It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise.
@@
 \begin{equation}
-R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)]
+R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)].
 \end{equation}  
-Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$:
+Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$. Now,
 \begin{equation}
@@
 Since $\hat H_{d}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
-After that, the Hamiltonian may be split into three parts:
+After that, the Hamiltonian may be split into three parts
 \begin{equation}
 \begin{aligned}
-\hat H^{D} &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
+\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
 \hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
@@
 The first part is diagonal, and the remaining two will be treated as perturbations.
-To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
-In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:H_mat}.
+To simplify further calculations, we consider the point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
+In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:dpt}.
+Using the degenerate perturbation theory for $\hat V_J$ summarized therein, we find the first-order corrected wave functions of $\hat H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.
 
-Using the degenerate perturbation theory with $\hat V_J$ summarized in Appendix \ref{sec:dpt}, we have found the first-order corrected wave functions of $\hat H^D$, labelled $\ket{k},\ k=1..6$.
+The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}.
+Using the corrected eigenstates $\ket{k}$ and neglecting small terms we obtain the following expression for the transition rates per unit time\cite{faisal2013theory}:
+\begin{equation}
+\begin{aligned}
+R^{(2)}_{1\rightarrow 6} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1$}\right)^2}{\alpha ^{6}\Omega_1^2},\\
+R^{(2)}_{2\rightarrow 5} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
+		$}\right)^2}{\alpha ^{6}\Omega_1^2}.
+\end{aligned}\label{eq:rates}
+\end{equation}
+From \eqref{eq:rates} follows that the sideband transitions are prohibited without the interaction in the SAM $(J=0)$, and the extra avoided crossings will not be observed.
 
-The theory for two-photon processes is given in Appendix \ref{sec:2pp}.
-The probability rate of two-photon transition per unit interaction time using corrected eigenstates $\ket{k}$ and neglecting small terms we obtain:
+\paragraph{Feature I.} Finally, we discuss the last Roman-numbered effect.
+It is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$: the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
+For the opposite case ($\Omega_1 \gg \Omega_2$), the logic is the same.
 
-\begin{equation}
-A^{(2)}_{1\rightarrow 6} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1
-		$}\right)^2}{\alpha ^{6}\Omega_1^2}
-\end{equation}
-\begin{equation}
-A^{(2)}_{2\rightarrow 5} = 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
-		$}\right)^2}{\alpha ^{6}\Omega_1^2}
-\end{equation}
-From here it follows that in the studied SAM the sideband transitions are prohibited without interaction $(J=0)$ even in the second order, and the avoided crossing we are interested can not be observed.
-
-\paragraph{Feature I.} Finally, we discuss the last of the dressing effects observed in the SAM.
-Its explanation is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$.
-In this case, the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
-For the opposite case, the explanation is the same.
-As one can see, only the two-photon transition $11/2$ is affected.
-When the transitions $01$ and $10$ are close resonance, its frequency is $\omega_{11/2} \approx \omega_1 \approx \omega_2$ Similarly to the previous case with II and III, in the dressed basis, this transitions becomes a single-photon doublet transition for $\hat H_d^2$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
-Note that in the experiment with only a single excitation frequency, it is not possible to observe both transitions at the same magnetic flux, and this is clearly visible in \autoref{fig:difdrive}.
+As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and experiences a frequency shift approaching the 01-10 intersection while the other spectral lines are not moving.
+Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
+We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}.
 Instead, we observe one line to the left and the other to the right from the $01-10$ intersection.
-This behaviour will be explained in the following section.
 
@@
 Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$.
-In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are:
+In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are
 \begin{equation}
@@
 
-Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ both at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear:
+Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ both at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear at
 \begin{equation}
@@
 \omega_{(10-02)/2} &= \omega_d,\\
-\omega_{12/2} &= \omega_d
+\omega_{12/2} &= \omega_d.
 \end{aligned}
@@
 When $\Omega_1 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_1 - \omega_d|$.
-Intriguingly, they are the three-photon and single-photon transition frequencies in the laboratory frame:
+Intriguingly, they are the three-photon and single-photon transition frequencies in the laboratory frame
 \begin{equation}
-\omega_d = \begin{cases} \frac{\alpha_2}{3} + \frac{2 \omega_{2}}{3} + \frac{\omega_{1}}{3}, \\ \alpha_2 + 2 \omega_{2} - \omega_{1}\end{cases}
+\omega_d = \begin{cases} \frac{\alpha_2}{3} + \frac{2 \omega_{2}}{3} + \frac{\omega_{1}}{3}, \\ \alpha_2 + 2 \omega_{2} - \omega_{1}.\end{cases}
 \end{equation}
@@
 \begin{equation}
-\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{2}}{3} - \frac{\omega_{1}}{3} \pm \frac{\sqrt{3 \Omega_{1}^{2} + \left( \alpha_2 + 2 (\omega_{2} - \omega_{1})\right)^{2}}}{3}
+\omega_d = \frac{2 \alpha_2}{3} + \frac{4 \omega_{2}}{3} - \frac{\omega_{1}}{3} \pm \frac{\sqrt{3 \Omega_{1}^{2} + \left( \alpha_2 + 2 (\omega_{2} - \omega_{1})\right)^{2}}}{3}.
 \label{eq:splitting_model}
@@
 The only free parameter left was $\Omega_2$.
-We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting on excitation amplitude (see \autoref{fig:splitting_linear}).
+We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting on excitation amplitude (see \autoref{fig:zoom}~(c)).
 
@@
 
-Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may change their order.
-For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \eqref{eq:two-photon}, and a two-photon to a zero-photon in \eqref{eq:zero-photon}.
+Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may smoothly change their order.
+For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \eqref{eq:two-photon}, and of a two-photon transition to a zero-photon in \eqref{eq:zero-photon}.
 
@@
 We are looking forward to investigating strong interaction with light in larger artificial structures such as one-dimensional and two dimensional chains and arrays of superconducting artificial atoms.
+
+\section{Acknowledgements}
+
+We want to thank our parents and our cat Coconut. Also FPI grant
 
@@
 \begin{equation*}
-\hat H^c_0 = \left[\begin{matrix}
+\hat H^c_0/\hbar = \left[\begin{matrix}
 0 & \Omega_{1} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
@@
 \begin{equation*}
-\hat H^c_1 = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{i t \omega_p}/2\\0 & \Omega_{2} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
+\hat H^c_1/\hbar = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{i t \omega_p}/2\\0 & \Omega_{2} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
 \end{equation*}
@@
 \begin{equation*}
-\hat H^c_3 = \left[\begin{matrix} 
+\hat H^c_3/\hbar = \left[\begin{matrix} 
 \frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
@@
 \begin{split}
-\hat H^q_0 = \omega_{01} \ket{1}\bra{1} + \omega_{02} \ket{2}\bra{2} + (\omega_{01}-\Delta) \hat a^\dag \hat a + \\\ g (\hat a^\dag + \hat a)\otimes (\ket{1}\bra{0}+\ket{0}\bra{1}),
+\hat H^q_0/\hbar = \omega_{01} \ket{1}\bra{1} + \omega_{02} \ket{2}\bra{2} + (\omega_{01}-\Delta) \hat a^\dag \hat a + \\\ g (\hat a^\dag + \hat a)\otimes (\ket{1}\bra{0}+\ket{0}\bra{1}),
 \end{split}
@@
 After moving to the rotating frame with $\hat R = \exp[i t (\omega_{01}-\Delta)(\hat a^\dag \hat a + \ket{1}\bra{1}+\ket{2}\bra{2})]$ and applying the RWA, the Hamiltonian transforms into
-\[
+\begin{equation}
 \begin{split}
-\hat H^q_1 = \Delta \ket{1}\bra{1} + (\omega_{12}+\Delta) \ket{2}\bra{2} + \\\ g \left[\hat a^\dag \otimes \ket{0}\bra{1} + \hat a \otimes \ket{1}\bra{0}\right].
+\hat H^q_1/\hbar = \Delta \ket{1}\bra{1} + (\omega_{12}+\Delta) \ket{2}\bra{2} + \\\ g \left[\hat a^\dag \otimes \ket{0}\bra{1} + \hat a \otimes \ket{1}\bra{0}\right].
 \end{split}
-\]
+\end{equation}
 If we presume that the resonator is in a coherent state $\ket{\alpha e^{-it(\omega_{01}-\Delta)}}$ with $\langle N\rangle = \alpha^2$ photons and average $\hat H_1^q$ over the resonator subspace, we from the interaction term will obtain again the classical driving strength $\Omega_1 = 2 \sqrt{\langle N \rangle} g$ in correspondence with the classical driving case.
-Similarly, the energy levels $\ket{1, N-1}$ and $\ket{0, N}$ become mixed due to the coupling, and their splitting changes from $\Delta$ to $\Omega_R = \sqrt{\Omega_1+\Delta}$.
+Similarly, the energy levels $\ket{1, N-1}$ and $\ket{0, N}$ become mixed due to the coupling, and their splitting changes from $\hbar\Delta$ to $\hbar\Omega_R = \hbar\sqrt{\Omega_1+\Delta}$.
 The following steps completely reproduce the classical case if we add the probe tone $\Omega_2$ in the last equation.
 
-\section{The dressed Hamiltonian in the matrix form} \label{sec:H_mat}
+\section{Degenerate perturbation theory}
+\label{sec:dpt}
 
 Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \eqref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
-
-Note that $\hat V_J = \hat S^T \hat H_{int} \hat S$ now has an sub- and super-diagonal block form coupling all the states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, \ket{b,j+1}$.
-
 The degeneracy between states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, \ket{b,2}$ occurs only in the resonant case $2\Delta_2   + \alpha_2 = 0$ meaning that the second transmon frame is rotated at its two-photon transition frequency.
 In this situation, its single-photon subspace is detuned by $-\alpha/2$.
+
+Note that $\hat V_J = \hat S^T \hat H_{int} \hat S$ that we treat as perturbation now has an sub- and super-diagonal block form and couples all the states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, \ket{b,j+1}$.
 
@@
 
-\section{Degenerate perturbation theory} \label{sec:dpt}
+The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation.
+However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace.
+Unfortunately, $\hat V$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V$.
+In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
 \begin{equation}
-H^R=H_0+V_J
+	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
 \end{equation}
-At our working point the equation $\Delta_2=\alpha/2$ is true and $H_0$ becomes degenerate. Let's consider our system in the basis of dressed states.
+Here, $\ket{n}$ and $\ket{n'}$ are the basis states from the degenerate subspace with energy $E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$.
+The sum is over all other zero-order states $\ket{m}$ outside the degenerate subspace.
+
+For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$)
+\renewcommand{\kbldelim}{[}% Left delimiter
+\renewcommand{\kbrdelim}{]}% Right delimiter
 \begin{equation}
-H_0^{d}= diag(-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2},\frac{(-\alpha-\Omega_{1})}{2},\frac{-\alpha+\Omega_{1}}{2},-\frac{\Omega_{1}}{2},\frac{\Omega_{1}}{2})
+	M_{15} =\kbordermatrix{&\ket{a,0} & \ket{a, 2}\\
+	\ket{a,0}&\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
+	\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\
+	\ket{a, 2}&\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
+	\frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}}.
 \end{equation}
-The choice of wave functions from a degenerate subspace is arbitrary because any linear combination of functions from this subspace will satisfy the Schrodinger equation.
-However, if we demand that the change of wave functions be small under the applied small perturbation, then the choice of wave functions become defined.
-To obtain correct wave functions we need to diagonalize $V_J^{d}$ in the degenerate subspace.
-However, we can notice that $V_J^{d}$ is identically the zero matrix in our subspace, so technically any choice of basis will diagonalize $V_J^{d}$.
-This means that the degeneracy is not lifted at first-order in perturbation theory.
-We have to pick eigenvectors which diagonalize following matrix:
+The normalized eigenvectors 
 \begin{equation}
-	\begin{matrix}
-	M_{nn'} = \sum_{m}\frac{V_{nm}V_{mn'}}{E_n-E_m}
-	\end{matrix}
+\ket{N} = C_n \ket{n} + C_{n'}\ket{n'}, 
+\ket{N'} = C'_{n}\ket{n} + C'_{n'}\ket{n'}
 \end{equation}
-Where $\ket{n}$ and $\ket{n'}$ are states with same energy $E_n$.  The sum is over all states $m$ not in the degenerate subspace.
-For example, in our case for one of degenerate subspaces:
+of the matrix are the desired zero-order superpositions. Next, we first-order correct them as usual:
 \begin{equation}
-	M_{15} =\left[\begin{matrix}\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} & \frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}\end{matrix}\right]
-\end{equation}
-The normalized eigenvectors $(C_n,C_{n'})$ of the matrix will give the desired zero approximation wave-functions.
-The first-order correction to the states from degenerate subspace:
-\begin{equation}
-	\ket{n^0}+\ket{n^1} = \sum_n C_{n}\ket{n^0} + \sum_{m\ne n}\ket{m^0}\frac{\bra{m^0}V\ket{n^0}}{E_n^0-E_m^0}
-\end{equation}
-The sum is over all states $n$ in the degenerate subspace $n=(n,n')$.
-The first-order corrections for not degenerate state compute by using the ordinary perturbation theory.
-\begin{equation}
-	\ket{j^1} = \sum_{m\ne j}\ket{m^0}\frac{\bra{m^0}V\ket{j^0}}{E_j^0-E_m^0}
+	\ket{N}+\ket{N^{1}} = \sum_{j=n,n'} C_{j}\ket{j} + \sum_{j\ne n, n'}\ket{j}\frac{\bra{j}\hat V\ket{N}}{E_n-E_j}.
 \end{equation}
 
-\section{Theoretical description of two-photon process}\label{sec:2pp}
-Perturbation theory allows semianalytical calculation of the transition rates for single and multi-photon processes\cite{faisal2013theory}.
-
-Let's consider the Hamiltonian $H = H_0+V(t)$, with time-dependent interaction $V(t)$ and "reference" part -- $H_0$ and wave function $\Psi(t)$.
-After switching to the interaction picture $V(t)$ modifies to $\tilde{V}(t) = \exp(i H_0 t)V(t)\exp(-i H_0 t)$ and Schrödinger equation gives by $i \derivative{\psi(t)}{t}=\tilde{V}(t)\psi(t)$, where $\psi(t)=\exp(i H_0 t)\Psi(t)$.
-The reference states of $H_0$ will be denoted $\ket{j}$, $H_0 \ket{j} = \omega_j \ket{j}$ whence it follows that matrix elements  of the modified interaction take the form $\bra{j}\tilde{V}(t)\ket{i}=\exp(i(\omega_j-\omega_i)t)\bra{j}V(t)\ket{i}$.
-A "solution" of Schrödinger equation in interaction picture corresponding to the initial reference state $\ket{i}$ is
-
-\begin{equation}\label{forpsi}
-	\tilde{\psi_i}(t)=\ket{i} - i \int_{-\infty}^{t}dt_1\tilde{V}(t_1)\ket{\tilde{\psi_i}(t_1)}
+Similarly, the first-order corrections for a non-degenerate state are
+\begin{equation}
+	\ket{m^1} = \sum_{j\ne m}\ket{m}\frac{\bra{j}\hat V\ket{m}}{E_m-E_j}.
 \end{equation}
 
-Mainly important for us is to find not the wave function but the probability of transition from the initial state $\ket{i}\rightarrow\ket{f}$, where $\ket{f}$ is the final state.
-Firstly, we find the transition amplitude $A_{fi} = \bra{f}U(t,t_0)\ket{i}=\bra{f}\psi_i(t)$ where $U(t,t_0)$ evolution operator.
+\section{Transition rates of the two-photon process}\label{sec:2pp}
+We will employ the time-dependent perturbation theory that gives analytical expressions for the transition rates for single and multi-photon processes\cite{faisal2013theory}.
 
-Solving \autoref{forpsi} by simple iteration gives the series solution
+Let's consider a time-dependent perturbation $\hat V(t) = \hat V \cos{\omega_d t}$ to the unperturbed Hamiltonian $\hat H$. In the interaction picture, the Schrödinger equation looks as 
+$$
+i\hbar \partial_t{\psi(t)} = \hat {V_I}(t)\psi(t),
+$$ 
+where 
+$$
+\hat {V}_I(t) = e^{\frac{it}{\hbar}\hat H}\hat V(t)e^{-\frac{it}{\hbar}\hat H}.
+$$
+The eigenstate of $\hat H$ with eigenvalue $E_j$ will be denoted as $\ket{j}$, whence it follows that
+$$
+\bra{j}\hat{V}_I(t)\ket{i} = e^{i\omega_{ij} t}\bra{j}\hat V(t)\ket{i},
+$$
+where $\hbar \omega_{ij} = E_j - E_i$. Formally, we can write down the solution of the Schrödinger equation in the interaction picture corresponding to the initial state $\ket{i}$ as
+\begin{equation}\label{forpsi}
+	\ket{\psi_i(t)}=\ket{i} - i \int_{-\infty}^{t} d\tau_1 \hat{V}_I(\tau_1)\ket{{\psi_i}(\tau_1)}.
+\end{equation} 
+Solving \eqref{forpsi} by simple iterations gives the series solution for it:
+\begin{align}
+	U(t,-\infty) &= 1 + \sum_{n} U^{(n)}(t,-\infty),\\
+	U^{(n)}(t,-\infty) &= -i^n \int\limits_{-\infty}^{t}d \tau_1\hat V_I(\tau_1)...\int\limits_{-\infty}^{\tau_{n-1}}d \tau_n\hat{V}_I(\tau_n),
+\end{align}
+where $U(t,-\infty)$ is the evolution operator.
+For a weak perturbation, this series may be truncated at a finite term $n$, and the $n^{\text{th}}$ order transition amplitude $\bra{f}U^{(n)}(t,-\infty)\ket{i}$ can be evaluated:
 \begin{equation}
-	U(t,t_0) = 1+\sum_{n}U^{(n)}(t,t_0)
+	\begin{aligned}
+	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-i\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-i\frac{\Omega}{2}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{B}\ket{i}+\\
+	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{B}\ket{i}\big].
+	\end{aligned}
 \end{equation}
 \begin{equation}
-	U^{(n)}(t,t_0) = -i^n \int_{t_0}^{t}d t_1\tilde{V}(t_1)...\int_{t_0}^{t_{n-1}}d t_n\tilde{V}(t_n)
+	\begin{aligned}
+	\bra{f}U^{(2)}(t,-\infty)\ket{i}=-\bra{f}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\int\limits_{-\infty}^{\tau_1}d\tau_2\hat{V}_I(\tau_2)\ket{i}=\\
+	-\sum_j\int\limits_{-\infty}^{t}d\tau_1 e^{i\omega_{jf}\tau_1}\bra{f}\hat V(\tau_1)\ket{j}\int\limits_{-\infty}^{\tau_1}d\tau_2 e^{i\omega_{ij}\tau_2}\bra{j}\hat V(\tau_2)\ket{i}.
+	\end{aligned}
 \end{equation}
-For "weak" interaction the series may be truncated to a fine term $n$ and the $n$th- order transition amplitude $\bra{f}U^{(n)}(t,t_0)\ket{i}$ can be evaluated. 
-In our case the interaction in interaction picture satisfies the following relation
+Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives\cite{faisal2013theory}
 \begin{equation}
 	\begin{split}
-	\tilde{V}(t)=\exp(i H_0 t) \Omega\cos(\omega_d t)(\hat b+\hat b^{\dagger})\exp(-i H_0 t)=\\\frac{\Omega}{2} \exp(i H_0 t) \hat{B}(e^{-i\omega_d t}+e^{i\omega_d t})\exp(-i H_0 t)
+	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\{2\pi i}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
+	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg].
 	\end{split}
 \end{equation}
-Where, $\hat{b}^{\dagger}+\hat{b}=\hat{B}$.
-Taking the matrix element between the initial and the final states $\ket{i}$ and $\ket{f}$, one immediately obtains
+The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is the square modulus of the corresponding amplitude, $P^{(2)}_{i\rightarrow f}= |\bra{f}\hat U^{(2)}(\infty, -\infty)\ket{i}|^2$.
+The rate (probability per unit interaction time $T$) of absorption of $2$ photons is defined as
 \begin{equation}
-	\begin{split}
-	\bra{f}U^{(1)}(t,t_0)\ket{i}=-i\int_{t_0}^{t}dt_1\tilde{V}(t_1)=\\-i\frac{\Omega}{2}\big[\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i-\omega_d)t_1}\bra{f}\hat{B}\ket{i}+\\
-	\int_{t_0}^{t}dt_1e^{i(\omega_f-\omega_i+\omega_d)t_1}\bra{f}\hat{B}\ket{i}\big]
-	\end{split}
+	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}.
 \end{equation}
-To calculate second-order term we used the following expression $\sum_{j}\ket{j}\bra{j}=\mathbbm{1}$.
-\begin{equation}
-	\begin{split}
-	\bra{f}U^{(2)}(t,t_0)\ket{i}=-\bra{f}\int_{t_0}^{t}dt_1\tilde{V}(t_1)\mathbbm{1}\int_{t_0}^{t_1}dt_2\tilde{V}(t_2)\ket{i}=\\-\int_{t_0}^{t}dt_1 e^{i(\omega_f-\omega_j)t_1}\bra{f}V(t_1)\ket{j}\int_{t_0}^{t_1}dt_2e^{i(\omega_j-\omega_i)t_2}\bra{j}V(t_2)\ket{i}
-	\end{split}
+To cancel out one of the delta functions in the resulting expression, we can use the identity 
+\begin{equation}\nonumber
+	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_{if}-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}.
 \end{equation} 
-Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives
-\begin{equation}
-	\begin{split}
-	\bra{f}U^{(2)}(\infty)\ket{i}=\\\frac{\pi i\Omega^2}{2}\bigg[\delta(\omega_f-\omega_i+2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
-	\delta(\omega_f-\omega_i)\bigg(\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i+\omega_d}+\\
-	\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg)+\\
-	\delta(\omega_f-\omega_i-2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg]
-	\end{split}
-\end{equation}
-The probability of two-photon transition from state $\ket{i}$ to state $\ket{f}$ is simply the square modulus of the corresponding amplitude.
-So, $P^{(2)}_{i\rightarrow f}= |	\bra{f}U^{(2)}(\infty)\ket{i}|^2$.
-The rate (probability per unit interaction time T) of absorption of $2$ photons is defined as:
-\begin{equation}
-	W^{(2)}_{i\rightarrow f}=\lim\limits_{T\rightarrow\infty}\frac{P^{(2)}_{i\rightarrow f}}{T}
-\end{equation}
-For simplifier the equation we have made use of the relation:
-\begin{equation}\nonumber
-	\delta(\omega_f-\omega_i-2\omega_d) =\frac{1}{2\pi} \lim\limits_{T\rightarrow\infty}\int_{-T/2}^{T/2}e^{i(\omega_f-\omega_i-2\omega_d)t}dt = \lim\limits_{T\rightarrow\infty}\frac{T}{2\pi}
-\end{equation} 
-For $\omega_f=\omega_i+2\omega_d$.
+In overall, for $\omega_d=\omega_{if}/2$:
 \begin{equation}\label{prob}
-\begin{split}
-	W^{(2)}_{i\rightarrow f}=\frac{\pi\Omega^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_j-\omega_i-\omega_d}\bigg|^2\delta(\omega_f-\omega_i-2\omega_d)=\\ A^{(2)}_{i\rightarrow f}\delta(\omega_f-\omega_i-2\omega_d)
-\end{split}
+\begin{aligned}
+	W^{(2)}_{i\rightarrow f}&=2\pi\bigg|\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
+	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}-2\omega_d).
+\end{aligned}
 \end{equation}

### 2019-12-02 Pictures/Plotting/MainPicturePlot.py

@@ -64,14 +64,14 @@ class MainPicturePlot:
                     arrowprops=dict(facecolor='black', width =1, headwidth = 5, headlength = 7, shrink=0.05))
 
 
-        ax.annotate("1", xy=(3.48, 5.23), xytext=(3.55, 5.21), ha="center", fontsize=10,
+        ax.annotate("1", xy=(3.5, 5.2325), xytext=(3.64, 5.2075), ha="right", fontsize=10,
                     arrowprops=dict(facecolor='black', width =.5, headwidth = 3, headlength = 3.5, shrink=0.05))
 
-        ax.annotate('2', xy=(5.07, 5.21), xytext=(5.07, 5.185), ha="center", fontsize=10,
+        ax.annotate('2', xy=(5.07, 5.21), xytext=(5.07, 5.18), ha="center", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.26), ha="center", fontsize=10,
+        ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.265), ha="center", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
@@ -79,7 +79,7 @@ class MainPicturePlot:
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        ax.annotate("5", xy=(3.515, 5.177), xytext=(3.585, 5.1795), ha="center", va="bottom", fontsize=10,
+        ax.annotate("5", xy=(3.516, 5.177), xytext=(3.61, 5.1795), ha="center", va="bottom", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
@@ -111,15 +111,15 @@ class MainPicturePlot:
         cb.locator = loc
         cb.update_ticks()
 
-        ax.annotate("1", xy=(3.48, 5.23), xytext=(3.55, 5.21), ha="center", fontsize=10,
+        ax.annotate("1", xy=(3.48, 5.23), xytext=(3.56, 5.205), ha="center", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
[…]

### 2019-12-02 Pictures/Plotting/StationaryPlot.py

@@ -15,7 +15,7 @@ class StationaryPlot:
         with open("stationary.pkl", "rb") as f:
             currs, freqs, population10, energies = pickle.load(f)
 
-        fig, ax = plt.subplots(1, 1, figsize=(4.25, 2.75), sharey=True)
+        fig, ax = plt.subplots(1, 1, figsize=(5, 3), sharey=True)
 
         # mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
         #                    cmap="Spectral_r")
@@ -42,15 +42,15 @@ class StationaryPlot:
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.26), ha="center", fontsize=10,
+        ax.annotate('3', xy=(3.31, 5.25), xytext=(3.31, 5.265), ha="center", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        ax.annotate('4', xy=(4.9, 5.195), xytext=(4.75, 5.195), ha="center", va="top", fontsize=10,
+        ax.annotate('4', xy=(4.9, 5.195), xytext=(4.76, 5.195), ha="center", va="top", fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
-        ax.annotate("5", xy=(3.5, 5.175), xytext=(3.65, 5.18), ha="center", va="center",
+        ax.annotate("5", xy=(3.5, 5.175), xytext=(3.63, 5.18), ha="center", va="center",
                     fontsize=10,
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
@@ -107,33 +107,33 @@ class StationaryPlot:
         plt.plot(currs, ((energies[:, 8].T - energies[:, 0]).T / 4), linestyle=typ2, linewidth=t,
                  color=secondary_colour);  # 00->22
 
-        plt.plot(currs, ((energies[:, 1].T - energies[:, 0]).T), label=r"$\left|10\right\rangle$",
[…]

### 2019-12-23 document.tex
Updates

@@
-% ****** Start of file aipsamp.tex ******
+% ****** Start of file aipsamp.tex ****m*
 %
@@
 \documentclass[%
- pra,
+ prx,
 % jmp,
@@
 \renewcommand*{\figureautorefname}{Fig.}
+\renewcommand*{\equationautorefname}{Eq.}
 
-\newcommand{\mytitile}{Effects of strong interaction between light and matter in a superconducting artificial molecule}
+\newcommand{\mytitile}{Light-dressing of a diatomic supercondufcing artificial molecule}
 
@@
 	\title[\mytitile]{\mytitile\\~}
-
 	\author{G.P. Fedorov}
@@
 	\affiliation{
-		National University of Science and Technology MISiS, Moscow, Russia
+		National University of Science and Technology MISIS, Moscow, Russia
 	}%
 	\author{V.B. Yursa}
+	\affiliation{ 
+		Skolkovo Institute of Science and Technology, Moscow, Russian Federation
+	}%
+
 \affiliation{ 
@@
 
+	\author{I.A. Rodionov}
+	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+
+	\author{A.A. Dobronosova}
+	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+
+	\author{D.O. Moskalev}
+	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
+
+	\author{A.A. Pischimova}
+	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+
 	\author{O.V. Astafiev}
@@
 		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
-	}%
+	}
+	\affiliation{Skolkovo Institute of Science and Technology, Moscow, Russian Federation}
+	\affiliation{Physics Department, Royal Holloway, University of London, Egham, Surrey TW20 0EX, United Kingdom}
+%
 
@@
 	\begin{abstract}
-	Since their demonstration, superconducting artificial atoms have been extensively used for studies in quantum optics.
-Their particular advantages compared to natural systems are the strong coupling to radiation and the high level of control over their state; these properties open the way to previously unexplored physics.
-In this work, we have irradiated a superconducting artificial molecule composed of two flux-tunable transmons with intense light while monitoring its state via joint dispersive readout.
-At certain configurations of its energy levels, the molecule has demonstrated a complex spectrum deviating qualitatively from the stationary solution.
-However, it was reproduced accurately by numerical simulations, and turned out to be a consequence of a modified Autler-Townes effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates.
-To quantify this effect, self-consistent models were employed accounting for both these processes at the same time.
-We note that this study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
+	In this work, we study a superconducting artificial molecule composed of two magnetic-flux-tunable transmons with intense light while monitoring its state via joint dispersive readout.
+At certain fluxes, the molecule demonstrates a complex spectrum deviating qualitatively from the solution of the Schrödinger equation without driving.
+We reproduce the observed extra spectral lines accurately by numerical simulations, and find them to be a consequence of an Autler-Townes-like effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates.
+We present self-consistent analytical models that account for both these processes at the same time and agree well with both experiment and numerical simulation.
+This study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
 	\end{abstract}
@@
 
-Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments confidently demonstrating the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
-Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered, and this makes them a particularly versatile tool for studies in quantum optics.
+Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments in a compelling demonstration of the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
+Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics.
 Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
-For example, the strong coupling regime, when the coupling strength between light and a quantum system approaches 1\% of their frequency, has been a major challenge for atoms, molecules, etc and was only reached using high-finesse cavities.
-In contrast, superconducting quantum systems have rapidly attained this milestone using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first demonstration\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
-Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime\cite{forn2019ultrastrong}.
 
-Strong interaction of a quantum system with light lead to various phenomena explained by resonant single- and multi-photon excitation of transitions between energy levels.
-The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.
+One of the most prominent milestones, that superconducting quantum circuits have attained just in a few years after their first demonstration, is the strong coupling with light in {circuit QED}\cite{wallraff2004strong, chiorescu2004coherent} meaning that the decoherence rates are smaller than the Rabi frequency.
+Currently, they are surpassing all other implementations of strong coupling in terms of coherence\cite{forn2019ultrastrong}.
+However, in sharp contrast with natural atoms and molecules, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all.
+The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is even beyond strong coupling regime\cite{forn2019ultrastrong}.
+To correctly describe the behaviour of an atom in these conditions, the so-called \textit{dressed atom approach}\cite{cohen1998atom} is employed when the radiation has to be directly included in the Hamiltonian and affects its level structure.
 
-In this work, we study effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM).
-In our experiment, we use two X-mons\cite{barends2013coherent} interacting with each other through a cavity bus\cite{majer2007coupling}.
-Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.
+So far, the main experiments in on-chip quantum optics with intense propagating light were focused on single artificial atoms\cite{baur2009measurement, sillanpaa2009autler, astafiev2010resonance, novikov2013autler, suri2013observation, koshino2013observation, braumuller2015multiphoton, peng2018vacuum, gasparinetti2019two}.
+In all these works, light dressing of the atom manifests itself through Mollow triplets or Autler-Townes splittings of different kinds.
+However, despite the recent successes in control of large arrays of interacting SAA\cite{Song574, ye2019propagation, arute2019quantum}, there were, up to our best knowledge, no experiments concerning interaction of such composite structures with intense propagating light.
+While studies has been done concerning dressing multi-atomic systems in a cavity\cite{fink2009dressed, macha2014implementation, shulga2017observation, yang2018probing}, their interaction with intense free radiation is also attractive since light frequency may be easily tuned to observe various absorption processes for arbitrary configurations of the system's parameters.
 
-It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we observe.
-The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
-However, the previous studies have  only involved just a single SAA and have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}); instead, a diatomic SAM allows to observe some qualitatively new spectral manifestations of the effect.
-Remarkably, besides its fundamental value, this experiment may be useful for future quantum computers: a quantum engineer should consider the observed behaviours as unwanted, and thus careful control of the driving power must be employed to avoid them (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
+In this work, we study an system of two strongly coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM).
+We use two Xmon-type\cite{barends2013coherent} transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
+Microwave radiation is applied to this system through an on-chip coplanar waveguide while its state can be monitored by dispersive readout using the same coupling cavity\cite{chow2010detecting}.
+We find that strong interaction of the SAM with microwaves calls forth multiphoton transitions and Autler-Townes-like effects that could only be explained in the dressed picture.
+We note that although the A-T splittings have been investigated before in a wide range of quantum systems (including natural molecules\cite{tamarat1995pump, ahmed2012autler}), we find some qualitatively new spectral manifestations of the dressing effect.
+One of the reasons for this is that the natural molecules which could in principle demonstrate such effects do not have enough controllability and coherence.
+Alternatively, previous studies with SAA have either involved just a single atom or have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}).
+
+Remarkably, besides its fundamental importance, this experiment may be useful for future quantum computers: a quantum engineer should account for the observed behaviours carefully controlling the driving power (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
 
 The manuscript consists of four main parts and an Appendix.
-Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research; finally, in Section IV we make a conclusion of our work and discuss future prospects.
+Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research, including extensive numerical simulations and analytical analysis; finally, in Section IV we make a conclusion of our work and discuss future prospects.
 The Appendix contains important details of the theoretical framework that we use.
@@
 \subsection{Device design and fabrication}
-We have designed the SAM as a pair of transmon (Xmon\cite{barends2013coherent}) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the qubits and allows the joint\cite{chow2010detecting} readout of their states.
+We have designed the SAM as a pair of transmon (Xmon) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} ($E^1_{J, \sum}/2\pi = 24.3$ GHz, $E^2_{J,\sum}/2\pi = 18.3$ GHz, $E^{1,2}_C = 220$ MHz, $d^{1,2} =0.75$) coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the transmons and allows the joint\cite{chow2010detecting} readout o	f their states.
 In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components.
@@
 Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux.
-Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
+Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second transmon (blue).
 Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
@@
 Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
-
-The fabrication process...
 
@@
 	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
-	$\alpha/2\pi$ [MHz] & 220 & 220 \\
+	$\alpha/2\pi$ [MHz] & -220 & -220 \\
 	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
 	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
-	$J/2\pi$ [MHz] &\multicolumn{2}{c}{10} 
+	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
 	\end{tabular}
@@
 	\caption{SAM parameters.
-Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.}
+Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.
+The coupling strength $J$ depends on the transmon frequencies and is specified here for $\omega_1 = \omega_2 = 5.32$ GHz.}
+	\label{tab:parameters}
 \end{table}
@@
 
-Now, the complete Hamiltonian of SAM contains two terms describing each of them in isolation (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
+Now, the complete Hamiltonian of SAM contains two terms describing each of them (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
@@
 where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
-In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
-\begin{align}
-&\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
-\end{align}
+Strictly speaking, $J = J(\omega_1, \omega_2)$ depends on the transmon frequencies\cite{koch2007charge}, but we take $J$ to be a constant as in \autoref{tab:parameters} due to its negligible variation for our range of frequencies.
+
+For brevity, the SAM Hamiltonian without driving terms and the corresponding eigenenergies will be denoted below as ``unperturbed''.
+
+In the following, we will also transform \autoref{Hsystem} into the frame rotating with both drives by an operator
+\begin{equation}
+\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}
+\end{equation}
+arriving at
+\begin{equation}
+\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
+\end{equation}
 Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
@@
 	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
-	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
+	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} + \hat b \hat c^\dag e^{-it(\omega_d^1 - \omega_d^2)}\right],\\
 	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
@@
 Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon.
-They are modelled using the Lindblad equation with the following collapse operators:
+They are modelled using the Lindblad equation with the following collapse operators\cite{bishop2010circuit}:
 \begin{equation}\
@@
 \hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
-\hat{{O}}_{\phi, 1} = \sqrt{2\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
+\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
 \hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
-\hat{{O}}_{\phi,2} = \sqrt{2\gamma_{ \phi,2}}\, \hat c^\dag \hat c.
+\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, \hat c^\dag \hat c,
 \end{split}
 \end{equation}
+where $\gamma_{1,2}$ are the individual relaxation rates, and $\gamma_{\phi (1,2)}$ are the pure dephasing rates.
 As one can see, the collapse operators are in a separable form, i.e.
@@
 
-Numerical simulations are crucial for studying the equation \eqref{eq:master} since is does not allow  analytical solution.
+Numerical simulations are crucial for studying \autoref{eq:master} since is does not allow  analytical solution.
 Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.
@@
 The first one is for the Liouvillians that do not explicitly depend on time (stationary case).
-In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \eqref{eq:master}
+In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \autoref{eq:master}
 \begin{equation}
-\partial_t \hat \rho = 0 = \mathcal{L} \hat \rho
+\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} \hat \rho = 0
 \end{equation}
 This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
-This method is applicable when the driving of the two transmons is at the same frequency since from \eqref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.
+This method is applicable when the driving of the two transmons is at the same frequency since from \autoref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.
 
-The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian.
-This is the case when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$).
-From \eqref{eq:RWA} we find that even in the doubly-rotating frame $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because this will lead to qualitatively different results.
-In this case, to find the steady state of the system we employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions.
-The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \eqref{eq:master}, it is defined as
+The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian or if one wants to solve the master equation in the laboratory frame.
+For example, when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$), from \autoref{eq:RWA} we find that even in the doubly-rotating frame, $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because it is inherent for the SAM.
+In this case, to find the steady state of the system one can employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions.
+The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \autoref{eq:master}, it is defined as
 \begin{equation}
@@
 
-	\includegraphics[width=.55\linewidth]{stationary}
+	\includegraphics[width=.495\linewidth]{main_picture_slices}
+	\includegraphics[width=.495\linewidth]{stationary}
 	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}.
@@
 Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator.
-Three avoided crossings not predicted by the stationary model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
-We also denote some of the transitions $00 - ij/n$ where $i,j$ stand for the final transmon energy levels and $/n$ is optional for an $n$-photon process.
-\textbf{(c)} Simulated population of the first qubit excited state ($\lg P_{\ket{10}}$ is shown with colour).
-Lines show various transition frequencies from the stationary Hamiltonian.
-The legend labels the transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
+Three avoided crossings not predicted by the unperturbed model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
+We also denote some of the transitions $ij/n$ (see Section \ref{sec:analysis} for notation).
+\textbf{(c)} Slices of the spectrum at various currents: 0.365 mA (feature III), 0.411 mA (sweet spot), 0.333 mA (feature I); experiment is gray, theory is black.
+Spectral lines where only one SAA is excited are highlighted with the corresponding colour from \autoref{fig:experiment}.
+Rabi frequencies $\Omega_{1,2}$ may be extracted as FWHM of the spectral lines 10 and 01, respectively.
+\textbf{(d)} Simulated population of the state $\ket{10}$ ($\lg P_{\ket{10}}$ is shown with colour).
+Lines show various transition frequencies from the unperturbed Hamiltonian.
+Legend labels transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
 	\label{fig:two-tone}
@@
 
-Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the stationary Hamiltonian without driving terms.
-We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(c).
+Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the Hamiltonian with no driving.
+We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(d).
 While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects.
@@
 
-To check whether the described features are present in the dynamic regime, we have solved the master equation \eqref{eq:master} to find the steady states of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcomes $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$ depending on the excitation frequency and magnetic flux.
+To check whether the described features are present in the dynamic regime, we have solved the master equation \autoref{eq:master} to find the steady states of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcomes $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$ depending on the excitation frequency and magnetic flux.
 Strikingly, all the experimental features are immediately reproduced using this approach with just 9 SAM states as shown in \autoref{fig:two-tone}~(b).
-We have solved \eqref{eq:master} with and without RWA (using the propagator approach \eqref{eq:propagator}) and did not find any noticeable difference in the results; though, the runtime of a single 401 by 401 points simulation was 9 hours without RWA vs.
+We have solved \autoref{eq:master} with and without RWA (using the propagator approach \autoref{eq:propagator}) and did not find any noticeable difference in the results; though, the runtime of the whole 401 by 401 points simulation was 9 hours without RWA vs.
 3 minutes with RWA.
+As can be seen from \autoref{fig:two-tone}~(c), the numerical results are in a good agreement with the experiment (the spurious resonance is softened).
+A small discrepancy is that $12/3$ line is much less pronounced in the numerical data.
 
@@
 Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz.
-\textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}).
+\qquad	\textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}).
 The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed.
@@
 Note that now colours show the population of the ground state.
-\textbf{(c)} Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, $\Omega_2 = V_{rms}\cdot 0.23$ MHz/mV.
+\textbf{(c)} Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ {\text{MHz}}/{\text{mV}}$.
 From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
@@
 In the bottom row, we show how the splittings vanish when the weaker driving is increased to match with the stronger one.
-Gray dashed lines show the stationary solution, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
+Gray dashed lines show the solution with no driving, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
 	\label{fig:difdrive}
@@
 
-\subsection{Analysis of the spectra}
+\subsection{Analysis of the spectra} \label{sec:analysis}
 
-\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the stationary model, it is possible to use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:two-tone}~(c)).
-In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon states after the transition from the ground state, and $/n$ is optional for an $n$-photon process.
-We put the labels at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
+\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the unperturbed model, we can use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:two-tone}~(d)).
+In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon state $\ket{ij}$ after the transition from the ground state $\ket{00}$, and $/n$ is optional for an $n$-photon process; we also use this notation throughout the text.
+The labels are put at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
 
 Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$.
-The ${02/2}$ and ${20/2}$ are very common for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
-Another two-photon process appears as $11/2$ line when two qubits are excited simultaneously.
+The ${02/2}$ and ${20/2}$ are very commonly found for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
+Another two-photon process appears as $11/2$ line when two SAAs are excited simultaneously.
 This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I.
@@
 
-From \autoref{fig:two-tone}~(c) we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
-The latter process is discernible in \autoref{fig:two-tone}~(c) as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}.
+From \autoref{fig:two-tone}~(d) we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ ($\ket{10}\rightarrow\ket{02}$) which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
+The latter process is discernible in \autoref{fig:two-tone}~(d) as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}~(a),(b).
 In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$.
-From additional measurements and simulations, we have found that the size of these anticrossings depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b).
-As one can see, the growth of the splitting with increasing power is linear: its width is roughly equal to the FWHM of the ${01}$ spectral line which is approximately $\Omega_2/2\pi$ Hz.
+From additional measurements and simulations, we find that the splitting depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b).
+As one can see, the growth of the splitting with increasing power is linear: it is roughly equal to the FWHM of the ${01}$ spectral line.
 To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}.
@@
 We note that two qualitatively different patterns arise depending on which of the transmons is driven stronger than the other.
-From this and from the shape of the splitting in feature I of \autoref{fig:experiment}~(a), we can infer that $\Omega_1 \approx 2\Omega_2$ there.
+From this and from the shape of the splitting in feature I of \autoref{fig:two-tone}~(a), we can infer that $\Omega_1/\Omega_2 \approx 2$ there (also consistent with the 01, 10 linewidths in \autoref{fig:two-tone}~(c)).
 
-These observations mean that I -- III are caused by light dressing.
+These observations mean that effects I -- III are caused by light dressing.
 In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
-We will discuss these effects in greater detail in \autoref{sec:theory}.
+We will discuss these effects in greater detail in Section \ref{sec:theory}.
 
-\paragraph{Secondary features.} Using \autoref{fig:two-tone}~(c), we can get an insight into the features 1 -- 5 as well.
+\paragraph{Secondary features.} Using \autoref{fig:two-tone}~(d), we can get an insight into the features 1 -- 5 as well.
 
 Feature 1 is a small avoided crossing between ${02/2}$ and ${21/3}$.
-It is missing in the stationary solution and thus is caused by the light dressing just as I -- III.
+It is missing in the unperturbed solution and thus is caused by the light dressing just as I -- III.
 Feature 2 is its twin: ${12/3}$ and ${20/2}$ intersect there but the anticrossing is smaller due to the asymmetry of the driving strengths and is not resolved.
@@
 Feature 3 is a large avoided crossing between three-photon processes ${12/3}$ and ${21/3}$.
-It is predicted by the stationary model, and direct diagonalization yields the splitting of $\frac{4}{3}J$.
+It is predicted by the unperturbed model, and direct diagonalization yields the splitting of $\frac{4}{3}J$.
 A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator in the third order.
 
-Feature 4 is also explained by the stationary model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:two-tone}~(c)).
+Feature 4 is also explained by the unperturbed model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:two-tone}~(d)).
 It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise.
@@
 
-Since we had already connected the additional avoided crossings with the light dressing, it was natural to expect the Autler-Townes effect to be at the root of the avoided crossings.
+Since we had already connected the additional avoided crossings with the light dressing, it was natural to expect an Autler-Townes-like effect to be at the root of the additional spectral lines.
 For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
@@
 First of all, since during the spectroscopy we apply only a single microwave tone ($\omega_d^1 = \omega_d^2$), for the A-T effect it has to be simultaneously the coupler and the probe; the latter must be much weaker than the former, as well.
-These conditions are satisfied when $\omega_{(2,1)} = \omega_{(1,2)}+\alpha_{(1,2)}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively) because the of the two-photon probe.
+These conditions are satisfied when $\omega_{\{2,1\}} = \omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively).
 Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure.
-In contrast, the single-photon excitation is enough to dress the system.
+In contrast, single-photon excitation is strong enough to dress the system.
 In other words, in our case the A-T coupling operator is $\hat H_{d}^1$ (strong), and the probing operator is $\hat H_{d}^2$ (weak in the two-photon regime).
-Their separation in our case is not in frequency but in the Hilbert subspaces they act upon.
+However, their separation in our case is not in frequency, but in the Hilbert subspaces they act upon.
 
-Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$.
-However, as we demonstrate in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
+Similarly, for feature I, the simultaneously excited transitions are $01(10)$ and the two-photon $11/2$.
+However, as we demonstrate in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.
 
@@
 Dressing by the strong excitation increases this splitting to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$.
-\textbf{(d)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by $\hat H_{d}^2$ are shown with blue ellipses).
+\textbf{(d)} Transitions in the light-dressed system when the second transmon is excited (level subspaces coupled by $\hat H_{d}^2$ are shown with blue ellipses).
 In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
@@
 For simplicity, we will temporarily assume that each transmon is driven at its own frequency (this assumption will be lifted in the following section).
-For convenience, in \autoref{fig:main_scheme}~(a) we schematically reproduce the transitions near III where the first transmon (orange) is below the second (blue), and the resonance point in current is shown with dashed red line.
-Next, \autoref{fig:main_scheme}~(b) demonstrates the stationary level structure of the SAM at 0.36 mA.
+For convenience, in \autoref{fig:main_scheme}~(a) we schematically reproduce the transitions near III where the first transmon (orange) is below the second (blue), and the resonance point in current is shown with a dashed red line.
+Next, \autoref{fig:main_scheme}~(b) demonstrates the level structure of the SAM at 0.36 mA.
 Nearly-resonant with $10$ (detuning $\Delta_1$) single-photon driving with $\hat H_d^1$ is shown with orange ellipses while much weaker two-photon $\hat H_d^2$ is not shown yet.
@@
 The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(c)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}.
-Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its the new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$.
+Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$.
 Meanwhile, the second transmon energies stay the same.
@@
 Now, we will repeat this reasoning using a quantitative mathematical model.
-We start from the initial Hamiltonian \eqref{Hsystem}.
-To move to the rotating frame with \eqref{eq:rotation} and apply the RWA, will use the following operator:
+We start from the initial Hamiltonian \autoref{Hsystem}.
+To move to the rotating frame with \autoref{eq:rotation} and apply the RWA, will use the following operator:
 \begin{equation}
-R = \exp[-i\omega_d^1 t (b^{\dagger}b+c^{\dagger}c)].
+R = \exp[-it \omega_d^1 (b^{\dagger}b+c^{\dagger}c)].
 \end{equation}  
@@
 \begin{aligned}
-\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}+\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
+\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}-\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
 \hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
@@
 To simplify further calculations, we consider the point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
-In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:dpt}.
+In these conditions, $H^D$ becomes degenerate as can be seen in \autoref{eq:ham_matrix} of Appendix \ref{sec:dpt}.
 Using the degenerate perturbation theory for $\hat V_J$ summarized therein, we find the first-order corrected wave functions of $\hat H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.
@@
 \begin{aligned}
-R^{(2)}_{1\rightarrow 6} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1$}\right)^2}{\alpha ^{6}\Omega_1^2},\\
-R^{(2)}_{2\rightarrow 5} &= 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
-		$}\right)^2}{\alpha ^{6}\Omega_1^2}.
+R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1$}\right)^2}{\alpha ^{6}\Omega_1^2},\\
+R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
+		$}\right)^2}{\alpha ^{6}\Omega_1^2},
 \end{aligned}\label{eq:rates}
 \end{equation}
-From \eqref{eq:rates} follows that the sideband transitions are prohibited without the interaction in the SAM $(J=0)$, and the extra avoided crossings will not be observed.
+when $\alpha \gg \Omega_1, \Omega_2, J$ which is true for our setup.
+From \autoref{eq:rates} follows that the sideband transitions are prohibited without the interaction in the SAM $(J=0)$, and the extra avoided crossings will not be observed.
 
 \paragraph{Feature I.} Finally, we discuss the last Roman-numbered effect.
-It is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$: the second qubit is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
+It is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$: the second transmon is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
 For the opposite case ($\Omega_1 \gg \Omega_2$), the logic is the same.
@@
 \paragraph{Features II, III.}As shown in \autoref{fig:main_scheme}~(d), the sideband transitions are formed by two-photon processes for $\hat H_d^2$.
-On the other hand, we know from the stationary solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon).
+On the other hand, we know from the unperturbed solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon).
 This means that there should be a smooth transformation between 1-, 2- and 3-photon processes when the system approaches the resonant point.
 Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$.
-In the frame rotating with the first qubit (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first qubit), their frequencies are
+In the frame rotating with the first transmon (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first transmon), their frequencies are
 \begin{equation}
@@
 The minimal splitting between these lines is found at the resonant point and equals $\frac{2 \sqrt{3}}{{3}} \Omega_1$.
-All these calculations may be repeated exactly for the feature II by reversing the order of the transmons; in that case, the maximal splitting will be $\frac{2 \sqrt{3}}{{3}} \Omega_2$
+All these calculations may be repeated exactly for the feature II by swapping the transmons; in that case, the splitting will be $\frac{2 \sqrt{3}}{{3}} \Omega_2$.
 
-We find excellent agreement between our analytical model \eqref{eq:splitting_model} and both the experimental and simulated data as can be seen in \autoref{fig:zoom}.
-To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \eqref{eq:splitting_model}; $\alpha_1$ is known from spectroscopy.
+We find excellent agreement between our analytical model \autoref{eq:splitting_model} and both the experimental and simulated data as can be seen in \autoref{fig:zoom}.
+To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \autoref{eq:splitting_model}; $\alpha_1$ is known from spectroscopy.
 The only free parameter left was $\Omega_2$.
@@
 
-When $\Omega_1 \gg \Omega_2$, besides the replacement $\Omega_2 \rightarrow \Omega_1$, the equation \eqref{eq:topo_1} changes the sign:
+When $\Omega_1 \gg \Omega_2$, besides the replacement $\Omega_2 \rightarrow \Omega_1$, \autoref{eq:topo_1} changes the sign:
 \begin{equation}
@@
 \end{equation}
-Solving it for $\omega_d$, we obtain the generalization of \eqref{eq:topo_1} and \eqref{eq:topo_1_inv}:
+Solving it for $\omega_d$, we obtain the generalization of \autoref{eq:topo_1} and \autoref{eq:topo_1_inv}:
 \begin{equation}
@@
 
-The equation \eqref{eq:topo_comm} is used to plot the black dashed curves in \autoref{fig:difdrive} taking the $\Omega_{1,2}$ values from the simulation parameters shown therein.
+\autoref{eq:topo_comm} is used to plot the black dashed curves in \autoref{fig:difdrive} taking the $\Omega_{1,2}$ values from the simulation parameters shown therein.
 The frequencies $\omega_{1,2}$ are extracted from the fits to the visible spectral lines.
@@
 We have performed spectroscopy measurements of an isolated diatomic superconducting artificial molecule (SAM) in a regime of strong interaction with classical light.
-Using joint dispersive readout to directly access population of the SAM eigenstates, we have located several anomalies in the spectral data that were impossible to explain using the simple stationary model of the system.
+Using joint dispersive readout to directly access population of the SAM eigenstates, we have located several anomalies in the spectral data that were impossible to explain using the unperturbed model of the system.
 By using extensive numerical modelling explicitly including the interaction with light, we have reproduced the experimentally discovered effects and attributed them to an altered version of the well-known Autler-Townes effect.
@@
 In the standard A-T effect, the coupler and the probe tone are separated in frequency and power.
-In our case, there is only a single spectroscopic frequency interacting with the system; therefore, the is has to be the coupler tone and the probe tone at the same time.
+In our case, there is only a single spectroscopic frequency interacting with the system; therefore, it has to be both the coupler tone and the probe tone at the same time.
 However, since there are two components in the driving operator (one for each transmon), the separation between the coupler and the probe may be in the Hilbert space rather than in frequency.
 Moreover, the effectively weak driving for the probe is achieved when it stimulates a two-photon transition while the coupler tone is resonant with a single-photon one and is dressing the system.
-We have build a self-consistent model in the frame rotating with the dressed qubit to model the experimental splittings induced by the same field that probes them, and found a good agreement between the model, the experiment, and the numerical simulation.
+We have build a self-consistent model in the frame rotating with the dressed transmon to model the experimental splittings induced by the same field that probes them, and found a good agreement between the model, the experiment, and the numerical simulation.
 Interestingly, just as in the standard A-T effect on transmons reported previously, no new transitions appear in this more complex case.
@@
 In additional simulations with full freedom of choice for the parameter values, we have studied this effect in detail and observed two possible topologically different configurations of this splitting depending on which driving amplitude is larger.
-Notably, the frequency of $11/2$ transition far from resonance is also changed noticeably with changing power, which means that a fast bSWAP gate should be performed at a different frequency than the stationary model predicts.
+Notably, the frequency of $11/2$ transition far from resonance is also changed noticeably with changing power, which means that a fast bSWAP gate should be performed at a different frequency than the unperturbed model predicts.
 
 Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may smoothly change their order.
-For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \eqref{eq:two-photon}, and of a two-photon transition to a zero-photon in \eqref{eq:zero-photon}.
+For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \autoref{eq:two-photon}, and of a two-photon transition to a zero-photon in \autoref{eq:zero-photon}.
 
@@
 
-Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \eqref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
+Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \autoref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
 The degeneracy between states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, \ket{b,2}$ occurs only in the resonant case $2\Delta_2   + \alpha_2 = 0$ meaning that the second transmon frame is rotated at its two-photon transition frequency.
@@
 \end{equation} 
-Solving \eqref{forpsi} by simple iterations gives the series solution for it:
+Solving \autoref{forpsi} by simple iterations gives the series solution for it:
 \begin{align}
@@
 Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters.
-The additional on-chip attenuation (due to the small capacitive coupling) between the qubit drive line and the qubits was calculated in Sonnet to be around 70 dB @ 6 GHz.
+The additional on-chip attenuation (due to the small capacitive coupling) between the drive line and the transmons was calculated in Sonnet to be around 70 dB @ 6 GHz.
 Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well.
@@
 
+\section{Sample fabrication}\label{sec:fab}
+The device was fabricated on a high-resistivity
+Si wafer (10 kOhm$\cdot$cm).
+First, Si wafers were cleaned with Pirahna, HF and then coated with bilayer MMA/PMMA resist stack.
+The nominal after-bake thickness of the MAA and PMMA are 800 and 100 nm, respectively.
+The
+bilayer resist stack was exposed using a 50kV Raith Voyager EBL system and then developed. Next, the sample was placed into a high-vacuum electron-beam evaporation
+chamber (Plassys) and after a gentle ion-milling step, a double-angle evaporation technique at 10 is used to deposit Al/AlOx/Al layer.
+Finally, hot NMP followed by IPA was used to lift off the resist mask stack
+
 \bibliography{papers_bibliography}% Produces the bibliography via BibTeX.	

### 2019-12-23 Pictures/Plotting/MainPicturePlot.py

@@ -97,7 +97,7 @@ class MainPicturePlot:
         #     self._cache[self.nstate] = C
 
         C = np.real(self._C_th.T)
-        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.027+(0.027/2-0.005)# + np.random.normal(scale=0.001,
+        C = (C-np.min(C)-np.ptp(C)/2)/np.ptp(C)*0.02+(0.02/2+0.0025)# + np.random.normal(scale=0.001,
                                                            #                    size=C.shape)
         C = C
         data = self._X_th, self._Y_th, C

### 2019-12-23 Pictures/Plotting/StationaryPlot.py

@@ -15,7 +15,7 @@ class StationaryPlot:
         with open("stationary.pkl", "rb") as f:
             currs, freqs, population10, energies = pickle.load(f)
 
-        fig, ax = plt.subplots(1, 1, figsize=(5, 3), sharey=True)
+        fig, ax = plt.subplots(1, 1, figsize=(5*0.9, 3*0.9), sharey=True)
 
         # mappable = axes[0].pcolormesh(currs, freqs, log10(array(population10)), rasterized=True,
         #                    cmap="Spectral_r")
@@ -107,13 +107,14 @@ class StationaryPlot:
         plt.plot(currs, ((energies[:, 8].T - energies[:, 0]).T / 4), linestyle=typ2, linewidth=t,
                  color=secondary_colour);  # 00->22
 
-        plt.plot(currs, ((energies[:, 1].T - energies[:, 0]).T), label=r"10",
-                 linewidth=m,
-                 linestyle=typ1);  # 00->10
 
         plt.plot(currs, ((energies[:, 2].T - energies[:, 0]).T), label=r"01",
                  linewidth=m,
                  linestyle=typ1);  # 00->01
+
+        plt.plot(currs, ((energies[:, 1].T - energies[:, 0]).T), label=r"10",
+                 linewidth=m,
+                 linestyle=typ1);  # 00->10
 
         plt.plot(currs, ((energies[:, 3].T - energies[:, 0]).T / 2),
                  label=r"20/2",
@@ -138,7 +139,7 @@ class StationaryPlot:
 
         plt.ylim(5.1, 5.5)
         plt.xlim(2,6)
-        ax.set_ylabel("Frequency [GHz]")
+        ax.set_ylabel("$\omega_{d}^{1,2}/2\pi$ [GHz]")
 
         ax.set_xlabel("Current [$10^{-4}$ A]")
         plt.legend(ncol=3, fontsize=7)
@@ -152,7 +153,7 @@ class StationaryPlot:
         cb.ax.set_title(r"$ P_{\left|10\right\rangle}$", position=(1.125, -3.5))
 
 
-        plt.text(-0.15, 1.1, "(c)", fontdict={"name": "STIX"}, fontsize=18,
+        plt.text(-0.15, 1.1, "(d)", fontdict={"name": "STIX"}, fontsize=17,
                  transform=ax.transAxes)
 
         plt.savefig("../stationary.pdf", bbox_inches="tight", dpi=600)

### 2019-12-23 document.tex
Commit

--- 2019-11-26 document.tex
@@
 	\begin{abstract}
-	Since their demonstration, superconducting artificial atoms have been extensively used for studies in quantum optics.
-Their particular advantages compared to natural systems are the strong coupling to radiation and the high level of control over their state; these properties open the way to previously unexplored physics.
-In this work, we have irradiated a superconducting artificial molecule composed of two flux-tunable transmons with intense light while monitoring its state via joint dispersive readout.
-At certain configurations of its energy levels, the molecule has demonstrated a complex spectrum deviating qualitatively from the stationary solution.
-However, it was reproduced accurately by numerical simulations, and turned out to be a consequence of a modified Autler-Townes effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates.
-To quantify this effect, self-consistent models were employed accounting for both these processes at the same time.
-We note that this study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
+		To build a full-scale quantum processor it is necessary to automate as many steps as possible on the physical, hardware level.
+Circuit quantum electrodynamics (cQED) is a contemporary architecture for dispersive readout and Purcell protection of superconducting qubits of various types, and thus it is necessary to develop software that is able to perform every kind of automatic calibration of such systems from scratch without any human participation.
+An important step towards this goal is to build a noise-insensitive and accurate computer vision tool to process three-dimensional spectroscopic data.
+In this work, we present and describe two scalable algorithms that are able to extract the Hamiltonian parameters of the cQED systems from spectroscopic data.
 	\end{abstract}
@@
 Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
-For example, the strong coupling regime, when the coupling strength between light and a quantum system approaches 1\% of their frequency, has been a major challenge for atoms, molecules, etc and was only reached using high-finesse cavities.
-In contrast, superconducting quantum systems have rapidly attained this milestone using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first demonstration\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
-Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime\cite{forn2019ultrastrong}.
+For example, the strong coupling regime when the coupling strength between light and a quantum system approaches 1\% of their frequency has been a major milestone for atoms, molecules, etc and was only reached using high-finesse cavities.
+In contrast, superconducting quantum systems have rapidly attained this landmark using \textit{circuit QED}\cite{wallraff2004strong} just in a few years after their first discovery\cite{chiorescu2004coherent} and have already surpassed other strongly-coupled systems in terms of coherence\cite{forn2019ultrastrong}.
+Moreover, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strong with the free-propagating EM-waves in the on-chip 1D waveguides\cite{astafiev2010resonance} without having to use cavities at all.
+The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is already the ultra-strong coupling regime.
 
-Strong interaction of a quantum system with light lead to various phenomena explained by resonant single- and multi-photon excitation of transitions between energy levels.
+In general, a quantum system exposed to strong external driving can experience various quantum phenomena explained by resonant single- and multi-photon transitions between energy levels.
 The most known examples are coherent population trapping, electromagnetically induced transparency (EIT)\cite{boller1991observation}, stimulated Raman adiabatic passage\cite{bergmann1998coherent} and Autler-Townes (A-T) splitting\cite{autler1955stark}.
 
-In this work, we study effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM).
-In our experiment, we use two X-mons\cite{barends2013coherent} interacting with each other through a cavity bus\cite{majer2007coupling}.
+In this work, we are studying effects of light-matter interaction that occur in a system of two coupled artificial atoms: a superconducting artificial molecule (SAM).
+In our experiment, we use two transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
 Microwave radiation is applied to this system through a coplanar on-chip antenna and transmon states may be monitored by dispersive readout using the same coupling cavity \cite{chow2010detecting}.
 
-It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we observe.
+It turns out that due to the strong interaction of SAM with the microwave drive, multiphoton transitions and the Autler-Townes effect are playing the crucial role in the phenomena that we have discovered.
 The A-T splitting has been observed before in atomic\cite{picque1976direct}, molecular systems\cite{tamarat1995pump}, quantum dots\cite{xu2007coherent}, and for SAA as well\cite{baur2009measurement, sillanpaa2009autler, novikov2013autler, suri2013observation, peng2018vacuum}.
@@
 The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances.
-A capacitively coupled excitation line is also shown in green.
+The capacitively coupled excitation line is also shown in green.
 Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux.
-Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
+Since the effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second qubit (blue).
 Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
-This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency.
+This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are staying close to each other in frequency.
 Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
@@
 Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
-Frequency control lines come from both sides, and from below a microwave excitation waveguide is connected (green).
+From both sides come the frequency control flux lines, and from below a microwave excitation waveguide is connected (green).
 \textbf{(b)} The equivalent electrical circuit.
-Tunable Josephson junctions are SQUIDs with magnetic flux control.
-\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (proportional to the currents applied to control lines).
-In this work, we focus on the area inside the dashed rectangle.}
+Tunable Josephson junctions are in fact SQUIDs with magnetic flux control.
+\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (coloured correspondingly).
+In this work, we concentrate on the area inside the dashed rectangle.}
 	\label{fig:experiment}
@@
 
-\subsection{Theoretical background}
+\subsection{Theoretical description of the SAM}
 
 A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
+Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$ ($\hbar = 1$):
 \begin{equation}
-\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
+\hat{{H}}_{tr} = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
 \end{equation}
-where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
+where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or the  $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
 Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
@@
 
-To drive a quantum system, one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
-The driving term between the transmon and the field is then modelled by the following operator:
+To induce state transitions in a transmon one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
+The interaction term between the transmon and the field is then modelled by the following operator:
 \begin{equation}
-\hat H_{d} = \hbar \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
+\hat H_{d} = \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
 \end{equation}
-where $\Omega$ is the driving amplitude coinciding with the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.
+where $\Omega$ stands for the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.
 
@@
 \begin{equation}\label{Hsystem}
-\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
+\hat H = \hat H_{tr1}+\hat H_{tr2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
 \end{equation}
-where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
-In the following, we will also transform \eqref{Hsystem} into the frame rotating with both drives by an operator
+where $\hat H_{int} = J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
+In the following, we will also transform \eqref{eq:master} into the frame rotating with both drives by an operator
 \begin{align}
 &\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}\\
-&\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
+&\hat H_R = \hat R^{\dagger}\hat H \hat R - i\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
 \end{align}
-Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA:
+After the transformation and application of the RWA:
 \begin{equation}
@@
 	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
-	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{-(\omega_d^1 - \omega_d^2)t}\right],\\
-	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
+	\hat H_{int} &\rightarrow J \left[\hat b^\dag \hat c e^{-(\omega_d^1 - \omega_d^2)t} + \hat b \hat c^\dag e^{(\omega_d^1 - \omega_d^2)t}\right],\\
+	\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c  + \hat c^\dag).
 \end{aligned}
@@
 \begin{equation}
-\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
+\partial_t \hat \rho = {i}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
 \end{equation}
@@
 
-The readout resonator is not included in the model since in the dispersive regime it does not affect the dynamics of the SAM.
+The readout resonator is not included in the model since in the dispersive regime is does not affect the dynamics of the SAM.
 Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
@@
 Their frequency depends on the applied current, and at multiple points they become resonant with each other.
-At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numbers.
+At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numerals.
 Some secondary details are shown with Arabic-numbered markers.
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
 	\includegraphics[width=\linewidth]{topological_splittings}
-	\caption{Simulated population of the ground state when the transmons are driven at the same frequency but at different amplitudes $\Omega_{1,2}$.
-In the top row (middle row), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const} \ll \Omega_{1(2)}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
-In the bottom row, we show how the splittings vanish when the weaker driving is increased to match with the stronger one.
+	\caption{Simulated population of the ground state when the transmons are driven at different amplitudes $\Omega_{1,2}$ but at the same frequency.
+In the left (right), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
 Gray dashed lines show the stationary solution, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
 	\label{fig:difdrive}
-\end{figure*}
+\end{figure}
 
@@
 Similarly, for feature I, the simultaneously excited transitions are $01 (10)$ and the two-photon $11/2$.
-However, as we demonstrate in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
+However, as we have demonstrated in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{(1,2)} \gg \Omega_{(2,1)}$.
 
@@
 \omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
-\hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
-\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
-\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
+\hat H_{int} &\rightarrow J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
+\hat H_{d}^1 &\rightarrow \frac{\Omega_1}{2} \hat \sigma_x,\ 
+\hat H_{d}^2 \rightarrow \frac{\Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
 \end{aligned}
@@
 To simplify futher calculations, we take the working point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
-In these conditions, $H^D$ becomes degenerate as can be seen in \eqref{eq:ham_matrix} of Appendix \ref{sec:H_mat}.
+In these conditions, $H^D$ becomes degenerate as can be seen below in \eqref{eq:ham_matrix}:
 
@@
 \end{aligned}
-\label{eq:two-photon}
 \end{equation}
@@
 \Omega_1^R \pm \Omega_2^R = 0.
-\label{eq:zero-photon}
 \end{equation}
@@
 
-\section{Discussion}
-
-We have performed spectroscopy measurements of an isolated diatomic superconducting artificial molecule (SAM) in a regime of strong interaction with classical light.
-Using joint dispersive readout to directly access population of the SAM eigenstates, we have located several anomalies in the spectral data that were impossible to explain using the simple stationary model of the system.
-By using extensive numerical modelling explicitly including the interaction with light, we have reproduced the experimentally discovered effects and attributed them to an altered version of the well-known Autler-Townes effect.
-
-In the standard A-T effect, the coupler and the probe tone are separated in frequency and power.
-In our case, there is only a single spectroscopic frequency interacting with the system; therefore, the is has to be the coupler tone and the probe tone at the same time.
-However, since there are two components in the driving operator (one for each transmon), the separation between the coupler and the probe may be in the Hilbert space rather than in frequency.
-Moreover, the effectively weak driving for the probe is achieved when it stimulates a two-photon transition while the coupler tone is resonant with a single-photon one and is dressing the system.
-We have build a self-consistent model in the frame rotating with the dressed qubit to model the experimental splittings induced by the same field that probes them, and found a good agreement between the model, the experiment, and the numerical simulation.
-Interestingly, just as in the standard A-T effect on transmons reported previously, no new transitions appear in this more complex case.
-Instead, for example, spectral lines $12/3$ (three-photon) and $10-02$ (single photon) form an avoided crossing of a non-standard size of $\frac{2\sqrt{3}}{3} \Omega_1$.
-
-Another interesting effect occurs when both components of the driving operator are in the single-photon regime.
-Now, both transmons are dressed and probed simultaneously.
-In this case, the $11/2$ transition is split at the resonance into a hyperbolic curve, never forming a doublet in frequency.
-Moreover, its shape and visibility depends on the relation between the driving amplitudes: if they are equal, it disappears completely.
-In our sample, we have a fixed ratio of approximately 2 between $\Omega_1$ and $\Omega_2$ which allows us to distinguish the splitting experimentally.
-In additional simulations with full freedom of choice for the parameter values, we have studied this effect in detail and observed two possible topologically different configurations of this splitting depending on which driving amplitude is larger.
-Notably, the frequency of $11/2$ transition far from resonance is also changed noticeably with changing power, which means that a fast bSWAP gate should be performed at a different frequency than the stationary model predicts.
-
-Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may change their order.
-For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \eqref{eq:two-photon}, and a two-photon to a zero-photon in \eqref{eq:zero-photon}.
-
-In overall, irradiating an individual diatomic artificial molecule with intense light calls forth a plethora of effects which can not be directly observed in natural systems and extend the validity of the well-known light-dressing models.
-Relative ease in attaining powers that cause multiphoton transitions promises even more complex dynamics in multi-atom systems.
-We are looking forward to investigating strong interaction with light in larger artificial structures such as one-dimensional and two dimensional chains and arrays of superconducting artificial atoms.
-
 \appendix
@@
 
-\begin{figure}[b]	
+\begin{figure}
 	\includegraphics[width=\linewidth]{intro_scheme}
@@
 \hat R = \left[\begin{matrix} 
-1 & 0 & 0\\0 & e^{- i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{- i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
+1 & 0 & 0\\0 & e^{i t \left(\omega_{01}- \Delta\right)} & 0\\0 & 0 & e^{i t \left(\omega_{01}- \Delta\right)}\end{matrix}\right].
 \]
 Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$.
-The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R - i \hat{R}^\dag \partial_t  \hat R$.
+The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R + i \dot{\hat{R}}^\dag \hat R$.
 The level structure without driving  is shown in the left part of \autoref{fig:at-standard}~(b).
@@
 
-\section{The dressed Hamiltonian in the matrix form} \label{sec:H_mat}
+\section{The dressed Hamiltonian in the matrix form}
 
-Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \eqref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
-
-Note that $\hat V_J = \hat S^T \hat H_{int} \hat S$ now has an sub- and super-diagonal block form coupling all the states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, \ket{b,j+1}$.
-
-The degeneracy between states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, \ket{b,2}$ occurs only in the resonant case $2\Delta_2   + \alpha_2 = 0$ meaning that the second transmon frame is rotated at its two-photon transition frequency.
-In this situation, its single-photon subspace is detuned by $-\alpha/2$.
+\vspace{1cm}
 

### 2019-12-27 document.tex
Short lines

--- 2019-12-23 document.tex
@@
 \documentclass[%
- prx,
+ pra,
 % jmp,
@@
 
-\newcommand{\mytitile}{Light-dressing of a diatomic supercondufcing artificial molecule}
+\newcommand{\mytitile}{Light-dressing of a 
+diatomic supercondufcing artificial molecule}
 
@@
 	\affiliation{ 
-		Skolkovo Institute of Science and Technology, Moscow, Russian Federation
+		Skolkovo Institute of Science and 
+		Technology, Moscow, Russian Federation
 	}%
@@
 \affiliation{ 
-	Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
+	Moscow Institute of Physics and Technology, 
+	Dolgoprundiy, Russia
 }%
@@
 	\author{I.A. Rodionov}
-	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
-	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+	\affiliation{FMN Laboratory, Bauman Moscow 
+	State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research 
+	Institute, (VNIIA), Moscow, Russia}
 
 	\author{A.A. Dobronosova}
-	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
-	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+	\affiliation{FMN Laboratory, Bauman Moscow 
+	State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research 
+	Institute, (VNIIA), Moscow, Russia}
 
 	\author{D.O. Moskalev}
-	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
+	\affiliation{FMN Laboratory, Bauman Moscow 
+	State Technical University, Moscow, Russia}
 
 	\author{A.A. Pischimova}
-	\affiliation{FMN Laboratory, Bauman Moscow State Technical University, Moscow, Russia}
-	\affiliation{Dukhov Automatics Research Institute, (VNIIA), Moscow, Russia}
+	\affiliation{FMN Laboratory, Bauman Moscow 
+	State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research 
+	Institute, (VNIIA), Moscow, Russia}
 
@@
 	}
-	\affiliation{Skolkovo Institute of Science and Technology, Moscow, Russian Federation}
-	\affiliation{Physics Department, Royal Holloway, University of London, Egham, Surrey TW20 0EX, United Kingdom}
+	\affiliation{Skolkovo Institute of Science 
+	and Technology, Moscow, Russian Federation}
+	\affiliation{Physics Department, Royal 
+	Holloway, University of London, Egham, Surrey 
+	TW20 0EX, United Kingdom}
 %
@@
 	\begin{abstract}
-	In this work, we study a superconducting artificial molecule composed of two magnetic-flux-tunable transmons with intense light while monitoring its state via joint dispersive readout.
-At certain fluxes, the molecule demonstrates a complex spectrum deviating qualitatively from the solution of the Schrödinger equation without driving.
-We reproduce the observed extra spectral lines accurately by numerical simulations, and find them to be a consequence of an Autler-Townes-like effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates.
-We present self-consistent analytical models that account for both these processes at the same time and agree well with both experiment and numerical simulation.
-This study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
+	In this work, we irradiate a superconducting 
+	artificial molecule composed of two 
+	magnetic-flux-tunable transmons with 
+	microwave light while monitoring its state 
+	via joint dispersive readout. At certain 
+	fluxes, the molecule demonstrates a complex 
+	spectrum deviating qualitatively from the 
+	solution of the Schrödinger equation without 
+	driving. We reproduce the observed extra 
+	spectral lines accurately by numerical 
+	simulations, and find them to be a 
+	consequence of an Autler-Townes-like effect 
+	when a single tone is simultaneously dressing 
+	the system and probing the transitions 
+	between new eigenstates. We present 
+	self-consistent analytical models accounting 
+	both these processes at the same time that 
+	agree well with both experiment and numerical 
+	simulation. This study is an important step 
+	towards understanding the behaviour of more 
+	complex systems of many atoms interacting 
+	with strong radiation.
 	\end{abstract}
@@
 
-Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments in a compelling demonstration of the validity of fundamental quantum mechanical laws\cite{you2011atomic}.
-Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics.
-Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.
-
-One of the most prominent milestones, that superconducting quantum circuits have attained just in a few years after their first demonstration, is the strong coupling with light in {circuit QED}\cite{wallraff2004strong, chiorescu2004coherent} meaning that the decoherence rates are smaller than the Rabi frequency.
-Currently, they are surpassing all other implementations of strong coupling in terms of coherence\cite{forn2019ultrastrong}.
-However, in sharp contrast with natural atoms and molecules, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all.
-The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is even beyond strong coupling regime\cite{forn2019ultrastrong}.
-To correctly describe the behaviour of an atom in these conditions, the so-called \textit{dressed atom approach}\cite{cohen1998atom} is employed when the radiation has to be directly included in the Hamiltonian and affects its level structure.
-
-So far, the main experiments in on-chip quantum optics with intense propagating light were focused on single artificial atoms\cite{baur2009measurement, sillanpaa2009autler, astafiev2010resonance, novikov2013autler, suri2013observation, koshino2013observation, braumuller2015multiphoton, peng2018vacuum, gasparinetti2019two}.
-In all these works, light dressing of the atom manifests itself through Mollow triplets or Autler-Townes splittings of different kinds.
-However, despite the recent successes in control of large arrays of interacting SAA\cite{Song574, ye2019propagation, arute2019quantum}, there were, up to our best knowledge, no experiments concerning interaction of such composite structures with intense propagating light.
-While studies has been done concerning dressing multi-atomic systems in a cavity\cite{fink2009dressed, macha2014implementation, shulga2017observation, yang2018probing}, their interaction with intense free radiation is also attractive since light frequency may be easily tuned to observe various absorption processes for arbitrary configurations of the system's parameters.
-
-In this work, we study an system of two strongly coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM).
-We use two Xmon-type\cite{barends2013coherent} transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}.
-Microwave radiation is applied to this system through an on-chip coplanar waveguide while its state can be monitored by dispersive readout using the same coupling cavity\cite{chow2010detecting}.
-We find that strong interaction of the SAM with microwaves calls forth multiphoton transitions and Autler-Townes-like effects that could only be explained in the dressed picture.
-We note that although the A-T splittings have been investigated before in a wide range of quantum systems (including natural molecules\cite{tamarat1995pump, ahmed2012autler}), we find some qualitatively new spectral manifestations of the dressing effect.
-One of the reasons for this is that the natural molecules which could in principle demonstrate such effects do not have enough controllability and coherence.
-Alternatively, previous studies with SAA have either involved just a single atom or have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}).
-
-Remarkably, besides its fundamental importance, this experiment may be useful for future quantum computers: a quantum engineer should account for the observed behaviours carefully controlling the driving power (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).
-
-The manuscript consists of four main parts and an Appendix.
-Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research, including extensive numerical simulations and analytical analysis; finally, in Section IV we make a conclusion of our work and discuss future prospects.
-The Appendix contains important details of the theoretical framework that we use.
+Over the past twenty years, superconducting 
+artificial atoms (SAAs) were used in numerous 
+experiments in a compelling demonstration of the 
+validity of fundamental quantum mechanical 
+laws\cite{you2011atomic}. Due to synthetic nature 
+of SAAs, their Hamiltonians can be pre-designed 
+and engineered which makes them a particularly 
+versatile tool for studies in quantum optics. 
+Notably, high controllability of their parameters 
+allows direct observation of novel physical 
+effects previously inaccessible for natural 
+systems.
+
+One of the most prominent milestones that 
+superconducting quantum circuits have reached so 
+far is the strong coupling with light in {circuit 
+QED}\cite{wallraff2004strong, 
+chiorescu2004coherent} when the decoherence rates 
+appear smaller than the Rabi frequency. 
+Currently, they are surpassing all other 
+implementations of strong coupling in terms of 
+coherence\cite{forn2019ultrastrong}. 
+However, in sharp contrast with natural atoms and 
+molecules, SAAs do not even require confined 
+radiation to implement strong coupling with 
+light: they may be coupled unprecedently strongly 
+to free-propagating electromagnetic waves in 1D 
+on-chip waveguides\cite{astafiev2010resonance} 
+without using cavities at all. The Rabi frequency 
+in this case may reach 50\% of the transition 
+frequency\cite{deng2015observation} which is even 
+beyond strong coupling 
+regime\cite{forn2019ultrastrong}. To correctly 
+describe the behaviour of an atom in these 
+conditions, the so-called \textit{dressed atom 
+approach}\cite{cohen1998atom} is employed when 
+the radiation has to be directly included in the 
+Hamiltonian and affects its level structure.
+
+So far, main experiments in on-chip quantum 
+optics with intense propagating light were 
+focused on single artificial 
+atoms\cite{baur2009measurement, 
+sillanpaa2009autler, astafiev2010resonance, 
+novikov2013autler, suri2013observation, 
+koshino2013observation, 
+braumuller2015multiphoton, peng2018vacuum, 
+gasparinetti2019two}. In all these works, light 
+dressing of the atom manifests itself through 
+Mollow triplets or Autler-Townes splittings of 
+different kinds. However, despite the recent 
+successes in control of large arrays of 
+interacting SAAs\cite{Song574, ye2019propagation, 
+arute2019quantum}, there were, up to our best 
+knowledge, no experiments concerning interaction 
+of such composite structures with intense free 
+radiation. While there were studies on dressing 
+of multi-atomic systems in a 
+cavity\cite{fink2009dressed, 
+macha2014implementation, shulga2017observation, 
+yang2018probing}, their interaction with free 
+radiation is no less attractive since its 
+frequency may be easily tuned to observe various 
+absorption processes for arbitrary configurations 
+of the system parameters.
+
+In this work, we study a pair of strongly coupled 
+artificial atoms: a superconducting artificial 
+molecule\cite{kou2017fluxonium} (SAM). We use two 
+Xmon-type\cite{barends2013coherent} 
+transmons\cite{koch2007charge} interacting with 
+each other through a cavity 
+bus\cite{majer2007coupling}. Microwave radiation 
+is applied to this system through an on-chip 
+coplanar waveguide while its state can be 
+monitored by joint dispersive readout using the 
+same coupling cavity\cite{chow2010detecting}. We 
+find that strong interaction with microwaves not 
+only calls forth multiphoton transitions of 
+various orders between SAM states, but also 
+significantly modifies its level structure. Even 
+in a simple diatomic molecule, this leads to 
+complex Autler-Townes-like effects involving 
+single- and multiphoton  transitions that can 
+only be explained in the dressed picture. We note 
+that although the A-T splittings have been 
+investigated before in a wide range of quantum 
+systems (including natural 
+molecules\cite{tamarat1995pump, 
+ahmed2012autler}), we find qualitatively new 
+spectral manifestations of light dressing when 
+SAAs are irradiated unequally. We note that there 
+were no such experiments with natural molecules, 
+which could in principle demonstrate same 
+effects, because they lack controllability and 
+coherence of superconducting quantum devices, and 
+previous studies of SAAs and free radiation have 
+either involved just a single atom or have 
+demonstrated only the standard spectral 
+signatures known from the quantum optics (see 
+Appendix \ref{sec:3-level-at}).
+
+Besides its fundamental importance, this 
+experiment may be useful for future quantum 
+computers: a quantum engineer should account for 
+the observed behaviours carefully controlling the 
+driving power (for instance, as we will show, the 
+bSWAP gate\cite{poletto2012entanglement} is 
+directly affected by light dressing).
+
+The manuscript consists of four main parts and an 
+Appendix. Section I is this introduction; Section 
+II is devoted to the approaches that were used in 
+our study; Section III contains the results of 
+our experimental and theoretical research, 
+including numerical simulations and analytical 
+analysis; finally, in Section IV we make a 
+conclusion of our work and discuss future 
+prospects. The Appendix contains important 
+details of the theoretical framework that we use.
 
@@
 
-\subsection{Device design and fabrication}
-We have designed the SAM as a pair of transmon (Xmon) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} ($E^1_{J, \sum}/2\pi = 24.3$ GHz, $E^2_{J,\sum}/2\pi = 18.3$ GHz, $E^{1,2}_C = 220$ MHz, $d^{1,2} =0.75$) coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the transmons and allows the joint\cite{chow2010detecting} readout o	f their states.
-In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components.
-The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed.
-In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler.
-Flux lines that allow independent control of the transmon frequencies are coming from the sides.
-Finally, the excitation waveguide coming from below directs microwave signal towards the SAM.
-In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device.
-The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances.
-A capacitively coupled excitation line is also shown in green.
-Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux.
-Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second transmon (blue).
-Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)).
-This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency.
-Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.
+\subsection{Device design and control}
+We have designed the SAM as a pair of transmon 
+(Xmon) SAAs with asymmetric 
+SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
+\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
+$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
+to a single notch-type\cite{probst2015efficient} 
+$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
+1/100\ \text{ns}^{-1}$) which both 
+couples\cite{majer2007coupling} the transmons and 
+allows joint\cite{chow2010detecting} readout of 
+their states. In \autoref{fig:experiment}~(a), 
+the optical photograph of the device is shown 
+depicting the layout of the components. The 
+resonator in its upper part is connected to a 
+coplanar waveguide through which the readout is 
+performed. In its lower part, it is coupled to 
+the transmons by a dual 
+``claw''\cite{barends2013coherent} coupler. Flux 
+lines that allow independent control of the 
+transmon frequencies are coming from the sides. 
+Finally, the excitation waveguide coming from 
+below directs microwave signal towards the SAM. 
+In \autoref{fig:experiment}~(b), the equivalent 
+electrical circuit of the device is shown. The 
+resonator fundamental mode is approximated as an 
+LC-circuit (in the middle), the transmons are 
+shown in colour on the sides; their SQUIDs are 
+represented as tunable Josephson junctions. A 
+capacitively coupled excitation line is also 
+shown in green. Finally, in 
+\autoref{fig:experiment}~(c) we show 
+schematically the frequencies of the transmons 
+depending on electric current $I$ which we apply 
+to an external coil wound around the sample 
+holder. Since the effective junction of the first 
+transmon is larger, its spectrum (orange) lies 
+higher in frequency than the spectrum of the 
+second transmon (blue). Using individual 
+flux-control lines, it is possible to align the 
+SAAs so that the lower sweet-spot of the orange 
+transmon is just below the upper sweet-spot of 
+the blue transmon (see the dashed rectangle,  
+\autoref{fig:experiment}~(c)). This configuration 
+is, as we will show in the following, convenient 
+to track the energies of highly excited levels 
+via multi-photon transitions in a single 
+spectroscopic scan. Additionally, the transmons 
+are better protected from the flux noise in this 
+area being close to their sweet spots.
 
@@
 	 	\includegraphics[width=\linewidth]{experiment_2}
-	\caption{\textbf{(a)} Optical photograph of the device (false coloured).
-Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator.
-Frequency control lines come from both sides, and from below a microwave excitation waveguide is connected (green).
-\textbf{(b)} The equivalent electrical circuit.
-Tunable Josephson junctions are SQUIDs with magnetic flux control.
-\textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (proportional to the currents applied to control lines).
-In this work, we focus on the area inside the dashed rectangle.}
+	\caption{\textbf{(a)} Optical photograph of 
+	the device (false coloured). Two transmons 
+	(orange, 1 and blue, 2) are coupled 
+	capacitively to a $\lambda/4$ coplanar 
+	resonator. Frequency control lines come from 
+	both sides, and from below a waveguide for 
+	microwave excitation  is connected (green). 
+	\textbf{(b)} The equivalent electrical 
+	circuit. Tunable Josephson junctions are 
+	SQUIDs with magnetic flux control. 
+	\textbf{(c)} Frequencies of the fundamental 
+	transitions of the transmons $\omega_1(I)$ 
+	and $\omega_2(I)$ depending on the current 
+	$I$ in an external coil when correctly 
+	aligned by the individual flux control lines. 
+	In this work, we focus on the area inside the 
+	dashed rectangle.}
 	\label{fig:experiment}
@@
 	\end{ruledtabular}
-	\caption{SAM parameters.
-Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}.
-The coupling strength $J$ depends on the transmon frequencies and is specified here for $\omega_1 = \omega_2 = 5.32$ GHz.}
+	\caption{SAM parameters. Transmons are only 
+	different in the frequency tuning range and 
+	coherence times measured in the lower sweet 
+	spot for the 1\textsuperscript{st} one and in 
+	the higher sweet spot for the 
+	2\textsuperscript{nd}. The coupling strength 
+	$J$ depends on the transmon frequencies and 
+	is specified here for $\omega_1/2\pi = 
+	\omega_2/2\pi = 5.32$ GHz.}
 	\label{tab:parameters}
@@
 
-A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity.
-Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
-\begin{equation}
-\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
-\end{equation}
-where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or from ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon.
-Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}.
-In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).
-
-To drive a quantum system, one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line.
-The driving term between the transmon and the field is then modelled by the following operator:
+A single transmon SAA can be regarded as an 
+oscillator with a quartic perturbation describing 
+the leading-order anharmonicity. Therefore, in 
+the main text we do not use the charge and phase 
+operators and write down its Hamiltonian using 
+only the annihilation operator $\hat b$:
+\begin{equation}
+\hat{{H}}_{tr}/\hbar = \omega \hat 
+b^{\dagger}\hat b +\frac{1}{2}\alpha \hat 
+b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
+\label{eq:h1tr}
+\end{equation}
+where $\omega$ is its 
+$\ket{0}\rightarrow\ket{1}$, or fundamental, 
+transition frequency and $\alpha$ is the 
+anharmonicity of the transmon. By applying 
+magnetic flux to the transmon's SQUID (either via 
+an individual on-chip line or via an external 
+coil) it is possible\cite{koch2007charge} to 
+directly  control $\omega$. In our modelling, we 
+take into account the three lowest states of the 
+transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).
+
+\autoref{eq:h1tr} describes the SAA without 
+interaction with light. To model a monochromatic 
+microwave signal of frequency $\omega_d$ applied 
+through a capacitively coupled transmission line, 
+the following driving term should be included in 
+the Hamiltonian:
 \begin{equation}
@@
 
-Now, the complete Hamiltonian of SAM contains two terms describing each of them (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
+Next, we assemble the model for two coupled 
+transmons with the corresponding annihilation 
+operators $\hat b$ and $\hat c$, the fundamental 
+frequencies $\omega_{1,2}$ and anharmonicities 
+$\alpha_{1,2}$. The corresponding Hamiltonian of 
+the SAM contains two terms representing each 
+transmon, two terms representing the interaction 
+of each transmon with the driving field at the 
+same frequency $\omega_d$, and the 
+transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
@@
 \end{equation}
-where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms.
-Strictly speaking, $J = J(\omega_1, \omega_2)$ depends on the transmon frequencies\cite{koch2007charge}, but we take $J$ to be a constant as in \autoref{tab:parameters} due to its negligible variation for our range of frequencies.
-
-For brevity, the SAM Hamiltonian without driving terms and the corresponding eigenenergies will be denoted below as ``unperturbed''.
-
-In the following, we will also transform \autoref{Hsystem} into the frame rotating with both drives by an operator
-\begin{equation}
-\hat R = \exp[-i t (\omega_d^1 b^{\dagger}b+\omega_d^2 c^{\dagger}c)],\label{eq:R}
+where $\hat H_{int} = \hbar J (\hat b +\hat 
+b^\dag)(\hat c+\hat c^{\dagger})$ is the 
+transverse interaction between the atoms. 
+Strictly speaking, $J = J(\omega_1, \omega_2)$ 
+depends on the transmon 
+frequencies\cite{koch2007charge}, but we take $J$ 
+to be a constant as in \autoref{tab:parameters} 
+due to its negligible variation for our range of 
+frequencies.
+
+For brevity, the SAM Hamiltonian without driving 
+terms and the corresponding eigenenergies will be 
+referred below as ``unperturbed''. Since we take 
+3 levels for each transmon, there will be total 9 
+basis states of the SAM $\ket{i}\otimes \ket{j} = 
+\ket{ij}$, where $i$ and $j$ show the number of 
+excitations in the first transmon, and in the 
+second one, respectively.
+
+In the following, we will also transform 
+\autoref{Hsystem} into the frame rotating with 
+both drives by an operator
+\begin{equation}
+\hat R = \exp[-i t (\omega_d^1 
+b^{\dagger}b+\omega_d^2 
+c^{\dagger}c)],\label{eq:R}
 \end{equation}
@@
 \begin{equation}
-\hat H_R = \hat R^{\dagger}\hat H \hat R -	 {i}\hat R^{\dagger}\partial_t \hat R.\label{eq:rotation}
+\hat H_R = \hat R^{\dagger}\hat H \hat R -	 
+{i}\hat R^{\dagger}\partial_t \hat 
+R.\label{eq:rotation}
 \end{equation}
@@
 	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
-	\hat H_{int} &\rightarrow \hbar J \left[\hat b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} + \hat b \hat c^\dag e^{-it(\omega_d^1 - \omega_d^2)}\right],\\
+	\hat H_{int} &\rightarrow \hbar J \left[\hat 
+	b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} 
+	+ \hat b \hat c^\dag e^{-it(\omega_d^1 - 
+	\omega_d^2)}\right],\\
 	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
@@
 
-Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon.
-They are modelled using the Lindblad equation with the following collapse operators\cite{bishop2010circuit}:
+Besides the unitary evolution, we take into 
+account the incoherent processes of relaxation 
+and dephasing for each transmon. They are 
+modelled using the Lindblad equation with the 
+following collapse 
+operators\cite{bishop2010circuit}:
 \begin{equation}\
@@
 \hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
-\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
+\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
+\hat b^\dag \hat b,\\
 \hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
-\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, \hat c^\dag \hat c,
+\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
+\hat c^\dag \hat c,
 \end{split}
 \end{equation}
-where $\gamma_{1,2}$ are the individual relaxation rates, and $\gamma_{\phi (1,2)}$ are the pure dephasing rates.
-As one can see, the collapse operators are in a separable form, i.e.
-acting only upon a single transmon each.
-This is a valid approach until the coupling strength $J$ is not too large\cite{beaudoin2011dissipation}.
-Therefore, the complete evolution equation for the system density matrix $\hat \rho$ is
-\begin{equation}
-\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
-\end{equation}
-where $\mathcal{D}[\hat{{O}}]\hat \rho = \hat{{O}} \hat \rho \hat{{O}}^\dag - \frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat \rho\}$ and $\mathcal{L}$ is the Liouville superoperator or the Liouvillian.
-
-The readout resonator is not included in the model since in the dispersive regime it does not affect the dynamics of the SAM.
-Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}.
-Another way to find $\hat M(f_p)$ is to calculate the transmission by offsetting the experimental resonance curve using the dispersive shifts corresponding to these states.
-Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters.
-Finally, the observable value for any state $\hat \rho$ is calculated as $S_{21}^{sim}(f_p) = \Tr[\hat M(f_p) \hat \rho]$.
+where $\gamma_{1,2}$ are the individual 
+relaxation rates, and $\gamma_{\phi (1,2)}$ are 
+the pure dephasing rates. As one can see, the 
+collapse operators are in a separable form, i.e. 
+acting only upon a single transmon each. This is 
+a valid approach until the coupling strength $J$ 
+is not too large\cite{beaudoin2011dissipation}. 
+Therefore, the complete evolution equation for 
+the system density matrix $\hat \rho$ is
+\begin{equation}
+\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
+\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
+\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
+= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
+\end{equation}
+where $\mathcal{D}[\hat{{O}}]\hat \rho = 
+\hat{{O}} \hat \rho \hat{{O}}^\dag - 
+\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
+\rho\}$ and $\mathcal{L}$ is the Liouville 
+superoperator, or the Liouvillian; $_{(R)}$ 
+denotes if the Hamiltonian and the corresponding 
+solution density matrix are in the rotating frame 
+with RWA. In this work, we do not alter the 
+dissipator terms when changing the reference 
+frame despite that it may not be correct in 
+general\cite{shavit2019bridging}.
+
+The readout resonator is not included in the 
+model since in the dispersive regime it does not 
+affect the dynamics of the SAM. Hence, the 
+readout is modelled just by some measurement 
+operator $\hat M(f_p)$ that can be obtained by 
+finding the transmission $S_{21}(f_p)$ ($f_p$ is 
+the probe frequency near the resonance) through 
+the sample after preparing various states of the 
+SAM. Another way to find $\hat M(f_p)$ is to 
+calculate $S_{21}(f_p)$ via offsetting the 
+experimental resonance curve measured when the 
+SAM is in the ground state by the dispersive 
+shifts corresponding to the SAM basis 
+states\cite{filipp2009two}. Since we have not 
+directly measured these dispersive shifts, in our 
+modelling they are treated as fitting parameters. 
+Finally, the observable value for any state $\hat 
+\rho$ is calculated as $S_{21}^{sim}(f_p) = 
+\Tr[\hat M(f_p) \hat \rho]$.
 
@@
 
-Numerical simulations are crucial for studying \autoref{eq:master} since is does not allow  analytical solution.
-Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.
-
-Two distinct modes of simulation were used during the modelling.
-The first one is for the Liouvillians that do not explicitly depend on time (stationary case).
-In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \autoref{eq:master}
-\begin{equation}
-\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} \hat \rho = 0
-\end{equation}
-This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
-This method is applicable when the driving of the two transmons is at the same frequency since from \autoref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.
-
-The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian or if one wants to solve the master equation in the laboratory frame.
-For example, when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$), from \autoref{eq:RWA} we find that even in the doubly-rotating frame, $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because it is inherent for the SAM.
-In this case, to find the steady state of the system one can employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions.
-The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \autoref{eq:master}, it is defined as
+Numerical simulations are necessary for studying 
+\autoref{eq:master} since is does not have an 
+analytical solution. We have been using the 
+\textit{qutip}\cite{johansson2013qutip} (quantum 
+optics toolbox in Python) to simulate the 
+dynamics and to find the steady state of the 
+system for various parameter combinations of the 
+Liouvillian.
+
+Two distinct modes of simulation were used in the 
+modelling. The first one is for the Liouvillians 
+that do not explicitly depend on time. In this 
+case, the steady state $\hat \rho_{ss}$ of the 
+system should be calculated from the set of 
+linear equations obtained from \autoref{eq:master}
+\begin{equation}
+\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
+\hat \rho = 0
+\label{eq:steady}
+\end{equation}
+This equation is solved with the qutip's 
+\textit{steadystate} 
+function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
+ This method is applicable when the driving 
+frequency for both transmons is the same because 
+from \autoref{eq:RWA} follows that $\hat H_{int}$ 
+is time independent when $\omega_d^1 = 
+\omega_d^2$.
+
+The second mode is required when it is not 
+possible to avoid the time-dependence of the 
+Liouvillian or if one wants to solve the master 
+equation in the laboratory frame. For example, 
+when the transmons have to be excited at 
+different frequencies ($\omega_d^1 - \omega_d^2 = 
+\delta \neq 0$), from \autoref{eq:RWA} we find 
+that even in the doubly-rotating frame, $\hat 
+H_{int}$ is oscillating, and it is not possible 
+to simply drop this term in RWA because it is 
+inherent for the SAM. In this case, to find the 
+steady state of the system one can employ the 
+qutip's \textit{propagator} and 
+\textit{propagator\_steadystate} functions. The 
+propagator is a completely positive map 
+$\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow 
+\hat \rho(t_1)$ describing the time evolution of 
+the system density matrix; for 
+\autoref{eq:master}, it is defined as
 \begin{equation}
@@
 \end{equation}
-where $\mathcal T$ is the time-ordering superoperator.
-Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}.
-Upon infinite applications of $\Lambda$
+where $\mathcal T$ is the time-ordering 
+superoperator. Since the Liouvillian is periodic 
+with a period of $T = 2\pi/\delta$, it is 
+possible to calculate the steady state as the 
+eigenvector $\hat \rho_{ss}$ of the single-period 
+propagator $\Lambda(T, 0)$ corresponding to its 
+largest eigenvalue\cite{dittrich1998quantum, 
+rivas2012open}. Upon infinitely many applications 
+of $\Lambda$
 \[
@@
 	\includegraphics[width=.495\linewidth]{stationary}
-	\caption{Two-tone spectroscopy: experiment \textbf{(a)} and numerical modelling \textbf{(b)}.
-Colour shows the real part of complex transmission  through the sample.
-Two transmons are aligned as in \autoref{fig:experiment}~(c) and form a symmetric picture.
-Experimental data contain an additional horizontal line from a parasitic resonance interacting with the readout resonator.
-Three avoided crossings not predicted by the unperturbed model are shown in insets I, II and III; other pronounced features reproduced by the modelling are shown with numbered markers (see text for description).
-We also denote some of the transitions $ij/n$ (see Section \ref{sec:analysis} for notation).
-\textbf{(c)} Slices of the spectrum at various currents: 0.365 mA (feature III), 0.411 mA (sweet spot), 0.333 mA (feature I); experiment is gray, theory is black.
-Spectral lines where only one SAA is excited are highlighted with the corresponding colour from \autoref{fig:experiment}.
-Rabi frequencies $\Omega_{1,2}$ may be extracted as FWHM of the spectral lines 10 and 01, respectively.
-\textbf{(d)} Simulated population of the state $\ket{10}$ ($\lg P_{\ket{10}}$ is shown with colour).
-Lines show various transition frequencies from the unperturbed Hamiltonian.
-Legend labels transitions at the sweet spot current; if elsewhere any two lines cross, the labels should be swapped after the intersection.}
+	\caption{Two-tone spectroscopy: experiment 
+	and numerical modelling. \textbf{(a)} 
+	Experimental data. Colour shows the real part 
+	of complex transmission  through the sample. 
+	Two transmons are aligned as in 
+	\autoref{fig:experiment}~(c) and form a 
+	symmetric picture. Experimental data contain 
+	an additional horizontal line from a 
+	parasitic resonance interacting with the 
+	readout resonator. Three avoided crossings 
+	not predicted by the unperturbed model are 
+	shown in insets I, II and III; other 
+	pronounced features reproduced by the 
+	modelling are shown with Arabic markers (see 
+	text for description). \textbf{(b)} Numerical 
+	simulation reproducing experimental results 
+	with labelled transitions (see Section 
+	\ref{sec:analysis} for notation). 
+	\textbf{(c)} Slices of (a) and (b) at various 
+	currents: 0.365 mA (feature III), 0.411 mA 
+	(sweet spot), 0.333 mA (feature I); 
+	experiment is gray, simulation is black. 
+	Spectral lines where only one SAA is excited 
+	are highlighted with the corresponding colour 
+	from \autoref{fig:experiment}. Rabi 
+	frequencies $\Omega_{1,2}$ may be extracted 
+	as FWHM of the spectral lines 10 and 01, 
+	respectively. \textbf{(d)} Simulated 
+	population of the state $\ket{10}$ ($\lg 
+	P_{\ket{10}}$ is shown with colour). Lines 
+	show various transition frequencies from the 
+	unperturbed Hamiltonian. Legend labels 
+	transitions near the sweet spot current; if 
+	elsewhere any two lines form an avoided 
+	crossing, the labels should be swapped after 
+	the intersection.}
 	\label{fig:two-tone}
@@
 
-Experiment was conducted as described in Appendix \ref{sec:meas_setup}.
-We have used high-power two-tone spectroscopy to probe transitions between eigenstates of our SAM; the result is shown in \autoref{fig:two-tone}~(a).
-As one can see, several spectral lines are visible besides the $ge$ ones shown in \autoref{fig:experiment}~(c).
-Their frequency depends on the applied current, and at multiple points they become resonant with each other.
-At three pairs of these resonant points, we observe distinct features shown in insets marked with Roman numbers.
-Some secondary details are shown with Arabic-numbered markers.
-
-Remarkably, in areas I, II and III we could observe avoided crossings and triplet transitions which turn out to be impossible to explain using only the Hamiltonian with no driving.
-We confirm this by numerically diagonalizing $\hat H_{tr}^1+\hat H_{tr}^2+\hat H_{int}$ taking 3 levels for each transmon (and total 9 basis states of SAM); all possible transitions between all eigenlevels of the SAM are shown in \autoref{fig:two-tone}~(d).
-While correctly reproducing, for instance, the avoided crossing labelled as feature 3 in \autoref{fig:two-tone}~(a), it completely misses the Roman-numbered effects.
-Taking into account more energy levels for transmons does not help, and is not even necessary to reproduce the experiment, as we will show in the following.
-
-To check whether the described features are present in the dynamic regime, we have solved the master equation \autoref{eq:master} to find the steady states of the system $\hat \rho_{ss}$ and the corresponding expected measurement outcomes $\mathfrak{Re}\left[\Tr[\hat M \hat \rho_{ss}]\right]$ depending on the excitation frequency and magnetic flux.
-Strikingly, all the experimental features are immediately reproduced using this approach with just 9 SAM states as shown in \autoref{fig:two-tone}~(b).
-We have solved \autoref{eq:master} with and without RWA (using the propagator approach \autoref{eq:propagator}) and did not find any noticeable difference in the results; though, the runtime of the whole 401 by 401 points simulation was 9 hours without RWA vs.
-3 minutes with RWA.
-As can be seen from \autoref{fig:two-tone}~(c), the numerical results are in a good agreement with the experiment (the spurious resonance is softened).
-A small discrepancy is that $12/3$ line is much less pronounced in the numerical data.
+Experiment was conducted as described in Appendix 
+\ref{sec:meas_setup}. We use high-power two-tone 
+spectroscopy to probe transitions between 
+eigenstates of the SAM; the result is shown in 
+\autoref{fig:two-tone}~(a). As one can see, some 
+new spectral lines are visible besides the 
+fundamental ones that were shown in 
+\autoref{fig:experiment}~(c). Their frequency 
+also depends on the applied current, and at 
+several points they become resonant with each 
+other. At three pairs of such resonant points, we 
+observe distinct features shown in insets marked 
+with Roman numbers. Some secondary details are 
+shown with Arabic-numbered markers.
+
+In areas I, II and III, we observe peculiar 
+avoided crossings forming triplet transitions. In 
+I and II, they are barely visible, however in III 
+the splitting is very pronounced. To check 
+whether our theoretical model summarized in 
+\autoref{eq:master} can reproduce the 
+experimental spectrum, we have solved the master 
+equation \autoref{eq:master} finding the steady 
+states of the system $\hat \rho_{ss}$ and the 
+corresponding expected measurement outcomes 
+$\mathfrak{Re} \Tr[\hat M \hat \rho_{ss}]$ 
+depending on the excitation frequency and 
+magnetic flux. The results are shown in 
+\autoref{fig:two-tone}~(b) where all the 
+experimental details are immediately reproduced 
+with just 9 SAM states (i.e., 3 levels for each 
+transmon). We have solved \autoref{eq:master} in 
+the rotating frame with RWA using 
+\autoref{eq:steady} and in the lab frame (using 
+the propagator approach \autoref{eq:propagator}) 
+and did not find any noticeable difference in the 
+results; though, the runtime of the whole 401 by 
+401 points simulation was 9 hours without RWA vs. 
+3 minutes with RWA. As can be seen from three 
+slices of \autoref{fig:two-tone}~(a),(b) in 
+\autoref{fig:two-tone}~(c), the numerical results 
+are in a good agreement with the experiment (the 
+spurious resonance is softened). The parameters 
+of model were chosen to match with the 
+experimental data.
+
+Remarkably, features I, II and III turn out to be 
+impossible to explain using only the unperturbed 
+Hamiltonian; we confirm this by numerical 
+diagonalization taking the same 9 SAM states as 
+in the previous simulation. All possible 
+transitions between all resulting eigenlevels of 
+the SAM depending on the coil current are shown 
+in \autoref{fig:two-tone}~(d) with solid and 
+dashed lines. While correctly reproducing, for 
+instance, the avoided crossing labelled as 
+feature 3 in \autoref{fig:two-tone}~(a), it 
+completely misses the Roman-numbered effects.
+
+So far, we have established the fact that the 
+same model SAM yields different spectra depending 
+on the presence of the driving, and that the full 
+model \autoref{eq:master} agrees well with 
+experimental data. To understand the nature of I, 
+II and III, we describe \autoref{fig:two-tone} in 
+more detail in a separate section below.
 
@@
 	\includegraphics[width=.7\linewidth]{powerscan_1d}
-	\caption{Power dependence of feature II: experiment and theory.
-Dashed are the model curves turning to dotted when the model is not expected to be valid (see Sections \ref{sec:theory} and \ref{sec:münchhausen}); model values for $\Omega_2$ are the same for both (a) and (b): $\Omega_{2}/2\pi=$ 4.5, 11.25, 22.5 and 45 MHz.
-\qquad	\textbf{(a)} Experiment (second cooldown; the parameters are different to those in \autoref{fig:experiment}).
-The power of the microwave source is increased from -20 to 0 dBm and the corresponding growth of the splitting and the widths of the spectral lines is observed.
-\textbf{(b)} Simulation with amplitudes of the driving $\Omega_{1,2}$ equal to the model values; other parameters as in \autoref{fig:two-tone}.
-Note that now colours show the population of the ground state.
-\textbf{(c)} Linear dependence of the splitting size on the driving voltage of the microwave source $V_{rms} = \sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ {\text{MHz}}/{\text{mV}}$.
-From Section \ref{sec:theory}, the splitting size is $\frac{2\sqrt{3}}{3} \Omega_2$.}
+	\caption{Power dependence of feature II: 
+	experiment, simulation and theory. Dashed are 
+	the model curves turning to dotted when the 
+	model is not expected to be valid (see 
+	Sections \ref{sec:theory} and 
+	\ref{sec:münchhausen}); model values for 
+	$\Omega_{1,2}$ are the same for both (a) and 
+	(b): $\Omega_{1,2}/2\pi=$ 4.5, 11.25, 22.5 
+	and 45 MHz. \textbf{(a)} Experiment (second 
+	cooldown; the parameters are different to 
+	those in \autoref{fig:experiment}). The power 
+	of the microwave source is increased from -20 
+	to 0 dBm, and the corresponding growth of the 
+	splitting and the widths of the spectral 
+	lines is observed. \textbf{(b)} Simulation 
+	with amplitudes of the driving $\Omega_{1,2}$ 
+	equal to the model values; other parameters 
+	as in \autoref{fig:two-tone}. Note that now 
+	colours show the population of the ground 
+	state. \textbf{(c)} Linear dependence of the 
+	splitting size on the driving voltage of the 
+	microwave source $V_{rms} = 
+	\sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 
+	50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
+	{\text{MHz}}/{\text{mV}}$. From Section 
+	\ref{sec:theory}, the splitting size is 
+	$\frac{2\sqrt{3}}{3} \Omega_2$.}
 	\label{fig:zoom}
@@
 	\includegraphics[width=\linewidth]{topological_splittings}
-	\caption{Simulated population of the ground state when the transmons are driven at the same frequency but at different amplitudes $\Omega_{1,2}$.
-In the top row (middle row), $\Omega_{1(2)}$ is increased while $\Omega_{2(1)} = \text{const} \ll \Omega_{1(2)}$; two topologically different types of anticrossings arise depending on which transmon is driven stronger.
-In the bottom row, we show how the splittings vanish when the weaker driving is increased to match with the stronger one.
-Gray dashed lines show the solution with no driving, in black are the model curves based on Sections \ref{sec:theory} and \ref{sec:münchhausen}.}
+	\caption{Simulated population of the ground 
+	state when the transmons are driven at the 
+	same frequency but at different amplitudes 
+	$\Omega_{1,2}$. In the top row (middle row), 
+	$\Omega_{1(2)}$ is increased while 
+	$\Omega_{2(1)} = \text{const} \ll 
+	\Omega_{1(2)}$; two topologically different 
+	types of anticrossings arise depending on 
+	which transmon is driven stronger. In the 
+	bottom row, we show how the splittings vanish 
+	when the weaker driving is increased to match 
+	with the stronger one. Gray dashed lines show 
+	the solution with no driving, in black are 
+	the model curves based on Sections 
+	\ref{sec:theory} and \ref{sec:münchhausen}.}
 	\label{fig:difdrive}
@@
 
-\subsection{Analysis of the spectra} \label{sec:analysis}
-
-\paragraph{Identification of the spectral lines.} Though it is not possible to describe all of the experimental features with the unperturbed model, we can use it to find which spectral lines correspond to which transitions in the system (see \autoref{fig:two-tone}~(d)).
-In \autoref{fig:two-tone}~(b), we have labelled the brightest lines with $ij/n$ where $i,j$ denote the final transmon state $\ket{ij}$ after the transition from the ground state $\ket{00}$, and $/n$ is optional for an $n$-photon process; we also use this notation throughout the text.
-The labels are put at the points where the SAM states are nearly factorized (dispersive regime for two coupled SAAs) and thus may be easily distinguished.
-
-Due to the strong driving, we observe several multiphoton transitions besides the main lines at $\omega_{(1,2)}(\Phi_e)/2\pi$.
-The ${02/2}$ and ${20/2}$ are very commonly found for transmons and lie $|\alpha_{(1,2)}|/2$ lower than the main lines $\omega_{(1,2)}(\Phi_e)$.
-Another two-photon process appears as $11/2$ line when two SAAs are excited simultaneously.
-This process is used, for example, for doing the bSWAP gate\cite{poletto2012entanglement}; in our case, it is taking part in formation of feature I.
-A three-photon process $12/3$ is also clearly visible just below the $02/2$ line.
-As we will see, it is involved in forming features II and III.
-Notably, transitions $11/2$ and ${12/3}$ are forbidden when there is no interaction ($J=0$).
-Therefore, it is expected that all Roman-numbered features should only appear with non-vanishing $\hat H_{int}$.
-
-When two lines intersect, they may form an avoided crossing if the corresponding matrix element of $\hat H_{int}$ is non-zero.
-In such cases, the SAM becomes inseparable with some of the eigenstates becoming superpositions of the factorized states.
-For a two-transmon SAM, such points are, for instance, crossings between ${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $).
-Additionally, marked as feature 3 in \autoref{fig:two-tone}, we see an avoided crossing between ${12}/3,\ {21}/3$ at the same $\Phi_e$ where ${01}$, ${10}$ intersect.
+\subsection{Analysis of the spectra} 
+\label{sec:analysis}
+
+\paragraph{Identification of the spectral lines.} 
+Though it is not possible to describe all of the 
+experimental features with the unperturbed model, 
+we can still use it to identify most of the 
+observed transitions as follows. As said above, 
+by numerical diagonalization, we calculate the 
+unperturbed frequencies of the undriven SAM as 
+$\omega_{mn} = (E_n - E_m)/h$ where $n>m,\  
+n,m=0..9$. In \autoref{fig:two-tone}~(d), we 
+place them over the heatmap data depicting the 
+population of $\ket{10}$ optionally dividing 
+$\omega_{mn}$ by some integer $n$ to find the 
+frequency of an $n$-photon process to find a 
+match among the visible lines in the heatmap. 
+Since the number of SAM states is finite, we can 
+quickly find all such correspondences.
+
+Next, at the sweet spot, we name the found lines 
+as $ij/n$ where $i,j$ denote the final basis 
+state $\ket{ij}$ of the SAM after the transition 
+from the ground state, and $/n$ is optional for 
+an $n$-photon process. We can do that because at 
+the sweet spot the transmons are detuned from 
+each other, and thus SAM eigenstates are nearly 
+factorized (dispersive regime). Using this 
+notation, we label lines in 
+\autoref{fig:two-tone}~(b),(c), as well. One 
+should be careful because for 
+\autoref{fig:two-tone}~(d) this notation is valid 
+only near the sweet spot before any two lines 
+form an avoided crossing. When they do, their 
+names should be swapped.
+
+Having settled the naming system, we continue to 
+analyse the plots. Due to the strong driving, we 
+observe several multiphoton transitions besides 
+the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
+$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
+are very commonly found for transmons and lie 
+$|\alpha_{(1,2)}|/2$ lower than the main lines 
+$\omega_{(1,2)}(I	)$. Another two-photon process 
+appears as $11/2$ line when two SAAs are excited 
+simultaneously. This process is used, for 
+example, for doing the bSWAP 
+gate\cite{poletto2012entanglement}; in our case, 
+it is taking part in formation of feature I. A 
+three-photon process $12/3$ is also clearly 
+visible just below the $02/2$ line. As we will 
+see, it is involved in forming features II and 
+III. Notably, transitions $11/2$, ${21/3}$ and 
+${12/3}$ are forbidden when there is no 
+interaction between transmons ($J=0$). Therefore, 
+it is expected that all Roman-numbered features 
+should only appear with non-vanishing $\hat 
+H_{int}$.
+
+When two lines intersect, they may form an 
+avoided crossing if the corresponding matrix 
+element of $\hat H_{int}$ is non-zero. In such 
+cases, the SAM becomes inseparable with some of 
+the eigenstates becoming superpositions of the 
+factorized states. For a two-transmon SAM, such 
+points are, for instance, crossings between 
+${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $). 
+Additionally, marked as feature 3 in 
+\autoref{fig:two-tone}, we see an avoided 
+crossing between ${12}/3,\ {21}/3$ at the same 
+$\Phi_e$ where ${01}$, ${10}$ intersect.
 
@@
 
-From \autoref{fig:two-tone}~(d) we conclude that avoided crossing in III is between two transitions: ${12/3}$ and ${10} - {02}$ ($\ket{10}\rightarrow\ket{02}$) which are of the same frequency when $\omega_1 = \omega_2+\alpha_2/2$.
-The latter process is discernible in \autoref{fig:two-tone}~(d) as it depopulates ${10}$, but is not visible in \autoref{fig:two-tone}~(a),(b).
-In II, the reversed is true: ${21/3}$ and ${01} - {20}$ are crossing when $\omega_2 = \omega_1+\alpha_1/2$.
-From additional measurements and simulations, we find that the splitting depends on the driving power; the experimental and simulated results for II are shown in \autoref{fig:zoom}~(a), (b).
-As one can see, the growth of the splitting with increasing power is linear: it is roughly equal to the FWHM of the ${01}$ spectral line.
-To fully quantify the shape of this splitting, in Section \ref{sec:theory} we derive analytical expressions for the dashed curves fitting the spectral lines in \autoref{fig:zoom}.
-By measuring the dependence of the splitting size on the microwave power we confirm its proportionality to the signal amplitude (see \autoref{fig:zoom}~(c)).
-
-We see a similar behaviour for feature I: increasing drive amplitude on one of the transmons while keeping the other one small and constant again elicits avoided crossings with the proportional size.
-In \autoref{fig:difdrive} we show only the simulation results; an experiment is not possible with our sample because there is no way to adjust the driving amplitudes $\Omega_{1,2}$ individually.
-We note that two qualitatively different patterns arise depending on which of the transmons is driven stronger than the other.
-From this and from the shape of the splitting in feature I of \autoref{fig:two-tone}~(a), we can infer that $\Omega_1/\Omega_2 \approx 2$ there (also consistent with the 01, 10 linewidths in \autoref{fig:two-tone}~(c)).
-
-These observations mean that effects I -- III are caused by light dressing.
-In the case III, the first transmon is dressed by a strong resonant field; in case II, the second one; finally, in case I, both transmons are dressed at the same time.
-We will discuss these effects in greater detail in Section \ref{sec:theory}.
-
-\paragraph{Secondary features.} Using \autoref{fig:two-tone}~(d), we can get an insight into the features 1 -- 5 as well.
-
-Feature 1 is a small avoided crossing between ${02/2}$ and ${21/3}$.
-It is missing in the unperturbed solution and thus is caused by the light dressing just as I -- III.
-Feature 2 is its twin: ${12/3}$ and ${20/2}$ intersect there but the anticrossing is smaller due to the asymmetry of the driving strengths and is not resolved.
-
-Feature 3 is a large avoided crossing between three-photon processes ${12/3}$ and ${21/3}$.
-It is predicted by the unperturbed model, and direct diagonalization yields the splitting of $\frac{4}{3}J$.
-A remarkable detail here is that the dim lower branch implies the presence of a dark state with respect to the driving operator in the third order.
-
-Feature 4 is also explained by the unperturbed model and is caused by several spectral lines and a pair of avoided crossings near a single point (dotted lines in \autoref{fig:two-tone}~(d)).
-It appears at the point where ${02/2}$ intersects ${20/2}$ and is just barely visible in the experimental data because of the noise.
-Feature 5 is located at the intersection between ${20/2}$ and normally invisible ${10} - {02}$, and can be found in the experimental data, too.
+From \autoref{fig:two-tone}~(d) we conclude that 
+avoided crossing in III is between two 
+transitions: ${12/3}$ and ${10} - {02}$ 
+($\ket{10}\rightarrow\ket{02}$) which are of the 
+same frequency when $\omega_1 = 
+\omega_2+\alpha_2/2$. The latter process is 
+discernible in \autoref{fig:two-tone}~(d) as it 
+depopulates ${10}$, but is not visible in 
+\autoref{fig:two-tone}~(a),(b). In II, the 
+reversed is true: ${21/3}$ and ${01} - {20}$ are 
+crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
+From additional measurements and simulations, we 
+find that the splitting depends on the driving 
+power; the experimental and simulated results for 
+II are shown in \autoref{fig:zoom}~(a), (b). As 
+one can see, the growth of the splitting with 
+increasing power is linear: it is roughly equal 
+to the FWHM of the ${01}$ spectral line. To fully 
+quantify the shape of this splitting, in Section 
+\ref{sec:theory} we derive analytical expressions 
+for the dashed curves fitting the spectral lines 
+in \autoref{fig:zoom}. By measuring the 
+dependence of the splitting size on the microwave 
+power we confirm its proportionality to the 
+signal amplitude (see \autoref{fig:zoom}~(c)).
+
+We see a similar behaviour for feature I: 
+increasing drive amplitude on one of the 
+transmons while keeping the other one small and 
+constant again elicits avoided crossings with the 
+proportional size. In \autoref{fig:difdrive} we 
+show only the simulation results; an experiment 
+is not possible with our sample because there is 
+no way to adjust the driving amplitudes 
+$\Omega_{1,2}$ individually. We note that two 
+qualitatively different patterns arise depending 
+on which of the transmons is driven stronger than 
+the other. From this and from the shape of the 
+splitting in feature I of 
+\autoref{fig:two-tone}~(a), we can infer that 
+$\Omega_1/\Omega_2 \approx 2$ there (also 
+consistent with the 01, 10 linewidths in 
+\autoref{fig:two-tone}~(c)).
+
+These observations mean that effects I -- III are 
+caused by light dressing. In the case III, the 
+first transmon is dressed by a strong resonant 
+field; in case II, the second one; finally, in 
+case I, both transmons are dressed at the same 
+time. We will discuss these effects in greater 
+detail in Section \ref{sec:theory}.
+
+\paragraph{Secondary features.} Using 
+\autoref{fig:two-tone}~(d), we can get an insight 
+into the features 1 -- 5 as well.
+
+Feature 1 is a small avoided crossing between 
+${02/2}$ and ${21/3}$. It is missing in the 
+unperturbed solution and thus is caused by the 
+light dressing just as I -- III. Feature 2 is its 
+twin: ${12/3}$ and ${20/2}$ intersect there but 
+the anticrossing is smaller due to the asymmetry 
+of the driving strengths and is not resolved.
+
+Feature 3 is a large avoided crossing between 
+three-photon processes ${12/3}$ and ${21/3}$. It 
+is predicted by the unperturbed model, and direct 
+diagonalization yields the splitting of 
+$\frac{4}{3}J$. A remarkable detail here is that 
+the dim lower branch implies the presence of a 
+dark state with respect to the driving operator 
+in the third order.
+
+Feature 4 is also explained by the unperturbed 
+model and is caused by several spectral lines and 
+a pair of avoided crossings near a single point 
+(dotted lines in \autoref{fig:two-tone}~(d)). It 
+appears at the point where ${02/2}$ intersects 
+${20/2}$ and is just barely visible in the 
+experimental data because of the noise. Feature 5 
+is located at the intersection between ${20/2}$ 
+and normally invisible ${10} - {02}$, and can be 
+found in the experimental data, too.
 
@@
 
-Since we had already connected the additional avoided crossings with the light dressing, it was natural to expect an Autler-Townes-like effect to be at the root of the additional spectral lines.
-For a three-level system, the standard A-T effect is reviewed in Appendix \ref{sec:3-level-at}.
-However, in our case the level structure and the effect itself are more complicated.
-
-First of all, since during the spectroscopy we apply only a single microwave tone ($\omega_d^1 = \omega_d^2$), for the A-T effect it has to be simultaneously the coupler and the probe; the latter must be much weaker than the former, as well.
-These conditions are satisfied when $\omega_{\{2,1\}} = \omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we can simultaneously excite transitions $01 (10)$ and $20/2 (02/2)$ (features II and III, respectively).
-Since the two-photon Rabi frequency is much smaller than the single-photon $\Omega_2$, it is natural to view this two-photon excitation as the probing process which does not affect the level structure.
-In contrast, single-photon excitation is strong enough to dress the system.
-In other words, in our case the A-T coupling operator is $\hat H_{d}^1$ (strong), and the probing operator is $\hat H_{d}^2$ (weak in the two-photon regime).
-However, their separation in our case is not in frequency, but in the Hilbert subspaces they act upon.
-
-Similarly, for feature I, the simultaneously excited transitions are $01(10)$ and the two-photon $11/2$.
-However, as we demonstrate in \autoref{fig:difdrive}, for the avoided crossings in I to be clearly observed it is required that $\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.
+Since we had already connected the additional 
+avoided crossings with the light dressing, it was 
+natural to expect an Autler-Townes-like effect to 
+be at the root of the additional spectral lines. 
+For a three-level system, the standard A-T effect 
+is reviewed in Appendix \ref{sec:3-level-at}. 
+However, in our case the level structure and the 
+effect itself are more complicated.
+
+First of all, since during the spectroscopy we 
+apply only a single microwave tone ($\omega_d^1 = 
+\omega_d^2$), for the A-T effect it has to be 
+simultaneously the coupler and the probe; the 
+latter must be much weaker than the former, as 
+well. These conditions are satisfied when 
+$\omega_{\{2,1\}} = 
+\omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we 
+can simultaneously excite transitions $01 (10)$ 
+and $20/2 (02/2)$ (features II and III, 
+respectively). Since the two-photon Rabi 
+frequency is much smaller than the single-photon 
+$\Omega_2$, it is natural to view this two-photon 
+excitation as the probing process which does not 
+affect the level structure. In contrast, 
+single-photon excitation is strong enough to 
+dress the system. In other words, in our case the 
+A-T coupling operator is $\hat H_{d}^1$ (strong), 
+and the probing operator is $\hat H_{d}^2$ (weak 
+in the two-photon regime). However, their 
+separation in our case is not in frequency, but 
+in the Hilbert subspaces they act upon.
+
+Similarly, for feature I, the simultaneously 
+excited transitions are $01(10)$ and the 
+two-photon $11/2$. However, as we demonstrate in 
+\autoref{fig:difdrive}, for the avoided crossings 
+in I to be clearly observed it is required that 
+$\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.
 
@@
 	\includegraphics[width=\linewidth]{main_scheme_2}  
-	\caption{Explaining feature III.
-\textbf{(a)} Schematic of the transition frequencies near III (not to scale).
-Red dashed line shows the current (0.36 mA) where the first transmon (orange) is below the second one (blue) exactly by $\alpha_2/2$ and several transitions become resonant.
-So far we assume that each transmon is driven at its own frequency.
-\textbf{(b)} System level structure at the resonant point including the driving $\hat H_{d}^1$ of the first transmon by a strong signal of amplitude $\Omega_1$ (orange ellipses) at a small detuning $\Delta_1$ from $\omega_1$.
-The second transmon driving is not shown here.
-Action of $\hat H_{int}$ in RWA is depicted as orange-blue circles.
-\textbf{(c)} In the frame rotating with the drive of the first transmon, all the states $\ket{0j},\ket{1j}$ become nearly degenerate ($\omega_1 \rightarrow \Delta_1$).
-Dressing by the strong excitation increases this splitting to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$.
-\textbf{(d)} Transitions in the light-dressed system when the second transmon is excited (level subspaces coupled by $\hat H_{d}^2$ are shown with blue ellipses).
-In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted: the green transitions are not shifted in frequency, the red are red-shifted by $\Omega^R_1/2$ and the blue are blue-shifted by $\Omega^R_1/2$.
-In the right part, the most contributing trajectories are depicted; red crosses show transitions that are forbidden without the coupling $J$.}
+	\caption{Explaining feature III. \textbf{(a)} 
+	Schematic of the transition frequencies near 
+	III (not to scale). Red dashed line shows the 
+	current (0.36 mA) where the first transmon 
+	(orange) is below the second one (blue) 
+	exactly by $\alpha_2/2$ and several 
+	transitions become resonant. So far we assume 
+	that each transmon is driven at its own 
+	frequency. \textbf{(b)} System level 
+	structure at the resonant point including the 
+	driving $\hat H_{d}^1$ of the first transmon 
+	by a strong signal of amplitude $\Omega_1$ 
+	(orange ellipses) at a small detuning 
+	$\Delta_1$ from $\omega_1$. The second 
+	transmon driving is not shown here. Action of 
+	$\hat H_{int}$ in RWA is depicted as 
+	orange-blue circles. \textbf{(c)} In the 
+	frame rotating with the drive of the first 
+	transmon, all the states $\ket{0j},\ket{1j}$ 
+	become nearly degenerate ($\omega_1 
+	\rightarrow \Delta_1$). Dressing by the 
+	strong excitation increases this splitting to 
+	$\Omega_1^R = \sqrt{\Omega_1^2 + 
+	\Delta_1^2}$. \textbf{(d)} Transitions in the 
+	light-dressed system when the second transmon 
+	is excited (level subspaces coupled by $\hat 
+	H_{d}^2$ are shown with blue ellipses). In 
+	the left part of the panel, all possible 
+	two-photon transitions near $\omega_1$ are 
+	depicted: the green transitions are not 
+	shifted in frequency, the red are red-shifted 
+	by $\Omega^R_1/2$ and the blue are 
+	blue-shifted by $\Omega^R_1/2$. In the right 
+	part, the most contributing trajectories are 
+	depicted; red crosses show transitions that 
+	are forbidden without the coupling $J$.}
 	\label{fig:main_scheme}
@@
 
-In \autoref{fig:main_scheme}, we elaborate on how exactly the A-T effect occurs for feature III.
-For simplicity, we will temporarily assume that each transmon is driven at its own frequency (this assumption will be lifted in the following section).
-For convenience, in \autoref{fig:main_scheme}~(a) we schematically reproduce the transitions near III where the first transmon (orange) is below the second (blue), and the resonance point in current is shown with a dashed red line.
-Next, \autoref{fig:main_scheme}~(b) demonstrates the level structure of the SAM at 0.36 mA.
-Nearly-resonant with $10$ (detuning $\Delta_1$) single-photon driving with $\hat H_d^1$ is shown with orange ellipses while much weaker two-photon $\hat H_d^2$ is not shown yet.
-Since from numerical simulations we know that the third level of the first transmon is not necessary to observe the splitting, $\ket{02}$ is shown transparent, and hereinafter the states $\ket{j2},\ j=0..2$ are not used in the modelling.
-
-The next step is to view the system in the frame rotating with the first transmon (\autoref{fig:main_scheme}~(c)) and then move to the  dressed picture similarly to Appendix \ref{sec:3-level-at}.
-Now, the first transmon splitting equals $\Omega_{1}^R = \sqrt{\Omega_1^2+\Delta_1^2}$, and its new eigenstates (dressed states) are denoted $\ket{a}$ and $\ket{b}$.
-Meanwhile, the second transmon energies stay the same.
+In \autoref{fig:main_scheme}, we elaborate on how 
+exactly the A-T effect occurs for feature III. 
+For simplicity, we will temporarily assume that 
+each transmon is driven at its own frequency 
+(this assumption will be lifted in the following 
+section). For convenience, in 
+\autoref{fig:main_scheme}~(a) we schematically 
+reproduce the transitions near III where the 
+first transmon (orange) is below the second 
+(blue), and the resonance point in current is 
+shown with a dashed red line. Next, 
+\autoref{fig:main_scheme}~(b) demonstrates the 
+level structure of the SAM at 0.36 mA. Detuned by 
+$\Delta_1$ from $10$, single-photon driving of 
+$\hat H_d^1$ is shown with orange ellipses while 
+much weaker two-photon $\hat H_d^2$ is not shown 
+yet. Since from numerical simulations we know 
+that the third level of the first transmon is not 
+necessary to observe the splitting, $\ket{20}$ is 
+shown transparent, and states $\ket{21},\ 
+\ket{22}$ are not shown.
+
+The next step is to view the system in the frame 
+rotating with the first transmon 
+(\autoref{fig:main_scheme}~(c)) and then move to 
+the  dressed picture similarly to Appendix 
+\ref{sec:3-level-at}. Now, the first transmon 
+splitting equals $\Omega_{1}^R = 
+\sqrt{\Omega_1^2+\Delta_1^2}$, and its new 
+eigenstates (dressed states) are denoted 
+$\ket{a}$ and $\ket{b}$. Meanwhile, the second 
+transmon energies stay the same.
 
@@
 
-Now, we will repeat this reasoning using a quantitative mathematical model.
-We start from the initial Hamiltonian \autoref{Hsystem}.
-To move to the rotating frame with \autoref{eq:rotation} and apply the RWA, will use the following operator:
-\begin{equation}
-R = \exp[-it \omega_d^1 (b^{\dagger}b+c^{\dagger}c)].
+Now, we will repeat this reasoning using a 
+quantitative mathematical model. We start from 
+the initial Hamiltonian \autoref{Hsystem}. To 
+move to the rotating frame with 
+\autoref{eq:rotation} and apply the RWA, will use 
+the following operator:
+\begin{equation}
+R = \exp[-it \omega_d^1 
+(b^{\dagger}b+c^{\dagger}c)].
 \end{equation}  
@@
 \begin{aligned}
-\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} \hat{\mathbbm{1}}-\frac{\Omega_1^R}{2}\hat \sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b +\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),\\
+\hat H^{D}/\hbar &= \left[\frac{\Delta_1}{2} 
+\hat{\mathbbm{1}}-\frac{\Omega_1^R}{2}\hat 
+\sigma_z\right] + \Delta_2 \hat b^{\dagger}\hat b 
++\frac{1}{2}\alpha_2 \hat b^{\dagger}\hat b(\hat 
+b^{\dagger}\hat b-1),\\
 \hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
@@
 \end{equation}
-The first part is diagonal, and the remaining two will be treated as perturbations.
-To simplify further calculations, we consider the point where $\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$.
-In these conditions, $H^D$ becomes degenerate as can be seen in \autoref{eq:ham_matrix} of Appendix \ref{sec:dpt}.
-Using the degenerate perturbation theory for $\hat V_J$ summarized therein, we find the first-order corrected wave functions of $\hat H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.
+The first part is diagonal, and the remaining two 
+will be treated as perturbations. To simplify 
+further calculations, we consider the point where 
+$\Delta_1 = 0$ and $\Delta_2 = - \alpha_2/2$. In 
+these conditions, $H^D$ becomes degenerate as can 
+be seen in \autoref{eq:ham_matrix} of Appendix 
+\ref{sec:dpt}. Using the degenerate perturbation 
+theory for $\hat V_J$ summarized therein, we find 
+the first-order corrected wave functions of $\hat 
+H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.
 
@@
 \begin{aligned}
-R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha + \text{$\Omega_1$}\right)^2}{\alpha ^{6}\Omega_1^2},\\
-R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 \frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
+R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 
+\frac{18 J^4 \left(2 \alpha + 
+\text{$\Omega_1$}\right)^2}{\alpha 
+^{6}\Omega_1^2},\\
+R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 
+\frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
 		$}\right)^2}{\alpha ^{6}\Omega_1^2},
@@
 \end{equation}
-when $\alpha \gg \Omega_1, \Omega_2, J$ which is true for our setup.
-From \autoref{eq:rates} follows that the sideband transitions are prohibited without the interaction in the SAM $(J=0)$, and the extra avoided crossings will not be observed.
-
-\paragraph{Feature I.} Finally, we discuss the last Roman-numbered effect.
-It is illustrated in \autoref{fig:featureI} for the case when $\Omega_2 \gg \Omega_1$: the second transmon is dressed, and the splitting has the shape shown in \autoref{fig:featureI}~(a).
-For the opposite case ($\Omega_1 \gg \Omega_2$), the logic is the same.
+when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
+true for our setup. From \autoref{eq:rates} 
+follows that the sideband transitions are 
+prohibited without the interaction in the SAM 
+$(J=0)$, and the extra avoided crossings will not 
+be observed.
+
+\paragraph{Feature I.} Finally, we discuss the 
+last Roman-numbered effect. It is illustrated in 
+\autoref{fig:featureI} for the case when 
+$\Omega_2 \gg \Omega_1$: the second transmon is 
+dressed, and the splitting has the shape shown in 
+\autoref{fig:featureI}~(a). For the opposite case 
+($\Omega_1 \gg \Omega_2$), the logic is the same.
 
@@
 
-\paragraph{Features II, III.}As shown in \autoref{fig:main_scheme}~(d), the sideband transitions are formed by two-photon processes for $\hat H_d^2$.
-On the other hand, we know from the unperturbed solution that in the laboratory frame the two transitions forming the avoided crossing are $10 - 02$ (one-photon) and $12/3$ (three-photon).
-This means that there should be a smooth transformation between 1-, 2- and 3-photon processes when the system approaches the resonant point.
-Let's consider two-photon transitions $(10 - 02)/2$ and $12/2$.
-In the frame rotating with the first transmon (like in \autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 0 (no driving yet on the first transmon), their frequencies are
+\paragraph{Features II, III.}As shown in 
+\autoref{fig:main_scheme}~(d), the sideband 
+transitions are formed by two-photon processes 
+for $\hat H_d^2$. On the other hand, we know from 
+the unperturbed solution that in the laboratory 
+frame the two transitions forming the avoided 
+crossing are $10 - 02$ (one-photon) and $12/3$ 
+(three-photon). This means that there should be a 
+smooth transformation between 1-, 2- and 3-photon 
+processes when the system approaches the resonant 
+point. Let's consider two-photon transitions $(10 
+- 02)/2$ and $12/2$. In the frame rotating with 
+the first transmon (like in 
+\autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 
+0 (no driving yet on the first transmon), their 
+frequencies are
 \begin{equation}
@@
 \end{equation}
-The minimal splitting between these lines is found at the resonant point and equals $\frac{2 \sqrt{3}}{{3}} \Omega_1$.
-All these calculations may be repeated exactly for the feature II by swapping the transmons; in that case, the splitting will be $\frac{2 \sqrt{3}}{{3}} \Omega_2$.
-
-We find excellent agreement between our analytical model \autoref{eq:splitting_model} and both the experimental and simulated data as can be seen in \autoref{fig:zoom}.
-To plot the model curves we have fitted the $\omega_{(1,2)}(\Phi_e)$ transitions with simple linear functions and substituted them in \autoref{eq:splitting_model}; $\alpha_1$ is known from spectroscopy.
-The only free parameter left was $\Omega_2$.
-We have repeated this approximation for a range of microwave powers to confirm the linear dependence of the splitting on excitation amplitude (see \autoref{fig:zoom}~(c)).
+The minimal splitting between these lines is 
+found at the resonant point and equals $\frac{2 
+\sqrt{3}}{{3}} \Omega_1$. All these calculations 
+may be repeated exactly for the feature II by 
+swapping the transmons; in that case, the 
+splitting will be $\frac{2 \sqrt{3}}{{3}} 
+\Omega_2$.
+
+We find excellent agreement between our 
+analytical model \autoref{eq:splitting_model} and 
+both the experimental and simulated data as can 
+be seen in \autoref{fig:zoom}. To plot the model 
+curves we have fitted the 
+$\omega_{(1,2)}(\Phi_e)$ transitions with simple 
+linear functions and substituted them in 
+\autoref{eq:splitting_model}; $\alpha_1$ is known 
+from spectroscopy. The only free parameter left 
+was $\Omega_2$. We have repeated this 
+approximation for a range of microwave powers to 
+confirm the linear dependence of the splitting on 
+excitation amplitude (see \autoref{fig:zoom}~(c)).
 
@@
 
-When $\Omega_1 \gg \Omega_2$, besides the replacement $\Omega_2 \rightarrow \Omega_1$, \autoref{eq:topo_1} changes the sign:
+When $\Omega_1 \gg \Omega_2$, besides the 
+replacement $\Omega_2 \rightarrow \Omega_1$, 
+\autoref{eq:topo_1} changes the sign:
 \begin{equation}
@@
 \end{equation}
-Solving it for $\omega_d$, we obtain the generalization of \autoref{eq:topo_1} and \autoref{eq:topo_1_inv}:
+Solving it for $\omega_d$, we obtain the 
+generalization of \autoref{eq:topo_1} and 
+\autoref{eq:topo_1_inv}:
 \begin{equation}
@@
 
-\autoref{eq:topo_comm} is used to plot the black dashed curves in \autoref{fig:difdrive} taking the $\Omega_{1,2}$ values from the simulation parameters shown therein.
-The frequencies $\omega_{1,2}$ are extracted from the fits to the visible spectral lines.
-We find good agreement between the model and the simulated data.
+\autoref{eq:topo_comm} is used to plot the black 
+dashed curves in \autoref{fig:difdrive} taking 
+the $\Omega_{1,2}$ values from the simulation 
+parameters shown therein. The frequencies 
+$\omega_{1,2}$ are extracted from the fits to the 
+visible spectral lines. We find good agreement 
+between the model and the simulated data.
 
@@
 
-We have performed spectroscopy measurements of an isolated diatomic superconducting artificial molecule (SAM) in a regime of strong interaction with classical light.
-Using joint dispersive readout to directly access population of the SAM eigenstates, we have located several anomalies in the spectral data that were impossible to explain using the unperturbed model of the system.
-By using extensive numerical modelling explicitly including the interaction with light, we have reproduced the experimentally discovered effects and attributed them to an altered version of the well-known Autler-Townes effect.
-
-In the standard A-T effect, the coupler and the probe tone are separated in frequency and power.
-In our case, there is only a single spectroscopic frequency interacting with the system; therefore, it has to be both the coupler tone and the probe tone at the same time.
-However, since there are two components in the driving operator (one for each transmon), the separation between the coupler and the probe may be in the Hilbert space rather than in frequency.
-Moreover, the effectively weak driving for the probe is achieved when it stimulates a two-photon transition while the coupler tone is resonant with a single-photon one and is dressing the system.
-We have build a self-consistent model in the frame rotating with the dressed transmon to model the experimental splittings induced by the same field that probes them, and found a good agreement between the model, the experiment, and the numerical simulation.
-Interestingly, just as in the standard A-T effect on transmons reported previously, no new transitions appear in this more complex case.
-Instead, for example, spectral lines $12/3$ (three-photon) and $10-02$ (single photon) form an avoided crossing of a non-standard size of $\frac{2\sqrt{3}}{3} \Omega_1$.
-
-Another interesting effect occurs when both components of the driving operator are in the single-photon regime.
-Now, both transmons are dressed and probed simultaneously.
-In this case, the $11/2$ transition is split at the resonance into a hyperbolic curve, never forming a doublet in frequency.
-Moreover, its shape and visibility depends on the relation between the driving amplitudes: if they are equal, it disappears completely.
-In our sample, we have a fixed ratio of approximately 2 between $\Omega_1$ and $\Omega_2$ which allows us to distinguish the splitting experimentally.
-In additional simulations with full freedom of choice for the parameter values, we have studied this effect in detail and observed two possible topologically different configurations of this splitting depending on which driving amplitude is larger.
-Notably, the frequency of $11/2$ transition far from resonance is also changed noticeably with changing power, which means that a fast bSWAP gate should be performed at a different frequency than the unperturbed model predicts.
-
-Interestingly, the self-consistent models for the observed effects are implying that multi-photon processes may smoothly change their order.
-For example, for features II and III, we observe a continuous transformation of a three-photon and a single-photon processes to the second order in \autoref{eq:two-photon}, and of a two-photon transition to a zero-photon in \autoref{eq:zero-photon}.
+We have performed spectroscopy measurements of an 
+isolated diatomic superconducting artificial 
+molecule (SAM) in a regime of strong interaction 
+with classical light. Using joint dispersive 
+readout to directly access population of the SAM 
+eigenstates, we have located several anomalies in 
+the spectral data that were impossible to explain 
+using the unperturbed model of the system. By 
+using extensive numerical modelling explicitly 
+including the interaction with light, we have 
+reproduced the experimentally discovered effects 
+and attributed them to an altered version of the 
+well-known Autler-Townes effect.
+
+In the standard A-T effect, the coupler and the 
+probe tone are separated in frequency and power. 
+In our case, there is only a single spectroscopic 
+frequency interacting with the system; therefore, 
+it has to be both the coupler tone and the probe 
+tone at the same time. However, since there are 
+two components in the driving operator (one for 
+each transmon), the separation between the 
+coupler and the probe may be in the Hilbert space 
+rather than in frequency. Moreover, the 
+effectively weak driving for the probe is 
+achieved when it stimulates a two-photon 
+transition while the coupler tone is resonant 
+with a single-photon one and is dressing the 
+system. We have build a self-consistent model in 
+the frame rotating with the dressed transmon to 
+model the experimental splittings induced by the 
+same field that probes them, and found a good 
+agreement between the model, the experiment, and 
+the numerical simulation. Interestingly, just as 
+in the standard A-T effect on transmons reported 
+previously, no new transitions appear in this 
+more complex case. Instead, for example, spectral 
+lines $12/3$ (three-photon) and $10-02$ (single 
+photon) form an avoided crossing of a 
+non-standard size of $\frac{2\sqrt{3}}{3} 
+\Omega_1$.
+
+Another interesting effect occurs when both 
+components of the driving operator are in the 
+single-photon regime. Now, both transmons are 
+dressed and probed simultaneously. In this case, 
+the $11/2$ transition is split at the resonance 
+into a hyperbolic curve, never forming a doublet 
+in frequency. Moreover, its shape and visibility 
+depends on the relation between the driving 
+amplitudes: if they are equal, it disappears 
+completely. In our sample, we have a fixed ratio 
+of approximately 2 between $\Omega_1$ and 
+$\Omega_2$ which allows us to distinguish the 
+splitting experimentally. In additional 
+simulations with full freedom of choice for the 
+parameter values, we have studied this effect in 
+detail and observed two possible topologically 
+different configurations of this splitting 
+depending on which driving amplitude is larger. 
+Notably, the frequency of $11/2$ transition far 
+from resonance is also changed noticeably with 
+changing power, which means that a fast bSWAP 
+gate should be performed at a different frequency 
+than the unperturbed model predicts.
+
+Interestingly, the self-consistent models for the 
+observed effects are implying that multi-photon 
+processes may smoothly change their order. For 
+example, for features II and III, we observe a 
+continuous transformation of a three-photon and a 
+single-photon processes to the second order in 
+\autoref{eq:two-photon}, and of a two-photon 
+transition to a zero-photon in 
+\autoref{eq:zero-photon}.
 
@@
 
-Since the Hamiltonian in the dressed basis is a useful illustration for \autoref{fig:main_scheme}, we provide it below in \autoref{eq:ham_matrix} for the case $\Delta_1 = 0$, $\delta = \omega_d^2 - 	\omega_d^1 = \omega_d^2 - \omega_1$.
-The degeneracy between states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, \ket{b,2}$ occurs only in the resonant case $2\Delta_2   + \alpha_2 = 0$ meaning that the second transmon frame is rotated at its two-photon transition frequency.
-In this situation, its single-photon subspace is detuned by $-\alpha/2$.
-
-Note that $\hat V_J = \hat S^T \hat H_{int} \hat S$ that we treat as perturbation now has an sub- and super-diagonal block form and couples all the states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, \ket{b,j+1}$.
-
-\renewcommand{\kbldelim}{[}% Left delimiter
-\renewcommand{\kbrdelim}{]}% Right delimiter
-\begin{widetext}
-	\begin{equation}
-	\hat H^D + \hat V_J + \hat V_t  = \kbordermatrix{
-		&\ket{a,0} & \ket{b,0} & \ket{a,1} & \ket{b,1} & \ket{a,2} & \ket{b,2} \\
-		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & \frac{\Omega_{2}e^{i \text{$\delta$} t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 \\
-		\ket{b,0} & 0 & \frac{\Omega_1}{2} & -\frac{J}{2} & \frac{\Omega_2 e^{i \delta t}}{2} + \frac{J}{2} & 0 & 0 \\
-		\ket{a,1} &\frac{\Omega_2 e^{-i \text{$\delta$} t} }{2}  - \frac{J}{2} & -\frac{J}{2} & - \frac{\alpha}{2} - \frac{\Omega_1}{2}&
-		0 & \frac{\text{$\Omega_2$} e^{i \text{$\delta$} t}}{\sqrt{2}} -\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
-		\ket{b,1} & \frac{J}{2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{2} +\frac{J}{2} & 0 & - \frac{\alpha}{2} + \frac{\Omega_1}{2} & -\frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{i \text{$\delta
-					$} t}}{\sqrt 2} + \frac{J}{\sqrt 2} \\
-		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i \delta t}}{2} - \frac{J}{\sqrt 2} & -\frac{J}{\sqrt 2} &
-		-\frac{\Omega_{1}}{2} & 0 \\
-		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & \frac{\text{$\Omega_2$} e^{-i \text{$\delta $} t}}{\sqrt 2} + \frac{J}{\sqrt 2} & 0 & \frac{\Omega_{1}}{2}\\
-	}
-	\label{eq:ham_matrix}
-	\end{equation}
-\end{widetext}
+Since the Hamiltonian in the dressed basis is a 
+useful illustration for 
+\autoref{fig:main_scheme}, we provide it below in 
+\autoref{eq:ham_matrix} for the case $\Delta_1 = 
+0$, $\delta = \omega_d^2 - 	\omega_d^1 = 
+\omega_d^2 - \omega_1$. The degeneracy between 
+states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, 
+\ket{b,2}$ occurs only in the resonant case 
+$2\Delta_2   + \alpha_2 = 0$ meaning that the 
+second transmon frame is rotated at its 
+two-photon transition frequency. In this 
+situation, its single-photon subspace is detuned 
+by $-\alpha/2$.
+
+Note that $\hat V_J = \hat S^T \hat H_{int} \hat 
+S$ that we treat as perturbation now has an sub- 
+and super-diagonal block form and couples all the 
+states $\ket{a, j}, \ket{a,j+1}$ and $\ket{b, j}, 
+\ket{b,j+1}$.
 
@@
 \end{equation}
-Here, $\ket{n}$ and $\ket{n'}$ are the basis states from the degenerate subspace with energy $E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$.
-The sum is over all other zero-order states $\ket{m}$ outside the degenerate subspace.
+Here, $\ket{n}$ and $\ket{n'}$ are the basis 
+states from the degenerate subspace with energy 
+$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
+The sum is over all other zero-order states 
+$\ket{m}$ outside the degenerate subspace.
+
+\renewcommand{\kbldelim}{[}% Left delimiter
+\renewcommand{\kbrdelim}{]}% Right delimiter
+\begin{widetext}
+	\begin{equation}
+	\hat H^D + \hat V_J + \hat V_t  = 
+	\kbordermatrix{
+		&\ket{a,0} & \ket{b,0} & \ket{a,1} & 
+		\ket{b,1} & \ket{a,2} & \ket{b,2} \\
+		\ket{a,0}& -\frac{\Omega_1}{2} & 0 & 
+		\frac{\Omega_{2}e^{i \text{$\delta$} 
+		t}}{2} -\frac{J}{2} & \frac{J}{2} & 0 & 0 
+		\\
+		\ket{b,0} & 0 & \frac{\Omega_1}{2} & 
+		-\frac{J}{2} & \frac{\Omega_2 e^{i \delta 
+		t}}{2} + \frac{J}{2} & 0 & 0 \\
+		\ket{a,1} &\frac{\Omega_2 e^{-i 
+		\text{$\delta$} t} }{2}  - \frac{J}{2} & 
+		-\frac{J}{2} & - \frac{\alpha}{2} - 
+		\frac{\Omega_1}{2}&
+		0 & \frac{\text{$\Omega_2$} e^{i 
+		\text{$\delta$} t}}{\sqrt{2}} 
+		-\frac{J}{\sqrt2} & \frac{J}{\sqrt2} \\
+		\ket{b,1} & \frac{J}{2} & 
+		\frac{\text{$\Omega_2$} e^{-i 
+		\text{$\delta $} t}}{2} +\frac{J}{2} & 0 
+		& - \frac{\alpha}{2} + \frac{\Omega_1}{2} 
+		& -\frac{J}{\sqrt 2} & 
+		\frac{\text{$\Omega_2$} e^{i \text{$\delta
+					$} t}}{\sqrt 2} + 
+					\frac{J}{\sqrt 2} \\
+		\ket{a,2} & 0 & 0 & \frac{\Omega_2 e^{-i 
+		\delta t}}{2} - \frac{J}{\sqrt 2} & 
+		-\frac{J}{\sqrt 2} &
+		-\frac{\Omega_{1}}{2} & 0 \\
+		\ket{b,2} & 0 & 0 & \frac{J}{\sqrt 2} & 
+		\frac{\text{$\Omega_2$} e^{-i 
+		\text{$\delta $} t}}{\sqrt 2} + 
+		\frac{J}{\sqrt 2} & 0 & 
+		\frac{\Omega_{1}}{2}\\
+	}
+	\label{eq:ham_matrix}
+	\end{equation}
+\end{widetext}
 
@@
 \end{equation} 
-Solving \autoref{forpsi} by simple iterations gives the series solution for it:
+Solving \autoref{forpsi} by simple iterations 
+gives the series solution for it:
 \begin{align}
@@
 
-\section{Measurement setup and methods}\label{sec:meas_setup}
+\section{Measurement setup and 
+methods}\label{sec:meas_setup}
 The sample was measured in a BlueFors LD250 dilution refrigerator at 16 mK.
@@
 
-Input microwave lines were isolated from high-temperature noise with 60 dB of attenuation (10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and custom-made IR filters.
-The additional on-chip attenuation (due to the small capacitive coupling) between the drive line and the transmons was calculated in Sonnet to be around 70 dB @ 6 GHz.
-Coaxial flux-bias lines were attenuated by 20 dB @ 4K and IR filtered as well.
-Output path contained two 20 dB isolators and two amplifiers: the 4-14 GHz LNF amplifier at the 4 K stage and the room-temperature LNF amplifier.
+Input microwave lines were isolated from 
+high-temperature noise with 60 dB of attenuation 
+(10 @ 4K, 10 @ 1K, 20 @ 100 and 16 mK) and 
+custom-made IR filters. The additional on-chip 
+attenuation (due to the small capacitive 
+coupling) between the drive line and the 
+transmons was calculated in Sonnet to be around 
+70 dB @ 6 GHz. Coaxial flux-bias lines were 
+attenuated by 20 dB @ 4K and IR filtered as well. 
+Output path contained two 20 dB isolators and two 
+amplifiers: the 4-14 GHz LNF amplifier at the 4 K 
+stage and the room-temperature LNF amplifier.
 
@@
 The device was fabricated on a high-resistivity
-Si wafer (10 kOhm$\cdot$cm).
-First, Si wafers were cleaned with Pirahna, HF and then coated with bilayer MMA/PMMA resist stack.
-The nominal after-bake thickness of the MAA and PMMA are 800 and 100 nm, respectively.
-The
-bilayer resist stack was exposed using a 50kV Raith Voyager EBL system and then developed. Next, the sample was placed into a high-vacuum electron-beam evaporation
-chamber (Plassys) and after a gentle ion-milling step, a double-angle evaporation technique at 10 is used to deposit Al/AlOx/Al layer.
-Finally, hot NMP followed by IPA was used to lift off the resist mask stack
+Si wafer (10 kOhm$\cdot$cm). First, Si wafers 
+were cleaned with Pirahna, HF and then coated 
+with bilayer MMA/PMMA resist stack. The nominal 
+after-bake thickness of the MAA and PMMA are 800 
+and 100 nm, respectively. The
+bilayer resist stack was exposed using a 50kV 
+Raith Voyager EBL system and then developed. 
+Next, the sample was placed into a high-vacuum 
+electron-beam evaporation
+chamber (Plassys) and after a gentle ion-milling 
+step, a double-angle evaporation technique at 10 
+is used to deposit Al/AlOx/Al layer. Finally, hot 
+NMP followed by IPA was used to lift off the 
+resist mask stack.
 

### 2019-12-27 Pictures/Plotting/MainPictureSlices.py
Slices source

@@ -1,0 +1,124 @@
+import pickle
+import numpy as np
+import matplotlib
+from matplotlib import ticker, colorbar as clb, patches
+
+matplotlib.use('Qt5Agg')
+
+from matplotlib import pyplot as plt
+from mpl_toolkits.axes_grid1.inset_locator import zoomed_inset_axes
+
+
+class MainPictureSlices:
+
+    def __init__(self):
+        self._cmap = "Spectral"
+        self.nstate = 0
+
+
+    def plot(self):
+        self._load_data()
+        indices = [99, 124, 158]
+        indices_th  = (np.array(indices)/len(self._C_exp[0,:])*len(self._C_th[0,:])).astype(int)
+        print(indices, indices_th)
+        titles = ["Feature I", "Feature III", "Sweet spot"]
+        fig, axes = plt.subplots(1, 3, figsize=(5*0.9,3*0.9), sharey=True)
+
+        for counter, ax, index in zip(range(3), axes, indices):
+            data = self._X_exp, self._Y_exp, np.real(self._C_exp)
+        # plt.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap=self._cmap)
+        #     ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap=self._cmap)
+
+            # ax.plot([self._X_exp[index]]*2, [self._Y_exp[0], self._Y_exp[-1]], 'black', lw=0.1)
+            ax.plot(np.real(self._C_exp[:,index]), self._Y_exp, zorder=1, color="gray",
+                    label="Exp.")
+            ax.plot(np.real(self._C_th[:,indices_th[counter]]), self._Y_exp, zorder=3,
+                    color="black", lw=.5, label ="Sim.")
+
+            rect = patches.Rectangle((np.min(np.real(self._C_exp[:,index]))-.001, 5.3575),
+                                     np.ptp(np.real(self._C_exp[:,index]))+0.002, .02, linewidth=1, edgecolor='none',
+                                     facecolor='white', zorder=2, alpha=0.66)
+            ax.add_patch(rect)
+            # ax.set_title("I=%.2f mA"%(self._X_exp[index]/10), fontsize=9)
+            ax.set_title(titles[counter], fontsize=10)
+
+            print(self._X_exp[index])
+
+            if counter==2:
[…]

### 2020-01-19 document.tex
add minor corrections
Updates

@@
 	show various transition frequencies from the 
-	unperturbed Hamiltonian. Legend labels 
-	transitions near the sweet spot current; if 
+	unperturbed Hamiltonian. In the legend, the 
+	transitions are labelled near the sweet spot current; if 
 	elsewhere any two lines form an avoided 
@@
 	\caption{Power dependence of feature II: 
-	experiment, simulation and theory. Dashed are 
-	the model curves turning to dotted when the 
+	experiment, simulation and analytic model. Dashed are the model curves turning to dotted when the 
 	model is not expected to be valid (see 
@@
 	with the stronger one. Gray dashed lines show 
-	the solution with no driving, in black are 
+	the solution without driving, in black are 
 	the model curves based on Sections 
@@
 $|\alpha_{(1,2)}|/2$ lower than the main lines 
-$\omega_{(1,2)}(I	)$. Another two-photon process 
+$\omega_{(1,2)}(I)$. Another two-photon process 
 appears as $11/2$ line when two SAAs are excited 
@@
 When two lines intersect, they may form an 
-avoided crossing if the corresponding matrix 
+avoided crossing even for an unperturbed model if 
+the corresponding matrix 
 element of $\hat H_{int}$ is non-zero. In such 
@@
 factorized states. For a two-transmon SAM, such 
-points are, for instance, crossings between 
-${01}$, ${10}$ or $ {11} $, $ {02} $($ {20} $). 
+points are, for instance, anticrossings between 
+${01}$,${10}$ or $ {11} $,$ {02} $($ {20} $) 
+visible clearly in \autoref{fig:two-tone}~(d). 
 Additionally, marked as feature 3 in 
@@
 crossing between ${12}/3,\ {21}/3$ at the same 
-$\Phi_e$ where ${01}$, ${10}$ intersect.
-
-\paragraph{Features I, II and III.} First, we have focused on the feature III and have reproduced this avoided crossing in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for the transmon 2.
-Upon this, it has become clear that feature II and feature III actually are of the same nature and differ only by the ordering of the transmons: for II, they appear whence the transition ${01}$ intersects with the two-photon one ${20/2}$ (${10}$ intersects ${02/2}$ in III); one can see this clearly in \autoref{fig:two-tone}~(b).
+current where ${01}$, ${10}$ intersect.
+
+\paragraph{Analysing features I, II and III.} 
+First, we have reproduced the avoided crossing of feature III in an additional numerical simulation taking only 2 levels for the transmon 1 and three levels for 
+the transmon 2. Upon this, it has become clear 
+that features II and III are actually of 
+the same nature and differ only by the ordering 
+of the transmons: for II, they appear whence the 
+transition ${01}$ intersects with the two-photon 
+one ${20/2}$, and for III when ${10}$ intersects ${02/2}$; 
+one can see this clearly in 
+\autoref{fig:two-tone}~(b).
 
@@
 same frequency when $\omega_1 = 
-\omega_2+\alpha_2/2$. The latter process is 
-discernible in \autoref{fig:two-tone}~(d) as it 
-depopulates ${10}$, but is not visible in 
-\autoref{fig:two-tone}~(a),(b). In II, the 
-reversed is true: ${21/3}$ and ${01} - {20}$ are 
+\omega_2+\alpha_2/2$. The latter process depopulating $01$ is better discernible in \autoref{fig:two-tone}~(d) 
+than in \autoref{fig:two-tone}~(a), (b). For II, the 
+opposite is true: ${21/3}$ and ${01} - {20}$ are 
 crossing when $\omega_2 = \omega_1+\alpha_1/2$. 
@@
 power; the experimental and simulated results for 
-II are shown in \autoref{fig:zoom}~(a), (b). As 
-one can see, the growth of the splitting with 
+II are shown in colour in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
 increasing power is linear: it is roughly equal 
@@
 for the dashed curves fitting the spectral lines 
-in \autoref{fig:zoom}. By measuring the 
-dependence of the splitting size on the microwave 
-power we confirm its proportionality to the 
-signal amplitude (see \autoref{fig:zoom}~(c)).
-
-We see a similar behaviour for feature I: 
-increasing drive amplitude on one of the 
+in \autoref{fig:zoom}.
+In \autoref{fig:zoom}~(c), blue points, we present splitting sizes extracted by fitting of the model to the data as in \autoref{fig:zoom}~(a) for various power values of the microwave generator connected to the excitation waveguide.
+As one can see from the linear approximation of the points, the splitting indeed is simply proportional to the RMS voltage of the signal.
+From the model, we expect that the minimal distance between curves in the anticrossing is equal to $\frac{2\sqrt{3}}{3} \Omega_2$; using this relation, we extract the proportionality coefficient between $\Omega_2$ and $V_{rms}$ is around $0.23$ MHz/mV from the linear fit.
+
+In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing drive amplitude on one of the 
 transmons while keeping the other one small and 
 constant again elicits avoided crossings with the 
-proportional size. In \autoref{fig:difdrive} we 
-show only the simulation results; an experiment 
-is not possible with our sample because there is 
-no way to adjust the driving amplitudes 
+proportional size. We  show only the simulation results; an experiment is not possible with our sample because, since we have just a single excitation line, there is 
+no way for us to control the driving amplitudes 
 $\Omega_{1,2}$ individually. We note that two 
@@
 \autoref{fig:two-tone}~(c)).
-
-These observations mean that effects I -- III are 
-caused by light dressing. In the case III, the 
+If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes.
+As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}}.
+
+From all presented observations, we conclude that effects I -- III 
+are caused by light dressing. In the case III, the 
 first transmon is dressed by a strong resonant 
 field; in case II, the second one; finally, in 
-case I, both transmons are dressed at the same 
+case I, both transmons may be dressed at the same 
 time. We will discuss these effects in greater 
-detail in Section \ref{sec:theory}.
+detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}.
 
@@
 ${20/2}$ and is just barely visible in the 
-experimental data because of the noise. Feature 5 
-is located at the intersection between ${20/2}$ 
-and normally invisible ${10} - {02}$, and can be 
+experimental data because of the noise.
+
+Feature 5 is located at the intersection between ${20/2}$ 
+and ${10} - {02}$, and can be 
 found in the experimental data, too.
 
-Finally, when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details.
+In conclusion to this section, we note that when the coupling is turned off ($J=0$) in the simulation, the system does not demonstrate any of the described details.
 This means that all these effects can only be attributed to the SAM as a whole.
@@
 For a three-level system, the standard A-T effect 
-is reviewed in Appendix \ref{sec:3-level-at}. 
+is revised in Appendix \ref{sec:3-level-at}. 
 However, in our case the level structure and the 
@@
 apply only a single microwave tone ($\omega_d^1 = 
-\omega_d^2$), for the A-T effect it has to be 
-simultaneously the coupler and the probe; the 
-latter must be much weaker than the former, as 
-well. These conditions are satisfied when 
+\omega_d^2$), it has to be 
+simultaneously the coupler and the probe
+in terms of the standard A-T effect; moreover, the 
+probe must be much weaker than the coupler. 
+Fortunately, all these conditions are satisfied near feature II(III) when 
 $\omega_{\{2,1\}} = 
@@
 can simultaneously excite transitions $01 (10)$ 
-and $20/2 (02/2)$ (features II and III, 
-respectively). Since the two-photon Rabi 
+and $20/2 (02/2)$. Since the two-photon Rabi 
 frequency is much smaller than the single-photon 
@@
 separation in our case is not in frequency, but 
-in the Hilbert subspaces they act upon.
-
-Similarly, for feature I, the simultaneously 
-excited transitions are $01(10)$ and the 
-two-photon $11/2$. However, as we demonstrate in 
-\autoref{fig:difdrive}, for the avoided crossings 
-in I to be clearly observed it is required that 
+in the Hilbert subspaces they act upon and in the number of participating photons.
+
+For feature I, the simultaneously 
+excited transitions are $01,\ 10$ and the 
+two-photon $11/2$.
+In this case, the weak two-photon process is probing transitions in the doubly-dressed SAM.
+We find that if SAAs are dressed equally, $11/2$ does not form an avoided crossing, and for it to be clearly observed it is required that
 $\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.
@@
 	exactly by $\alpha_2/2$ and several 
-	transitions become resonant. So far we assume 
+	transitions become resonant. Here we assume 
 	that each transmon is driven at its own 
 	frequency. \textbf{(b)} System level 
-	structure at the resonant point including the 
-	driving $\hat H_{d}^1$ of the first transmon 
-	by a strong signal of amplitude $\Omega_1$ 
+	structure at the resonant point and the first transmon 
+	driving of amplitude $\Omega_1$ 
 	(orange ellipses) at a small detuning 
@@
 	orange-blue circles. \textbf{(c)} In the 
-	frame rotating with the drive of the first 
-	transmon, all the states $\ket{0j},\ket{1j}$ 
+	frame rotating with $\hat 
+	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
 	become nearly degenerate ($\omega_1 
-	\rightarrow \Delta_1$). Dressing by the 
-	strong excitation increases this splitting to 
+	\rightarrow \Delta_1$). Dressing increases this splitting to 
 	$\Omega_1^R = \sqrt{\Omega_1^2 + 
 	\Delta_1^2}$. \textbf{(d)} Transitions in the 
-	light-dressed system when the second transmon 
-	is excited (level subspaces coupled by $\hat 
-	H_{d}^2$ are shown with blue ellipses). In 
+	dressed system induced by $\hat 
+	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
 	the left part of the panel, all possible 
 	two-photon transitions near $\omega_1$ are 
-	depicted: the green transitions are not 
-	shifted in frequency, the red are red-shifted 
-	by $\Omega^R_1/2$ and the blue are 
-	blue-shifted by $\Omega^R_1/2$. In the right 
+	depicted: the blue transitions are not 
+	shifted in frequency, the light blue ones are shifted 
+	by $\pm\Omega^R_1/2$. In the right 
 	part, the most contributing trajectories are 
-	depicted; red crosses show transitions that 
+	depicted; gray crosses show transitions that 
 	are forbidden without the coupling $J$.}
@@
 
-In \autoref{fig:main_scheme}, we elaborate on how 
-exactly the A-T effect occurs for feature III. 
+In \autoref{fig:main_scheme}, we elaborate on which transitions
+are involved in the A-T-like effect for feature III. 
 For simplicity, we will temporarily assume that 
@@
 
-Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the resulting eigenstates due to $\hat H_{d}^2$.
-In the left part of the panel, the unmodified transition at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$.
+Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the dressed states induced by the second transmon driving $\hat H_{d}^2$.
+In the left part of the panel, one can find the unmodified two-photon transition $02/2$ at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$.
+This picture finally explains the observed triplet transition of feature III.
 The right part describes the mechanism of these two-photon processes through virtual excitations of the intermediate states.
@@
 However, we will show that they become allowed in the second order in $J$ when the coupling is turned on.
-Remarkably, due to the two-photon nature of the transitions, the Autler-Townes splitting in this case will be just $\Omega_1^R$.
 
@@
 move to the rotating frame with 
-\autoref{eq:rotation} and apply the RWA, will use 
+\autoref{eq:rotation} and apply the RWA, we use 
 the following operator:
@@
 \end{equation}  
-Note that we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$. Now,
+Note that now we rotate both transmon subspaces simultaneously in contrast to what is shown in \autoref{fig:main_scheme} because below it will be convenient to have time-independent $\hat H_{int}$.
+Now,
 \begin{equation}
@@
 The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}.
-Using the corrected eigenstates $\ket{k}$ and neglecting small terms we obtain the following expression for the transition rates per unit time\cite{faisal2013theory}:
+Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time\cite{faisal2013theory}:
 \begin{equation}
@@
 
-As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and experiences a frequency shift approaching the 01-10 intersection while the other spectral lines are not moving.
+As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum when approaching the 01-10 intersection while the other spectral lines are not moving.
 Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
 We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}.
-Instead, we observe one line to the left and the other to the right from the $01-10$ intersection.
+Instead, we observe one line to the left and the other to the right from the 01-10 intersection.
 
@@
 
-\paragraph{Features II, III.}As shown in 
+\paragraph{Features II, III.} We start again with feature III. As shown in 
 \autoref{fig:main_scheme}~(d), the sideband 
 transitions are formed by two-photon processes 
-for $\hat H_d^2$. On the other hand, we know from 
+with $\hat H_d^2$. On the other hand, we know from 
 the unperturbed solution that in the laboratory 
@@
 (three-photon). This means that there should be a 
-smooth transformation between 1-, 2- and 3-photon 
+smooth transformation between these 1-, 2- and 3-photon 
 processes when the system approaches the resonant 
-point. Let's consider two-photon transitions $(10 
+point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$. Let us consider hypothetical two-photon transitions $(10 
 - 02)/2$ and $12/2$. In the frame rotating with 
-the first transmon (like in 
-\autoref{fig:main_scheme}~(c)) when $\Omega_1$ = 
-0 (no driving yet on the first transmon), their 
+the first transmon like in 
+\autoref{fig:main_scheme}~(c) when $\Omega_1$ = 
+0, their 
 frequencies are
@@
 \omega_{(10-02)/2} &= (\alpha_2 + 2 \omega_{2} - \Delta_1)/2,\\
- \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_2)/2.
+ \omega_{12/2} &= (\alpha_2 + 2 \omega_{2} + \Delta_1)/2.
 \end{aligned}
@@
 When the first transmon becomes dressed by $\Omega_1 \neq 0$, its splitting $\Delta_1$ changes to $\Omega^R_1 =\sqrt{\Omega_{1}^2 + \left(\omega_{1} - \omega_{d}\right)^{2}}$.
-At this point it becomes clear that at the resonant point where $\alpha_2 + 2 \omega_{2} = 2\omega_1$, $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established above and thus should be used to model the splitting behaviour.
-
-Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ both at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear at
+Substituting this new splitting into the equations above we find that $\omega_{(10-02)/2}$ and $\omega_{12/2}$ are exactly equal to the two-photon sideband frequencies $\omega_1 \pm \Omega_1^R/2$ established in the previous section.
+Therefore, it is logical to use them to model the splitting behaviour beyond the resonant point.
+
+Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear
 \begin{equation}
@@
 \sqrt{3}}{{3}} \Omega_1$. All these calculations 
-may be repeated exactly for the feature II by 
+can be repeated exactly for the feature II by 
 swapping the transmons; in that case, the 
@@
 
-We find excellent agreement between our 
-analytical model \autoref{eq:splitting_model} and 
+We find excellent agreement between this self-consistent analytical model \autoref{eq:splitting_model} and 
 both the experimental and simulated data as can 
@@
 
-The upper branch is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
+The upper branch of the fitted anticrossing is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
 The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon moving the avoided crossing 3 closer to the feature II; however, it is not important for our reasoning.
@@
 \paragraph{Feature I.} Feature I may be explained using the same dressing model.
-Looking at \autoref{fig:featureI} for the case $\Omega_2 \gg \Omega_1$, we can write the other pair of self-consistent equations:
+Looking at \autoref{fig:featureI} for the case $\Omega_2 \gg \Omega_1$, we can write another pair of self-consistent equations:
 \begin{equation}
@@
 \end{equation}
-Due to the fact that $\Omega_2^R = \sqrt{\Omega_2^2 + (\omega_2 - \omega_d)^2}$, these equations only have the same single solution:
+Due to the fact that $\Omega_2^R = \sqrt{\Omega_2^2 + (\omega_2 - \omega_d)^2}$, this system has a single solution:
 \begin{equation}
@@
 When $\Omega_2$ is non-zero, the solution near the point $\omega_1 \approx \omega_2$ is a hyperbolic curve, which agrees well with the numerical simulation.
-However, due to the finite coupling $J$ between the transmons, they never reach each other in frequency, and thus this model is not applicable when $|\omega_1 - \omega_2| \leq J$.
+However, in reality we do not observe the asymptotically vertical parts of this model since it becomes invalid when $|\omega_1 - \omega_2| \leq J$ due to the finite coupling $J$ between the transmons.
+Since they never reach each other in frequency, the denominator in \eqref{eq:topo_1} is limited from below and there is no divergence.
 
@@
 $\omega_{1,2}$ are extracted from the fits to the 
-visible spectral lines. We find good agreement 
+visible spectral lines. We again find good agreement 
 between the model and the simulated data.
@@
 In the standard A-T effect, the coupler and the 
-probe tone are separated in frequency and power. 
+probe lasers are separated both in frequency and power. 
 In our case, there is only a single spectroscopic 
-frequency interacting with the system; therefore, 
+tone interacting with the system; therefore, 
 it has to be both the coupler tone and the probe 
@@
 each transmon), the separation between the 
-coupler and the probe may be in the Hilbert space 
-rather than in frequency. Moreover, the 
-effectively weak driving for the probe is 
+coupler and the probe occurs in the Hilbert space and in the number of photons involved 
+rather than in frequency and amplitude. The 
+effectively weak driving limit for the probe part is 
 achieved when it stimulates a two-photon 
-transition while the coupler tone is resonant 
-with a single-photon one and is dressing the 
-system. We have build a self-consistent model in 
-the frame rotating with the dressed transmon to 
+transition while the coupler part is resonant 
+with a single-photon one being strong enough to dress the 
+system. We have built self-consistent models in 
+rotating frame to 
 model the experimental splittings induced by the 
@@
 agreement between the model, the experiment, and 
-the numerical simulation. Interestingly, just as 
-in the standard A-T effect on transmons reported 
-previously, no new transitions appear in this 
+the numerical simulation. Interestingly, no new spectral lines appear in this 
 more complex case. Instead, for example, spectral 
 lines $12/3$ (three-photon) and $10-02$ (single 
-photon) form an avoided crossing of a 
+photon) morph to an additional avoided crossing of a 
 non-standard size of $\frac{2\sqrt{3}}{3} 
@@
 in frequency. Moreover, its shape and visibility 
-depends on the relation between the driving 
-amplitudes: if they are equal, it disappears 
+depends qualitatively on the relation between the driving 
+amplitudes; for instant, if they are equal, it disappears 
 completely. In our sample, we have a fixed ratio 
 of approximately 2 between $\Omega_1$ and 
-$\Omega_2$ which allows us to distinguish the 
-splitting experimentally. In additional 
-simulations with full freedom of choice for the 
-parameter values, we have studied this effect in 
-detail and observed two possible topologically 
-different configurations of this splitting 
-depending on which driving amplitude is larger. 
-Notably, the frequency of $11/2$ transition far 
+$\Omega_2$ which still allows us to distinguish the 
+splitting experimentally. Notably, the frequency of $11/2$ transition far 
 from resonance is also changed noticeably with 

### 2020-01-19 Pictures/Plotting/MainPicturePlot.py

@@ -34,7 +34,7 @@ class MainPicturePlot:
         self.plot_experiment(ax1)
         self.plot_theory(ax2)
 
-        plt.savefig("../main_picture.pdf", bbox_inches="tight", dpi=600)
+        plt.savefig("../main_picture.pdf", bbox_inches="tight", dpi=800)
 
         with open(self._cache_file, "wb") as f:
             pickle.dump(self._cache, f)

### 2020-01-21 document.tex
Yursa's edits

@@
 	\author{O.V. Astafiev}
-	\affiliation{ 
-		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
-	}
 	\affiliation{Skolkovo Institute of Science 
 		and Technology, Moscow, Russian Federation}
+	\affiliation{ 
+		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia}
 	\affiliation{Physics Department, Royal 
@@
 	TW20 0EX, United Kingdom}
+\affiliation{National Physical Laboratory, Teddington, TW11 0LW, United Kingdom}
 %
@@
 validity of fundamental quantum mechanical 
-laws\cite{you2011atomic}. Due to synthetic nature 
-of SAAs, their Hamiltonians can be pre-designed 
+laws\cite{you2011atomic}. Their Hamiltonians can be pre-designed 
 and engineered which makes them a particularly 
-versatile tool for studies in quantum optics. 
-Notably, high controllability of their parameters 
+versatile tool for studies in quantum optics, and high controllability of their parameters 
 allows direct observation of novel physical 
@@
 (Xmon) SAAs with asymmetric 
-SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
+SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
 \sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
-$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
+charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
 to a single notch-type\cite{probst2015efficient} 
@@
 	 	\includegraphics[width=\linewidth]{experiment_2}
-	\caption{\textbf{(a)} Optical photograph of 
+	\caption{\textbf{(a)} Optical image of 
 	the device (false coloured). Two transmons 
@@
 shifts corresponding to the SAM basis 
-states\cite{filipp2009two}. Since we have not 
+states\cite{filipp2009two, chow2010detecting}. Since we have not 
 directly measured these dispersive shifts, in our 
@@
 	splitting size on the driving voltage of the 
-	microwave source $V_{rms} = 
-	\sqrt{10^{P_{exc}/10}\cdot 1 \text{ mW} \cdot 
-	50\ \Omega}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
+	microwave source $V_{rms}$, ${\Omega_2}/{V_{rms}} = 0.23\ 
 	{\text{MHz}}/{\text{mV}}$. From Section 
@@
 	$\Omega_{1(2)}$ is increased while 
-	$\Omega_{2(1)} = \text{const} \ll 
+	$\Omega_{2(1)} = \text{const},\ \Omega_{2(1)} \ll 
 	\Omega_{1(2)}$; two topologically different 
@@
 we can still use it to identify most of the 
-observed transitions as follows. As said above, 
-by numerical diagonalization, we calculate the 
+observed transitions as follows. By numerical diagonalization, we calculate the 
 unperturbed frequencies of the undriven SAM as 
@@
 n,m=0..9$. In \autoref{fig:two-tone}~(d), we 
-place them over the heatmap data depicting the 
-population of $\ket{10}$ optionally dividing 
-$\omega_{mn}$ by some integer $n$ to find the 
-frequency of an $n$-photon process to find a 
-match among the visible lines in the heatmap. 
+place them over the heatmap data optionally dividing 
+$\omega_{mn}$ by some integer $n$ for $n$-photon processes. 
 Since the number of SAM states is finite, we can 
-quickly find all such correspondences.
+quickly find all matches between the heatmap and the calculated eigenlevels.
 
@@
 
-Having settled the naming system, we continue to 
-analyse the plots. Due to the strong driving, we 
-observe several multiphoton transitions besides 
+As one can see, various multiphoton transitions besides 
 the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
-$01$ and $10$ lines). The ${02/2}$ and ${20/2}$ 
+$01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$ 
 are very commonly found for transmons and lie 
@@
 gate\cite{poletto2012entanglement}; in our case, 
-it is taking part in formation of feature I. A 
+it is taking part in feature I. A 
 three-photon process $12/3$ is also clearly 
@@
 	\rightarrow \Delta_1$). Dressing increases this splitting to 
-	$\Omega_1^R = \sqrt{\Omega_1^2 + 
-	\Delta_1^2}$. \textbf{(d)} Transitions in the 
+	$\Omega_1^R$. \textbf{(d)} Transitions in the 
 	dressed system induced by $\hat 
@@
 level structure of the SAM at 0.36 mA. Detuned by 
-$\Delta_1$ from $10$, single-photon driving of 
+$\Delta_1$ from $\omega_1$, single-photon driving by 
 $\hat H_d^1$ is shown with orange ellipses while 
-much weaker two-photon $\hat H_d^2$ is not shown 
-yet. Since from numerical simulations we know 
+much weaker two-photon driving by $\hat H_d^2$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know 
 that the third level of the first transmon is not 
@@
 
-As one can see from \autoref{fig:difdrive}, only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum when approaching the 01-10 intersection while the other spectral lines are not moving.
+As one can see from \autoref{fig:difdrive}, near the 01, 10 intersection only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum while the spectral lines 01, 10 do not shift.
 Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
-We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously; this is clearly visible in \autoref{fig:difdrive}.
-Instead, we observe one line to the left and the other to the right from the 01-10 intersection.
+We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously which is also clear from \autoref{fig:difdrive} where we observe one line to the left and the other to the right from the 01, 10 intersection.
 
@@
 
-The upper branch of the fitted anticrossing is expected to deviate from the model (see dashed curves in \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
+The upper branch of the fitted anticrossing is expected to deviate from the model (see \autoref{fig:zoom}) because of the avoided crossing marked as the secondary feature 3 which was not incorporated in the simple linear model.
 The small discrepancy between the experimental and simulated data in the upper branch is caused by a slight elevation of the lower sweet spot of the first transmon moving the avoided crossing 3 closer to the feature II; however, it is not important for our reasoning.
@@
 dressed and probed simultaneously. In this case, 
-the $11/2$ transition is split at the resonance 
-into a hyperbolic curve, never forming a doublet 
-in frequency. Moreover, its shape and visibility 
+the $11/2$ transition is being split at the resonance between $01$ and $10$ into a hyperbolic curve, though never forming a doublet transition. The shape of the splitting and its visibility 
 depends qualitatively on the relation between the driving 
-amplitudes; for instant, if they are equal, it disappears 
-completely. In our sample, we have a fixed ratio 
+amplitudes; for instant, if they are equal, the splitting does not appear at all. In our sample, we have a fixed ratio 
 of approximately 2 between $\Omega_1$ and 
@@
 	\includegraphics[width=\linewidth]{intro_scheme}
-	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame ($\hbar=1$ here).
-\textbf{(a)} A three-level system is driven strongly by a ``coupler'' tone of amplitude $\Omega$ at frequency $\omega_{01}-\Delta$ which induces Rabi oscillations between $\ket{0}$ and $\ket{1}$ at the generalized Rabi frequency $\Omega_R = \sqrt{\Omega^2 + \Delta^2}$.
-\textbf{(b)} Moving to the frame rotating with the drive, we effectively change the $\ket{0}\rightarrow \ket{1}$ transition frequency to $\Delta$.
-However, when the RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\Omega^R$.
-Now, the experimenter may observe a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$.}
+	\caption{Illustrating the A-T splitting by  the classical driving in the rotating frame.
+\textbf{(a)} A three-level system is driven strongly by the coupler tone of amplitude $\Omega_c$ at frequency $\omega_c = \omega_{01}-\Delta$.
+\textbf{(b)} In the frame rotating with the drive changes, the $\ket{0}\rightarrow \ket{1}$ transition frequency changes to $\Delta$.
+However, when the RWA is applied and Hamiltonian is re-diagonalized, the splitting between two lowest levels (dressed states $\ket{a}$ and $\ket{b}$) becomes $\hbar \Omega^R$.
+Now, a doublet transition from these levels to the state $\ket{2}$ at frequencies $\omega_{12}+(\Delta \pm \Omega^R)/2$ may be observed.}
 	\label{fig:at-standard}
@@
 \paragraph{Classical derivation.} In the classical case, the mathematical description goes as follows.
-At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_1$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$ (the \textit{coupler} tone).
-Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_2$ between $\ket{1}$ and $\ket{2}$ (the \textit{probe} tone).
+At first, there is a three-level system which is driven by a strong radiation with an amplitude $\Omega_c$ at a frequency detuned by $\Delta$ from the $\ket{0}\rightarrow \ket{1}$ transition with a frequency $\omega_{01}$ (the \textit{coupler} tone).
+Additionally, we have a weak probe radiation at a frequency $\omega_{p}$ and with an amplitude $\Omega_p$ between $\ket{1}$ and $\ket{2}$ (the \textit{probe} tone).
 This step is illustrated in \autoref{fig:at-standard}~(a).
@@
 \begin{equation*}
-\hat H^c_0/\hbar = \left[\begin{matrix}
-0 & \Omega_{1} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
-\Omega_{1} \cos{\left(\omega_{01} - \Delta \right)t}   & \omega_{01} &\Omega_{2} \cos\omega_p t  \\
-0 & \Omega_{2} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
+\hat H_0/\hbar = \left[\begin{matrix}
+0 & \Omega_{c} \cos{\left(\omega_{01}- \Delta \right)t} & 0\\
+\Omega_{c} \cos{\left(\omega_{01} - \Delta \right)t}   & \omega_{01} &\Omega_{p} \cos\omega_p t  \\
+0 & \Omega_{p} \cos{\omega_p t}  & \omega_{02}\end{matrix}\right].
 \end{equation*}
@@
 \]
-Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_2$.
+Note here that level $\ket{2}$ is also rotated: this is convenient to preserve the frequency of the driving term with $\Omega_p$.
 The new Hamiltonian should be calculated as follows: $\hat H_1 = \hat R^\dag \hat H_0 \hat R - i \hat{R}^\dag \partial_t  \hat R$.
@@
 \begin{equation*}
-\hat H^c_1/\hbar = \left[\begin{matrix}0 &\Omega_{1}/2 & 0\\\Omega_{1}/2 & \Delta & \Omega_{2} e^{i t \omega_p}/2\\0 & \Omega_{2} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
+\hat H_1/\hbar = \left[\begin{matrix}0 &\Omega_{c}/2 & 0\\\Omega_{c}/2 & \Delta & \Omega_{p} e^{i t \omega_p}/2\\0 & \Omega_{p} e^{-i t \omega_p}/2 & \omega_{02} - \omega_{01}+\Delta \end{matrix}\right].
 \end{equation*}
@@
 \begin{equation*}
-\hat H^c_3/\hbar = \left[\begin{matrix} 
-\frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
+\hat H_3/\hbar = \left[\begin{matrix} 
+\frac{\Delta}{2} - \frac{\sqrt{\Delta^{2} + \Omega_{c}^{2}}}{2} & 
 0 &
-\frac{\Omega_{2} e^{i t \omega_{p}}}{2}\sin(\theta)
+\frac{\Omega_{p} e^{i t \omega_{p}}}{2}\sin(\theta)
 \\
 0 & 
-\frac{\Delta}{2} + \frac{\sqrt{\Delta^{2} + \Omega_{1}^{2}}}{2} & 
-\frac{\Omega_{2} e^ {i t \omega_p}}{2}\cos(\theta)
+\frac{\Delta}{2} + \frac{\sqrt{\Delta^{2} + \Omega_{c}^{2}}}{2} & 
+\frac{\Omega_{p} e^ {i t \omega_p}}{2}\cos(\theta)
 \\
-\frac{\Omega_{2} e^{-i t \omega_{p}} }{2}\sin(\theta) & 
-\frac{\Omega_{2} e^{-i t \omega_{p}}}{2} \cos(\theta) & 
+\frac{\Omega_{p} e^{-i t \omega_{p}} }{2}\sin(\theta) & 
+\frac{\Omega_{p} e^{-i t \omega_{p}}}{2} \cos(\theta) & 
 \omega_{12} +\Delta 
@@
 
-One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + \dfrac{(\Delta \pm \Omega^R)}{2}$, where $\Omega^R = \sqrt{\Omega_1^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\frac{\Omega_1}{\Delta}$.
+One may see that now resonant conditions for the probe drive are $\omega_p = \omega_{12} + {(\Delta \pm \Omega^R)}/{2}$, where $\Omega^R = \sqrt{\Omega_c^2 + \Delta^2}$, $\omega_{12} = \omega_{02}- \omega_{01}$, and its amplitude is renormalized by an angle $\theta,\ \tan 2\theta = -\Omega_c/\Delta$.
 
@@
 \begin{split}
-\hat H^q_0/\hbar = \omega_{01} \ket{1}\bra{1} + \omega_{02} \ket{2}\bra{2} + (\omega_{01}-\Delta) \hat a^\dag \hat a + \\\ g (\hat a^\dag + \hat a)\otimes (\ket{1}\bra{0}+\ket{0}\bra{1}),
+\hat H_0/\hbar = \omega_{01} \ket{1}\bra{1} + \omega_{02} \ket{2}\bra{2} + (\omega_{01}-\Delta) \hat a^\dag \hat a + \\\ g (\hat a^\dag + \hat a)\otimes (\ket{1}\bra{0}+\ket{0}\bra{1}),
 \end{split}
@@
 \begin{split}
-\hat H^q_1/\hbar = \Delta \ket{1}\bra{1} + (\omega_{12}+\Delta) \ket{2}\bra{2} + \\\ g \left[\hat a^\dag \otimes \ket{0}\bra{1} + \hat a \otimes \ket{1}\bra{0}\right].
+\hat H_1/\hbar = \Delta \ket{1}\bra{1} + (\omega_{12}+\Delta) \ket{2}\bra{2} + \\\ g \left[\hat a^\dag \otimes \ket{0}\bra{1} + \hat a \otimes \ket{1}\bra{0}\right].
 \end{split}
 \end{equation}
-If we presume that the resonator is in a coherent state $\ket{\alpha e^{-it(\omega_{01}-\Delta)}}$ with $\langle N\rangle = \alpha^2$ photons and average $\hat H_1^q$ over the resonator subspace, we from the interaction term will obtain again the classical driving strength $\Omega_1 = 2 \sqrt{\langle N \rangle} g$ in correspondence with the classical driving case.
-Similarly, the energy levels $\ket{1, N-1}$ and $\ket{0, N}$ become mixed due to the coupling, and their splitting changes from $\hbar\Delta$ to $\hbar\Omega_R = \hbar\sqrt{\Omega_1+\Delta}$.
-The following steps completely reproduce the classical case if we add the probe tone $\Omega_2$ in the last equation.
+If we presume that the resonator is in a coherent state $\ket{\alpha e^{-it(\omega_{01}-\Delta)}}$ with $\langle N\rangle = \alpha^2$ photons and average $\hat H_1^q$ over the resonator subspace, from the interaction term we will obtain again the classical driving term $\Omega_c \left(\ket{0}\bra{1} + \ket{1}\bra{0}\right)$, where $\Omega_c = 2 g \sqrt{\langle N \rangle}$ in correspondence with the previous case.
+Similarly, the energy levels $\ket{1, N-1}$ and $\ket{0, N}$ become mixed due to the coupling, and their splitting changes from $\hbar\Delta$ to $\hbar\Omega_R$.
+The following steps completely reproduce the classical case if we add the probe tone $\Omega_p$ in the last equation.
 
@@
 \begin{equation}\label{forpsi}
-	\ket{\psi_i(t)}=\ket{i} - i \int_{-\infty}^{t} d\tau_1 \hat{V}_I(\tau_1)\ket{{\psi_i}(\tau_1)}.
+	\ket{\psi_i(t)}=\ket{i} - \frac{i}{\hbar} \int_{-\infty}^{t} d\tau_1 \hat{V}_I(\tau_1)\ket{{\psi_i}(\tau_1)}.
 \end{equation} 
@@
 	U(t,-\infty) &= 1 + \sum_{n} U^{(n)}(t,-\infty),\\
-	U^{(n)}(t,-\infty) &= -i^n \int\limits_{-\infty}^{t}d \tau_1\hat V_I(\tau_1)...\int\limits_{-\infty}^{\tau_{n-1}}d \tau_n\hat{V}_I(\tau_n),
+	U^{(n)}(t,-\infty) &= \left(-\frac{i}{\hbar}\right)^n \int\limits_{-\infty}^{t}d \tau_1\hat V_I(\tau_1)...\int\limits_{-\infty}^{\tau_{n-1}}d \tau_n\hat{V}_I(\tau_n),
 \end{align}
@@
 	\begin{aligned}
-	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-i\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-i\frac{\Omega}{2}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{B}\ket{i}+\\
-	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{B}\ket{i}\big].
+	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-\frac{i}{\hbar}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-\frac{i}{2\hbar}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}+\\
+	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}\big].
 	\end{aligned}
@@
 	\begin{aligned}
-	\bra{f}U^{(2)}(t,-\infty)\ket{i}=-\bra{f}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\int\limits_{-\infty}^{\tau_1}d\tau_2\hat{V}_I(\tau_2)\ket{i}=\\
-	-\sum_j\int\limits_{-\infty}^{t}d\tau_1 e^{i\omega_{jf}\tau_1}\bra{f}\hat V(\tau_1)\ket{j}\int\limits_{-\infty}^{\tau_1}d\tau_2 e^{i\omega_{ij}\tau_2}\bra{j}\hat V(\tau_2)\ket{i}.
+	\bra{f}U^{(2)}(t,-\infty)\ket{i}=-\frac{1}{\hbar^2}\bra{f}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\int\limits_{-\infty}^{\tau_1}d\tau_2\hat{V}_I(\tau_2)\ket{i}=\\
+	-\frac{1}{\hbar^2}\sum_j\int\limits_{-\infty}^{t}d\tau_1 e^{i\omega_{jf}\tau_1}\bra{f}\hat V(\tau_1)\ket{j}\int\limits_{-\infty}^{\tau_1}d\tau_2 e^{i\omega_{ij}\tau_2}\bra{j}\hat V(\tau_2)\ket{i}.
 	\end{aligned}
@@
 	\begin{split}
-	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\{2\pi i}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}+\omega_d}+\\
-	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}+\omega_d}+\\
-	\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
-	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg].
+	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\\frac{2\pi i}{4\hbar^2}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
+	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg].
 	\end{split}
@@
 \begin{aligned}
-	W^{(2)}_{i\rightarrow f}&=2\pi\bigg|\sum_j\frac{\bra{f}\hat{B}\ket{j}\bra{j}\hat{B}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
+	W^{(2)}_{i\rightarrow f}&=\frac{\pi}{8\hbar^4}\bigg|\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
 	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}-2\omega_d).
@@
 \end{equation}
+
+For our case, $\hat V = \hbar \Omega_2 (\hat b + \hat b^\dag),\ \omega_d = \delta$ which leads to \eqref{eq:rates}.
 

### 2020-01-22 document.tex
Probabilities

@@
 \begin{aligned}
-R^{(2)}_{1\rightarrow 6} &\approx 2\pi\Omega_2^4 
-\frac{18 J^4 \left(2 \alpha + 
-\text{$\Omega_1$}\right)^2}{\alpha 
-^{6}\Omega_1^2},\\
-R^{(2)}_{2\rightarrow 5} &\approx 2\pi\Omega_2^4 
-\frac{18 J^4 \left(2 \alpha - \text{$\Omega_1
-		$}\right)^2}{\alpha ^{6}\Omega_1^2},
+R^{(2)}_{1\rightarrow 6} &\approx \pi\Omega_2^4 
+\frac{16 J^4 \left(3 \alpha^2 + 
+\text{$7\Omega_1^2$}\right)^2}{\alpha 
+^{10}},\\
+R^{(2)}_{5\rightarrow 2} &\approx \pi\Omega_2^4 
+\frac{4 J^4 \left(5 \alpha - \text{$3\Omega_1
+		$}\right)^2}{\alpha ^{8}},
 \end{aligned}\label{eq:rates}
@@
 
-Let's consider a time-dependent perturbation $\hat V(t) = \hat V \cos{\omega_d t}$ to the unperturbed Hamiltonian $\hat H$. In the interaction picture, the Schrödinger equation looks as 
+Let's consider a time-dependent perturbation $\hat V(t) =\frac{\hbar\Omega_{2}}{2}(\hat{c}e^{i\omega_d t}+\hat{c}^{\dagger}e^{-i\omega_d t}) $ to the unperturbed Hamiltonian $\hat H$.
+In the interaction picture, the Schrödinger equation looks as
 $$
@@
 	\begin{aligned}
-	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-\frac{i}{\hbar}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-\frac{i}{2\hbar}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}+\\
-	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{V}\ket{i}\big].
+	\bra{f}U^{(1)}(t,-\infty)\ket{i}&=-\frac{i}{\hbar}\int\limits_{-\infty}^{t}d\tau_1\hat{V}_I(\tau_1)\\ &=-\frac{i\Omega_2}{2}\big[\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}-\omega_d)\tau_1}\bra{f}\hat{c}^{\dagger}\ket{i}+\\
+	&\quad\quad\quad\quad\int\limits_{-\infty}^{t}d\tau_1 e^{i(\omega_{if}+\omega_d)\tau_1}\bra{f}\hat{c}\ket{i}\big].
 	\end{aligned}
@@
 	\begin{split}
-	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\\frac{2\pi i}{4\hbar^2}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
-	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}+\omega_d}+\\
-	\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
-	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg].
+	\bra{f}U^{(2)}(t, -\infty)\ket{i}=\\\frac{2\pi i\Omega_2^2}{4}\bigg[\delta(\omega_{if}+2\omega_d)\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\delta(\omega_{if})\bigg(\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}+\\
+	\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg)+\\
+	\delta(\omega_{if}-2\omega_d)\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg].
 	\end{split}
@@
 \end{equation} 
-In overall, for $\omega_d=\omega_{if}/2$:
+A two-photon emission:
 \begin{equation}\label{prob}
 \begin{aligned}
-	W^{(2)}_{i\rightarrow f}&=\frac{\pi}{8\hbar^4}\bigg|\sum_j\frac{\bra{f}\hat{V}\ket{j}\bra{j}\hat{V}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
-	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}-2\omega_d).
+	W^{(2)}_{i\rightarrow f}&=\frac{\pi\Omega_2^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{c}\ket{j}\bra{j}\hat{c}\ket{i}}{\omega_{ij}+\omega_d}\bigg|^2\delta(\omega_{if}+2\omega_d)\\ 
+	&=R_{i\rightarrow f}^{(2)}\delta(\omega_{if}+2\omega_d).
 \end{aligned}
@@
 
-For our case, $\hat V = \hbar \Omega_2 (\hat b + \hat b^\dag),\ \omega_d = \delta$ which leads to \eqref{eq:rates}.
+A two-photon absorption:
+\begin{equation}\label{prob1}
+\begin{aligned}
+W^{(2)}_{f\rightarrow i}&=\frac{\pi\Omega_2^4}{8}\bigg|\sum_j\frac{\bra{f}\hat{c}^{\dagger}\ket{j}\bra{j}\hat{c}^{\dagger}\ket{i}}{\omega_{ij}-\omega_d}\bigg|^2\delta(\omega_{if}-2\omega_d)\\ 
+&=R_{f\rightarrow i}^{(2)}\delta(\omega_{if}-2\omega_d).
+\end{aligned}
+\end{equation}
+
+For our case, $ \omega_d = \delta$ which leads to \eqref{eq:rates}.
 

### 2020-01-23 document.tex
additions from Lesha

--- 2020-01-19 document.tex
@@
 	simulation. This study is an important step 
-	towards understanding the behaviour of more 
-	complex systems of many atoms interacting 
-	with strong radiation.
+	towards understanding the behaviour of complex
+	systems of many atoms interacting	with strong radiation.
 	\end{abstract}
@@
 validity of fundamental quantum mechanical 
-laws\cite{you2011atomic}. Due to synthetic nature 
+laws. Due to synthetic nature 
 of SAAs, their Hamiltonians can be pre-designed 
 and engineered which makes them a particularly 
-versatile tool for studies in quantum optics. 
-Notably, high controllability of their parameters 
-allows direct observation of novel physical 
+versatile tool for studies in microwave quantum 
+optics \cite{you2011atomic,Qopt_1300refs}. Notably, high controllability
+of their parameters allows direct observation of novel physical 
 effects previously inaccessible for natural 
@@
 QED}\cite{wallraff2004strong, 
-chiorescu2004coherent} when the decoherence rates 
+chiorescu2004coherent} when the relaxation and decoherence rates 
 appear smaller than the Rabi frequency. 
@@
 
-So far, main experiments in on-chip quantum 
-optics with intense propagating light were 
+So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were 
 focused on single artificial 
@@
 dressing of the atom manifests itself through 
-Mollow triplets or Autler-Townes splittings of 
+Mollow triplets or Autler-Townes (A-T) splittings of 
 different kinds. However, despite the recent 
@@
 knowledge, no experiments concerning interaction 
-of such composite structures with intense free 
-radiation. While there were studies on dressing 
+of similar composite structures with intense driving field. While there were studies on dressing 
 of multi-atomic systems in a 
@@
 macha2014implementation, shulga2017observation, 
-yang2018probing}, their interaction with free 
-radiation is no less attractive since its 
+yang2018probing}, their interaction with external dressing field is not less attractive since its 
 frequency may be easily tuned to observe various 
@@
 is applied to this system through an on-chip 
-coplanar waveguide while its state can be 
+coplanar antenna while its state can be 
 monitored by joint dispersive readout using the 
@@
 find that strong interaction with microwaves not 
-only calls forth multiphoton transitions of 
+only results in multiphoton transitions of 
 various orders between SAM states, but also 
@@
 coherence of superconducting quantum devices, and 
-previous studies of SAAs and free radiation have 
+previous studies of SAAs under strong driving field 
 either involved just a single atom or have 
@@
 couples\cite{majer2007coupling} the transmons and 
-allows joint\cite{chow2010detecting} readout of 
+allows joint readout \cite{chow2010detecting} of 
 their states. In \autoref{fig:experiment}~(a), 
-the optical photograph of the device is shown 
-depicting the layout of the components. The 
+the optical photograph of the device is shown, where the layout of the components is presented. The 
 resonator in its upper part is connected to a 
@@
 LC-circuit (in the middle), the transmons are 
-shown in colour on the sides; their SQUIDs are 
+shown in color on the sides; their SQUIDs are 
 represented as tunable Josephson junctions. A 
@@
 visible just below the $02/2$ line. As we will 
-see, it is involved in forming features II and 
-III. Notably, transitions $11/2$, ${21/3}$ and 
+see, processes $12/3$~and~$21/3$ are involved in forming features III and II, respectively. Notably, transitions $11/2$, ${21/3}$ and 
 ${12/3}$ are forbidden when there is no 
@@
 avoided crossing in III is between two 
-transitions: ${12/3}$ and ${10} - {02}$ 
+transitions: ${12/3}$ (three-photon transition $\ket{00}\rightarrow\ket{12}$) and ${10} - {02}$ 
 ($\ket{10}\rightarrow\ket{02}$) which are of the 
 same frequency when $\omega_1 = 
-\omega_2+\alpha_2/2$. The latter process depopulating $01$ is better discernible in \autoref{fig:two-tone}~(d) 
+\omega_2+\alpha_2/2$. The latter process is depopulating $10$ and it is better discernible in \autoref{fig:two-tone}~(d) 
 than in \autoref{fig:two-tone}~(a), (b). For II, the 
@@
 If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes.
-As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}}.
+As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}.
 
@@
 	Schematic of the transition frequencies near 
-	III (not to scale). Red dashed line shows the 
+	III (not to scale). Black dashed line shows the 
 	current (0.36 mA) where the first transmon 
@@
 (blue), and the resonance point in current is 
-shown with a dashed red line. Next, 
+shown with a dashed black line. Next, 
 \autoref{fig:main_scheme}~(b) demonstrates the 
@@
 \end{aligned}
+\label{eq:two-photon_lab}
 \end{equation}
@@
 When $\Omega_1 = 0$, these equations yield indentical pairs of solutions due to the properties of the modulus $|\omega_1 - \omega_d|$.
-Intriguingly, they are the three-photon and single-photon transition frequencies in the laboratory frame
+Substituting \autoref{eq:two-photon} into \autoref{eq:two-photon_lab}, we obtain the frequencies and identify them as the three-photon and single-photon transition frequencies in the laboratory frame:
 \begin{equation}
@@
 \begin{equation}
-\omega_d = \frac{\omega_{1} - \omega_{2}}{2} + \frac{\Omega_{1}^{2} - \Omega_{2}^{2}}{ 2\left(\omega_{1} - \omega_{2}\right)}
+\omega_d = \frac{\omega_{1} + \omega_{2}}{2} + \frac{\Omega_{1}^{2} - \Omega_{2}^{2}}{ 2\left(\omega_{1} - \omega_{2}\right)}
 \label{eq:topo_comm}
@@
 
-\section{Standard Autler-Townes effect for a three-level atom} \label{sec:3-level-at}
+\section{Standard Autler-Townes effect for a three-level $\Xi$ atom} \label{sec:3-level-at}
 
@@
 The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation.
-However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace.
-Unfortunately, $\hat V$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V$.
+However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V_J$, they become determined and are given by diagonalization of $\hat V_J$ in the degenerate subspace.
+Unfortunately, $\hat V_J$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V_J$.
 In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
@@
 states from the degenerate subspace with energy 
-$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
+$E_n$, and $V_{mn} = \bra{m} \hat  V_J \ket{n}$. 
 The sum is over all other zero-order states 
@@
 
-For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$)
+For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$) we obtain the following matrix:
 \renewcommand{\kbldelim}{[}% Left delimiter

### 2020-01-23 document.tex
Topo text color + minor DPT edits

--- 2020-01-21 document.tex
@@
 However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace.
-Unfortunately, $\hat V$ is zero in both our subspaces, so technically any choice of zero-order states will diagonalize $\hat V$.
-In other words, the degeneracy is not lifted in the first-order, and thus we have diagonalize the matrix\cite{landau2013quantum}
+Unfortunately, all matrix elements of $\hat V = \hat V_J$ are zero in both our degenerate subspaces, so technically any choice of zero-order states will diagonalize it.
+In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix\cite{landau2013quantum}
 \begin{equation}

### 2020-01-30 document.tex
Merge branch 'dm'
# Conflicts:
#	document.tex

@@
 validity of fundamental quantum mechanical 
-laws\cite{you2011atomic}. Their Hamiltonians can be pre-designed 
+laws\cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed
 and engineered which makes them a particularly 
@@
 QED}\cite{wallraff2004strong, 
-chiorescu2004coherent} when the decoherence rates 
+chiorescu2004coherent} when the relaxation and decoherence rates
 appear smaller than the Rabi frequency. 
@@
 
-So far, main experiments in on-chip quantum 
-optics with intense propagating light were 
+So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were
 focused on single artificial 
@@
 dressing of the atom manifests itself through 
-Mollow triplets or Autler-Townes splittings of 
+Mollow triplets or Autler-Townes (A-T) splittings of
 different kinds. However, despite the recent 
@@
 knowledge, no experiments concerning interaction 
-of such composite structures with intense free 
-radiation. While there were studies on dressing 
+of similar composite structures with intense driving field. While there were studies on dressing
 of multi-atomic systems in a 
@@
 macha2014implementation, shulga2017observation, 
-yang2018probing}, their interaction with free 
-radiation is no less attractive since its 
+yang2018probing}, their interaction with external dressing field is not less attractive since its
 frequency may be easily tuned to observe various 
@@
 is applied to this system through an on-chip 
-coplanar waveguide while its state can be 
+coplanar antenna while its state can be
 monitored by joint dispersive readout using the 
@@
 find that strong interaction with microwaves not 
-only calls forth multiphoton transitions of 
+only results in multiphoton transitions of
 various orders between SAM states, but also 
@@
 coherence of superconducting quantum devices, and 
-previous studies of SAAs and free radiation have 
+previous studies of SAAs under strong driving field
 either involved just a single atom or have 
@@
 couples\cite{majer2007coupling} the transmons and 
-allows joint\cite{chow2010detecting} readout of 
+allows joint readout \cite{chow2010detecting} of
 their states. In \autoref{fig:experiment}~(a), 
-the optical photograph of the device is shown 
-depicting the layout of the components. The 
+the optical photograph of the device is shown, where the layout of the components is presented. The
 resonator in its upper part is connected to a 
@@
 LC-circuit (in the middle), the transmons are 
-shown in colour on the sides; their SQUIDs are 
+shown in color on the sides; their SQUIDs are
 represented as tunable Josephson junctions. A 
@@
 visible just below the $02/2$ line. As we will 
-see, it is involved in forming features II and 
-III. Notably, transitions $11/2$, ${21/3}$ and 
+see, processes $12/3$~and~$21/3$ are involved in forming features III and II, respectively. Notably, transitions $11/2$, ${21/3}$ and
 ${12/3}$ are forbidden when there is no 
@@
 avoided crossing in III is between two 
-transitions: ${12/3}$ and ${10} - {02}$ 
+transitions: ${12/3}$ (three-photon transition $\ket{00}\rightarrow\ket{12}$) and ${10} - {02}$
 ($\ket{10}\rightarrow\ket{02}$) which are of the 
 same frequency when $\omega_1 = 
-\omega_2+\alpha_2/2$. The latter process depopulating $01$ is better discernible in \autoref{fig:two-tone}~(d) 
+\omega_2+\alpha_2/2$. The latter process is depopulating $10$ and it is better discernible in \autoref{fig:two-tone}~(d)
 than in \autoref{fig:two-tone}~(a), (b). For II, the 
@@
 	Schematic of the transition frequencies near 
-	III (not to scale). Red dashed line shows the 
+	III (not to scale). Black dashed line shows the
 	current (0.36 mA) where the first transmon 
@@
 (blue), and the resonance point in current is 
-shown with a dashed red line. Next, 
+shown with a dashed black line. Next,
 \autoref{fig:main_scheme}~(b) demonstrates the 
@@
 states from the degenerate subspace with energy 
-$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
+$E_n$, and $V_{mn} = \bra{m} \hat  V_J \ket{n}$.
 The sum is over all other zero-order states 

### 2020-01-30 Pictures/Plotting/MainPicturePlot.py
APS style plots

@@ -45,9 +45,9 @@ class MainPicturePlot:
         img1 = ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap = self._cmap)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
-        ax.set_xlabel('Current [$10^{-4}$ A]');
-        ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
-        cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$", position=(1.125,-1.5))
+        ax.set_xlabel('Current ($10^{-4}$ A)');
+        ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
+        cb.ax.set_title(r"$\mathfrak{Re}\ S^{exp}_{21}$", position=(1.125,-1.5))
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc
         cb.update_ticks()
@@ -104,9 +104,9 @@ class MainPicturePlot:
         img1 = ax.pcolormesh(*data, rasterized=True, vmax = 1.025*np.max(C), cmap = self._cmap)
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(1,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
-        ax.set_xlabel('Current [$10^{-4}$ A]');
+        ax.set_xlabel('Current ($10^{-4}$ A)');
         # ax.set_ylabel('Frequency [GHz]');
-        cb.ax.set_title(r"$\mathfrak{Re} [S^{sim}_{21}]$", position=(-0.125,-1.5))
+        cb.ax.set_title(r"$\mathfrak{Re}\ S^{sim}_{21}$", position=(-0.125,-1.5))
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc
         cb.update_ticks()

### 2020-01-30 Pictures/Plotting/MainPictureSlices.py

@@ -96,8 +96,8 @@ class MainPictureSlices:
 
 
 
-        axes[0].set_ylabel("$\omega_d^{1,2}/2\pi$ [GHz]")
-        axes[1].set_xlabel(r"$\mathfrak{Re} [S^{exp,\,sim}_{21}]$")
+        axes[0].set_ylabel("$\omega_d^{1,2}/2\pi$ (GHz)")
+        axes[1].set_xlabel(r"$\mathfrak{Re}\ S^{exp,\,sim}_{21}$")
 
 
         plt.text(-0.53, 1.1, "(c)", fontdict={"name": "STIX"}, fontsize=17,

### 2020-01-30 Pictures/Plotting/Powerscan.py

@@ -30,10 +30,10 @@ class ZoomPlot:
 
             m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 2 == 0:
-                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
+                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
                 ax.yaxis.set_major_locator(MultipleLocator(0.01))
             if idx > 1:
-                ax.set_xlabel('Current [$10^{-4}$ A]');
+                ax.set_xlabel('Current ($10^{-4}$ A)');
 
         self._Omega_2s = array([6e-3, 15e-3, 30e-3, 60e-3])*0.75
         self._plot_theory(axes)
@@ -54,7 +54,6 @@ class ZoomPlot:
         plt.text(.375, .025, r"$P_{exc} =$-20 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='left', color="black")
 
-
         plt.text(.66, .025, r"-12 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,1].transAxes, ha='left', color="black")
 
@@ -65,11 +64,11 @@ class ZoomPlot:
                  transform=axes[1,1].transAxes, ha='left', color="black")
 
 
-        cbaxes1 = fig.add_axes([0.125,.95,0.5,.015])
+        cbaxes1 = fig.add_axes([0.125,.95,0.6,.015])
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$ [mU]", position=(1.3,-2))
+        cb.ax.set_title(r"$\mathfrak{Re}\ S^{exp}_{21}$", position=(1.15,-2))
 
         plt.text(-0.35, 1.15, "(a)", fontdict={"name": "STIX"}, fontsize=20,
                  transform=axes[0,0].transAxes)

### 2020-01-30 Pictures/Plotting/StationaryPlot.py

@@ -139,9 +139,9 @@ class StationaryPlot:
 
         plt.ylim(5.1, 5.5)
         plt.xlim(2,6)
-        ax.set_ylabel("$\omega_{d}^{1,2}/2\pi$ [GHz]")
+        ax.set_ylabel("$\omega_{d}^{1,2}/2\pi$ (GHz)")
 
-        ax.set_xlabel("Current [$10^{-4}$ A]")
+        ax.set_xlabel("Current ($10^{-4}$ A)")
         plt.legend(ncol=3, fontsize=7)
 
         cbaxes1 = fig.add_axes([0.15, .975, 0.6, .02])

### 2020-01-30 Pictures/Plotting/TopologicalSplitting.py

@@ -38,9 +38,9 @@ class TopologicalSplitting:
             m = ax.pcolormesh(self._X, self._Y, array(self._plots[idx]).T,
                               vmin=0, vmax=1, cmap="Spectral", rasterized=True)
             if idx in [8, 7, 6]:
-                ax.set_xlabel("Current [$10^{-4}$ A]")
+                ax.set_xlabel("Current ($10^{-4}$ A)")
             if idx in [0, 3, 6]:
-                ax.set_ylabel("$\omega_d^{1,2}/2\pi$ [GHz]")
+                ax.set_ylabel("$\omega_d^{1,2}/2\pi$ (GHz)")
             if idx in [0]:
                 plt.text(.5, .7, "$\Omega_1: {0}$ MHz\n$\Omega_2: {1}$ MHz".format(Omegas[idx][0],
                                                                                    Omegas[idx][
@@ -130,7 +130,7 @@ class TopologicalSplitting:
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$P_{\left|00\right\rangle}$", position=(1.125, -2))
+        cb.ax.set_title(r"$P_{\left|00\right\rangle}$", position=(1.05, -2), fontsize=13)
 
         plt.savefig("../topological_splittings.pdf", bbox_inches="tight", dpi=600)
 

### 2020-01-30 Pictures/Plotting/ZoomPlot.py

@@ -22,9 +22,9 @@ class ZoomPlot:
             m = ax.pcolormesh(self._X, self._Y, real(array(self._plots[idx]).T),
                               vmax=1, vmin=0, rasterized=True, cmap="Spectral")
             if idx % 2 == 0:
-                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ [GHz]');
+                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
             if idx > 1:
-                ax.set_xlabel('Current [$10^{-4}$ A]');
+                ax.set_xlabel('Current ($10^{-4}$ A)');
 
 
         self._Omega_2s = array([6e-3, 15e-3, 30e-3, 60e-3])*0.75
@@ -60,7 +60,7 @@ class ZoomPlot:
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$P_{\left|00\right\rangle}$", position=(1.125,-2))
+        cb.ax.set_title(r"$P_{\left|00\right\rangle}$", position=(1.125,-2), fontsize=13)
 
         plt.text(-0.35, 1.15, "(b)", fontdict={"name": "STIX"}, fontsize=20,
                  transform=axes[0,0].transAxes)

### 2020-01-30 Pictures/Plotting/ZoomPlot_for_1D.py

@@ -30,12 +30,12 @@ class Powerscan1D:
 
             m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 3 == 0:
-                ax.set_ylabel('Frequency [GHz]');
+                ax.set_ylabel('Frequency (GHz)');
                 ax.yaxis.set_major_locator(MultipleLocator(0.01))
                 ax.set_xlabel("")
                 ax.set_xticklabels([])
             if idx > 8:
-                ax.set_xlabel('Current [$10^{-4}$ A]');
+                ax.set_xlabel('Current ($10^{-4}$ A)');
 
         self._Omega_2s = array([6e-3, 7.55e-3, 9.5e-3, 11.9e-3, 15e-3, 19e-3,
                                 23e-3, 30e-3, 37.8e-3, 47.65e-3, 60e-3]) * 0.75
@@ -46,7 +46,7 @@ class Powerscan1D:
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$\mathfrak{Re} [S^{exp}_{21}]$ [mU]", position=(1.3, -2))
+        cb.ax.set_title(r"$\mathfrak{Re}\ S^{exp}_{21}$", position=(1.3, -2))
 
         plt.text(-0.35, 1.15, "(a)", fontdict={"name": "STIX"}, fontsize=22,
                  transform=axes[0, 0].transAxes)
@@ -65,8 +65,8 @@ class Powerscan1D:
         #         sqrt(3) / 3 * 2 / 5),
         #          fontdict={"name": "STIX"}, fontsize=12,
         #          transform=plt.gca().transAxes)
-        plt.xlabel("$V_{rms}$ [mV]")
-        plt.ylabel("Splitting [MHz]")
+        plt.xlabel("$V_{rms}$ (mV)")
+        plt.ylabel("Splitting (MHz)")
         plt.legend()
         plt.grid(color='black', linestyle=':', linewidth=1)
 

### 2020-01-30 document.tex
Brackets and BMSTU corrections

@@
 \documentclass[%
- pra,
+ aps, prx,
 % jmp,
@@
 % Conference Proceedings
-]{revtex4-1}
+superscriptaddress
+]{revtex4-2}
 
@@
 \usepackage{xcolor}
+\usepackage{url}
 
@@
 \newcommand{\mytitile}{Light-dressing of a 
-diatomic supercondufcing artificial molecule}
+diatomic superconducting artificial molecule}
 
@@
 	\author{V.B. Yursa}
-	\affiliation{ 
-		Skolkovo Institute of Science and 
-		Technology, Moscow, Russian Federation
-	}%
+	\affiliation{Skolkovo Institute of Science 
+		and Technology, Moscow, Russian Federation}%
 
@@
 
-	\author{A.A. Pischimova}
+	\author{A.A. Pishchimova}
 	\affiliation{FMN Laboratory, Bauman Moscow 
@@
 	\affiliation{ 
-		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia}
+		Moscow Institute of Physics and Technology, 
+		Dolgoprundiy, Russia
+	}
 	\affiliation{Physics Department, Royal 
@@
 	towards understanding the behaviour of complex
-	systems of many atoms interacting	with strong radiation.
+	systems of many atoms interacting coherently with strong radiation.
 	\end{abstract}
@@
 validity of fundamental quantum mechanical 
-laws\cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed
+laws \cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed 
 and engineered which makes them a particularly 
 versatile tool for studies in quantum optics, and high controllability of their parameters 
-allows direct observation of novel physical 
-effects previously inaccessible for natural 
+allows direct observation of novel physical effects previously inaccessible for natural 
 systems.
@@
 far is the strong coupling with light in {circuit 
-QED}\cite{wallraff2004strong, 
+QED} \cite{wallraff2004strong, 
 chiorescu2004coherent} when the relaxation and decoherence rates 
@@
 implementations of strong coupling in terms of 
-coherence\cite{forn2019ultrastrong}. 
+coherence \cite{forn2019ultrastrong}. 
 However, in sharp contrast with natural atoms and 
@@
 to free-propagating electromagnetic waves in 1D 
-on-chip waveguides\cite{astafiev2010resonance} 
+on-chip waveguides \cite{astafiev2010resonance} 
 without using cavities at all. The Rabi frequency 
 in this case may reach 50\% of the transition 
-frequency\cite{deng2015observation} which is even 
+frequency \cite{deng2015observation} which is even 
 beyond strong coupling 
-regime\cite{forn2019ultrastrong}. To correctly 
+regime \cite{forn2019ultrastrong}. To correctly 
 describe the behaviour of an atom in these 
 conditions, the so-called \textit{dressed atom 
-approach}\cite{cohen1998atom} is employed when 
+approach} \cite{cohen1998atom} is employed when 
 the radiation has to be directly included in the 
@@
 focused on single artificial 
-atoms\cite{baur2009measurement, 
+atoms \cite{baur2009measurement, 
 sillanpaa2009autler, astafiev2010resonance, 
@@
 successes in control of large arrays of 
-interacting SAAs\cite{Song574, ye2019propagation, 
+interacting SAAs \cite{Song574, ye2019propagation, 
 arute2019quantum}, there were, up to our best 
@@
 of multi-atomic systems in a 
-cavity\cite{fink2009dressed, 
+cavity \cite{fink2009dressed, 
 macha2014implementation, shulga2017observation, 
@@
 artificial atoms: a superconducting artificial 
-molecule\cite{kou2017fluxonium} (SAM). We use two 
-Xmon-type\cite{barends2013coherent} 
-transmons\cite{koch2007charge} interacting with 
+molecule \cite{kou2017fluxonium} (SAM). We use two 
+Xmon-type \cite{barends2013coherent} 
+transmons \cite{koch2007charge} interacting with 
 each other through a cavity 
-bus\cite{majer2007coupling}. Microwave radiation 
+bus \cite{majer2007coupling}. Microwave radiation 
 is applied to this system through an on-chip 
@@
 monitored by joint dispersive readout using the 
-same coupling cavity\cite{chow2010detecting}. We 
+same coupling cavity \cite{chow2010detecting}. We 
 find that strong interaction with microwaves not 
@@
 systems (including natural 
-molecules\cite{tamarat1995pump, 
+molecules \cite{tamarat1995pump, 
 ahmed2012autler}), we find qualitatively new 
@@
 driving power (for instance, as we will show, the 
-bSWAP gate\cite{poletto2012entanglement} is 
+bSWAP gate \cite{poletto2012entanglement} is 
 directly affected by light dressing).
@@
 (Xmon) SAAs with asymmetric 
-SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J,
+SQUIDs \cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
 \sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
 charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
-to a single notch-type\cite{probst2015efficient} 
+to a single notch-type \cite{probst2015efficient} 
 $\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
 1/100\ \text{ns}^{-1}$) which both 
-couples\cite{majer2007coupling} the transmons and 
+couples \cite{majer2007coupling} the transmons and 
 allows joint readout  \cite{chow2010detecting} of 
@@
 the transmons by a dual 
-``claw''\cite{barends2013coherent} coupler. Flux 
+``claw'' \cite{barends2013coherent} coupler. Flux 
 lines that allow independent control of the 
@@
 an individual on-chip line or via an external 
-coil) it is possible\cite{koch2007charge} to 
+coil) it is possible \cite{koch2007charge} to 
 directly  control $\omega$. In our modelling, we 
@@
 depends on the transmon 
-frequencies\cite{koch2007charge}, but we take $J$ 
+frequencies \cite{koch2007charge}, but we take $J$ 
 to be a constant as in \autoref{tab:parameters} 
@@
 \begin{aligned}
-	\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{(1,2)},\\
+	\omega_{\{1,2\}} &\rightarrow \Delta_{\{1,2\}} = \omega_{\{1,2\}} - \omega_d^{\{1,2\}},\\
 	\hat H_{int} &\rightarrow \hbar J \left[\hat 
@@
 following collapse 
-operators\cite{bishop2010circuit}:
+operators \cite{bishop2010circuit}:
 \begin{equation}\
@@
 a valid approach until the coupling strength $J$ 
-is not too large\cite{beaudoin2011dissipation}. 
+is not too large \cite{beaudoin2011dissipation}. 
 Therefore, the complete evolution equation for 
@@
 frame despite that it may not be correct in 
-general\cite{shavit2019bridging}.
+general \cite{shavit2019bridging}.
 
@@
 shifts corresponding to the SAM basis 
-states\cite{filipp2009two, chow2010detecting}. Since we have not
+states \cite{filipp2009two, chow2010detecting}. Since we have not 
 directly measured these dispersive shifts, in our 
@@
 analytical solution. We have been using the 
-\textit{qutip}\cite{johansson2013qutip} (quantum 
+\textit{qutip} \cite{johansson2013qutip} (quantum 
 optics toolbox in Python) to simulate the 
@@
 system for various parameter combinations of the 
-Liouvillian.
+Liouvillian. The source code for the simulations can be found on GitHub \footnote{\url{https://github.com/vdrhtc/Examples/tree/master/transmon-simulations/two_transmons}}.
 
@@
 \textit{steadystate} 
-function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
+function \footnote{\url{http://qutip.org/docs/4.0.2/guide/guide-steady.html}}.
  This method is applicable when the driving 
@@
 propagator $\Lambda(T, 0)$ corresponding to its 
-largest eigenvalue\cite{dittrich1998quantum, 
+largest eigenvalue  \cite{dittrich1998quantum, 
 rivas2012open}. Upon infinitely many applications 
@@
 	respectively. \textbf{(d)} Simulated 
-	population of the state $\ket{10}$ ($\lg 
+	population of the state $\ket{10}$ ($\log_{10} 
 	P_{\ket{10}}$ is shown with colour). Lines 
@@
 corresponding expected measurement outcomes 
-$\mathfrak{Re} \Tr[\hat M \hat \rho_{ss}]$ 
+$\mathfrak{Re}\ \Tr[\hat M \hat \rho_{ss}]$ 
 depending on the excitation frequency and 
@@
 As one can see, various multiphoton transitions besides 
-the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
+the main lines at $\omega_{\{1,2\}}(I)/2\pi$ (or 
 $01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$ 
 are very commonly found for transmons and lie 
-$|\alpha_{(1,2)}|/2$ lower than the main lines 
-$\omega_{(1,2)}(I)$. Another two-photon process 
+$|\alpha_{\{1,2\}}|/2$ lower than the main lines 
+$\omega_{\{1,2\}}(I)$. Another two-photon process 
 appears as $11/2$ line when two SAAs are excited 
@@
 example, for doing the bSWAP 
-gate\cite{poletto2012entanglement}; in our case, 
+gate \cite{poletto2012entanglement}; in our case, 
 it is taking part in feature I. A 
@@
 H^D + \hat V_J$, labelled $\ket{k},\ k=1..6$.
+We find the mean relative element-wise error of around 3\% between numerically obtained eigenvectors and perturbative ones for our experimental parameters.
 
 The time-dependent perturbation theory that we use to calculate the transition rates of the two-photon processes stimulated by $\hat V_t$ is reviewed in Appendix \ref{sec:2pp}.
-Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time\cite{faisal2013theory}:
+Using the corrected eigenstates $\ket{k}$ and neglecting small terms, we obtain the following expressions for the transition rates per unit time \cite{faisal2013theory}:
 \begin{equation}
 \begin{aligned}
-R^{(2)}_{1\rightarrow 6} &\approx \pi\Omega_2^4
+R^{(2)}_{2\rightarrow 5} &\approx \pi\Omega_2^4 
 \frac{16 J^4 \left(3 \alpha^2 + 
@@
 ^{10}},\\
-R^{(2)}_{5\rightarrow 2} &\approx \pi\Omega_2^4
+R^{(2)}_{1\rightarrow 6} &\approx \pi\Omega_2^4 
 \frac{4 J^4 \left(5 \alpha - \text{$3\Omega_1
@@
 when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
-true for our setup. From \autoref{eq:rates} 
+true for our setup. Tailor expansion here leads to errors of less than 0.5\%.  From \autoref{eq:rates} 
 follows that the sideband transitions are 
@@
 curves we have fitted the 
-$\omega_{(1,2)}(\Phi_e)$ transitions with simple 
+$\omega_{\{1,2\}}(\Phi_e)$ transitions with simple 
 linear functions and substituted them in 
@@
 
-We want to thank our parents and our cat Coconut. Also FPI grant
+We gratefully acknowledge valuable discussions with I. Besedin, V. Ryazanov and A. Ustinov. 
+Experimental investigation was conducted with the support of Russian Science Foundation, Grant No.
+16-12-00070.
+Numerical simulations were supported by the Russian Science Foundation (contract no.
+16-12-00095).
+Theoretical work was supported by Ministry of Science and Higher Education of Russian Federation in the framework of Increase Competitiveness Program of the NUST MISIS (contract no.
+K2-2017-081).
+Devices/Samples were fabricated at the BMSTU Nanofabrication Facility (Functional Micro/Nanosystems, FMNS REC, ID 74300)
 
@@
 Unfortunately, all matrix elements of $\hat V = \hat V_J$ are zero in both our degenerate subspaces, so technically any choice of zero-order states will diagonalize it.
-In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix\cite{landau2013quantum}
+In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix \cite{landau2013quantum}
 \begin{equation}
@@
 \section{Transition rates of the two-photon process}\label{sec:2pp}
-We will employ the time-dependent perturbation theory that gives analytical expressions for the transition rates for single and multi-photon processes\cite{faisal2013theory}.
+We will employ the time-dependent perturbation theory that gives analytical expressions for the transition rates for single and multi-photon processes \cite{faisal2013theory}.
 
@@
 \end{equation}
-Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives\cite{faisal2013theory}
+Go over the long-time limit $t\rightarrow\infty$ in the final integral and collect the terms belongings to the same delta functions. This gives \cite{faisal2013theory}
 \begin{equation}

### 2020-04-16 document.tex
referee answers

@@
 
+	\author{E.I. Malevannaya}
+	\affiliation{FMN Laboratory, Bauman Moscow 
+		State Technical University, Moscow, Russia}
+	\affiliation{Dukhov Automatics Research 
+		Institute, (VNIIA), Moscow, Russia}
+
 	\author{O.V. Astafiev}
@@
 
+	\vspace*{-5cm}
 	\maketitle
@@
 
-So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were 
-focused on single artificial 
+So far, there have been many experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics with artificial 
 atoms \cite{baur2009measurement, 
@@
 macha2014implementation, shulga2017observation, 
-yang2018probing}, their interaction with external dressing field is not less attractive since its 
+yang2018probing}, their interaction with external dressing field is no less attractive since its 
 frequency may be easily tuned to observe various 
@@
 is applied to this system through an on-chip 
-coplanar antenna while its state can be 
+coplanar waveguide antenna while its state can be 
 monitored by joint dispersive readout using the 
-same coupling cavity \cite{chow2010detecting}. We 
+same coupling cavity \cite{chow2010detecting}. Examining our high-resolution data, we
 find that strong interaction with microwaves not 
-only results in multiphoton transitions of 
+only results in rich variety of multiphoton transitions of 
 various orders between SAM states, but also 
@@
 spectral manifestations of light dressing when 
-SAAs are irradiated unequally. We note that there 
-were no such experiments with natural molecules, 
-which could in principle demonstrate same 
-effects, because they lack controllability and 
-coherence of superconducting quantum devices, and 
-previous studies of SAAs under strong driving field 
-either involved just a single atom or have 
+SAAs are irradiated unequally. We could not find any reports of similar effects in the 
+previous studies of SAAs under strong driving field because they
+either involved just a single atom \cite{baur2009measurement, 
+	sillanpaa2009autler, astafiev2010resonance, 
+	novikov2013autler, 
+	koshino2013observation, 
+	braumuller2015multiphoton, peng2018vacuum, 
+	gasparinetti2019two} or have 
 demonstrated only the standard spectral 
-signatures known from the quantum optics (see 
+signatures known from the quantum optics \cite{suri2013observation} (see 
 Appendix \ref{sec:3-level-at}).
-
-Besides its fundamental importance, this 
-experiment may be useful for future quantum 
-computers: a quantum engineer should account for 
+Moreover, most of the previous spectroscopic experiments with coupled transmons were done at low powers and resolved only the most prominent single-photon transitions \cite{majer2007coupling, filipp2011multimode}, or used two distinct excitation frequencies to reach higher energy levels \cite{dicarlo2009demonstration}, or did not study the spectral data with necessary resolution \cite{kounalakis2018tuneable}, or used non-tunable transmons \cite{poletto2012entanglement}.
+In contrast, we put a tunable system in a new regime of intense driving which allows to discover and quantify both experimentally and theoretically its novel unexplored behaviours.
+Likewise, we could not find reports of such effects in natural molecules,
+which could in principle be observed there; most probably, this is caused by reduced controllability and 
+coherence compared to superconducting quantum devices.
+
+We believe that our results are valuable to the domain of molecular physics and quantum optics beyond just superconducting Josephson systems since the reported effects are universally possible for any kind of light-matter interaction.
+Given similar conditions, they will emerge in any diatomic molecule regardless of its nature, and modification of molecular spectra using light is now a topic of active research \cite{hertzog2019strong}.
+In this regard we note that the presented theoretical framework is important, too, as it will be useful in analysis of similar effects in the future.
+Besides, we consider this experiment to be useful for superconducting quantum
+computing: one should account for 
 the observed behaviours carefully controlling the 
 driving power (for instance, as we will show, the 
-bSWAP gate \cite{poletto2012entanglement} is 
+bSWAP gate \cite{poletto2012entanglement} may be 
 directly affected by light dressing).
+Finally, the high-power excitation regime is useful to directly obtain information about higher energy levels of the system while using minimum equipment; this is an important problem that should be addressed to facilitate scaling of control electronics for superconducting quantum processors (see, i.e.
+\cite{hornibrook2015cryogenic}).
 
@@
 (Xmon) SAAs with asymmetric 
-SQUIDs \cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
-\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
-charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
+SQUIDs \cite{hutchings2017tunable}. Single-transmon parameters determined from spectroscopy: maximal Josephson energies $E^{(1)}_{J, 
+\sum}/h = 24.3$ GHz, $E^{(2)}_{J,\sum}/h = 18.3$ GHz, 
+charging energies $E^{(1,2)}_C/h = 220$ MHz, SQUID asymmetries $d^{(1,2)} = 0.75$ defined as in \cite{koch2007charge}) coupled 
 to a single notch-type \cite{probst2015efficient} 
@@
 	\caption{\textbf{(a)} Optical image of 
-	the device (false coloured). Two transmons 
+	the device (false colored). Two transmons 
 	(orange, 1 and blue, 2) are coupled 
@@
 	SQUIDs with magnetic flux control. 
-	\textbf{(c)} Frequencies of the fundamental 
+	\textbf{(c)} A sketch of the frequencies of the fundamental 
 	transitions of the transmons $\omega_1(I)$ 
@@
 
-\begin{table}
-	\begin{ruledtabular}
-	\begin{tabular}{rll}
-	Parameter & Transmon 1  & Transmon 2\\\hline
-	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
-	$\alpha/2\pi$ [MHz] & -220 & -220 \\
-	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
-	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
-	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
-	\end{tabular}
-	\end{ruledtabular}
-	\caption{SAM parameters. Transmons are only 
-	different in the frequency tuning range and 
-	coherence times measured in the lower sweet 
-	spot for the 1\textsuperscript{st} one and in 
-	the higher sweet spot for the 
-	2\textsuperscript{nd}. The coupling strength 
-	$J$ depends on the transmon frequencies and 
-	is specified here for $\omega_1/2\pi = 
-	\omega_2/2\pi = 5.32$ GHz.}
-	\label{tab:parameters}
-\end{table}
-
-\subsection{Theoretical background}
+\vspace{-.5cm}
+\subsection{Quantum-mechanical description}
 
@@
 transmon, two terms representing the interaction 
-of each transmon with the driving field at the 
-same frequency $\omega_d$, and the 
+of transmons with driving fields at the 
+frequencies $\omega_d^{(1,2)}$, and the 
 transmon-transmon interaction term:
 \begin{equation}\label{Hsystem}
-\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
-\end{equation}
-where $\hat H_{int} = \hbar J (\hat b +\hat 
-b^\dag)(\hat c+\hat c^{\dagger})$ is the 
-transverse interaction between the atoms. 
+\hat H = \hat H_{tr}^{(1)}+\hat H_{tr}^{(2)}+\hat H_{d}^{(1)}+\hat H_{d}^{(2)}+\hat H_{int},
+\end{equation}
+where the superscripts numerate the transmons and $\hat H_{int} = \hbar J (\hat b +\hat 
+b^\dag)(\hat c+\hat c^{\dagger})$. 
 Strictly speaking, $J = J(\omega_1, \omega_2)$ 
@@
 frequencies \cite{koch2007charge}, but we take $J$ 
-to be a constant as in \autoref{tab:parameters} 
-due to its negligible variation for our range of 
-frequencies.
+to be a constant due to its negligible variation for our range of frequencies.
 
@@
 \begin{equation}
-\hat R = \exp[-i t (\omega_d^1 
-b^{\dagger}b+\omega_d^2 
+\hat R = \exp[-i t (\omega_d^{(1)}
+b^{\dagger}b+\omega_d^{(2)} 
 c^{\dagger}c)],\label{eq:R}
@@
 \end{equation}
-Here we use subscripts 1 and 2 to denote first and second SAAs. After the transformation and application of the RWA
+After the transformation and application of the RWA
 \begin{equation}
 \begin{aligned}
-	\omega_{\{1,2\}} &\rightarrow \Delta_{\{1,2\}} = \omega_{\{1,2\}} - \omega_d^{\{1,2\}},\\
+	\omega_{1,2} &\rightarrow \Delta_{1,2} = \omega_{1,2} - \omega_d^{(1,2)},\\
 	\hat H_{int} &\rightarrow \hbar J \left[\hat 
-	b^\dag \hat c e^{it(\omega_d^1 - \omega_d^2)} 
-	+ \hat b \hat c^\dag e^{-it(\omega_d^1 - 
-	\omega_d^2)}\right],\\
-	\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
+	b^\dag \hat c e^{it(\omega_d^{(1)} - \omega_d^{(2)})} 
+	+ \hat b \hat c^\dag e^{-it(\omega_d^{(1)} - 
+	\omega_d^{(2)})}\right],\\
+	\hat H_{d}^{(1)} &\rightarrow \frac{\hbar \Omega_1}{2}(\hat b  + \hat b^\dag),\ 	\hat H_{d}^{(2)} \rightarrow \frac{\hbar \Omega_2}{2}(\hat c  + \hat c^\dag).
 \end{aligned}
@@
 \begin{split}
-\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
-\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
+\hat{{O}}_{\gamma}^{(1)} = \sqrt{\gamma^{(1)}}\, \hat b,\ 
+\hat{{O}}_{\phi}^{(1)} = \sqrt{\gamma_{\phi}^{(1)}}\, 
 \hat b^\dag \hat b,\\
-\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
-\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
+\hat{{O}}_{\gamma}^{(2)} = \sqrt{\gamma^{(2)}}\, \hat c,\ 
+\hat{{O}}_{\phi}^{(2)} = \sqrt{\gamma_{ \phi}^{(2)}}\, 
 \hat c^\dag \hat c,
@@
 \end{equation}
-where $\gamma_{1,2}$ are the individual 
-relaxation rates, and $\gamma_{\phi (1,2)}$ are 
+where $\gamma^{(1,2)}$ are the individual 
+relaxation rates, and $\gamma_{\phi}^{(1,2)}$ are 
 the pure dephasing rates. As one can see, the 
 collapse operators are in a separable form, i.e. 
-acting only upon a single transmon each. This is 
-a valid approach until the coupling strength $J$ 
-is not too large \cite{beaudoin2011dissipation}. 
+acting only upon a single transmon each which is 
+a valid approach as long as the coupling strength $J \ll \omega_{1,2}$ 
+ \cite{beaudoin2011dissipation}. 
 Therefore, the complete evolution equation for 
@@
 \partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
-\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
-\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
+\rho, \hat H_{(R)}] + \sum_{\substack{\alpha = {\gamma, \phi},\\ i=1,2}} 
+\mathcal{D}[\hat{O}_{\alpha}^{(i)}] \hat \rho_{(R)} 
 = \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
@@
 general \cite{shavit2019bridging}.
+
+We summarize the parameters of the SAM model in \autoref{tab:parameters}.
+The coherence times $T_1 = 1/\gamma$, $T_2^{*} = 1/(\gamma/2 + \gamma_{\phi})$ were measured independently in the lower and upper sweet spot for transmons 1 and 2, respectively.
+The remaining parameters were extracted from the fits of the unperturbed model to the observed spectral lines; this procedure will be discussed in more detail in Section \ref{sec:level1}.
 
@@
 analytical solution. We have been using the 
-\textit{qutip} \cite{johansson2013qutip} (quantum 
-optics toolbox in Python) to simulate the 
+\textit{qutip} \cite{johansson2013qutip} package to simulate the 
 dynamics and to find the steady state of the 
@@
 from \autoref{eq:RWA} follows that $\hat H_{int}$ 
-is time independent when $\omega_d^1 = 
-\omega_d^2$.
+is time independent when $\omega_d^{(1)} = 
+\omega_d^{(2)} = 
+\omega_d$.
 
@@
 when the transmons have to be excited at 
-different frequencies ($\omega_d^1 - \omega_d^2 = 
+different frequencies ($\omega_d^{(1)} - \omega_d^{(2)} = 
 \delta \neq 0$), from \autoref{eq:RWA} we find 
@@
 	\includegraphics[width=.495\linewidth]{stationary}
-	\caption{Two-tone spectroscopy: experiment 
+	\caption{SAM spectroscopy: experiment 
 	and numerical modelling. \textbf{(a)} 
-	Experimental data. Colour shows the real part 
+	Experimental data. Color shows the real part 
 	of complex transmission  through the sample. 
@@
 	Spectral lines where only one SAA is excited 
-	are highlighted with the corresponding colour 
+	are highlighted with the corresponding color 
 	from \autoref{fig:experiment}. Rabi 
@@
 	respectively. \textbf{(d)} Simulated 
-	population of the state $\ket{10}$ ($\log_{10} 
-	P_{\ket{10}}$ is shown with colour). Lines 
+	population of the state $\ket{10}$. Lines 
 	show various transition frequencies from the 
-	unperturbed Hamiltonian. In the legend, the 
-	transitions are labelled near the sweet spot current; if 
+	unperturbed Hamiltonian. In the legend, the main
+	transitions that we will use below are labelled near the sweet spot current; if 
 	elsewhere any two lines form an avoided 
 	crossing, the labels should be swapped after 
-	the intersection.}
+	the intersection.
+Under label ``others'' we put all the remaining possible transitions (single- and multiphoton) between each pair levels of the system that fall into the relevant frequency range of the plot.}
 	\label{fig:two-tone}
@@
 Experiment was conducted as described in Appendix 
-\ref{sec:meas_setup}. We use high-power two-tone 
+\ref{sec:meas_setup}. We use high-power 
 spectroscopy to probe transitions between 
@@
 depending on the excitation frequency and 
-magnetic flux. The results are shown in 
+magnetic flux.
+The parameters of the unperturbed Hamiltonian were established by fitting the system transition frequencies obtained from numerical diagonalization to the observed spectral lines in \autoref{fig:two-tone}~(a).
+The transmon interaction strength $J$ is usually determined from the size of the avoided crossing between $\omega_1$ and $\omega_2$.
+However, die to the strong drive in our experiment it is smaller than the linewidths and is not resolved.
+Alternatively, $J$ can be determined from the size of the  splitting located at 5.3 GHz and $2.9\cdot 10^{-4}$A (or $5.4 \cdot 10^{-4}$A).
+It is a well-known effect \cite{dicarlo2009demonstration} widely used for CZ gates with transmons; its size is $(2 \cdot J_{eff})/2$, where $J_{eff} = \sqrt{2} J$ is the corresponding matrix element of $\hat H_{int}$ and division by two is required as we observe an intersection between two-photon processes in our data.
+
+The results are shown in 
 \autoref{fig:two-tone}~(b) where all the 
@@
 diagonalization taking the same 9 SAM states as 
-in the previous simulation. All possible 
-transitions between all resulting eigenlevels of 
-the SAM depending on the coil current are shown 
-in \autoref{fig:two-tone}~(d) with solid and 
-dashed lines. While correctly reproducing, for 
+in the previous simulation. To substantiate that claim, in \autoref{fig:two-tone}~(d) we show all possible 
+single and multiphoton transitions between all resulting pairs of the unperturbed eigenlevels that fall into the relevant frequency range depending on the coil current.
+While correctly reproducing, for
 instance, the avoided crossing labelled as 
-feature 3 in \autoref{fig:two-tone}~(a), it 
-completely misses the Roman-numbered effects.
+feature 3, there are no levels following the spectral lines observed in the Roman-numbered effects.
 
@@
 	as in \autoref{fig:two-tone}. Note that now 
-	colours show the population of the ground 
+	colors show the population of the ground 
 	state. \textbf{(c)} Linear dependence of the 
@@
 	\includegraphics[width=\linewidth]{topological_splittings}
-	\caption{Simulated population of the ground 
+	\caption{Simulating the behaviour of feature I. With color we show the population of the ground 
 	state when the transmons are driven at the 
@@
 As one can see, various multiphoton transitions besides 
-the main lines at $\omega_{\{1,2\}}(I)/2\pi$ (or 
+the main lines at $\omega_{1,2}(I)/2\pi$ (or 
 $01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$ 
 are very commonly found for transmons and lie 
-$|\alpha_{\{1,2\}}|/2$ lower than the main lines 
-$\omega_{\{1,2\}}(I)$. Another two-photon process 
+$|\alpha_{1,2}|/2$ lower than the main lines 
+$\omega_{1,2}(I)$. Another two-photon process 
 appears as $11/2$ line when two SAAs are excited 
@@
 points are, for instance, anticrossings between 
-${01}$,${10}$ or $ {11} $,$ {02} $($ {20} $) 
+${01}$, ${10}$ or $ {11} $, $ {02} $ ($ {20} $) 
 visible clearly in \autoref{fig:two-tone}~(d). 
@@
 power; the experimental and simulated results for 
-II are shown in colour in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
+II are shown in color in \autoref{fig:zoom}~(a), (b), respectively. As one can see, the growth of the splitting with 
 increasing power is linear: it is roughly equal 
@@
 First of all, since during the spectroscopy we 
-apply only a single microwave tone ($\omega_d^1 = 
-\omega_d^2$), it has to be 
+apply only a single microwave tone ($\omega_d^{(1)} = 
+\omega_d^{(2)}$), it has to be 
 simultaneously the coupler and the probe
@@
 Fortunately, all these conditions are satisfied near feature II(III) when 
-$\omega_{\{2,1\}} = 
-\omega_{\{1,2\}}+\alpha_{\{1,2\}}/2$  where we 
+$\omega_{2,1} = 
+\omega_{1,2}+\alpha_{1,2}/2$  where we 
 can simultaneously excite transitions $01 (10)$ 
@@
 dress the system. In other words, in our case the 
-A-T coupling operator is $\hat H_{d}^1$ (strong), 
-and the probing operator is $\hat H_{d}^2$ (weak 
+A-T coupling operator is $\hat H_{d}^{(1)}$ (strong), 
+and the probing operator is $\hat H_{d}^{(2)}$ (weak 
 in the two-photon regime). However, their 
@@
 We find that if SAAs are dressed equally, $11/2$ does not form an avoided crossing, and for it to be clearly observed it is required that
-$\Omega_{\{1,2\}} \gg \Omega_{\{2,1\}}$.
+$\Omega_{1,2} \gg \Omega_{2,1}$.
 
@@
 	frame rotating with $\hat 
-	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
+	H_{d}^{(1)}$, states $\ket{0j},\ket{1j}$ 
 	become nearly degenerate ($\omega_1 
@@
 	dressed system induced by $\hat 
-	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
+	H_{d}^{(2)}$ (coupled level subspaces are shown with blue ellipses). In 
 	the left part of the panel, all possible 
@@
 	\label{fig:main_scheme}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=.9\linewidth]{topo_scheme}
-	\caption{Explaining feature I.
-(a) Schematic of the transitions near I.
-(b) Transitions in the frame rotating with the second transmon with dressing.
-As will be shown in Section \ref{sec:münchhausen}, in our experiment there can only be one visible transition to the left or to the right from the resonance.}
-	\label{fig:featureI}
 \end{figure}
@@
 $\Delta_1$ from $\omega_1$, single-photon driving by 
-$\hat H_d^1$ is shown with orange ellipses while 
-much weaker two-photon driving by $\hat H_d^2$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know 
+$\hat H_d^{(1)}$ is shown with orange ellipses while 
+much weaker two-photon driving by $\hat H_d^{(2)}$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know 
 that the third level of the first transmon is not 
@@
 
-Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the dressed states induced by the second transmon driving $\hat H_{d}^2$.
+Finally, in \autoref{fig:main_scheme}~(d) we demonstrate possible two-photon transitions between the dressed states induced by the second transmon driving $\hat H_{d}^{(2)}$.
 In the left part of the panel, one can find the unmodified two-photon transition $02/2$ at $\omega_1$ and two sidebands at $\omega_1 \pm \Omega_1^R/2$.
@@
 \begin{equation}
-R = \exp[-it \omega_d^1 
+R = \exp[-it \omega_d^{(1)} 
 (b^{\dagger}b+c^{\dagger}c)].
@@
 \begin{aligned}
-\omega_{(1,2)} &\rightarrow \Delta_{(1,2)} = \omega_{(1,2)} - \omega_d^{1},\\
+\omega_{1,2} &\rightarrow \Delta_{1,2} = \omega_{1,2} - \omega_d^{(1)},\\
 \hat H_{int} &\rightarrow  \hbar J \left[\hat \sigma_+ \hat c + \hat \sigma_-\hat c^\dag \right],\\
-\hat H_{d}^1 &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
-\hat H_{d}^2 \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
+\hat H_{d}^{(1)} &\rightarrow \frac{\hbar \Omega_1}{2} \hat \sigma_x,\ 
+\hat H_{d}^{(2)} \rightarrow \frac{\hbar \Omega_2}{2}(\hat c e^{i\delta t}  + \hat c^\dag e^{-i\delta t}),
 \end{aligned}
 \end{equation}
-where $\delta = \omega_{d}^2 - \omega_{d}^1$.
-
-Since $\hat H_{d}^1$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
+where $\delta = \omega_{d}^{(2)} - \omega_{d}^{(1)}$.
+
+Since $\hat H_{d}^{(1)}$ is now time-independent, we can move to the dressed basis by applying a transformation $\hat S$ which diagonalizes the first transmon.
 After that, the Hamiltonian may be split into three parts
@@
 \hat V_J &= \hat S^\dag \hat H_{int}\hat S,\\
-\hat V_t &= \hat S^\dag \hat H_{d}^{2} \hat S \equiv \hat H_{d}^{2}.
+\hat V_t &= \hat S^\dag \hat H_{d}^{(2)} \hat S \equiv \hat H_{d}^{(2)}.
 \end{aligned}
@@
 when $\alpha \gg \Omega_1, \Omega_2, J$ which is 
-true for our setup. Tailor expansion here leads to errors of less than 0.5\%.  From \autoref{eq:rates} 
+true for our setup. Taylor expansion here leads to errors of less than 0.5\%.  From \autoref{eq:rates} 
 follows that the sideband transitions are 
@@
 As one can see from \autoref{fig:difdrive}, near the 01, 10 intersection only the two-photon transition $11/2$ is affected and deviates from unperturbed spectrum while the spectral lines 01, 10 do not shift.
-Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^1$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
+Similarly to II and III, in the frame rotating with the second transmon it tuns into two different single-photon transitions for $\hat H_d^{(1)}$ located at $\omega_1 \pm \Omega_2^R$, see \autoref{fig:featureI}~(b).
 We will show below that in the experiment with a single excitation frequency, it is not possible to observe both transitions simultaneously which is also clear from \autoref{fig:difdrive} where we observe one line to the left and the other to the right from the 01, 10 intersection.
+
+\begin{figure}
+	\includegraphics[width=.9\linewidth]{topo_scheme}
+	\caption{Explaining feature I.
+(a) Schematic of the transitions near I.
+(b) Transitions in the frame rotating with the second transmon with dressing.
+As will be shown in Section \ref{sec:münchhausen}, in our experiment there can only be one visible transition to the left or to the right from the resonance.}
+	\label{fig:featureI}
+\end{figure}
 
@@
 transitions are formed by two-photon processes 
-with $\hat H_d^2$. On the other hand, we know from 
+with $\hat H_d^{(2)}$. On the other hand, we know from 
 the unperturbed solution that in the laboratory 
@@
 
-Since we are simultaneously dressing the states by $\hat H_d^1$ and probing two-photon transitions between them with $\hat H_d^2$ at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear
+Since we are simultaneously dressing the states by $\hat H_d^{(1)}$ and probing two-photon transitions between them with $\hat H_d^{(2)}$ at $\omega_d$, self-consistent equations have to be solved to find at which $\omega_d$ the sideband spectral lines will appear
 \begin{equation}
@@
 curves we have fitted the 
-$\omega_{\{1,2\}}(\Phi_e)$ transitions with simple 
+$\omega_{1,2}(\Phi_e)$ transitions with simple 
 linear functions and substituted them in 
@@
 isolated diatomic superconducting artificial 
-molecule (SAM) in a regime of strong interaction 
+molecule in the regime of strong interaction 
 with classical light. Using joint dispersive 
 readout to directly access population of the SAM 
-eigenstates, we have located several anomalies in 
-the spectral data that were impossible to explain 
-using the unperturbed model of the system. By 
+eigenstates, we have located several anomalies in the spectrum not explained 
+by the unperturbed model of the system. By 
 using extensive numerical modelling explicitly 
@@
 
-Another interesting effect occurs when both 
+Another effect occurs when both 
 components of the driving operator are in the 
@@
 
-In overall, irradiating an individual diatomic artificial molecule with intense light calls forth a plethora of effects which can not be directly observed in natural systems and extend the validity of the well-known light-dressing models.
+In overall, irradiating an individual diatomic artificial molecule with intense light calls forth a plethora of effects that extend the validity of the well-known light-dressing models.
+These effects are much easier to find in human-made quantum devices than in natural coupled systems due to higher controllability and addressability of their parts.
 Relative ease in attaining powers that cause multiphoton transitions promises even more complex dynamics in multi-atom systems.
-We are looking forward to investigating strong interaction with light in larger artificial structures such as one-dimensional and two dimensional chains and arrays of superconducting artificial atoms.
+We are looking forward to investigating strong interaction with light in larger artificial structures such as one-dimensional and two dimensional chains and arrays of SAA.
 
@@
 \appendix
+
+\section{Derivation of the approximated SAM model}
 
@@
 \autoref{eq:ham_matrix} for the case $\Delta_1 = 
-0$, $\delta = \omega_d^2 - 	\omega_d^1 = 
-\omega_d^2 - \omega_1$. The degeneracy between 
+0$, $\delta = \omega_d^{(2)} - 	\omega_d^{(1)} = 
+\omega_d^{(2)} - \omega_1$. The degeneracy between 
 states $\ket{a, 0}, \ket{a,2}$ and $\ket{b, 0}, 
@@
 
-As the main experimental method, we have employed the two-tone spectroscopy which consists of exciting the SAM with monochromatic light at certain frequency until steady state is reached while simultaneously measuring the signal transmission at the readout resonator frequency.
-This measurement yields the average value of the joint measurement operator $\hat M$ in the steady-state.
+As the main experimental method, we have employed the so-called two-tone spectroscopy which consists of exciting the SAM with monochromatic light at certain frequency (first tone) until steady state is reached while simultaneously measuring the signal transmission at the readout resonator frequency (second tone).
+This technique yields the average value of the joint measurement operator $\hat M$ in the steady-state.
+To find the resonator frequency, we have been fitting its complex $S_{21}$ response for each current with the second tone turned off with a method similar to the one described in our prior work \cite{fedorov2019automated} which employs the \textit{circlefit} library \cite{probst2015efficient}; the source code of our measurement script may be found at GitHub \footnote{\url{https://github.com/vdrhtc/Measurement-automation/blob/master/lib2/FastTwoToneSpectroscopy.py}}.
 

### 2020-04-16 Pictures/Plotting/MainPicturePlot.py

@@ -46,8 +46,8 @@ class MainPicturePlot:
         cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current ($10^{-4}$ A)');
-        ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
-        cb.ax.set_title(r"$\mathfrak{Re}\ S^{exp}_{21}$", position=(1.125,-1.5))
+        ax.set_ylabel('$\omega_d^{(1,2)}/2\pi$ (GHz)');
+        cb.ax.set_title(r"Re $S^{exp}_{21}$", position=(1.125,-1.5))
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc
         cb.update_ticks()
@@ -83,10 +83,22 @@ class MainPicturePlot:
                     arrowprops=dict(facecolor='black', width=.5, headwidth=3, headlength=3.5,
                                     shrink=0.05))
 
+        J_eff = 8e-3*np.sqrt(2)
+        lower_branch = 5.283
+        x_pos = 5.41
+        bar_size = 5e-2
+        # ax.plot([x_pos+bar_size]*2, [lower_branch, lower_branch+J_eff], color="black", lw=.5)
+        ax.plot([x_pos, x_pos + bar_size], [lower_branch] * 2, color="black", lw=.5)
+        ax.plot([x_pos, x_pos + bar_size], [lower_branch+J_eff] * 2, color="black", lw=.5)
+
+
+        ax.annotate(r"J$\sqrt{2}$", xy=(x_pos+bar_size+.01, lower_branch+J_eff/2), xytext=(x_pos+bar_size+.11, lower_branch+.01),
+                    ha="left", va="bottom", fontsize=7,
+                    arrowprops=dict(facecolor="black", width=.1, headwidth=3, headlength=3.5,
+                                    shrink=0.1))
         self._zoom(ax, data, vmin=-0.005, vmax = 0.022)
 
     def plot_theory(self, ax):
-
         # try:
         #     C = self._cache[self.nstate]
         # except KeyError:
@@ -106,7 +118,7 @@ class MainPicturePlot:
[…]

### 2020-04-16 Pictures/Plotting/MainPictureSlices.py

@@ -96,8 +96,8 @@ class MainPictureSlices:
 
 
 
-        axes[0].set_ylabel("$\omega_d^{1,2}/2\pi$ (GHz)")
-        axes[1].set_xlabel(r"$\mathfrak{Re}\ S^{exp,\,sim}_{21}$")
+        axes[0].set_ylabel("$\omega_d^{(1,2)}/2\pi$ (GHz)")
+        axes[1].set_xlabel(r"Re $S^{exp,\,sim}_{21}$")
 
 
         plt.text(-0.53, 1.1, "(c)", fontdict={"name": "STIX"}, fontsize=17,

### 2020-04-16 Pictures/Plotting/Powerscan.py

@@ -16,7 +16,7 @@ class ZoomPlot:
         self._load_data()
 
 
-        fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(5, 5))
+        fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(4.5, 4.5))
         plt.subplots_adjust(wspace=.2, hspace=.2)
 
         for idx, ax in enumerate(axes.ravel()[:]):
@@ -30,7 +30,7 @@ class ZoomPlot:
 
             m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
             if idx % 2 == 0:
-                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
+                ax.set_ylabel('$\omega_d^{(1,2)}/2\pi$ (GHz)');
                 ax.yaxis.set_major_locator(MultipleLocator(0.01))
             if idx > 1:
                 ax.set_xlabel('Current ($10^{-4}$ A)');
@@ -51,24 +51,24 @@ class ZoomPlot:
         plt.text(.7, .9, r"$01$", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='center', color="black", rotation=70)
 
-        plt.text(.375, .025, r"$P_{exc} =$-20 dBm", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.30, .025, r"$P_{exc} =$-20 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='left', color="black")
 
-        plt.text(.66, .025, r"-12 dBm", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.62, .025, r"-12 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,1].transAxes, ha='left', color="black")
 
-        plt.text(.7, .025, r"-6 dBm", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.67, .025, r"-6 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[1,0].transAxes, ha='left', color="black")
 
         plt.text(.7, .025, r"0 dBm", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[1,1].transAxes, ha='left', color="black")
 
 
[…]

### 2020-04-16 Pictures/Plotting/StationaryPlot.py

@@ -61,8 +61,8 @@ class StationaryPlot:
         m = 1
         t = .5
         typ1 = (0, (5, 0))
-        typ2 = (0, (1, 2))
-        secondary_colour = (0.5, 0.5, 0.2)
+        typ2 = "-" #(0, (1, 2))
+        secondary_colour = (0.5, 0.5, 0.5, 0.25)
 
         energies = energies[len(currs)//2+12:, :]
         currs = currs[len(currs)//2+12:]
@@ -117,29 +117,29 @@ class StationaryPlot:
                  linestyle=typ1);  # 00->10
 
         plt.plot(currs, ((energies[:, 3].T - energies[:, 0]).T / 2),
-                 label=r"20/2",
-                 linewidth=m, linestyle=typ1);  # 00->20
+                 label=r"20/2", color = "C1",
+                 linewidth=m, linestyle=":");  # 00->20
 
         plt.plot(currs, ((energies[:, 4].T - energies[:, 0]).T / 2),
-                 label=r"02/2",
-                 linewidth=m, linestyle=typ1);  # 00->02
+                 label=r"02/2",color = "C0",
+                 linewidth=m, linestyle=":");  # 00->02
 
         plt.plot(currs, ((energies[:, 4].T - energies[:, 1]).T),
                  label=r"10-02", linewidth=m,
-                 linestyle=typ1);  # 10->02
+                 linestyle="--");  # 10->02
 
         plt.plot(currs, ((energies[:, 5].T - energies[:, 0]).T / 2), label=r"11/2",
-                 linewidth=m, linestyle=typ1)  # , color='black');  # 00->11
+                 linewidth=m, linestyle="--", color="C5")  # , color='black');  # 00->11
 
         plt.plot(currs, ((energies[:, 6].T - energies[:, 0]).T / 3), label=r"21/3",
-                 linestyle=typ1, linewidth=m , color='C7');  # 00->21/3
+                 linestyle="-.", linewidth=m , color='C7');  # 00->21/3
 
         plt.plot(currs, ((energies[:, 7].T - energies[:, 0]).T / 3), label=r"12/3",
-                 linestyle=typ1, linewidth=m, color="C9");  # 00->12
+                 linestyle="-.", linewidth=m, color="C9");  # 00->12
 
         plt.ylim(5.1, 5.5)
         plt.xlim(2,6)
[…]

### 2020-04-16 Pictures/Plotting/TopologicalSplitting.py

@@ -40,7 +40,7 @@ class TopologicalSplitting:
             if idx in [8, 7, 6]:
                 ax.set_xlabel("Current ($10^{-4}$ A)")
             if idx in [0, 3, 6]:
-                ax.set_ylabel("$\omega_d^{1,2}/2\pi$ (GHz)")
+                ax.set_ylabel("$\omega_d^{(1,2)}/2\pi$ (GHz)")
             if idx in [0]:
                 plt.text(.5, .7, "$\Omega_1: {0}$ MHz\n$\Omega_2: {1}$ MHz".format(Omegas[idx][0],
                                                                                    Omegas[idx][

### 2020-04-16 Pictures/Plotting/ZoomPlot.py

@@ -15,14 +15,14 @@ class ZoomPlot:
         with open('zoom2.pkl', 'rb') as f:
             self._X, self._Y, self._plots = pickle.load(f)
 
-        fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(5, 5))
+        fig, axes = plt.subplots(2, 2, sharex=True, sharey=True, figsize=(4.5, 4.5))
         plt.subplots_adjust(wspace=.2, hspace=.2)
 
         for idx, ax in enumerate(axes.ravel()):
             m = ax.pcolormesh(self._X, self._Y, real(array(self._plots[idx]).T),
                               vmax=1, vmin=0, rasterized=True, cmap="Spectral")
             if idx % 2 == 0:
-                ax.set_ylabel('$\omega_d^{1,2}/2\pi$ (GHz)');
+                ax.set_ylabel('$\omega_d^{(1,2)}/2\pi$ (GHz)');
             if idx > 1:
                 ax.set_xlabel('Current ($10^{-4}$ A)');
 
@@ -42,14 +42,14 @@ class ZoomPlot:
         plt.text(.7, .9, r"$01$", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0, 0].transAxes, ha='center', color="black", rotation=70)
 
-        plt.text(.15, .025, r"$\Omega_{1,2} / 2\pi  = $4.5 MHz ", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.12, .025, r"$\Omega_{1,2} / 2\pi  = $4.5 MHz ", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,0].transAxes, ha='left', color="black")
 
 
-        plt.text(.57, .025, r"11.25 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.52, .025, r"11.25 MHz", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[0,1].transAxes, ha='left', color="black")
 
-        plt.text(.6, .025, r"22.5 MHz", fontdict={"name": "STIX"}, fontsize=12,
+        plt.text(.55, .025, r"22.5 MHz", fontdict={"name": "STIX"}, fontsize=12,
                  transform=axes[1,0].transAxes, ha='left', color="black")
 
         plt.text(.65, .025, r"45 MHz", fontdict={"name": "STIX"}, fontsize=12,

### 2020-04-16 document.tex
restored table 1

@@
 
+\begin{table}
+	\begin{ruledtabular}
+		\begin{tabular}{rll}
+			Parameter & Transmon 1  & Transmon 2\\\hline
+			$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
+			$\alpha/2\pi$ [MHz] & -220 & -220 \\
+			$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
+			$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
+			$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
+		\end{tabular}
+	\end{ruledtabular}
+	\caption{SAM model parameters. Transmons are only 
+		different in the frequency tuning range and 
+		coherence times measured in the lower sweet 
+		spot for the 1\textsuperscript{st} one and in 
+		the higher sweet spot for the 
+		2\textsuperscript{nd}. The coupling strength 
+		$J$ depends on the transmon frequencies and 
+		is specified here for $\omega_1/2\pi = 
+		\omega_2/2\pi = 5.32$ GHz.}
+	\label{tab:parameters}
+\end{table}
+
 The readout resonator is not included in the 

### 2020-05-12 PRA_referee_response.tex
Referee response

\documentclass{article}

\usepackage{physics}
\usepackage{url}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{hyperref}

\begin{document}

\section{Referee 1}

\begin{enumerate}
\item \textbf{Fig. 1(c) consists of a sketch of the qubit frequencies, which is
	fine, but the authors seem to refer to it in the caption and the main
	text as if it is a measurement of the actual flux modulations for the
	qubits. Simply inserting “Sketch of” or “Schematic of” at the start of
	the caption for 1(c) would solve the issue.}

Yes, we agree, inserted "sketch of" in Fig.1c

\item \textbf{For the coupling strength J in Table I, the authors should describe
	how J was determined. This could be explained in an appendix.}

This is a good question. We have determined $J$ experimentally while matching the measured and simulated spectra by looking at the size of the avoided crossing between 11/2 and 20/2; it is clearly visible in Fig.2a,b. Its size is $(2\sqrt{2} J)/2$ where the $\sqrt{2}$ comes from the matrix element $\bra{20}\hat H_{int}\ket{11}$ and division by 2 is necessary because it is formed by two-photon processes. The accuracy of this method is not very high (around 10\%), but is enough to prove that the two transmons are indeed coupled to each other.

We have moved the table to Section II B and added a description for it in the text containing a reference to Section III A where we put the explanation from the first paragraph of this answer.

\item \textbf{In the first paragraph of Sec. II.A, the authors should include a
	definition of the asymmetry parameter d.}

We have included a reference to the original transmon paper and specified that these are the SQUID asymmetries.

\item \textbf{The notation with superscript numbers in Eqs. (3, 4) is a bit
	confusing. It would be better to use a different notation, perhaps
	move the numbers denoting qubits to subscripts? or keep them in
	superscripts but inside of parentheses? Also, the text after Eq. (5)
	mistakenly says that numbers denoting qubits are in subscripts, when
	they are actually superscripts.}

Thank you, all superscripts are now in parentheses.

\item \textbf{In the text just before Eq. (8) — “valid approach until the
	coupling strength J is not too large” — is presumably not what was
	intended. “until” should be perhaps “as long as”. Also, it would help
	to be more quantitative here and explain at what scale of J the
	theoretical approach would break down.}

Thank you, we have clarified the sentence and have explicitly said that $J$ should be much less than $\omega_{1,2}$. More details may be found in the paper referenced there.

\item \textbf{For the spectroscopy measurements in Fig. 2 and 3, the use of the
	term two-tone spectroscopy is a bit confusing...}

Yes, indeed. We have now resolved this ambiguity, two-tone spectroscopy is now only mentioned in the Appendix with clear description of what that means.

\item \textbf{For the experimental description, the authors should include more
	details about how the qubit readout was done. Presumably S21 was
	measured on the center of the readout cavity dip when neither qubit is
	being excited, or perhaps the readout frequency was tuned to be
	somewhere on the side of the resonance for greater response? Simply
	plotting S21 at a particular frequency, rather than extracting the
	readout resonance frequency for each spectroscopy point, relies on the
	dispersive shift of the cavity being less than its linewidth. Perhaps
	that is the case here? These details of the readout procedure should
	be discussed, at least in the Appendix.}

No, indeed our script has been fitting the notch-type $S_{21}$ response at each point and then setting the readout frequency to match the lowest point in the transmission. We have added a note in Appendix E along with the link to the source code of the measurement class defining the logic of the experiment.

\item \textbf{ In Fig. 2(d), the use of only color to distinguish the various
	curves is difficult to follow, particularly if one prints out the
	paper in black and white. Also, I couldn’t find a description of the
	dotted-line curves that are labeled “others” in the legend. It’s not
	clear what these are.}

Agreed. Added different types of dash for the plot, should be more readable now in print; 'others' label is now also clarified.

\item \textbf{9) In the first line of text after Eq. (14) — “Tailor” should be
	“Taylor”.}

Thank you, fixed.

\end{enumerate}

\section{Referee 2}

\begin{enumerate}
	\item \textbf{ In the introduction the authors say their work is "bridging
		superconducting devices with atomic optics". What does that mean?}

Thank you, this was indeed not a clear statement. Our message was that our experiment is very similar to what is usually done with natural molecules (we use a straightforward spectroscopic approach and then explain the origins of the observed spectroscopic lines) and that our results may be interesting not only to the scientists in the field of superconducting quantum devices, but to a broader audience studying the phenomena arising in composite quantum systems.

We will rephrase that sentence to be more clear and to convey exactly the idea above.

	\item \textbf{In the conclusion they say that these effects "can not be observed
		with natural systems". Why is that? The actual origin of the observed
		transverse interaction is not discussed in any detail, nor is its
		strength and the specific relationship and the potential limitations
		of atomic and molecular systems.}

	We would like to change the phrasing -- these effects are surely possible to observe in principle in any kind of diatomic system but the conditions for that are rather strict as can be seen from the paper. For example, we need a resonance between transitions of different orders for ``II'' and ``III'', and individual addressability of the atoms to observe effect ``I'' to ensure different Rabi frequencies.

	It seems that for natural molecules that can't be tuned in frequency and whose parts can't be addressed individually due to their size, this may be a rare case. However, it is indeed not impossible.

	Considering the origin of the transverse interaction: we have avoided discussing it, firstly, because it has already been very densely covered for transmons in literature, and, secondly, to make the model of the system as simple as possible to make it understandable for a wider audience while retaining all the effects present (nevertheless, we will now discuss it in new Appendix B). For natural molecules, the interaction Hamiltonian will certainly be different. However, as long as it ensures hybridization of states and, therefore, non-zero transition matrix elements of the first system driving operator between the states, the reported effects should work exactly the same. We think that for each individual case the calculations will be individual, too, but the general idea above will apply everywhere.

	The strength of interaction in our case is moderate, and it certainly does not exceed the coupling in natural molecules. Therefore, it will not be a prohibiting parameter for the emergence of the effects in other coupled systems.

	Considering the relationship of our interaction with the real interactions in natural molecules, we can't state anything quantitatively because we are not experts in that field. But as long as we now do not use such a strong wording regarding the ``impossibility'' to observe the described effects, this should not really be necessary!

	\item \textbf{ It would help the appeal of the paper a lot if the authors could
	find and mention additional motivation for this quite technical work.
	Why are these nicely looking features interesting? One could think
	about how these interactions and the participating states are
	different from any other ones observed so far?}

	As we have been looking through a lot of published works, we are certain that all the processes labelled I (please, see our following answers regarding Filipp2011), II and III are novel and have not been analysed previously. For example, the interplay between transitions 12/3 and 10-02 was not discussed in literature before, just as the splitting of the line 11/2 in feature I. Moreover, there were no examples of high-intensity spectroscopy of two-transmon systems in literature; we think that this regime should definitely be covered and shown to comply with theory just as well as the low-power studies, especially if these effects can be easily reproduced just by a single-tone excitation of the SAM. Finally, we have introduced the concept of self-consistency in the rotating frame that predicts the actual frequencies of Autler-Townes-like sideband transitions when they are caused by the same field that forms the levels participating in the transition. While this idea looks quite clear now, it was completely not obvious in the beginning due to the complexity of the level structure.

	We have bolstered the 4th and 5th paragraphs of the introduction with these thoughts and new references to literature, and hope that now the paper presents itself better.

	\item \textbf{In general I find the review of previous work quite comprehensive with
	one exception I am aware of, i.e. S. Filipp PRA 83, 063827 (2011),
	which I find relevant in multiple contexts of this work (see also
	below) and the authors should clearly communicate how their work is
	different and which parts are related.}

	Thank you for this thorough and extensive paper. We were not aware of it, and will discuss the differences between our results and theirs below.

	We now have also added some new works containing examples of previous spectroscopic studies of two-transmon systems to our list, including Filipp2011

	\item \textbf{looking at the design, I see 2 potential reasons for qubit-qubit
		interactions. Direct capacitive coupling and dispersive coupling via
		the resonator. The authors should quantify the two effects and discuss
		what type of interactions are generated in the two cases. Why are
		capacitive effects negligible?}

	Thank you for that question, it has helped us to significantly improve our paper.

	We indeed were aware of both these mechanisms, but while designing the chip in the simulations we were only tracking the full $J$ from the numerical diagonalization and did not evaluate explicitly its parts. Moreover, we did not take into account the other modes.

	It turns out that the contributions from these two mechanisms are of different signs for our case, and in overall the system is nearly identical to what is described here: Yan, Fei et al, Physical Review Applied 10.5 (2018), 054062 except for the fact that our coupling resonator has many modes.

	Now, in a new Appendix A, we do all the math and find that actually the direct coupling dominates even though the capacitance between the transmons is just 0.3 fF. Moreover, we use there the recently published results to find the relevant cutoff frequency to find the multimode coupling. Please, see Appendix A for our results.

	\item \textbf{even just taking into account the dispersive interaction, using the
	nonlinear oscillator basis hides in some ways an intuitive
	understanding of how these systems interact as would be obtained in
	the qubit (sigma) basis (transverse flip flop) and loosing information
	about the symmetries. I would find it important to at least mention
	explicitly the state that are formed in this basis and the type of
	interaction they get (and contrast it to e.g. the direct capacitive).
	}

	Since now in Appendix A we explicitly follow Yan, Fei et al, Physical Review Applied 10.5 (2018), 054062, we should not be loosing any symmetries. The non-linear oscillator basis matches 
	with the linear oscillator basis up to the factor of $i$ and thus just a global phase. This can be seen from the representation of the charge operator:
	\[
	\hat n \propto \hat a^\dag + a\  \text{ in the transmon eigenbasis or}\ \hat n \propto i(\hat a^\dag - a)\ \text{in the oscillator basis}  
	\]

	Thus, in RWA we recover exactly the same meaning of $\hat H_{int}$: the tunnelling of photons between oscillators which generalizes the tunnelling of an excitation back and forth between two-level systems. In RWA,  $\hat H_{int}$ are identical in both representations, and truncated to two levels fully recover the sigma operators. The counter-RWA parts, in contrast, have opposite signs, but this only matters for the dispersive coupling and is cleared with the right choice of the Schrieffer-Wolff transformation.

	To defend our choice further, we want to highlight that using the multilevel basis is a widely adopted formalism now for describing transmon arrays with the Bose-Hubbard model, for example ``Hacohen-Gourgy, Shay, et al. Physical review letters 115.24 (2015): 240501'' and  ``Neill, Charles, et al. Science 360.6385 (2018): 195-199)''.

	\item \textbf{the qubit to resonator coupling strength is not mentioned and it
		would be good to see that the observe J coupling is actually in
		agreement with the expected J coupling due to the dispersive
		interaction with the resonator (potentially including higher resonator
		modes). One should be able to back out the gs from the dispersive
		shifts and detuning quite accurately.}

	This is now done thoroughly in Appendix A, thank you. Indeed, we have found interesting results and probably even new directions for us to work on from this.

	\item \textbf{J(omega) is mentioned to be approximately constant but its physics
	(or the physics of the origin of J) and the experiments investigating
	it are not mentioned (multi-mode aspects, cut off frequencies, change
		of matrix elements, symmetries and selection rules, ...). In my
		opinion the authors should mention that this has been done. Ideally
		they should also quantify how constant J is for their range of qubit
		frequencies and if it agrees with the observed dispersive shifts (and
		state the two g1 and g2).}

	We have now covered the question of origins of $J$ extensively in Appendix A. Since our frequency span of the transmons is around 10\%, thus the change of $g_1, g_2$ should be around 5\% due to their square root dependence. However, since the transmons move in opposite directions, the change is of order 2.5\%, which is comparable to our linewidths and thus $J$ should be acceptable as constant.

	Multimode aspects are now covered, especially the cut-off problem. The change of the matrix elements for transmons are very well described by the square root dependence on their frequency. Using the location of the dark state in the lower branch of the avoided crossing between 01 and 10 (see below) and the positive symmetry of the drive we confirm the positive sign of $J$ for our case.

	\item \textbf{The discussion of feature I, which as far as I can tell is the same
		as what has been studied in Filipp2011, seems to be at odds in some
		aspects (see also below).}

	Actually, no, by ``feature I'' we mean a different effect: the ``avoided crossing'', as we have called it, in I is formed by the transitions 11/2 and 01 (or 10 depending on the interplay between $\Omega_2$ and $\Omega_2$). Note the quotes that we use because I is not an avoided crossing in the usual sense. If we look closely at Fig. 4 of our paper, we see that the line 11/2 bends when approaching the intersection of 10, 01 from one side and then finally gets absorbed by one of them. It then reappears on the other side, emerging from the same line it was absorbed by before. That deformation and apparent splitting of the line 11/2 is what we call feature I, and we apologize for the ambiguity.

	In sharp contrast, in Filipp2011 the avoided crossing is between 01 and 10, while 11/2 is passing straight through the center of the anticrossing. We have observed the same effect for lower drive powers, which can be seen in \autoref{fig:0110xx} (data from the second cooldown, driving through the resonator), and in \autoref{fig:dark_state_exp} (first cooldown, driving through the charge line). 
	Moreover, the anticrossing from Filipp2011 is reproduced by the unperturbed model, as can be seen in Fig. 2(d) of our paper, while feature I is not.

	In Fig. 2 of our paper, the avoided crossing from \autoref{fig:0110xx} is smaller than the linewidths of 01 and 10 and can not be resolved, just as in Fig. 4 of our paper.

	\begin{figure}
		\centering
		\includegraphics[width=.7\linewidth]{{Pictures/10-01XX}}
		\caption{The avoided crossing between 01 and 10 for our system at low power, reproducing the result from Filipp2011 (the transmons are driven through the resonator here, in contrast to what is presented in Fig. 2 of our paper). The lines are the numerical diagonalization result. The dark state, however, is not visible in this scan even though we see it when driving the SAM through the antenna for similar power and resolution.}
		\label{fig:0110xx}
	\end{figure}

\begin{figure}
	\includegraphics[width=.49\linewidth]{Pictures/dark_state_exp}
	\includegraphics[width=.49\linewidth]{Pictures/dark_state_exp_2}
	\caption{Two of the experimental scans which has captured the dark state at lower power (the driving is via the microwave antenna). The visible asymmetry is consistent with the drive asymmetry.} 
	\label{fig:dark_state_exp}

\end{figure}

	So, due to the different nature of the effect that we call feature I, our results do not contradict any previous well established results. Please see also \autoref{fig:dark_state} for clarification of what happens with the transition 11/2 when the drive power is increased.

	\begin{figure}
		\includegraphics[width=\linewidth]{Pictures/dark_state}
		\caption{The avoided crossing between 01 and 10 for increasing drive strengths $\Omega_1 = 2\Omega_2$. As one can see, the dark state is shifted to the left when the asymmetry of the eigenstates matches the drive asymmetry, by vanishes gradually when the drive is increased. At the largest power, the avoided crossing between 01 and 10 disappears, and the lines look simply passing through each other with no deformation. Instead, the line 11/2 is now deformed peculiarly. This is what we call feature I. Note also the population inversion that occurs here at high powers.} 
		\label{fig:dark_state}	
	\end{figure}

	\item \textbf{The symmetry of the drive seems to be not important in these new
	experiments and there is no observation of dark states in the
	spectroscopic lines. Why is this? Maybe because the transmons are
	located on the same end of the resonator? Or because they are driven
	via the external (common) charge line?}

	First of all, yes, the qubits are driven through a common charge line. From what is covered in literature, the dark state is expected to appear only for the intersection between 01 and 10 when there are certain conditions on the symmetry of the drive.

 	In \autoref{fig:0110xx} and \autoref{fig:dark_state_exp}, we have shown our corresponding data, and in \autoref{fig:dark_state} we reproduce this dark state in a numerical simulation with the same model that was used in our paper. One can see that the dark state is indeed present, but can't be seen for high powers because even the smallest matrix element of the drive already saturates the qubit in the steady state (drives it into the state with zero Z projection).
	In \autoref{fig:0110xx} and similar scans that are done through the resonator, we do not see that dark state, but the scans via the charge line do reveal it exactly where it is expected to appear; we provide two scans in \autoref{fig:dark_state_exp}. We can't explain quantitatively now why the dark state is not visible in the first scan. Most probably, the drive is composed both of the direct (over the resonator) and the dispersive (through the resonator) parts with different asymmetries, therefore no superposition is dark with respect to such drive. However, the 11/2 transition is still visible the best only in the area of the avoided crossing so the logic from Filipp2011, Section V, should imply that there is indeed a suppression of one of the transition amplitudes. But since this avoided crossing is not what we are trying to explain in our paper, we believe that the investigation of this fact should be postponed, especially as long as the charge line behaves as expected.

	Another point we would like to highlight answering this question is that, we in fact do see one dark state which is in the lower branch of the avoided crossing named as feature 3 (Arabic). It is particularly fascinating as it is the three-photon dark state, and appears not shifted and thus insensitive to the symmetry of the drive (we did not thoroughly check that). Unfortunately, we could not explain it so far (even though it is reproduced in the numerical simulation), but we still mention it in Section III B, paragraph \textit{c}.

	We will add another picture of the spectrum (from the second cooldown) in the Appendix at even a higher power where it is visible even better.

	\item \textbf{Are there any other differences of this new work compared to the
		previous one that I am missing?}

	We would say that we do not intersect with Filipp2011 in any way concerning the results, and the only common object of the study is the system itself (except that the we have two coupling mechanisms but we did not use that fact in our theoretical modelling).

	The results of Filipp2011 are (transmons are treated as qubits): multimode model for coupling strength including spurious resonances, the explanation of the dark state origins and location in the avoided crossing 01-10, two-photon transition 00 - 11 explanation.

	In contrast, we are from the beginning treating transmons as multilevel systems (qutrits is enough to capture the effects). In the main text, we do not study the coupling mechanisms, do not present the avoided crossing between 01 and 10 in the experimental data, as it is not visible for our drive powers; consequently and we do not state anything about the symmetry and location of its dark state.

	Moreover, now we have included the multimode analysis for the coupling and cut-offs, which we believe is very valuable to the field, and should be further investigated given new theoretical results.

	From said above it should be clear that all of our results were not reported before. We report not just the multiphoton transitions that can occur in a two-qubit system, but we look at those occuring in a two-qutrit system. And what is more important, we do not just show them, but demonstrate how the dressing by intense driving even just with a single tone affects them, modifying their frequencies and qualitative appearance according to standard quantum mechanical laws. Finally, we present accurate steady-state modelling for qutrits which was not done before in Filipp2011 for two qubits.

	\item \textbf{Feature I in Fig2d (right hand side) clearly shows an anti-crossing
		(also the lines which according to the legend represent the
		unperturbed Hamiltonian) but later on it is said that feature I does
		not show an avoided level crossing if either the drives are the same
		or the Hamiltonian is unperturbed. Maybe the authors could clarify
		this.}

	We apologize again for this ambiguity. We name as feature I the apparent splitting of the transition 11/2 and the deviation of its frequency from the unperturbed Hamiltonian prediction while the avoided crossing 01 vs 10 is vanished and already not visible at such power. Looking closely at the color data in Fig. 2d of our paper, especially left hand side, one can not 
	resolve an anticrossing formed by the lines 01, 10 drawn as the model lines in the right. The only effect that is seen is that 11/2 is being bent and split, and that's exactly what we are interested in. So the problem is that we did not state explicitly the difference between feature I and the avoided crossing of 01, 10, and now we are doing that in the beginning of section III A.

	We will change the wording considering feature I. We will now call it a ``splitting of the spectral line 11/2'' to avoid confusion with the effect well studied in Filipp2011.

	``but later on it is said that feature I does
	not show an avoided level crossing if either the drives are the same
	or the Hamiltonian is unperturbed''

	We couldn't find the exact quote in our paper, but we can clarify this: yes, the splitting of 11/2 is not observed when the drive is symmetric, though from Fig. 4 of our paper we can see that its frequency is somewhat shifted upwards (we could not explain that). And if the Hamiltonian is unperturbed (no driving), then we only have the eigenlevels which of course yield continuous 11/2 line, as shown in Fig. 2 d of our paper. Additionally, if the Hamiltonian has no coupling term, 11/2 will not be visible, so feature I will not be present as well.

	\item \textbf{The discussion of feature I seems also to be inconsistent with what
		has already been observed in Filipp2011 where the qubits were driven
		via the resonator with approximately equal strength. Maybe the authors
		could clarify this point as well.}

	As I hope is clear from above, this is not the case, we just should have been more explicit in the paper stating the difference between feature I and the standard anticrossing located at the same point.

	\item \textbf{Specifically, why does the avoided crossing vanish for equal drive
		strength?}

	Talking about the feature I how we mean it (splitting of 11/2): this is explained it in the section III D, paragraph b, using Fig. 6 of our paper.

	The usual avoided crossing covered in Filipp2011 truly does not depend on the drive since it is not a consequence of light dressing, but one can't resolve it for our powers and linewidths in Fig. 4 of our paper.

	\item \textbf{Why is there no dark state (in feature I)?}

	We don't know why there are no selection rules in that case (how we mean it). But the numerical simulation supports that.

	Considering the usual avoided crossing, we have shown above that we can see it, and it is consistent with Filipp2011.

	\item \textbf{- the design looks beautiful and symmetric. Do the authors have a
	suspicion why the charge line couple twice as strong to one qubit than
	the other? Maybe there is a capacitive of even inductive interaction
	at play as well? If so, how would that modify the assumptions about
	the J coupling interaction?}

	Actually, the design is a bit asymmetric, as can be seen from Fig. 1a of our paper, the charge line goes closer to the higher frequency transmon (with larger Josephson junctions). Even though the line goes relatively far from it, and should have bean screened by airbridges, it still seems to couple stronger to the closer transmon. The coupling is still capacitive.

	We do not suspect inductive interaction since transmons are far less sensitive to that even for asymmetric SQUIDs (see the original paper, Koch2007), and we bring an open end of the line to the SAM, so the magnetic fields should be suppressed there.

	All that should not modify the assumptions about
	the $J$ coupling interaction because the resonator itself is symmetric, and we do not find any differences in the coupling capacitances to is both experimentally and from FEM modelling (see Appendix A.)

	\item \textbf{- at which flux/qubit frequencies were the T1 and T2 times extracted?
		Were they assumed to be frequency independent in the numerical model?}

	Yes, at the sweet spots, we mentioned that in the table. We assumed frequency-independent parameters in the model, which worked well enough because we have very strong driving and the linewidths are mostly larger than the dissipation rates.

	\item \textbf{- it is mentioned that the parameters changed due to a second
		cooldown. How and why did they change? What are the new values?}

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{Pictures/II-TTS}
		\caption{The spectrum of the SAM in the second cooldown.}
		\label{fig:ii-tts}
	\end{figure}

	This is a valid question, please find the new spectrum equivalent to Fig.2(a) of our paper in \autoref{fig:ii-tts}. The Josephson energies and sweet spot locations are shifting between cooldowns. While sweet spots can be readjusted, the frequency locations of the maxima and minima of the qubits can not, therefore we had a problem that feature III became too deformed with the new configuration of the transmon frequencies, and Feature I in now interfering with the spurious resonance.

	We chose not to reestimate the parameters for the numerical model because it is a cumbersome process and does not affect our final conclusions.

	\newpage

	\item \textbf{
		- it is mentioned that the change of the spectrum is of topological
		nature. What does that mean in this context?}

	We mean that the resulting configurations in Fig. 4 of our paper (row 1 vs. 2) can not be transformed into each other by a continuous deformation; this is because the lines that participate are different.

\end{enumerate}

\end{document}

### 2020-05-12 document.tex
fixed hole
Referee response

@@
 
-	\vspace*{-5cm}
 	\maketitle
@@
 Appendix \ref{sec:3-level-at}).
-Moreover, most of the previous spectroscopic experiments with coupled transmons were done at low powers and resolved only the most prominent single-photon transitions \cite{majer2007coupling, filipp2011multimode}, or used two distinct excitation frequencies to reach higher energy levels \cite{dicarlo2009demonstration}, or did not study the spectral data with necessary resolution \cite{kounalakis2018tuneable}, or used non-tunable transmons \cite{poletto2012entanglement}.
+Moreover, most of the previous spectroscopic experiments with coupled transmons were done at low powers and resolved only the most prominent single-photon transitions \cite{majer2007coupling, filipp2011multimode}, or used simultaneous excitation at two distinct frequencies to reach higher energy levels \cite{dicarlo2009demonstration}, or did not study the spectral data with necessary resolution \cite{kounalakis2018tuneable}, or used non-tunable transmons \cite{poletto2012entanglement}.
 In contrast, we put a tunable system in a new regime of intense driving which allows to discover and quantify both experimentally and theoretically its novel unexplored behaviours.
@@
 conclusion of our work and discuss future 
-prospects. The Appendix contains important 
-details of the theoretical framework that we use.
-
-\section{Methods}
+prospects. The Appendix contains the 
+details of the theoretical framework that we use and additional information about the sample and the measurement techniques.
+
+\section{Methods}\label{sec:methods}
 
 \subsection{Device design and control}
-We have designed the SAM as a pair of transmon 
-(Xmon) SAAs with asymmetric 
-SQUIDs \cite{hutchings2017tunable}. Single-transmon parameters determined from spectroscopy: maximal Josephson energies $E^{(1)}_{J, 
-\sum}/h = 24.3$ GHz, $E^{(2)}_{J,\sum}/h = 18.3$ GHz, 
-charging energies $E^{(1,2)}_C/h = 220$ MHz, SQUID asymmetries $d^{(1,2)} = 0.75$ defined as in \cite{koch2007charge}) coupled 
-to a single notch-type \cite{probst2015efficient} 
-$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
-1/100\ \text{ns}^{-1}$) which both 
-couples \cite{majer2007coupling} the transmons and 
-allows joint readout  \cite{chow2010detecting} of 
-their states. In \autoref{fig:experiment}~(a), 
-the optical photograph of the device is shown, where the layout of the components is presented. The 
-resonator in its upper part is connected to a 
-coplanar waveguide through which the readout is 
-performed. In its lower part, it is coupled to 
-the transmons by a dual 
-``claw'' \cite{barends2013coherent} coupler. Flux 
-lines that allow independent control of the 
-transmon frequencies are coming from the sides. 
-Finally, the excitation waveguide coming from 
-below directs microwave signal towards the SAM. 
-In \autoref{fig:experiment}~(b), the equivalent 
-electrical circuit of the device is shown. The 
-resonator fundamental mode is approximated as an 
-LC-circuit (in the middle), the transmons are 
-shown in color on the sides; their SQUIDs are 
-represented as tunable Josephson junctions. A 
-capacitively coupled excitation line is also 
-shown in green. Finally, in 
-\autoref{fig:experiment}~(c) we show 
-schematically the frequencies of the transmons 
-depending on electric current $I$ which we apply 
-to an external coil wound around the sample 
-holder. Since the effective junction of the first 
-transmon is larger, its spectrum (orange) lies 
-higher in frequency than the spectrum of the 
-second transmon (blue). Using individual 
-flux-control lines, it is possible to align the 
-SAAs so that the lower sweet-spot of the orange 
-transmon is just below the upper sweet-spot of 
-the blue transmon (see the dashed rectangle,  
-\autoref{fig:experiment}~(c)). This configuration 
-is, as we will show in the following, convenient 
-to track the energies of highly excited levels 
-via multi-photon transitions in a single 
-spectroscopic scan. Additionally, the transmons 
-are better protected from the flux noise in this 
-area being close to their sweet spots.
 
@@
 
-\vspace{-.5cm}
+We have designed the SAM as a pair of tunable Xmon SAAs with asymmetric 
+SQUIDs \cite{hutchings2017tunable, koch2007charge, barends2013coherent}. They are coupled 
+to a single notch-type \cite{probst2015efficient} 
+$\lambda/4$ resonator ($f_r = 7.34$ GHz, $Q_e \approx 1900,\ Q_l \approx 1100$) which 
+serves for the dispersive readout of their states \cite{chow2010detecting}. In \autoref{fig:experiment}~(a), 
+the optical photograph of the device is shown presenting the physical layout of the components. The 
+resonator in its upper part is connected to a 
+coplanar waveguide through which the readout is 
+performed. In its lower part, it is coupled to 
+the transmons by a dual 
+``claw'' \cite{barends2013coherent} coupler. Flux 
+lines allowing independent control of the 
+transmon frequencies are coming from the sides, and the excitation waveguide from 
+below directs the microwave signal towards the SAM (green). 
+In \autoref{fig:experiment}~(b), the equivalent 
+electrical circuit of the device is shown. The 
+resonator is inductively and capacitively coupled to the transmission line.
+Here we simplify the distributed coupling down to lumped elements, as in \cite{khalil2012analysis}, even though there is a more rigorous approach this case \cite{besedin2018quality}.
+The transmons 1 and 2 are colored orange and blue, respectively, and their SQUIDs are
+represented as tunable Josephson junctions.
+One can note that our design gives rise to two types of coupling in the SAM.
+The first is the dispersive virtual photon exchange through the multimode cavity\cite{majer2007coupling, filipp2011multimode} and the second is the direct coupling via a mutual capacitance.
+We find that both them contribute noticeably to the observed effective coupling strength, but with opposite signs (details can be found in Appendix \ref{sec:full_model}).
+
+Finally, in 
+\autoref{fig:experiment}~(c) we show 
+schematically the frequencies of the transmons 
+depending on electric current $I$ which we apply 
+to an external coil wound around the sample 
+holder. Since the effective junction of the first 
+transmon is larger, its spectrum (orange) lies 
+higher in frequency than the spectrum of the 
+second transmon (blue). Using individual 
+flux-control lines, it is possible to align the 
+SAAs so that the lower sweet-spot of the orange 
+transmon is just below the upper sweet-spot of 
+the blue transmon (see the dashed rectangle,  
+\autoref{fig:experiment}~(c)). This configuration 
+is, as we will show in the following, convenient 
+to track the energies of highly excited levels 
+via multi-photon transitions in a single 
+spectroscopic scan. Additionally, the transmons 
+are better protected from the flux noise in this 
+area being close to their sweet spots.
+
 \subsection{Quantum-mechanical description}
@@
 oscillator with a quartic perturbation describing 
-the leading-order anharmonicity. Therefore, in 
+the leading-order anharmonicity \cite{koch2007charge, yan2018tunable}. Therefore, in 
 the main text we do not use the charge and phase 
@@
 frequencies \cite{koch2007charge}, but we take $J$ 
-to be a constant due to its negligible variation for our range of frequencies.
+to be a constant due to its negligible variation for our range of frequencies (see also Appendix \ref{sec:full_model} for details).
 
@@
 We summarize the parameters of the SAM model in \autoref{tab:parameters}.
-The coherence times $T_1 = 1/\gamma$, $T_2^{*} = 1/(\gamma/2 + \gamma_{\phi})$ were measured independently in the lower and upper sweet spot for transmons 1 and 2, respectively.
+The coherence times $T_1 = 1/\gamma$, $T_2^{*} = 1/(\gamma/2 + \gamma_{\phi})$ were measured independently in the lower and the upper sweet spots for transmons 1 and 2, respectively.
 The remaining parameters were extracted from the fits of the unperturbed model to the observed spectral lines; this procedure will be discussed in more detail in Section \ref{sec:level1}.
+The underlying electrical parameters of the transmons are the Josephson energies $E^{(1)}_{J,
+\sum}/h = 24.3$ GHz, $E^{(2)}_{J,\sum}/h = 18.3$ GHz,  the charging energies $E^{(1,2)}_C/h = 220$ MHz, and SQUID asymmetries $d^{(1,2)} = 0.7$ (all these parameters are defined as in \cite{koch2007charge})
 
@@
 			Parameter & Transmon 1  & Transmon 2\\\hline
-			$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
-			$\alpha/2\pi$ [MHz] & -220 & -220 \\
-			$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
-			$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
-			$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
+			$\omega/2\pi$ (GHz) & 5.12 - 6.3  & 4 - 5.45\\
+			$\alpha/2\pi$ (MHz) & -220 & -220 \\
+			$T_1$ ($\mu$s)  & 6.82 &  4.41 \\
+			$T_2^*$ ($\mu$s)  & 5.14  &  3.33\\\hline
+			$J/2\pi$ (MHz) &\multicolumn{2}{c}{8.69} 
 		\end{tabular}
@@
 model since in the dispersive regime it does not 
-affect the dynamics of the SAM. Hence, the 
-readout is modelled just by some measurement 
+affect the dynamics of the SAM. Therefore, we model the 
+readout simply by a measurement 
 operator $\hat M(f_p)$ that can be obtained by 
 finding the transmission $S_{21}(f_p)$ ($f_p$ is 
-the probe frequency near the resonance) through 
+the probe frequency near the resonator frequency) through 
 the sample after preparing various states of the 
@@
 shifts corresponding to the SAM basis 
-states \cite{filipp2009two, chow2010detecting}. Since we have not 
-directly measured these dispersive shifts, in our 
-modelling they are treated as fitting parameters. 
+states \cite{filipp2009two, chow2010detecting}.
+We calculate them with the parameters that can be found in Appendix \ref{sec:full_model} according to \cite{koch2007charge}, Eq.
+D3.
 Finally, the observable value for any state $\hat
@@
 	and numerical modelling. \textbf{(a)} 
-	Experimental data. Color shows the real part 
-	of complex transmission  through the sample. 
+	Experimental data. Color shows the absolute deviation $|\Delta S_{21}| (I, \omega_d)$ of the complex transmission through the sample from its value in the lower left corner. 
 	Two transmons are aligned as in 
@@
 	parasitic resonance interacting with the 
-	readout resonator. Three avoided crossings 
+	readout resonator. Three effects
 	not predicted by the unperturbed model are 
@@
 	with labelled transitions (see Section 
-	\ref{sec:analysis} for notation). 
+	\ref{sec:analysis} for notation). The simulated $|\Delta S_{21}| (I, \omega_d)$ is multiplied by 1.3 to match with the experiment.
 	\textbf{(c)} Slices of (a) and (b) at various 
@@
 shown with Arabic-numbered markers.
-
-In areas I, II and III, we observe peculiar 
-avoided crossings forming triplet transitions. In 
-I and II, they are barely visible, however in III 
-the splitting is very pronounced. To check 
-whether our theoretical model summarized in 
+To avoid any possible confusion, we emphasize that by feature I we mean not the usual avoided crossing between $\omega_{1}(I)$ and $\omega_{2}(I)$, studied extensively in the past at lower powers, but its apparent disappearance and the noticeable change in the shape of the two-photon spectral line that would usually pass straight through it \cite{filipp2011multimode}.
+To check whether the standard theoretical model summarized in
 \autoref{eq:master} can reproduce the 
@@
 equation \autoref{eq:master} finding the steady 
-states of the system $\hat \rho_{ss}$ and the 
+states of the system $\hat \rho_{ss}(I, \omega_d)$ and the 
 corresponding expected measurement outcomes 
-$\mathfrak{Re}\ \Tr[\hat M \hat \rho_{ss}]$ 
-depending on the excitation frequency and 
-magnetic flux.
-The parameters of the unperturbed Hamiltonian were established by fitting the system transition frequencies obtained from numerical diagonalization to the observed spectral lines in \autoref{fig:two-tone}~(a).
-The transmon interaction strength $J$ is usually determined from the size of the avoided crossing between $\omega_1$ and $\omega_2$.
-However, die to the strong drive in our experiment it is smaller than the linewidths and is not resolved.
-Alternatively, $J$ can be determined from the size of the  splitting located at 5.3 GHz and $2.9\cdot 10^{-4}$A (or $5.4 \cdot 10^{-4}$A).
-It is a well-known effect \cite{dicarlo2009demonstration} widely used for CZ gates with transmons; its size is $(2 \cdot J_{eff})/2$, where $J_{eff} = \sqrt{2} J$ is the corresponding matrix element of $\hat H_{int}$ and division by two is required as we observe an intersection between two-photon processes in our data.
+$\Tr[\hat M \hat \rho_{ss}(I, \omega_d)]$ 
+depending on the external coil current, and the excitation frequency $\omega_d$.
 
@@
 401 points simulation was 9 hours without RWA vs. 
-3 minutes with RWA. As can be seen from three 
+3 minutes with RWA.
+The driving amplitudes $\Omega_{1,2}$ were chosen to be $20$ and $10$ MHz, respectively.
+The parameters of the unperturbed Hamiltonian summarized in \autoref{tab:parameters} were established by fitting the system transition frequencies obtained from numerical diagonalization to the observed spectral lines in \autoref{fig:two-tone}~(a).
+The transmon interaction strength $J$ is usually determined from the size of the avoided crossing between $\omega_1$ and $\omega_2$.
+However, due to the strong drive in \autoref{fig:two-tone}~(a) it is smaller than the linewidths and is not resolved.
+Fitting a separately measured data at lower power we have obtained $J = 8.69$ MHz.
+Alternatively, $J$ can be determined from the size of the  splitting located at 5.3 GHz and $2.9\cdot 10^{-4}$A (or $5.4 \cdot 10^{-4}$A).
+It is a well-known effect \cite{dicarlo2009demonstration} widely used for implementing cPhase gates on transmons; its size is $(2 \cdot J_{eff})/2$, where $J_{eff} = \sqrt{2} J$ is the corresponding matrix element of $\hat H_{int}$ and division by two is required as we observe an intersection between two-photon processes in our data.
+As can be seen from three
 slices of \autoref{fig:two-tone}~(a),(b) in 
@@
 are in a good agreement with the experiment (the 
-spurious resonance is softened). The parameters 
-of model were chosen to match with the 
-experimental data.
+spurious resonance is softened).
+
+One problem that we have faced when modelling the measurement operator was that the depth of the resonance dip reduced slightly upon SAM excitation.
+Therefore, the experimental response was in fact higher than that predicted by the dispersive shifts.
+Therefore, in \autoref{fig:two-tone}~(b,c) we had to artificially scale the theoretical data up approximately by 30\% to obtain the best match with the experiment.
+We believe that this problem is connected with the very low observed internal Q-factor of the readout resonator which was 100 times lower than the corresponding Q-factors of the test resonators and of the transmons on the same chip.
+We have observed this suppression of the readout resonator internal Q-factor for several similar devices, but so far we could not find an explanation for that.
+However, this problem does not affect our main results which only concern the behaviour of the SAM.
 
@@
 impossible to explain using only the unperturbed 
-Hamiltonian; we confirm this by numerical 
+Hamiltonian; we demonstrate this by numerical 
 diagonalization taking the same 9 SAM states as 
-in the previous simulation. To substantiate that claim, in \autoref{fig:two-tone}~(d) we show all possible 
+in the previous simulation. In \autoref{fig:two-tone}~(d) we show all possible 
 single and multiphoton transitions between all resulting pairs of the unperturbed eigenlevels that fall into the relevant frequency range depending on the coil current.
@@
 instance, the avoided crossing labelled as 
-feature 3, there are no levels following the spectral lines observed in the Roman-numbered effects.
+feature 3, the unperturbed model does not produce any transitions following the spectral lines observed in the Roman-numbered areas.
+Particularly, in I one can see that the unperturbed transition 11/2 passes straight in the middle of the avoided crossing between 01 and 10.
+The experiment and the full simulation demonstrate that this is not the case in the regime of strong driving.
 
@@
 	\Omega_{1(2)}$; two topologically different 
-	types of anticrossings arise depending on 
+	types of splittings arise depending on 
 	which transmon is driven stronger. In the 
@@
 
-In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing drive amplitude on one of the 
+In \autoref{fig:difdrive}, we demonstrate a similar power dependence of feature I: increasing the drive amplitude on one of the 
 transmons while keeping the other one small and 
-constant again elicits avoided crossings with the 
-proportional size. We  show only the simulation results; an experiment is not possible with our sample because, since we have just a single excitation line, there is 
+constant again result in a splitting of the line 11/2. We show only the simulation results; an experiment is not possible with our sample since we have just a single excitation line and there is 
 no way for us to control the driving amplitudes 
-$\Omega_{1,2}$ individually. We note that two 
+$\Omega_{1,2}$ independently. We note that two 
 qualitatively different patterns arise depending 
@@
 \autoref{fig:two-tone}~(c)).
-If in contrast both transmons are driven with equal amplitudes, the avoided crossing vanishes.
+If in contrast both transmons are driven with equal amplitudes, the splitting of 11/2 vanishes.
 As can be seen from black dashed lines in \autoref{fig:difdrive}, all these cases are explained well by our analytical model described in detail in Sections \ref{sec:theory} and \ref{sec:münchhausen}.
@@
 
-\subsection{Explaining extra avoided crossings}\label{sec:theory}
+\subsection{Explaining Roman-numbered effects}\label{sec:theory}
 
 Since we had already connected the additional 
-avoided crossings with the light dressing, it was 
+spectral features with the light dressing, it was 
 natural to expect an Autler-Townes-like effect to 
@@
 In this case, the weak two-photon process is probing transitions in the doubly-dressed SAM.
-We find that if SAAs are dressed equally, $11/2$ does not form an avoided crossing, and for it to be clearly observed it is required that
+We find that if SAAs are dressed equally, $11/2$ does not split, and for it to be clearly observed it is required that
 $\Omega_{1,2} \gg \Omega_{2,1}$.
@@
 
-\subsection{Self-consistent equations for the avoided crossings}
+\subsection{Self-consistent equations for the I, II, III}
 \label{sec:münchhausen}
@@
 
-\section{Derivation of the approximated SAM model}
+\section{Full circuit model}\label{sec:full_model}
+
+In this section we substantiate our use of the simplified model in \autoref{Hsystem} and compare our device with previous works.
+From the scheme in \autoref{fig:experiment}~(b) and from \cite{yan2018tunable} we can conclude, that we have two types of interaction between SAAs, and that our choice for $\hat H_{int}$ is valid.
+The only difference is in the representation of the charge operator $\hat n$ which we choose to be proportional to $\hat b^\dag + \hat b$ instead of $i(\hat b^\dag - \hat b)$ which is a question of the basis choice.
+The only change it causes is in the positive sign before counter-RWA terms important only for the coupling to the resonator, which leads to an altered rotation operator in the Schrieffer-Wolff transformation but identical final results.
+The symmetries of the driving and of the coupling operator remain the same.
+Therefore, we can proceed and calculate the coupling strengths.
+that are
+
+The first one, $J_{12}$, is caused by the direct capacitive coupling, and following \cite{yan2018tunable} we see that:
+\[
+J_{12} = \frac{1}{2}(1 + \eta)\frac{C_{12}}{\sqrt{C_1 C_2}} \sqrt{\omega_1 \omega_2},
+\] 
+where $C_{12}$ is the direct capacitance between the transmon islands, $C_{1,2}$ are their capacitances to the ground, and $\omega_{1,2}$ are defined as in the main text.
+The coefficient  $\eta$ is around 6$\cdot 10^{-2}$ for our parameters as will be shown later.
+
+The second coupling mechanism is via the multimode quantum bus, similar to \cite{majer2007coupling, filipp2011multimode}.
+However, the models used in these papers can now be improved using \cite{yan2018tunable} (counter-RWA terms must be taken into account for higher modes that are in the strong dispersive regime) and \cite{malekakhlagh2017cutoff, gely2017convergence} that have solved the divergence problems and found rigorously the effective cut-off frequency $f_{max}$ that we will employ.
+For our case, $f_{max}$ can be calculated using the equivalent capacitance of the network at the open end of the $\lambda/4$ resonator:
+\[
+C_{eff} \approx C_{claw} + (C_{g1}^{-1} + C_{1}^{-1})^{-1} + (C_{g2}^{-1} + C_{2}^{-1})^{-1},
+\] 
+where $C_{g1, g2}$ are the capacitances between the transmons and the resonator, $C_{claw}$ is the direct capacitance of the claw coupler to the ground plane, and $C_{12}$ and capacitances to the drive antenna are neglected.
+Now, to find $f_{max}$ we need to solve the equation
+\[
+\left|\frac{1}{i 2\pi f_{max} C_{eff}}\right| = |Z_{res}| \approx 50\ \Omega
+\]
+which marks the frequency above which the capacitive impedance at the end of the resonator will become small enough to effectively change the boundary condition there to a short, turning off the electric field and thus the capacitive coupling of the higher-frequency modes to the transmons.
+
+Next, we use the expression for the coupling through the j\textsuperscript{th} mode with the frequency $\omega_j$ based on \cite{yan2018tunable} with the counter-RWA terms:
+
+\begin{equation}
+\label{eq:bus_coupling}
+J^{(j)}_{bus} \approx \frac{g_1^{(j)}g_2^{(j)}}{2}\left(\frac{1}{\Delta_{1}^{(j)}}+\frac{1}{\Delta_{2}^{(j)}}-\frac{1}{\Sigma_{1}^{(j)}}-\frac{1}{\Sigma_2^{(j)}}\right),
+\end{equation}
+where $\Delta_{1, 2}^{(j)}=\omega_{1,2}-\omega_j < 0\ \forall j$, $\Sigma_{1,2}^{(j)}=\omega_{1,2}+\omega_j$, and
+\begin{equation}
+\label{eq:g}
+	g_{1,2}^{(j)} =\frac{1}{2}\frac{C_{g1, g2}}{\sqrt{C_{1,2}C_r}}\sqrt{\omega_{1,2}\omega_j},
+\end{equation}
+where the effective mode capacitance $C_r = C_r' l_r/2 + C_{claw}$ does not depend on $j$ \cite{yan2018tunable, pozar2009microwave}.
+$C_r' = 160$ fF/mm being the per-unit-length capacitance may be calculated for a CPW (center width of 7 $\mu$m, gap of 4 $\mu$m) with standard means (here and below we take the substrate $\varepsilon$ to be 11.45 \cite{krupka2006measurements}); $l_r = 3.477$ mm is the resonator length without the claw.
+$C_{claw}$ may be found from EM simulations or from the equation determining the observed resonator frequency:
+\begin{equation}
+	\label{eq:resonator_freq}
+	\omega_0 = \frac{1}{\sqrt{L_r^{(0)}(1+\alpha) (C_r' l_r/2 + C_{claw})}},
+\end{equation}
+where $\alpha = 0.14$ is the kinetic inductance contribution determined from two test resonators without claws and $L_r^{(0)} = 8 L_r' l_r/\pi^2$ is the geometric equivalent inductance of the fundamental mode, $L_r' = 0.4$ nH/mm.
+From EM simulation, we find $C_{claw}$ = 64 fF; however, from \autoref{eq:resonator_freq} we obtain $C_{claw} = $ 53 fF.
+We are unable to explain why the difference is so significant, even though we could successfully describe the frequencies of all 4 different resonators on the chip (two with transmon pairs and claws, at 6.840 and 7.340 GHz, and two test ones, at 7.700 and 7.800 GHz) up to MHz accuracy with \autoref{eq:resonator_freq} while fitting only $\alpha$ and $C_{claw}$.
+Below we will use the smaller value for $C_{claw}$ determined from the experimental data.
+
+\begin{figure}[b]
+	\includegraphics[width=\linewidth]{sts}
+	\caption{Determining the coupling strength from the resonator spectroscopy (external coil current is swept, flux bias lines turned off, transmission amplitude is shown).
+The transmon parameters $E_{J,\Sigma}^{(1,2)},\ E_C^{(1,2)},\ d^{(1,2)}$ are fixed to the values from Section \ref{sec:methods} A, and the bare cavity frequency, current sweet spots, current periods and coupling capacitance $C_g = C_{g1} = C_{g2}$ are the fitting parameters.
+The orange curve shows the theoretical prediction for the optimal values: $\omega_0/2\pi = 7.340$ GHz, sweet spots at -1.2 and 0.45 mA, periods of 1.15 and 0.74 mA, $C_g$ = 2.5 fF.}
+	\label{fig:sts}
+\end{figure}
+
+\begin{figure}[b]
+	\includegraphics[width=\linewidth]{multimode_J}
+	\caption{Multimode coupling vs $\omega_{j_{max}}$.
+Blue points show the RWA result (without the $\Sigma_{1,2}^{(j)}$ terms) and orange show the full calculation.
+Gray dashed line shows the calculated cut-off frequency of 55 GHz.
+The parameters for the calculation: $\omega_{1,2}/2\pi = 5.3$ GHz, $\omega_0/2\pi$ = 7.3 GHz, $C_{1,2} = $ 88 fF, $ C_r $ = 337 fF, $C_{g1,g2}$ = 2.5 fF giving $ g_{1,2}^{(0)}/2\pi = $ 45 MHz.}
+	\label{fig:Jbus}
+\end{figure}
+
+Knowing	$C_r = 337$ fF, the capacitances $C_{g1, g2}$ may be determined with high accuracy by fitting the fundamental mode frequency dependence on the flux using \autoref{eq:g} when the transmon parameters are known (see also \cite{fedorov2019automated}).
+$C_{1,2}$ can be extracted from the experimental anharmonicity using the equation
+\[
+-\hbar \alpha = E_{C}^{1,2} = \frac{e^2}{2 C_{1,2}},
+\]
+which yields $C_{1,2}\approx$ 88 fF (we use here the renormalized $ E_{C}^{1,2} $ from \cite{gely2017convergence}, Eq.
+6).
+The fit is shown in \autoref{fig:sts}, which yields the capacitances $C_{g1, g2}$ of 2.5 fF each, which agrees reasonably well with the value of 2.3 fF that we have obtained from EM simulation.
+We have checked that the sweet spots found this way agree with an independent direct SAM spectroscopy similar to \autoref{fig:two-tone}~(a).
+The discrepancy in $C_{g1,g2}$ probably arises from the real configuration of the ground electrode enclosing the chip in the sample holder which we do not include in the simulation.
+Similarly, we obtain simulated $C_{1,2}$ to be only 80 fF.
+This problem also hampers the accuracy of the calculated $C_{12}$ which unfortunately can not be found independently in this experiment.
+In overall, the total interaction
+\[
+J = J_{12} + \sum_{j=0}^{j_{max}} J^{(j)}_{bus},
+\]
+where $j_{max}: \omega_j \approx 2\pi f_{max}$.
+For our configuration, the first term is positive, and the second is negative.
+Note that in contrast to \cite{filipp2011multimode}, the contribution from every mode is of the same negative sign since the transmons are located at the same resonator end and are below all modes in frequency.
+Below, we calculate the value of $J$ at $\omega_{1,2} \approx$ 5.3 GHz where we can determine its value experimentally from the size of the avoided crossing.
+
+For the parameters $C_{1,2} = 88$ fF, $C_{g1, g2} = 2.5$ fF, $C_{claw} = 53$ fF we find that $C_{eff} \approx 59$ fF and $f_{max} \approx 55$ GHz.
+This means that we only need to include 4 terms for the multimode virtual interaction between the transmons because the frequency of the j\textsuperscript{th} mode for a $\lambda/4$ resonator is $\omega_j = (2j+1)\omega_0$, $\omega_0/2\pi \approx 7.3$ GHz, and $\omega_3/2\pi \approx 51 \text{ GHz} \approx f_{max}$.
+We note that this very low cut-off is due to the large direct capacitance of the claw to the ground.
+
+Having found the cut-off, we can evaluate the multimode contribution.
+In \autoref{fig:Jbus}, we show its value depending on the number of included modes with and without RWA.
+As one can see, the cumulative value at the cut-off is approximately $-3$ MHz for the non-RWA case, and 1.5 lower in magnitude for the RWA.
+For higher cut-off frequencies, their ratio tends to 2, since $\Sigma_{1,2}^{(j)} \approx -\Delta_{1,2}^{(j)}$ there.
+
+Next, we find the direct coupling constant.
+As we have already mentioned, the capacitance $C_{12}$ can only be determined in a FEM simulation; however, it depends on the configuration of the ground plane stronger than $C_{g1, g2}$ and $C_{1,2}$ and thus is less accurately determined.
+The root of this is in the large size of the transmon island electrodes comparable to the substrate thickness of 0.4 mm.
+We use a sample holder with a machined cavity under the chip, and for a realistic FEM model we obtain $C_{12} = 0.34$ fF.
+This yields $\eta = C_{g1}C_{g2}/C_{12}C_r = .059$, and the resulting direct coupling $J_{12} \approx 11$ MHz.
+
+In overall, adding both contributions, we find $J \approx 8$ MHz which agrees reasonably well with the experimental value of 8.69 MHz.
+The positive sign of the coupling is confirmed by the dark state in located the lower branch of the avoided crossing between 01 and 10 both in the simulation and in the experimental data \cite{filipp2011multimode}.
+Despite the uncertainty in $J_{12}$, this result confirms that the cut-off frequency for cQED with a transmission line resonator should be calculated regarding the effective capacitance at its end and may be quite low.
+However, our accuracy is not enough to demonstrate confidently the necessity of the counter-RWA terms.
+It is notable that, in contrast to this work, \cite{filipp2011multimode} describes the experimental data within RWA, but does not include possibly lower cut-off for their capacitances, so a separate study may be required to clarify the contribution of the counter-rotating terms.
+Additionally, it would be interesting to compare the results with \cite{solgun2019simple}, presenting a classical approach to the problem, suitable for low-anharmonicity circuits.
+
+To end this subsection, we would like to comment on the possible error sources in our reasoning.
+First, a more rigorous cut-off free analysis similar to \cite{gely2017convergence} should be conducted for our circuit to substantiate the use of the cut-off and find the renormalized Hamiltonian parameters.
+It would be possible if it is possible to find analytically the inverse capacitance matrix of the system, as was done in \cite{gely2017convergence}.
+Second, the use of the $(\hat b^\dag + \hat b) (\hat c^\dag + \hat c)$ form for the coupling via the bus is not absolutely rigorous, because for higher transmon levels \autoref{eq:bus_coupling} will include slightly different $\Delta_{1,2}^{(j)}$ and $\Sigma_{1,2}^{(j)}$ due to the non-zero $\alpha$ \cite{chow2010phd}.
 
@@
 $\ket{m}$ outside the degenerate subspace.
+
+For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$) we obtain the following matrix:
+\renewcommand{\kbldelim}{[}% Left delimiter
+\renewcommand{\kbrdelim}{]}% Right delimiter
+\begin{equation}
+	M_{15} =\kbordermatrix{&\ket{a,0} & \ket{a, 2}\\
+	\ket{a,0}&\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
+	\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\
+	\ket{a, 2}&\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
+	\frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}}.
+\end{equation}
+The normalized eigenvectors 
+\begin{equation}
+\ket{N} = C_n \ket{n} + C_{n'}\ket{n'}, 
+\ket{N'} = C'_{n}\ket{n} + C'_{n'}\ket{n'}
+\end{equation}
+of the matrix are the desired zero-order superpositions. Next, we first-order correct them as usual:
+\begin{equation}
+	\ket{N}+\ket{N^{1}} = \sum_{j=n,n'} C_{j}\ket{j} + \sum_{j\ne n, n'}\ket{j}\frac{\bra{j}\hat V\ket{N}}{E_n-E_j}.
+\end{equation}
+
+Similarly, the first-order corrections for a non-degenerate state are
+\begin{equation}
+	\ket{m^1} = \sum_{j\ne m}\ket{m}\frac{\bra{j}\hat V\ket{m}}{E_m-E_j}.
+\end{equation}
 
@@
 
-For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$) we obtain the following matrix:
-\renewcommand{\kbldelim}{[}% Left delimiter
-\renewcommand{\kbrdelim}{]}% Right delimiter
-\begin{equation}
-	M_{15} =\kbordermatrix{&\ket{a,0} & \ket{a, 2}\\
-	\ket{a,0}&\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
-	\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\
-	\ket{a, 2}&\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
-	\frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}}.
-\end{equation}
-The normalized eigenvectors 
-\begin{equation}
-\ket{N} = C_n \ket{n} + C_{n'}\ket{n'}, 
-\ket{N'} = C'_{n}\ket{n} + C'_{n'}\ket{n'}
-\end{equation}
-of the matrix are the desired zero-order superpositions. Next, we first-order correct them as usual:
-\begin{equation}
-	\ket{N}+\ket{N^{1}} = \sum_{j=n,n'} C_{j}\ket{j} + \sum_{j\ne n, n'}\ket{j}\frac{\bra{j}\hat V\ket{N}}{E_n-E_j}.
-\end{equation}
-
-Similarly, the first-order corrections for a non-degenerate state are
-\begin{equation}
-	\ket{m^1} = \sum_{j\ne m}\ket{m}\frac{\bra{j}\hat V\ket{m}}{E_m-E_j}.
-\end{equation}
-
 \section{Transition rates of the two-photon process}\label{sec:2pp}
@@
 chamber (Plassys) and after a gentle ion-milling 
-step, a double-angle evaporation technique at 10 
-is used to deposit Al/AlOx/Al layer. Finally, hot 
+step, a double-angle evaporation technique at 10 degrees 
+is used to deposit Al/AlOx/Al layer (25/45 nm). Finally, hot 
 NMP followed by IPA was used to lift off the 

### 2020-05-12 Pictures/Plotting/MainPicturePlot.py

@@ -13,7 +13,7 @@ class MainPicturePlot:
 
     def __init__(self):
         self._cache_file = "main_pic_cache.pkl"
-        self._cmap = "Spectral"
+        self._cmap = "Spectral_r"
         self.nstate = 0
         try:
             with open(self._cache_file, "rb") as f:
@@ -41,13 +41,14 @@ class MainPicturePlot:
 
 
     def plot_experiment(self, ax):
-        data = self._X_exp, self._Y_exp, np.real(self._C_exp)
-        img1 = ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap = self._cmap)
-        cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.075, anchor=(0,0))[0]
+
+        data = self._X_exp, self._Y_exp, np.abs(self._C_exp - self._C_exp[0,0])
+        img1 = ax.pcolormesh(*data, rasterized=True, vmin=0, vmax=.022, cmap = self._cmap)
+        cbaxes1 = clb.make_axes(ax, location="top", shrink=0.8, aspect=50, pad=0.09, anchor=(0,0))[0]
         cb = plt.colorbar(img1, ax=ax, cax=cbaxes1, orientation="horizontal")
         ax.set_xlabel('Current ($10^{-4}$ A)');
-        ax.set_ylabel('$\omega_d^{(1,2)}/2\pi$ (GHz)');
-        cb.ax.set_title(r"Re $S^{exp}_{21}$", position=(1.125,-1.5))
+        ax.set_ylabel('$\omega_d/2\pi$ (GHz)');
+        cb.ax.set_title(r"$|\Delta S^{exp}_{21}|$", position=(1.125,-2.5))
         loc = ticker.MultipleLocator(base=0.01)  # this locator puts ticks at regular intervals
         cb.locator = loc
         cb.update_ticks()
@@ -96,7 +97,7 @@ class MainPicturePlot:
                     ha="left", va="bottom", fontsize=7,
                     arrowprops=dict(facecolor="black", width=.1, headwidth=3, headlength=3.5,
                                     shrink=0.1))
-        self._zoom(ax, data, vmin=-0.005, vmax = 0.022)
+        self._zoom(ax, data, vmin=0, vmax = .022)
 
     def plot_theory(self, ax):
         # try:
@@ -108,17 +109,16 @@ class MainPicturePlot:
[…]

### 2020-05-12 Pictures/Plotting/MainPictureSlices.py

@@ -18,26 +18,26 @@ class MainPictureSlices:
 
     def plot(self):
         self._load_data()
-        indices = [99, 124, 158]
+        indices = [98, 124, 158]
         indices_th  = (np.array(indices)/len(self._C_exp[0,:])*len(self._C_th[0,:])).astype(int)
         print(indices, indices_th)
         titles = ["Feature I", "Feature III", "Sweet spot"]
         fig, axes = plt.subplots(1, 3, figsize=(5*0.9,3*0.9), sharey=True)
 
         for counter, ax, index in zip(range(3), axes, indices):
-            data = self._X_exp, self._Y_exp, np.real(self._C_exp)
+            C_exp = np.abs(self._C_exp - self._C_exp[3, 0])
         # plt.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap=self._cmap)
         #     ax.pcolormesh(*data, rasterized=True, vmin=-0.005, vmax=0.022, cmap=self._cmap)
 
             # ax.plot([self._X_exp[index]]*2, [self._Y_exp[0], self._Y_exp[-1]], 'black', lw=0.1)
-            ax.plot(np.real(self._C_exp[:,index]), self._Y_exp, zorder=1, color="gray",
+            ax.plot(np.real(C_exp[:,index]), self._Y_exp, zorder=1, color="gray",
                     label="Exp.")
-            th_slice = np.real(self._C_th[:,indices_th[counter]])
+            th_slice = np.real(self._C_th[:,indices_th[counter]])*1.3
             ax.plot(th_slice, np.linspace(self._Y_exp[0], self._Y_exp[-1], len(th_slice)), zorder=3,
                     color="black", lw=.5, label ="Sim.")
 
-            rect = patches.Rectangle((np.min(np.real(self._C_exp[:,index]))-.001, 5.3575),
-                                     np.ptp(np.real(self._C_exp[:,index]))+0.002, .02, linewidth=1, edgecolor='none',
+            rect = patches.Rectangle((np.min((C_exp[:,index]))-.001, 5.3575),
+                                     np.ptp((C_exp[:,index]))+0.002, .02, linewidth=1, edgecolor='none',
                                      facecolor='white', zorder=2, alpha=0.66)
             ax.add_patch(rect)
[…]

### 2020-05-12 Pictures/Plotting/Powerscan.py

@@ -21,14 +21,16 @@ class ZoomPlot:
 
         for idx, ax in enumerate(axes.ravel()[:]):
 
-            X, Y, data = self._data[idx]["Current [A]"]*1e4,\
+            X, Y = self._data[idx]["Current [A]"]*1e4,\
                          self._data[idx]["Frequency [Hz]"]/1e9, \
-                         real(self._data[idx]["data"]*exp(1j*pi/2)).T*1e3
+
 
             if idx in [0]:
-                data = data - median(data, axis=0)
+                data = abs(self._data[idx]["data"].T - median(self._data[idx]["data"].T[:,:], axis=0))*1e3
+            else:
+                data = abs(self._data[idx]["data"] - mean(self._data[idx]["data"][0, :])).T * 1e3
 
-            m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r")
+            m = ax.pcolormesh(X, Y, data, rasterized=True, cmap="Spectral_r", vmin=0, vmax=1)
             if idx % 2 == 0:
                 ax.set_ylabel('$\omega_d^{(1,2)}/2\pi$ (GHz)');
                 ax.yaxis.set_major_locator(MultipleLocator(0.01))
@@ -68,7 +70,8 @@ class ZoomPlot:
         # clb.make_axes(axes[0, 0], location="top", shrink=0.8,
         #                         aspect=50, pad=0.075, anchor=(0, 1))[0]
         cb = plt.colorbar(m, ax=axes[0, 0], cax=cbaxes1, orientation="horizontal")
-        cb.ax.set_title(r"$10^3$ Re $S^{exp}_{21}$", position=(1.2,-2))
+        cb.ax.set_title(r"$10^3 |\Delta S^{exp}_{21}|$", position=(1.2,-2))
+        # cb.ax.xaxis.set_major_locator(MultipleLocator(0.005))
 
         plt.text(-0.35, 1.15, "(a)", fontdict={"name": "STIX"}, fontsize=20,
                  transform=axes[0,0].transAxes)

### 2020-05-12 Pictures/Plotting/StationaryPlot.py

@@ -139,7 +139,7 @@ class StationaryPlot:
 
         plt.ylim(5.1, 5.5)
         plt.xlim(2,6)
-        ax.set_ylabel("$\omega_{d}^{(1,2)}/2\pi$ (GHz)")
+        ax.set_ylabel("$\omega_{d}/2\pi$ (GHz)")
 
         ax.set_xlabel("Current ($10^{-4}$ A)")
         plt.legend(ncol=3, fontsize=7)
